### 2023-09-11 ms/ms.qmd
Templates for ms and supp

---
title: "Empowering use of preprints in ecology and evolution: an exploration of the first 1000 preprints of EcoEvoRxiv"
bibliography: ../bib/refs.bib
csl: ../bib/nature.csl
format:
  docx:
    reference-doc: ../bib/template.docx
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: false
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: 'Figure'
  fig-labels: arabic
  title-delim: "-"
  fig-prefix: "Figure"
  tbl-prefix: "Table"
---

Authors: Daniel W.A. Noble, Malgorzata Lagisz, Hackathon Parts, Shinichi Nakagawa

### 2023-09-11 supp/supp.qmd
Templates for ms and supp

---
title: "Empowering use of preprints in ecology and evolution: an exploration of the first 1000 preprints of EcoEvoRxiv"
bibliography: ../bib/refs.bib
csl: ../bib/nature.csl
format:
  docx:
    reference-doc: ../bib/template.docx
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: false
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: 'Figure'
  fig-labels: arabic
  title-delim: "-"
  fig-prefix: "Figure"
  tbl-prefix: "Table"
---

# Introduction

This will give you a brief overview of how to write quarto docs. For more information, see the [quarto documentation](https://quarto.org/docs/).

# Code chunks

Code chunks are wrapped in ``` ``` and can be given a name and options. For example, the following code chunk is named `setup` and has the options `echo: false` and `include: false`. This means that the code will not be shown in the output and will not be included in the output. This is useful for loading packages and other things that you don't want to show up in the output.

```{r, setup}
#| label: setup
#| echo: false
#| include: false

# Put your R code here like you would normally. These are the packages I normally load by default. You can add more here
	#install.packages("pacman")
	pacman::p_load(tidyverse, flextable, here, brms, MCMCglmm, metafor, lme4)
```

# Figures

I recommend that each figure you want gets wrapped inside it's own code chunk with a clear label. All figs need to start with the prefix `fig-` and then the name of the figure. For example, `fig-fig1`. This is important because it will be used to reference the figure later. You can also add a figure caption using `fig-cap:`. This will be used to add a caption to the figure. You can also add a title to the figure using `fig-title:`. This will be used to add a title to the figure.

Now that we created the figure below we can make reference to it quite easily. If we look at @fig-fig1, we see the linear relationship.

```{r, fig-fig1}
#| label: fig-fig1
#| fig-cap: Here you can add text, references or even equations $y = m_{x} + b$ to your figure caption

# create some fake data and write this data. Use the here package to make sure that the data is written to the correct folder
	set.seed(2)
	    x = rnorm(100, 20, 3)
	data <- data.frame(x = x, 
					   y = rnorm(100, 0.2 + (1.2 * x), 2))

	write.csv(data, here("data", "fake_data.csv"))

# plot the data
	p1 <- ggplot(data = data, aes(x = x, y = y)) +
		geom_point() +
		geom_smooth(method = "lm", se = TRUE) +
		theme_classic()
	p1

# I always also save files directly because when you need these for the jorunal, you will need them in the correct format
	ggsave(plot = p1, filename = here("output/figs", "fig1.png"), width = 5, height = 5, units = "in", dpi = 300)

```

# Tables

Tables, in my opnion are the most challenging. But, `flextable` is an outsatnding package, but there are others that work well too. The problem with tables at the moment is that, for word docs, they can be 'buggy'. When we have the table, we also reference just as nrormal. For example, @tbl-tab1.

```{r, tbl-tab1}
#| label: tbl-tab1
#| tbl-cap: Labelling is roughly the same but does require some prefix changes to `tbl`

# Getting tables sorted, in my mind is easy as they are just dataframes. So, you can use the same dataframes that you use for your analysis. I like to use the `flextable` package because it is easy to use and has a lot of functionality. Lets just create a summary table and plot it

	tb <- data %>%
		summarise(mean = mean(x),
				  sd = sd(x),
				  n = n())

# Now we use flextable. We can modify the headers if we wnat too 
		flextable(tb)  %>% 
		compose(part = "header", value = as_paragraph(as_b(c("Mean", "Stdev", "Sample Size"))))  %>%  
		align(align = "center", part = "all") %>% 
		autofit()

```

# Equations

Ok, the last two bits that can be important. Sometimes we need equations (often for me). You can write in LateX and we can reference equations in the same way. For example, lets write a fancy equation:

$$
y = \left(\frac{m_{x}}{y} \right) + b \tilde{a}
$${#eq-eq1}

Then, we can refer to @eq-eq1. If you don't like the prefixes you can change them in the yaml header at the top of the document.

# References

Refs are easy, we simply refer to citekeys within the `.bib` file. For example, @Bulgarella2015-yl stated the equation above was correct. However, it is clear that this is not the case [@Burkner2018-ur; @Crow1958-fv].

Then, all refs will be formatted and put at the end of the document according to the style you have chosen. You can change the style in the yaml header at the top of the document.

# Bibliography

### 2023-09-11 ms/ms.qmd
First crack at writing intro section.

@@
 ---
-title: "Empowering use of preprints in ecology and evolution: an exploration of the first 1000 preprints of EcoEvoRxiv"
+title: "Empowering the use of preprints in ecology and evolution: an exploration of the first 1000 *EcoEvoRxiv* preprints"
 bibliography: ../bib/refs.bib
@@
 Authors: Daniel W.A. Noble, Malgorzata Lagisz, Hackathon Parts, Shinichi Nakagawa
+
+# Introduction
+
+Publishing preprints –- papers communicating non-peer-reviewed research findings –- are now an entrenched practice across a multitude of scientific disciplines in many countries.
+In ecology and evolution, new discpline specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disemminate research findings, promoting open science practices (e.g., ensuring papers are open access) and facilitating the rapid sharing of new discoveries that can have significant impacts on fundamental and applied (e.g., conservation outcomes) knowledge globally.
+Improtantly, *EcoEvoRxiv* is a community driven preprint server that has paved the way for new inititives that attempt to break down barriers to scientific dissemination, including accepting multilanguage preprints (i.e., Spanish and Portuguese), recognising and accepting registered reports and promoting the use of peer review and community discuission to improve the quality of preprints (e.g., Peer Community In -- PCI).

### 2023-09-11 supp/supp.qmd
Remove unecessary code

@@
 ---
-
-# Introduction
-
-This will give you a brief overview of how to write quarto docs. For more information, see the [quarto documentation](https://quarto.org/docs/).
-
-# Code chunks
-
-Code chunks are wrapped in ``` ``` and can be given a name and options.
-For example, the following code chunk is named `setup` and has the options `echo: false` and `include: false`.
-This means that the code will not be shown in the output and will not be included in the output.
-This is useful for loading packages and other things that you don't want to show up in the output.
-
-```{r, setup}
-#| label: setup
-#| echo: false
-#| include: false
-
-# Put your R code here like you would normally. These are the packages I normally load by default. You can add more here
-	#install.packages("pacman")
-	pacman::p_load(tidyverse, flextable, here, brms, MCMCglmm, metafor, lme4)
-```
-
-# Figures
-
-I recommend that each figure you want gets wrapped inside it's own code chunk with a clear label.
-All figs need to start with the prefix `fig-` and then the name of the figure.
-For example, `fig-fig1`.
-This is important because it will be used to reference the figure later.
-You can also add a figure caption using `fig-cap:`.
-This will be used to add a caption to the figure.
-You can also add a title to the figure using `fig-title:`.
-This will be used to add a title to the figure.
-
-Now that we created the figure below we can make reference to it quite easily. If we look at @fig-fig1, we see the linear relationship.
-
-```{r, fig-fig1}
-#| label: fig-fig1
-#| fig-cap: Here you can add text, references or even equations $y = m_{x} + b$ to your figure caption
-
-# create some fake data and write this data. Use the here package to make sure that the data is written to the correct folder
-	set.seed(2)
-	    x = rnorm(100, 20, 3)
-	data <- data.frame(x = x, 
-					   y = rnorm(100, 0.2 + (1.2 * x), 2))
-
-	write.csv(data, here("data", "fake_data.csv"))
-
-# plot the data
-	p1 <- ggplot(data = data, aes(x = x, y = y)) +
-		geom_point() +
-		geom_smooth(method = "lm", se = TRUE) +
-		theme_classic()
-	p1
-
-# I always also save files directly because when you need these for the jorunal, you will need them in the correct format
-	ggsave(plot = p1, filename = here("output/figs", "fig1.png"), width = 5, height = 5, units = "in", dpi = 300)
-
-```
-
-# Tables
-
-Tables, in my opnion are the most challenging.
-But, `flextable` is an outsatnding package, but there are others that work well too.
-The problem with tables at the moment is that, for word docs, they can be 'buggy'.
-When we have the table, we also reference just as nrormal.
-For example, @tbl-tab1.
-
-```{r, tbl-tab1}
-#| label: tbl-tab1
-#| tbl-cap: Labelling is roughly the same but does require some prefix changes to `tbl`
-
-# Getting tables sorted, in my mind is easy as they are just dataframes.
-So, you can use the same dataframes that you use for your analysis.
-I like to use the `flextable` package because it is easy to use and has a lot of functionality.
-Lets just create a summary table and plot it
-
-	tb <- data %>%
-		summarise(mean = mean(x),
-				  sd = sd(x),
-				  n = n())
-
-# Now we use flextable. We can modify the headers if we wnat too 
-		flextable(tb)  %>% 
-		compose(part = "header", value = as_paragraph(as_b(c("Mean", "Stdev", "Sample Size"))))  %>%  
-		align(align = "center", part = "all") %>% 
-		autofit()
-
-```
-
-# Equations
-
-Ok, the last two bits that can be important.
-Sometimes we need equations (often for me).
-You can write in LateX and we can reference equations in the same way.
-For example, lets write a fancy equation:
-
-$$
-y = \left(\frac{m_{x}}{y} \right) + b \tilde{a}
-$${#eq-eq1}
-
-Then, we can refer to @eq-eq1. If you don't like the prefixes you can change them in the yaml header at the top of the document.
-
-# References
-
-Refs are easy, we simply refer to citekeys within the `.bib` file.
-For example, @Bulgarella2015-yl stated the equation above was correct.
-However, it is clear that this is not the case [@Burkner2018-ur; @Crow1958-fv].
-
-Then, all refs will be formatted and put at the end of the document according to the style you have chosen. You can change the style in the yaml header at the top of the document.
-
-# Bibliography

### 2023-09-11 ms/ms.qmd
Add a ref

@@
 
-Authors: Daniel W.A. Noble, Malgorzata Lagisz, Hackathon Parts, Shinichi Nakagawa
+Authors: Daniel W.A. Noble, Malgorzata Lagisz, Hackathon Participants, Shinichi Nakagawa
 
@@
 
-Publishing preprints –- papers communicating non-peer-reviewed research findings –- are now an entrenched practice across a multitude of scientific disciplines in many countries.
-In ecology and evolution, new discpline specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disemminate research findings, promoting open science practices (e.g., ensuring papers are open access) and facilitating the rapid sharing of new discoveries that can have significant impacts on fundamental and applied (e.g., conservation outcomes) knowledge globally.
-Improtantly, *EcoEvoRxiv* is a community driven preprint server that has paved the way for new inititives that attempt to break down barriers to scientific dissemination, including accepting multilanguage preprints (i.e., Spanish and Portuguese), recognising and accepting registered reports and promoting the use of peer review and community discuission to improve the quality of preprints (e.g., Peer Community In -- PCI).
+Publishing preprints -- papers communicating non-peer-reviewed research findings -- is now an entrenched practice across a multitude of scientific disciplines in many countries.
+While preprint use in biology has had a slower uptake [@Berg2016], in ecology and evolution, new discpline specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disemminate research findings.
+Such practices promote open science (e.g., ensuring papers are open access) and facilitate the rapid sharing of new discoveries that can have significant impacts on fundamental and applied knowledge globally (e.g., conservation outcomes).
+Importantly, *EcoEvoRxiv* is a community driven preprint server that has paved the way for new inititives that attempt to break down barriers to scientific dissemination and improve research practice, including accepting multilanguage preprints (i.e., Spanish and Portuguese), recognising and accepting registered reports and promoting the use of peer review and community discuission to improve the quality of preprints and speed up their peer-reviewed publication (e.g., Peer Community In -- PCI).
+
+# References

### 2023-09-12 ms/ms.qmd
Update to MS

@@
 
-Publishing preprints -- papers communicating non-peer-reviewed research findings -- is now an entrenched practice across a multitude of scientific disciplines in many countries.
+Publishing preprints -- papers communicating non-peer-reviewed research findings -- is now an entrenched practice across a multitude of scientific disciplines in many countries [@Ginsparg2011].
 While preprint use in biology has had a slower uptake [@Berg2016], in ecology and evolution, new discpline specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disemminate research findings.
@@
 
+Preprint servers, such as *EcoEvoRxiv*, can empower researchers to make their findings more accessible, open and transparent but only if they are used, and used well.
+Significant barriers to preprint use still exist globally – from worry about XXX to XXX.
+Nonetheless, we lack a systematic understanding of the factors that influence preprint use in ecology and evolution which can help inform future initatives and help us begin to break down barriers to their use in our field.
+Here, we explore the first 1000 preprints uploaded to *EcoEvoRxiv* to understand preprint practices and use in our field, focusing on our attention on understanding: 1) how long it takes for a preprint to become published, and how many preprints remain unpublished; 2) what countries make use of preprints; 3) how career stage and gender impact preprint use; 4) whether data and code are more likely to be shared in preprints; and 5) the extent to which authors make use of preprint servers for registeretd reports and community driven peer review.
+
 # References

### 2023-09-28 ms/ms.qmd
test

@@
 Such practices promote open science (e.g., ensuring papers are open access) and facilitate the rapid sharing of new discoveries that can have significant impacts on fundamental and applied knowledge globally (e.g., conservation outcomes).
-Importantly, *EcoEvoRxiv* is a community driven preprint server that has paved the way for new inititives that attempt to break down barriers to scientific dissemination and improve research practice, including accepting multilanguage preprints (i.e., Spanish and Portuguese), recognising and accepting registered reports and promoting the use of peer review and community discuission to improve the quality of preprints and speed up their peer-reviewed publication (e.g., Peer Community In -- PCI).
+
+Preprints attempt to break down barriers to scientific publising by: 1) increasing the speed, visibility and output of research findings; 2) encouraging constructive and critical feedback from a research community; 3) helping establish precedence of research findings; and 4) removing financial barriers to publication [@Proulx2013 and others].
+Importantly, *EcoEvoRxiv* is a community driven preprint server that has paved the way for new inititives that attempt to further break down barriers to scientific dissemination and improve research practice, including accepting multilanguage preprints (i.e., Spanish and Portuguese), recognising and accepting registered reports and promoting the use of peer review and community discuission to improve the quality of preprints and speed up their peer-reviewed publication (e.g., Peer Community In -- PCI).
 

### 2023-10-10 ms/ms.qmd
fix block
works
Mucking around
fix
Spelling errors

--- 2023-09-11 ms/ms.qmd
@@
 
-Publishing preprints -- papers communicating non-peer-reviewed research findings -- is now an entrenched practice across a multitude of scientific disciplines in many countries.
-While preprint use in biology has had a slower uptake [@Berg2016], in ecology and evolution, new discpline specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disemminate research findings.
+Publishing preprints -- papers communicating non-peer-reviewed research findings -- is now an entrenched practice across a multitude of scientific disciplines in many countries [@Ginsparg2011].
+While preprint use in biology has had a slower uptake [@Berg2016], in ecology and evolution, new discipline specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disseminate research findings.
 Such practices promote open science (e.g., ensuring papers are open access) and facilitate the rapid sharing of new discoveries that can have significant impacts on fundamental and applied knowledge globally (e.g., conservation outcomes).
-Importantly, *EcoEvoRxiv* is a community driven preprint server that has paved the way for new inititives that attempt to break down barriers to scientific dissemination and improve research practice, including accepting multilanguage preprints (i.e., Spanish and Portuguese), recognising and accepting registered reports and promoting the use of peer review and community discuission to improve the quality of preprints and speed up their peer-reviewed publication (e.g., Peer Community In -- PCI).
+
+Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed, visibility and output of research findings; 2) encouraging constructive and critical feedback from a research community; 3) helping establish precedence of research findings; and 4) removing financial barriers to publication [@Proulx2013 and others].
+Importantly, *EcoEvoRxiv* is a community driven preprint server that has paved the way for new initiatives that attempt to further break down barriers to scientific dissemination and improve research practice, including accepting multilingual preprints (i.e., Spanish and Portuguese), recognising and accepting registered reports and promoting the use of peer review and community discussion to improve the quality of preprints and speed up their peer-reviewed publication (e.g., Peer Community In -- PCI).
+
+Preprint servers, such as *EcoEvoRxiv*, can empower researchers to make their findings more accessible, open and transparent but only if they are used, and used well.
+Significant barriers to preprint use still exist globally – from worry about XXX to XXX.
+Nonetheless, we lack a systematic understanding of the factors that influence preprint use in ecology and evolution which can help inform future initiatives and help us begin to break down barriers to their use in our field.
+Here, we explore the first 1000 preprints uploaded to *EcoEvoRxiv* to understand preprint practices and use in our field, focusing on our attention on understanding: 1) how long it takes for a preprint to become published, and how many preprints remain unpublished; 2) what countries make use of preprints; 3) how career stage and gender impact preprint use; 4) whether data and code are more likely to be shared in preprints; and 5) the extent to which authors make use of preprint servers for registered reports and community driven peer review.
 

### 2023-10-11 ms/ms.qmd
Fix

@@
 
-Publishing preprints -- papers communicating non-peer-reviewed research findings -- is now an entrenched practice across a multitude of scientific disciplines in many countries [@Ginsparg2011].
+Publishing preprints -- papers communicating non-peer-reviewed research findings -- is now an entrenched practice across a multitude of scientific disciplines [@Ginsparg2011].
 While preprint use in biology has had a slower uptake [@Berg2016], in ecology and evolution, new discipline specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disseminate research findings.

### 2023-10-11 ms/ms.qmd
INtro editing as I didn't like a few things

@@
 Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed, visibility and output of research findings; 2) encouraging constructive and critical feedback from a research community; 3) helping establish precedence of research findings; and 4) removing financial barriers to publication [@Proulx2013 and others].
-Importantly, *EcoEvoRxiv* is a community driven preprint server that has paved the way for new initiatives that attempt to further break down barriers to scientific dissemination and improve research practice, including accepting multilingual preprints (i.e., Spanish and Portuguese), recognising and accepting registered reports and promoting the use of peer review and community discussion to improve the quality of preprints and speed up their peer-reviewed publication (e.g., Peer Community In -- PCI).
+Importantly, *EcoEvoRxiv* is a community driven preprint server that has paved the way for new initiatives, including accepting multilingual preprints (i.e., Spanish and Portuguese), recognising and accepting registered reports and promoting the use of peer review and community discussion to improve the quality of preprints and speed up their peer-reviewed publication (e.g., Peer Community In -- PCI).
 
-Preprint servers, such as *EcoEvoRxiv*, can empower researchers to make their findings more accessible, open and transparent but only if they are used, and used well.
+Preprint servers, such as *EcoEvoRxiv*, can empower researchers to make their findings more accessible, open and transparent but only if they are used well.
 Significant barriers to preprint use still exist globally – from worry about XXX to XXX.
-Nonetheless, we lack a systematic understanding of the factors that influence preprint use in ecology and evolution which can help inform future initiatives and help us begin to break down barriers to their use in our field.
+Nonetheless, we lack a systematic understanding of the factors that influence preprint use in ecology and evolution which can help inform future initiatives and allow us to begin to break down barriers to their use in our field.
+
 Here, we explore the first 1000 preprints uploaded to *EcoEvoRxiv* to understand preprint practices and use in our field, focusing on our attention on understanding: 1) how long it takes for a preprint to become published, and how many preprints remain unpublished; 2) what countries make use of preprints; 3) how career stage and gender impact preprint use; 4) whether data and code are more likely to be shared in preprints; and 5) the extent to which authors make use of preprint servers for registered reports and community driven peer review.

### 2023-10-12 ms/ms.qmd
Finished first draft of intro

@@
 
-Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed, visibility and output of research findings; 2) encouraging constructive and critical feedback from a research community; 3) helping establish precedence of research findings; and 4) removing financial barriers to publication [@Proulx2013 and others].
-Importantly, *EcoEvoRxiv* is a community driven preprint server that has paved the way for new initiatives, including accepting multilingual preprints (i.e., Spanish and Portuguese), recognising and accepting registered reports and promoting the use of peer review and community discussion to improve the quality of preprints and speed up their peer-reviewed publication (e.g., Peer Community In -- PCI).
+Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed, visibility and output of research findings; 2) encouraging constructive and critical feedback from a research community; 3) helping establish precedence of research findings; and 4) removing financial barriers to publication [e.g., @Proulx2013].
+Importantly, *EcoEvoRxiv* is a community driven preprint server that has paved the way for new initiatives, including accepting multilingual preprints, recognising and accepting registered reports and non-traditional research reports, and promoting peer review and community discussion to improve the quality of preprints and speed up their peer-reviewed publication (e.g., Peer Community In -- PCI).
 
 Preprint servers, such as *EcoEvoRxiv*, can empower researchers to make their findings more accessible, open and transparent but only if they are used well.
-Significant barriers to preprint use still exist globally – from worry about XXX to XXX.
+Significant barriers to preprint use still exist globally – from lack of clarity around preprint policies at journals [@Klebel2020] to a stigma that preprints are viewed by a research community to be of poor quality [@Chiarelli2019].
 Nonetheless, we lack a systematic understanding of the factors that influence preprint use in ecology and evolution which can help inform future initiatives and allow us to begin to break down barriers to their use in our field.

### 2023-10-12 ms/ms.qmd
Updated MS with new paper

@@
 Preprint servers, such as *EcoEvoRxiv*, can empower researchers to make their findings more accessible, open and transparent but only if they are used well.
-Significant barriers to preprint use still exist globally – from lack of clarity around preprint policies at journals [@Klebel2020] to a stigma that preprints are viewed by a research community to be of poor quality [@Chiarelli2019].
+Significant barriers to preprint use still exist globally – from lack of clarity around preprint policies at journals [@Klebel2020] to a stigma that preprints are viewed by a research community to be of poor quality [@Chiarelli2019] (but see [@Faser2022]).
 Nonetheless, we lack a systematic understanding of the factors that influence preprint use in ecology and evolution which can help inform future initiatives and allow us to begin to break down barriers to their use in our field.
 
-Here, we explore the first 1000 preprints uploaded to *EcoEvoRxiv* to understand preprint practices and use in our field, focusing on our attention on understanding: 1) how long it takes for a preprint to become published, and how many preprints remain unpublished; 2) what countries make use of preprints; 3) how career stage and gender impact preprint use; 4) whether data and code are more likely to be shared in preprints; and 5) the extent to which authors make use of preprint servers for registered reports and community driven peer review.
+Here, we explore the first 1000 preprints uploaded to *EcoEvoRxiv* to understand preprint practices and use in our field, focusing our attention on understanding: 1) how long it takes for a preprint to become published, and how many preprints remain unpublished; 2) what countries make use of preprints; 3) how career stage and gender impact preprint use; 4) whether data and code are more likely to be shared in preprints; and 5) the extent to which authors make use of preprint servers for registered reports and community driven peer review.
 

### 2023-10-14 ms/ms.qmd
Bring in data to get some simple summary stats
Updated MS

@@
 
+```{r, setup}
+#| label: setup
+
+# Load packages
+#install.packages("pacman")
+pacman::p_load(tidyverse, here, patchwork, readxl)
+
+# Load in the data
+  data <- read_xlsx(here("data", "20231003_EER_preprints_metadata.xlsx"))
+
+pr <- length(unique(data$`Preprint ID`))
+```
+
 Authors: Daniel W.A. Noble, Malgorzata Lagisz, Hackathon Participants, Shinichi Nakagawa
@@
 
-Here, we explore the first 1000 preprints uploaded to *EcoEvoRxiv* to understand preprint practices and use in our field, focusing our attention on understanding: 1) how long it takes for a preprint to become published, and how many preprints remain unpublished; 2) what countries make use of preprints; 3) how career stage and gender impact preprint use; 4) whether data and code are more likely to be shared in preprints; and 5) the extent to which authors make use of preprint servers for registered reports and community driven peer review.
+Here, we explore the first preprints uploaded to *EcoEvoRxiv* to understand preprint practices and use in our field, focusing our attention on understanding: 1) how long it takes for a preprint to become published, and how many preprints remain unpublished; 2) what countries make use of preprints; 3) how career stage and gender impact preprint use; 4) whether data and code are more likely to be shared in preprints; and 5) the extent to which authors make use of preprint servers for registered reports and community driven peer review.
+
+We downloaded metadata on the `r pr` preprints currently available on *EcoEvoRxiv* (as of the 3rd October 2023).
 

### 2023-10-14 ms/ms.qmd
Just having a look at the date ranges and number published

@@
 
+# How many preprints?
   pr <- length(unique(data$`Preprint ID`))
+
+# Dates preprints were published, range and graph
+  dates <- range(data$`Published Date`)
 ```
@@
 
-We downloaded metadata on the `r pr` preprints currently available on *EcoEvoRxiv* (as of the 3rd October 2023).
+We downloaded metadata on the `r pr` preprints currently available on *EcoEvoRxiv* (as of the `r gsub("UTC", "", dates[2])`).
+
+```{r, figdates}
+#| label: fig-figdates
+#| fig-cap: Number of preprints publihsed on *EcoEvoRxiv* across the years.
+
+ggplot(data, aes(x = `Published Date`)) +
+  geom_histogram(fill = "grey", color = "black") +
+  labs(x = "Published Date", y = "Number of preprints") +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+```
 

### 2023-10-15 ms/ms.qmd
Added code to check preprint duplicates

@@
 
+# Check duplicate titles. Appears some folks submitted the same paper multiple times instead of simply updating their existing one.
+
+  # First make sure there is no case sensitivity 
+  data <- data %>% mutate(title = tolower(`Preprint Title`))
+
+  # Check for duplicates
+  dupl <-  data %>%
+    group_by(title) %>% 
+    summarise(n = n()) %>% 
+    filter(n > 1)
+
+  # Remove duplicates
+    data <- data %>% 
+            distinct(title, .keep_all = TRUE)
+
+  # Check success. Should be 1216. Yes
+    dupl <- data %>%
+            group_by(title) %>% 
+            summarise(n = n()) %>% 
+            filter(n > 1)
+
 # Dates preprints were published, range and graph
   dates <- range(data$`Published Date`)
+
 ```

### 2023-10-15 ms/ms.qmd
Updated numbers

@@
 
-# How many preprints?
-  pr <- length(unique(data$`Preprint ID`))
-
 # Check duplicate titles. Appears some folks submitted the same paper multiple times instead of simply updating their existing one.
@@
   # Check success. Should be 1216. Yes
-    dupl <- data %>%
+    dupl2 <- data %>%
             group_by(title) %>% 
@@
             filter(n > 1)
+
+# How many preprints?
+  pr <- length(unique(data$`Preprint ID`))
 
@@
 
-We downloaded metadata on the `r pr` preprints currently available on *EcoEvoRxiv* (as of the `r gsub("UTC", "", dates[2])`).
+We downloaded metadata on the `r pr` preprints currently available on *EcoEvoRxiv* (as of the `r gsub("UTC", "", dates[2])`), after removing `r dim(dupl)[1]` duplicate titles suggesting a few authors created multiple submissons for the same preprint rather than simply updated an existing submission.
 

### 2023-10-15 ms/ms.qmd
Fixes to wording

--- 2023-10-15 ms/ms.qmd
@@
 
-We downloaded metadata on the `r pr` preprints currently available on *EcoEvoRxiv* (as of the `r gsub("UTC", "", dates[2])`).
+We downloaded metadata on the preprints currently available on *EcoEvoRxiv* (as of the `r gsub("UTC", "", dates[2])`).
+After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissons for the same preprint rather than simply updated an existing submission – we had data for a total of `r pr` preprints.
 

### 2023-10-15 ms/ms.qmd
Update for line numbers in pdf

@@
     reference-doc: ../bib/template.docx
+  pdf:
+    include-in-header: 
+      text: '\usepackage{lineno}\linenumbers'
 editor_options: 
@@
 We downloaded metadata on the preprints currently available on *EcoEvoRxiv* (as of the `r gsub("UTC", "", dates[2])`).
-After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissons for the same preprint rather than simply updated an existing submission – we had data for a total of `r pr` preprints.
+After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissons for the same preprint rather than updating an existing submission – we had data for a total of `r pr` preprints with ~55-60 preprints published each month in the last two years (@fig-figdates).
 
@@
 #| label: fig-figdates
-#| fig-cap: Number of preprints publihsed on *EcoEvoRxiv* across the years.
+#| fig-cap: Number of preprints published monthly to *EcoEvoRxiv* between 2018 and 2023.
 

### 2023-10-19 R/1_data_processing.R
Code to start data processing and getting delegate details

@@ -1,0 +1,20 @@
+###–––––––––––––––––––––––––––––––––––––––––––––––––###
+# Purpose: Loading and cleaning Google Sheet Data
+###–––––––––––––––––––––––––––––––––––––––––––––––––###
+
+# Load packages
+	pacman::p_load(tidyverse, googlesheets4, janitor)
+
+# Load data from Google Sheets
+	# Delegate list
+	delegates <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Delegate Details")
+
+	# Export emails
+	write.csv(delegates$Email, "output/emails/delegates_emails.csv", row.names = FALSE)
+
+	# Master preprint list 
+	master_list <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Master List of Preprints")
+
+# Check on status
+	status <- master_list  %>% rename("completed" = "Completed_Yes_No_extractor") %>%
+			mutate(completed = str_to_title(completed))  %>% tabyl(completed)

### 2023-10-19 R/1_data_processing.R
Links to raw data

@@ -15,6 +15,12 @@
 	# Master preprint list 
 	master_list <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Master List of Preprints")
 
-# Check on status
+	# Check on status
 	status <- master_list  %>% rename("completed" = "Completed_Yes_No_extractor") %>%
 			mutate(completed = str_to_title(completed))  %>% tabyl(completed)
+
+	# raw data
+	data <- read_sheet("https://docs.google.com/spreadsheets/d/1032gLryvtCNJ7eJjKBjrn7txxDRUGql9SoIG18QnFrQ/edit?resourcekey#gid=1062856014")
+
+
+

### 2023-10-19 supp/supp.qmd
Adding in methods to supp

--- 2023-09-11 supp/supp.qmd
@@
 ---
-title: "Empowering the use of preprints in ecology and evolution: an exploration of the first 1000 *EcoEvoRxiv* preprints"
+title: "Supplementary Materials for: Empowering the use of preprints in ecology and evolution: an exploration of the first 1000 *EcoEvoRxiv* preprints"
 bibliography: ../bib/refs.bib
@@
 ---
+
+```{r, setup}
+#| label: setup
+
+# Load packages
+#install.packages("pacman")
+pacman::p_load(tidyverse, here, patchwork, readxl, googlesheets4, janitor)
+
+# Set rounding options
+options(scipen = 1, digits = 2)
+
+# Load in the data
+  data <- read_xlsx(here("data", "20231003_EER_preprints_metadata.xlsx"))
+
+# Check duplicate titles. Appears some folks submitted the same paper multiple times instead of simply updating their existing one.
+
+  # First make sure there is no case sensitivity 
+  data <- data %>% mutate(title = tolower(`Preprint Title`))
+
+  # Check for duplicates
+  dupl <-  data %>%
+    group_by(title) %>% 
+    summarise(n = n()) %>% 
+    filter(n > 1)
+
+  # Remove duplicates
+    data <- data %>% 
+            distinct(title, .keep_all = TRUE)
+
+  # Check success. Should be 1216. Yes
+    dupl2 <- data %>%
+            group_by(title) %>% 
+            summarise(n = n()) %>% 
+            filter(n > 1)
+
+# How many preprints?
+  pr <- length(unique(data$`Preprint ID`))
+
+# Dates preprints were published, range and graph
+  dates <- range(data$`Published Date`)
+
+# Delegate details
+delegates <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Delegate Details")
+
+del_details <- delegates  %>% rename("attend" = "Attended hackathon (yes/no)") %>%
+			mutate(attend = str_to_title(attend))  %>% tabyl(attend)
+
+# Raw data
+master_list <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Master List of Preprints")
+
+contr_extract <- master_list  %>%  tabyl(Extractor_Full_Name)
+
+```
+
+# Materials and Methods
+
+## Pre-registration, Data and Code Availability
+We preregistered the study on the Open Science Framework (OSF) (https://osf.io/d7zws) as an open-ended registration.
+We also created relevant updated study plan releases on our GitHub repository to capture key changes to the project as it developed (https://github.com/daniel1noble/ecoevo_1000).
+All data and code for reproducing the analyses and conclusions within our paper can be found on GitHub (https://github.com/daniel1noble/ecoevo_1000).
+
+## Data collection
+We downloaded metadata on all preprints lodged on *EcoEvoRxiv* between `r gsub("UTC", "", dates[1])` and `r gsub("UTC", "", dates[2])`.
+This information included data on preprint submission and acceptance dates, date when the preprint was last updated, the reuse license, preprint ID and Digitial Object Identifier (DOI), preprint title, submitting author and co-authors, the number of versions submitted by authors and, if available, a DOI for the published version of the preprint.
+
+As part of the Society for Open, Reliable and Transparent Ecology and Evolutionary Biology's (SORTEE - https://www.sortee.org) conference, we ran a workshop (i.e., Hackathon) where we invited interested SORTEE members and conference registrants to participate in the data collection process.
+We provided a detailed data collection protocol to all delegates prior to the workshop ([vers.
+1.0 - release](https://github.com/daniel1noble/ecoevo_1000/releases/tag/v1.0)).
+We used the workshop to train participants on how to collect data from *EcoEvoRxiv* preprints.
+This involved a demonstration of a single preprint followed by data collection by all attendees on the same preprint.
+Any confusion or questions were addressed by the workshop facilitators and the study data collection instructions and study plan were updated accordingly ([vers.1.1 - release](https://github.com/daniel1noble/ecoevo_1000/releases/tag/V1.1)).
+
+We had a total of `r del_details[2,2]` participants in the workshop, and an additional `r del_details[1,2]` that could not attend but were interested in contributing.
+Participants assigned themselves to collect data from between `r range(contr_extract$n)[1]` to `r range(contr_extract$n)[2]` preprints (mean = `r mean(contr_extract$n)`, standard deviation = `r sd(contr_extract$n)`).
+Data collection was achieved using a Google Form to standardise data input.
+Participants collected the following information for each of their assigned preprints:
+
+- **Preprint DOI**: Copy and pasted from the preprint meta-data file.
+- **Submitting/ corresponding authors firstname**: First name (given name) and second name (or initials, if provided) of the author submitting the preprint.
+Usually there was one submitting author in the meta-data preprint list.
+If there were multiple authors then the first author listed on the preprint was used.
+- **Submitting/ corresponding authors lastname**: Last name of the author submitting the preprint.
+Usually there was one submitting author in the meta-data preprint list.
+If there were multiple authors then the first author listed on the preprint was used.
+- **Country of the corresponding / submitting author**: Country of affiliation for the author submitting the preprint collecting accoring to standard ISO 3166 names.
+If teh country could not be determined the affiliation was considered as "NA".
+- **Year of first publication for corresponding/submitted author**: We used [Google Scholar](https://scholar.google.com.au) to collect publication year of the first journal article published by author submitting the preprint.
+If the submitting author had no profile or did not publish the value enetred was '0'.
+- **Taxa being studied**: We collected information about the broad group of taxa that were the focus of the preprint.
+These categories were "Plants", "Animals", "Fungi", "Algi", "Invertabrates", "Vertebrates", "Microorganisms (bacteria, viruses)", or "Other".
+Multiple categories could be selected if the preprint contained information on multiple taxa.
+- **Discussion on the preprint?**: We identified whether there were community discussions around the preprint on the landing page of each preprint.
+If there were, we indicated 'yes', otherwise we indicated 'no'.
+Additional discussions around a preprint may have occurred on other platforms (e.g., Twitter, Facebook, etc.) but we did not collect this information.
+- **Type of article**: *EcoEvoRxiv* publishes a greater diversity of preprints compared with other preprint servers.
+We therefore collected data on article type.
+The categories were: *Research Article*: any article-like manuscript intended for publication in research journals with new empirical findings; *Methods paper*: papers presenting new methodological or computational approaches; *Reviews and Meta-analyses*: papers quantitatively or qualitatively synthesising a given topic;  *Opinions*: usually short papers providing new perspectives on a topic; *Comments*: papers that explicitly comment on an already published research article; and *Other*: which includes any other category of preprint which may also be government, non-profit, or industry reports, white papers, or other documents that are not intended for publication in a research journal.
+- **Link to Data for Preprint**: We were explicitly interested in whether data for the preprint was already publically available.
+To collect these data we scrolled through the first version of the preprint and any related files on *EcoEvoRxiv* to see if a link (or accession number) to underlying data was provided.
+If it was reported we took the link to the data.
+If the preprint was not an empirical or equivalent article based on data and data analyses (so usually for opinions, comments, narrative reviews, theoretical paper, etc.) we entered 'NA'.
+If the preprint was based on data but no link (or accession number) to data repository was reported we entered 'none'.
+If multiple links were provided we took one.
+- **Link to Code for Preprint**: We were also interested in whether code for data analysis was already publically available.
+To collect these data we scrolled through the first version of the preprint and any related files on *EcoEvoRxiv* to see if a link (or accession number) to underlying code was provided.
+If it was reported we took the link to the code.
+If the preprint was not an empirical or equivalent article based on data and data analyses (so usually for opinions, comments, narrative reviews, theoretical paper, etc.) we entered 'NA'.
+If the preprint was based on data but no link (or accession number) to data repository with code was reported we entered 'none'.
+If multiple links were provided we took one.
+- **Number of citations to preprint**: To understand citation patterns of preprints on *EcoEvoRxiv* we used Google Sscholar to search for the number of citations attributed to the preprint.
+If the preprint version was not on Google Scholar or was merged with an already published version we considered it as 'NA' (coded as '999').
+If the preprint version was online and clearly indicated (i.e., EcoEvoRxiv) then we took the number of citations at the time of collection.
+While citation counts may vary slightly, the first round of data collection was done in a short time frame.
+As such, we do not anticipate that citation counts would have changed significantly between the time of data collection and the time of submission of this manuscript.
+- **PCI recommendation**: We also deteremined if the preprint been recomended by Peer Community In (PCI).
+To do this, we searched for any PCI recommendations associated with the preprint on the preprint landing page.
+If that none was available on the landing page then we searched "peercommunityin.org recommendation "TITLE OF PREPRINT"" on Google.
+If a link was discovered, we indicated 'yes' and took the DOI link.
+If not, then we assumed it was not recommended.
+- **Publication DOI**: If the preprint had been published as a journal article, we collected the published DOI of that article. 
+- **Journal name**: If the preprint had been published as a journal article we recorded the journal name.
+- **Publicaton Date**. If the preprint has been published as a journal article, we collected the (first) publication date (Month, Day, Year).
+- **Title Change**: If the preprint had been published as a journal article, we assessed whether the title had changed between the first version of the preprint and the published article.
+Note that any word change was sufficient for a 'yes'.
+- **Number of citations to publication**: We collected the number of citations to the published version of the article manually from [Google Scholar](https://scholar.google.com.au) if published.
+- **Link to Data for Publication**: If the preprint was published we collected the link to any published data provided on the publishers webpage or within the published paper.
+If a link to the data was not visble we recorded the paper as not having provided data ('none').
+If the paper had not been published or not based on data and data analyses (opinions, comments, narrative reviews, theoretical paper, etc.) we entered 'NA'.
+- **Link to Code for Publication**: If the preprint was published we collected the link to any published code provided on the publishers webpage or within the published paper.
+If a link to the data was not visble we recorded the paper as not having provided data ('none').
+If the paper had not been published or not based on data and data analyses (opinions, comments, narrative reviews, theoretical paper, etc.) we entered 'NA'.
+
+Additional variables of interest (i.e., journal impact factor, preprint and review policy, gender of submitting author) could be determined oustide of this data collection period.

### 2023-10-20 supp/supp.qmd
Adding fig to supplement rather than main MS

@@
 Additional variables of interest (i.e., journal impact factor, preprint and review policy, gender of submitting author) could be determined oustide of this data collection period.
+
+# Supplementary Results
+
+```{r, figdates}
+#| label: fig-figdates
+#| fig-cap: Number of preprints published monthly to *EcoEvoRxiv* between 2018 and 2023.
+
+ggplot(data, aes(x = `Published Date`)) +
+  geom_histogram(fill = "grey", color = "black") +
+  labs(x = "Published Date", y = "Number of preprints") +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+```

### 2023-10-20 supp/supp.qmd
Some writing and coding

@@
 
-# Raw data
+# Master preprint list
 master_list <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Master List of Preprints")
@@
 contr_extract <- master_list  %>%  tabyl(Extractor_Full_Name)
+
+# raw data
+	data_coll <- read_sheet("https://docs.google.com/spreadsheets/d/1032gLryvtCNJ7eJjKBjrn7txxDRUGql9SoIG18QnFrQ/edit?resourcekey#gid=1062856014")
 
@@
 
+## Data Checking and Validation
+Data from each preprint was cross checked by two authors to ensure accuracy and consistency of the data collected. Any discrepencies were either discussed or fixed prior to analysis.
+
 # Supplementary Results

### 2023-10-21 R/1_data_processing.R
Just cleaning annoting Google sheet names

@@ -13,14 +13,15 @@
 	write.csv(delegates$Email, "output/emails/delegates_emails.csv", row.names = FALSE)
 
 	# Master preprint list 
-	master_list <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Master List of Preprints")
+	master_list <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Master List of Preprints")  %>% clean_names()
 
 	# Check on status
-	status <- master_list  %>% rename("completed" = "Completed_Yes_No_extractor") %>%
+	status <- master_list  %>% rename("completed" = "completed_yes_no_extractor") %>%
 			mutate(completed = str_to_title(completed))  %>% tabyl(completed)
 
 	# raw data
 	data <- read_sheet("https://docs.google.com/spreadsheets/d/1032gLryvtCNJ7eJjKBjrn7txxDRUGql9SoIG18QnFrQ/edit?resourcekey#gid=1062856014")
 
+	data <- data  %>% clean_names()
 
 

### 2023-10-22 R/1_data_processing.R
Update on status, checks, 55% complete

@@ -22,6 +22,7 @@
 	# raw data
 	data <- read_sheet("https://docs.google.com/spreadsheets/d/1032gLryvtCNJ7eJjKBjrn7txxDRUGql9SoIG18QnFrQ/edit?resourcekey#gid=1062856014")
 
-	data <- data  %>% clean_names()
+	# clean raw data
+	data <- data %>% clean_names()
 
 

### 2023-10-23 R/1_data_processing.R
Added some more checks

@@ -7,8 +7,11 @@
 
 # Load data from Google Sheets
 	# Delegate list
-	delegates <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Delegate Details")
+	delegates <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Delegate Details")  %>%  clean_names()
 
+	# Check on who attended the hackathon
+	delegates  %>% tabyl("attended_hackathon_yes_no")
+	
 	# Export emails
 	write.csv(delegates$Email, "output/emails/delegates_emails.csv", row.names = FALSE)
 

### 2023-10-23 R/1_data_processing.R
writing master list

@@ -13,19 +13,21 @@
 	delegates  %>% tabyl("attended_hackathon_yes_no")
 	
 	# Export emails
-	write.csv(delegates$Email, "output/emails/delegates_emails.csv", row.names = FALSE)
+	write.csv(delegates$email, "output/emails/delegates_emails.csv", row.names = FALSE)
 
 	# Master preprint list 
 	master_list <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Master List of Preprints")  %>% clean_names()
+
+	# Export master list
+	write.csv(master_list, "output/data/master_list.csv", row.names = FALSE)
 
 	# Check on status
 	status <- master_list  %>% rename("completed" = "completed_yes_no_extractor") %>%
 			mutate(completed = str_to_title(completed))  %>% tabyl(completed)
 
 	# raw data
-	data <- read_sheet("https://docs.google.com/spreadsheets/d/1032gLryvtCNJ7eJjKBjrn7txxDRUGql9SoIG18QnFrQ/edit?resourcekey#gid=1062856014")
+	data <- read_sheet("https://docs.google.com/spreadsheets/d/1032gLryvtCNJ7eJjKBjrn7txxDRUGql9SoIG18QnFrQ/edit?resourcekey#gid=1062856014") %>% clean_names()
 
-	# clean raw data
-	data <- data %>% clean_names()
+
 
 

### 2023-10-27 R/1_data_processing.R
Adding more detail to keep track of how folks are going relative to the total they allocated to themselves

@@ -25,6 +25,15 @@
 	status <- master_list  %>% rename("completed" = "completed_yes_no_extractor") %>%
 			mutate(completed = str_to_title(completed))  %>% tabyl(completed)
 
+	# Check allocation of papers
+		contr_extract <- master_list  %>%  tabyl(extractor_full_name)
+
+	# Check how many each person has done relative to their total
+		contr_extract2 <- master_list %>% group_by(extractor_full_name) %>% summarise(n = n(), yes = sum(completed_yes_no_extractor == "Yes"), no = sum(completed_yes_no_extractor == "No"), prop = yes/n)  %>% data.frame()
+
+	# Check who hasn't yet started
+		not_done <- contr_extract2  %>% filter(prop != 1)
+	
 	# raw data
 	data <- read_sheet("https://docs.google.com/spreadsheets/d/1032gLryvtCNJ7eJjKBjrn7txxDRUGql9SoIG18QnFrQ/edit?resourcekey#gid=1062856014") %>% clean_names()
 

### 2023-10-27 supp/supp.qmd
Small update
Removing code
Small code update that got moved to processing

@@
 # Master preprint list
-master_list <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Master List of Preprints")
-
-contr_extract <- master_list  %>%  tabyl(Extractor_Full_Name)
+master_list <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Master List of Preprints") %>% clean_names()
 

### 2023-10-30 R/1_data_processing.R
Adding code to merge emails

@@ -7,7 +7,7 @@
 
 # Load data from Google Sheets
 	# Delegate list
-	delegates <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Delegate Details")  %>%  clean_names()
+	delegates <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Delegate Details")  %>%  clean_names()  %>% mutate(extractor_full_name = paste0(firstname, " ", lastname))
 
 	# Check on who attended the hackathon
 	delegates  %>% tabyl("attended_hackathon_yes_no")
@@ -34,6 +34,12 @@
 	# Check who hasn't yet started
 		not_done <- contr_extract2  %>% filter(prop != 1)
 	
+	# Grab emails of those not yet done so they can be emailed to be reminded
+		not_done_emails <- left_join(not_done, delegates, by = "extractor_full_name")  %>% select(extractor_full_name, n, yes,no,prop, email) 
+
+	# Write this sheet
+		write.csv(not_done_emails, file = here("output", "emails", "not_done_emails.csv"))
+
 	# raw data
 	data <- read_sheet("https://docs.google.com/spreadsheets/d/1032gLryvtCNJ7eJjKBjrn7txxDRUGql9SoIG18QnFrQ/edit?resourcekey#gid=1062856014") %>% clean_names()
 

### 2023-11-06 supp/supp.qmd
Added some notation

@@
 
-# raw data
+# raw data. For analysis
 	data_coll <- read_sheet("https://docs.google.com/spreadsheets/d/1032gLryvtCNJ7eJjKBjrn7txxDRUGql9SoIG18QnFrQ/edit?resourcekey#gid=1062856014")

### 2023-11-06 R/1_data_processing.R
Arranging contributions to data collection by amount

@@ -29,7 +29,7 @@
 		contr_extract <- master_list  %>%  tabyl(extractor_full_name)
 
 	# Check how many each person has done relative to their total
-		contr_extract2 <- master_list %>% group_by(extractor_full_name) %>% summarise(n = n(), yes = sum(completed_yes_no_extractor == "Yes"), no = sum(completed_yes_no_extractor == "No"), prop = yes/n)  %>% data.frame()
+		contr_extract2 <- master_list %>% group_by(extractor_full_name) %>% summarise(n = n(), yes = sum(completed_yes_no_extractor == "Yes"), no = sum(completed_yes_no_extractor == "No"), prop = yes/n)  %>% data.frame()  %>% arrange(n)
 
 	# Check who hasn't yet started
 		not_done <- contr_extract2  %>% filter(prop != 1)

### 2023-11-06 R/1_data_processing.R
Push code for delegate list combined with processing list

@@ -37,6 +37,10 @@
 	# Grab emails of those not yet done so they can be emailed to be reminded
 		not_done_emails <- left_join(not_done, delegates, by = "extractor_full_name")  %>% select(extractor_full_name, n, yes,no,prop, email) 
 
+	# Join together delegate list with master list
+		joined <- full_join(delegates, contr_extract2, by = "extractor_full_name", multiple = "all")  %>% arrange(extractor_full_name) %>% data.frame()
+
+
 	# Write this sheet
 		write.csv(not_done_emails, file = here("output", "emails", "not_done_emails.csv"))
 

### 2023-11-06 R/1_data_processing.R
Code to export the raw data from Google sheets

@@ -3,7 +3,7 @@
 ###–––––––––––––––––––––––––––––––––––––––––––––––––###
 
 # Load packages
-	pacman::p_load(tidyverse, googlesheets4, janitor)
+	pacman::p_load(tidyverse, googlesheets4, janitor, here)
 
 # Load data from Google Sheets
 	# Delegate list
@@ -19,7 +19,7 @@
 	master_list <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Master List of Preprints")  %>% clean_names()
 
 	# Export master list
-	write.csv(master_list, "output/data/master_list.csv", row.names = FALSE)
+	write.csv(master_list, "data/master_list.csv", row.names = FALSE)
 
 	# Check on status
 	status <- master_list  %>% rename("completed" = "completed_yes_no_extractor") %>%
@@ -40,13 +40,14 @@
 	# Join together delegate list with master list
 		joined <- full_join(delegates, contr_extract2, by = "extractor_full_name", multiple = "all")  %>% arrange(extractor_full_name) %>% data.frame()
 
-
 	# Write this sheet
 		write.csv(not_done_emails, file = here("output", "emails", "not_done_emails.csv"))
 
-	# raw data
-	data <- read_sheet("https://docs.google.com/spreadsheets/d/1032gLryvtCNJ7eJjKBjrn7txxDRUGql9SoIG18QnFrQ/edit?resourcekey#gid=1062856014") %>% clean_names()
+	# raw data, # Problem with the data link article. Some reason it's created it as a list and NULLs are a problem so this needs fixing so that it's a single column not a list within a dataframe
+	data <- read_sheet("https://docs.google.com/spreadsheets/d/1032gLryvtCNJ7eJjKBjrn7txxDRUGql9SoIG18QnFrQ/edit?resourcekey#gid=1062856014") %>% clean_names()  %>% data.frame()   %>% mutate(data_link_article = plyr::ldply(lapply(data_link_article, function(x) ifelse(is.null(x), "NULL", x)))[,1])
 
+	# Write the raw data
+		write.csv(data, file = here("data", "raw_data.csv"))
 
 
 

### 2023-11-06 R/1_data_processing.R
Adding ocde to export data-checking sheet

@@ -7,7 +7,11 @@
 
 # Load data from Google Sheets
 	# Delegate list
-	delegates <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Delegate Details")  %>%  clean_names()  %>% mutate(extractor_full_name = paste0(firstname, " ", lastname))
+
+	# Simplify a few names to avoid issues down the road
+	replace <- c("Stefan J.G. Vriend" = "Stefan Vriend", "Matt Grainger" = "Matthew Grainger", "Gideon Gywa Deme" = "Gideon Deme", "Magdalena M. Mair" = "Magdalena Mair", "Malgorzata Lagisz" = "Losia Lagisz")
+	
+	delegates <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Delegate Details")  %>%  clean_names()  %>% mutate(extractor_full_name = paste0(firstname, " ", lastname))  %>% mutate(extractor_full_name = str_replace_all(extractor_full_name, replace))  %>% data.frame() 
 
 	# Check on who attended the hackathon
 	delegates  %>% tabyl("attended_hackathon_yes_no")
@@ -31,6 +35,9 @@
 	# Check how many each person has done relative to their total
 		contr_extract2 <- master_list %>% group_by(extractor_full_name) %>% summarise(n = n(), yes = sum(completed_yes_no_extractor == "Yes"), no = sum(completed_yes_no_extractor == "No"), prop = yes/n)  %>% data.frame()  %>% arrange(n)
 
+	# Export final list of thos who extracted. 
+		write.csv(contr_extract2, file = here("data", "final_extractors.csv"))
+
 	# Check who hasn't yet started
 		not_done <- contr_extract2  %>% filter(prop != 1)
 	
@@ -38,13 +45,16 @@
 		not_done_emails <- left_join(not_done, delegates, by = "extractor_full_name")  %>% select(extractor_full_name, n, yes,no,prop, email) 
 
 	# Join together delegate list with master list
-		joined <- full_join(delegates, contr_extract2, by = "extractor_full_name", multiple = "all")  %>% arrange(extractor_full_name) %>% data.frame()
[…]

### 2023-11-08 R/1_data_processing.R
Getting organised to start looking at the data

@@ -1,11 +1,15 @@
 ###–––––––––––––––––––––––––––––––––––––––––––––––––###
 # Purpose: Loading and cleaning Google Sheet Data
 ###–––––––––––––––––––––––––––––––––––––––––––––––––###
-
+###-------------------------###
 # Load packages
+###-------------------------###
 	pacman::p_load(tidyverse, googlesheets4, janitor, here)
 
-# Load data from Google Sheets
+###-------------------------###
+# Load data from Google Sheets 
+# and save raw files
+###-------------------------###
 	# Delegate list
 
 	# Simplify a few names to avoid issues down the road
@@ -59,5 +63,9 @@
 	# Write the raw data
 		write.csv(data, file = here("data", "raw_data.csv"))
 
+###-------------------------###
+# Processing and fixing mistakes
+# in raw data
+###-------------------------###
 
 

### 2023-11-08 R/1_data_processing.R
Checking out data with some simple checks

@@ -68,4 +68,28 @@
 # in raw data
 ###-------------------------###
 
+# Have a look at how many preprint DOI's there should be 1216 unique ones
+		data  %>% select(preprint_doi)  %>% distinct()  %>% nrow() #1191....
+
+# Which preprint DOI's are in the master list but are not found in the data?
+		missing <- master_list  %>% filter(!preprint_doi %in% data$preprint_doi)  %>% select(preprint_doi)  %>% distinct()  %>% data.frame()
+		
+# Find out which preprints were missing, merge missing and masterlist to identify who
+		missed <- left_join(missing, master_list, by = "preprint_doi", suffix = c("_missing", "_master"))  %>% data.frame()
+		write.csv(missed, file = here("data", "missing_preprints.csv"))
+
+
+# We first need to filter out all the pilot runs from Losia and the hackathon.
+	# Remove losia's test runs
+		data <- data  %>% filter(!c(extractors_first_name == "Losia" & extractors_last_name == "Lagisz" & timestamp < "2023-10-17"))  %>% data.frame()
+
+	# Remove the training paper, but save a training data as that can be used to check for consistency
+		data2 <- data  %>% filter(!c(submitting_corresponding_author_last_name == "Nakagawa" & timestamp < as.Date("10/17/2023 21:51:35", format = "%m-%d-$Y")))  %>% data.frame()
+		
+		training_data <- data  %>% 
+						filter(c(submitting_corresponding_author_last_name == "Nakagawa" & timestamp < as.Date("10/17/2023", format = "%m-%d-$Y")))  %>% 
+						data.frame()
+
+# Merge together the masterlist information with the data
+		data <- left_join(data, master_list, by = "data_link_article", suffix = c("_data", "_master"))  %>% data.frame()
 

### 2023-11-08 R/1_data_processing.R
Found duplicated preprints that were extracted, a bunch of others where the wrong preprint DOI was used

@@ -78,6 +78,9 @@
 		missed <- left_join(missing, master_list, by = "preprint_doi", suffix = c("_missing", "_master"))  %>% data.frame()
 		write.csv(missed, file = here("data", "missing_preprints.csv"))
 
+# Lets assume maybe that the wrong DOI was entered in, so lets tally the same DOIs
+		doi_tally <- data  %>% group_by(preprint_doi) %>% summarise(n = n())  %>% 
+					filter(n>1)  %>% data.frame()
 
 # We first need to filter out all the pilot runs from Losia and the hackathon.
 	# Remove losia's test runs

### 2023-11-08 R/1_data_processing.R
Code for checking

@@ -69,7 +69,7 @@
 ###-------------------------###
 
 # Have a look at how many preprint DOI's there should be 1216 unique ones
-		data  %>% select(preprint_doi)  %>% distinct()  %>% nrow() #1191....
+		data  %>% select(preprint_doi)  %>% distinct()  %>% nrow() #1201....
 
 # Which preprint DOI's are in the master list but are not found in the data?
 		missing <- master_list  %>% filter(!preprint_doi %in% data$preprint_doi)  %>% select(preprint_doi)  %>% distinct()  %>% data.frame()

### 2023-11-08 R/1_data_processing.R
Notes on ToDO

@@ -68,6 +68,12 @@
 # in raw data
 ###-------------------------###
 
+# List of to DO
+# - [x] Check that the preprint DOI's are correct and that we have expected number
+# - [] Determine which preprints are missing and collect the data for these
+# - [] Filter out the training paper data (aside from one paper for inclusion in the data)
+# - [] check all pilot data has been removed
+
 # Have a look at how many preprint DOI's there should be 1216 unique ones
 		data  %>% select(preprint_doi)  %>% distinct()  %>% nrow() #1201....
 

### 2023-12-30 ms/ms.qmd
Small edits to sentence structure

@@
 While preprint use in biology has had a slower uptake [@Berg2016], in ecology and evolution, new discipline specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disseminate research findings.
-Such practices promote open science (e.g., ensuring papers are open access) and facilitate the rapid sharing of new discoveries that can have significant impacts on fundamental and applied knowledge globally (e.g., conservation outcomes).
+Such practices promote open science (e.g., ensuring papers are open access) and facilitate the rapid sharing of new discoveries that can have significant impacts on fundamental and applied knowledge globally.
 
 Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed, visibility and output of research findings; 2) encouraging constructive and critical feedback from a research community; 3) helping establish precedence of research findings; and 4) removing financial barriers to publication [e.g., @Proulx2013].
-Importantly, *EcoEvoRxiv* is a community driven preprint server that has paved the way for new initiatives, including accepting multilingual preprints, recognising and accepting registered reports and non-traditional research reports, and promoting peer review and community discussion to improve the quality of preprints and speed up their peer-reviewed publication (e.g., Peer Community In -- PCI).
+*EcoEvoRxiv* is a community driven preprint server that has paved the way for new initiatives, including accepting multilingual preprints, recognising and accepting registered reports and non-traditional research reports, and promoting peer review and community discussion to improve the quality of preprints and speed up their peer-reviewed publication (e.g., Peer Community In -- PCI).
 

### 2024-02-13 ms/ms.qmd
Remove words
Updates to MS and ignore file

@@
 ---
-title: "Empowering the use of preprints in ecology and evolution: an exploration of the first 1000 *EcoEvoRxiv* preprints"
+title: "Empowering the use of community driven preprints in ecology and evolution"
 bibliography: ../bib/refs.bib
@@
 
-We downloaded metadata on the preprints currently available on *EcoEvoRxiv* (as of the `r gsub("UTC", "", dates[2])`).
+We downloaded metadata on the preprints available on *EcoEvoRxiv* (as of the `r gsub("UTC", "", dates[2])`).
 After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissons for the same preprint rather than updating an existing submission – we had data for a total of `r pr` preprints with ~55-60 preprints published each month in the last two years (@fig-figdates).
@@
 
+- figure timeline of EcoEvoRxiv, aims and future and current developments infographics mixed with the data.
+- think about your preprint as workflow, continually evolving paper with support of the community. 
+- community driven peer review, can't update things with other preprints. 
+- our terms, we are not a journal, we are a preprint server. Cannot be company driven.
+
 # References

### 2024-02-14 R/3_final_dat_analysis.R
Script to import final data and merge with OA data from unpaywall

@@ -1,0 +1,46 @@
+########################################
+# Analysis of the final checked data file
+########################################
+
+###-------------------------###
+# Load packages
+###-------------------------###
+	pacman::p_load(tidyverse, googlesheets4, janitor, here, roadoi)
+
+###-------------------------###
+# Load data from Google Sheets 
+# and save raw files
+###-------------------------###
+
+	# Load data	
+	data <- read_csv(here("data", "final_data.csv"))  %>% 
+	mutate(
+		preprint_published_date = as.Date(preprint_published_date, format = "%d/%m/%Y"),
+	    publication_date = as.Date(publication_date, format = "%d/%m/%Y"),
+		time_between_preprint_and_pub_days = as.numeric(publication_date - preprint_published_date))
+	
+	# Have a look at columns
+	str(data)
+
+###-------------------------###
+# Extract whether a paper is open access or not
+###-------------------------###
+
+# Use the DOI for the published paper to get OA
+dois <- unique(data$publisher_doi) 
+length(dois) # 510, but one NA
+
+#connect and fetch the data
+OA_df <- roadoi::oadoi_fetch(dois = dois, email = "daniel.wa.noble@gmail.com") 
+
+#save fetched data
+readr::write_csv(OA_df, file = here("output", "data","OA_article_data_Unpaywall.csv")) 
+dim(OA_df) # 509, 11 1 missing because of empty string for NA values
+
+OA_df <- OA_df  %>% select(doi, journal_name, is_oa, oa_status)
+
+# Merge dois with OA data
+OA_df2 <- data.frame(doi = dois[-1], OA_df)
+
+# Merge with the main data
+data2 <- data  %>% left_join(OA_df2, by = c("publisher_doi" = "doi"))

### 2024-03-15 R/3_final_dat_analysis.R
Checking where we are at and doing some more processing

@@ -27,20 +27,24 @@
 ###-------------------------###
 
 # Use the DOI for the published paper to get OA
-dois <- unique(data$publisher_doi) 
-length(dois) # 510, but one NA
+dois <- unique(data$publisher_doi)[-1] # Remove 1 NA in first position
+length(dois) # 509
 
 #connect and fetch the data
 OA_df <- roadoi::oadoi_fetch(dois = dois, email = "daniel.wa.noble@gmail.com") 
 
 #save fetched data
 readr::write_csv(OA_df, file = here("output", "data","OA_article_data_Unpaywall.csv")) 
-dim(OA_df) # 509, 11 1 missing because of empty string for NA values
+dim(OA_df) # 509
 
 OA_df <- OA_df  %>% select(doi, journal_name, is_oa, oa_status)
 
 # Merge dois with OA data
-OA_df2 <- data.frame(doi = dois[-1], OA_df)
+OA_df2 <- data.frame(doi = dois, OA_df)
 
 # Merge with the main data
 data2 <- data  %>% left_join(OA_df2, by = c("publisher_doi" = "doi"))
+
+# We have now cross checked the paper in more detail to see if we missed any published papers. So, we should update the new time between preprint and publication dates, which is a time difference between the preprint and the published paper dates. CRoss checked two times to make sure they were calculated correct. Good!
+
+data2 <- data2  %>% mutate(time_between_preprint_and_pub_days = ymd(publication_date) - ymd(preprint_published_date))

### 2024-03-16 R/3_final_dat_analysis.R
Publication time.

@@ -48,3 +48,16 @@ data2 <- data  %>% left_join(OA_df2, by = c("publisher_doi" = "doi"))
 # We have now cross checked the paper in more detail to see if we missed any published papers. So, we should update the new time between preprint and publication dates, which is a time difference between the preprint and the published paper dates. CRoss checked two times to make sure they were calculated correct. Good!
 
 data2 <- data2  %>% mutate(time_between_preprint_and_pub_days = ymd(publication_date) - ymd(preprint_published_date))
+
+
+### Excluding postprints, how long does it take for a preprint to be published in Ecology and Evolution?
+
+data2  %>% filter(postprint == "preprint")  %>% ggplot(aes(x = time_between_preprint_and_pub_days)) + geom_histogram(binwidth = 30) + labs(title = "Time between preprint and publication in Ecology and Evolution", x = "Days", y = "Frequency") + theme_minimal()
+
+# Why are there weird dates (e.g, Should take at least 3 months to publish a paper, and also, anything below 0 should be a postprint.) Lets assue anything published within 3 months and those with negative dates are postprints.
+
+preprints <- data2  %>% filter(time_between_preprint_and_pub_days >= 90)
+preprints %>% ggplot(aes(x = time_between_preprint_and_pub_days)) + geom_histogram(binwidth = 30) + labs(title = "Time between preprint and publication in Ecology and Evolution", x = "Days", y = "Frequency") + theme_minimal()
+
+# what is the range
+preprints  %>% summarise(min = min(time_between_preprint_and_pub_days), max = max(time_between_preprint_and_pub_days), mean = mean(time_between_preprint_and_pub_days), median = median(time_between_preprint_and_pub_days), sd = sd(time_between_preprint_and_pub_days))

### 2024-03-16 R/3_final_dat_analysis.R
Adding some script and then if good moving the relevant scrip to supp.qmd

@@ -48,16 +48,34 @@ data2 <- data  %>% left_join(OA_df2, by = c("publisher_doi" = "doi"))
 # We have now cross checked the paper in more detail to see if we missed any published papers. So, we should update the new time between preprint and publication dates, which is a time difference between the preprint and the published paper dates. CRoss checked two times to make sure they were calculated correct. Good!
 
 data2 <- data2  %>% mutate(time_between_preprint_and_pub_days = ymd(publication_date) - ymd(preprint_published_date))
+write.csv(data2, file = here("data", "final_data2.csv"))
 
-
+########-------------------------###
 ### Excluding postprints, how long does it take for a preprint to be published in Ecology and Evolution?
+########-------------------------###
 
 data2  %>% filter(postprint == "preprint")  %>% ggplot(aes(x = time_between_preprint_and_pub_days)) + geom_histogram(binwidth = 30) + labs(title = "Time between preprint and publication in Ecology and Evolution", x = "Days", y = "Frequency") + theme_minimal()
 
-# Why are there weird dates (e.g, Should take at least 3 months to publish a paper, and also, anything below 0 should be a postprint.) Lets assue anything published within 3 months and those with negative dates are postprints.
+# Why are there weird dates (e.g, Should take at least 3 months to publish a paper, and also, anything below 0 should be a postprint.) I suppose it's possible to be published quuite quickly, but a month seems quite weird to me. Lets just take anything below a month out
 
-preprints <- data2  %>% filter(time_between_preprint_and_pub_days >= 90)
-preprints %>% ggplot(aes(x = time_between_preprint_and_pub_days)) + geom_histogram(binwidth = 30) + labs(title = "Time between preprint and publication in Ecology and Evolution", x = "Days", y = "Frequency") + theme_minimal()
+preprints <- data2  %>% filter(time_between_preprint_and_pub_days >= 30)
+preprints %>% ggplot(aes(x = time_between_preprint_and_pub_days)) + geom_histogram(binwidth = 30) + labs(title = "Time between preprint and publication in Ecology and Evolution", x = "Days", y = "Frequency") + theme_classic()
 
 # what is the range
[…]

### 2024-03-16 supp/supp.qmd
Adding relevant code from 3_ to supp.qmd with some context

@@
 ---
-title: "Supplementary Materials for: Empowering the use of preprints in ecology and evolution: an exploration of the first 1000 *EcoEvoRxiv* preprints"
+title: "Supplementary Materials for: Empowering the use of community driven preprints in ecology and evolution"
 bibliography: ../bib/refs.bib
@@
       text: '\usepackage{lineno}\linenumbers'
+  html: 
+    highlight: pygments
+    theme: solarized-light
 editor_options: 
@@
 
+# Check allocation of papers
+		contr_extract <- master_list  %>%  tabyl(extractor_full_name)
+
+	# Check how many each person has done relative to their total
+		contr_extract2 <- master_list %>% group_by(extractor_full_name) %>% summarise(n = n(), yes = sum(completed_yes_no_extractor == "Yes"), no = sum(completed_yes_no_extractor == "No"), prop = yes/n)  %>% data.frame()  %>% arrange(n)
+
 # raw data. For analysis
 	data_coll <- read_sheet("https://docs.google.com/spreadsheets/d/1032gLryvtCNJ7eJjKBjrn7txxDRUGql9SoIG18QnFrQ/edit?resourcekey#gid=1062856014")
+
+# Final Processed data
+  data2 <- read_csv(here("data", "final_data2.csv"))
 
@@
 
+## Preprint submission and publication dates over time
+*EcoEvoRxiv* was established in 2018 and there has been a steady increase in preprints (and postprints) to the journal since that time (@fig-figdates).
+
 ```{r, figdates}
@@
 ```
+
+## Publication time of preprints
+*EcoEvoRxiv* accepts postprints which means that, technically, a 'preprint' can be published before being lodged on the preprint server.
+It is difficult to know exactly what would be a postprint because authors may have had the acceptance and then put the paper online as a preprint while they waited for it to go online in a research journal.
+In many cases, identifying a postprint is straightforward.
+These are papers that have preprint publication dates that are later than the journal publication date.
+However, papers that were 'quick' to be accepted could also be postprints, as mentioned above.
+It seems highly unlikely for a paper to be accepted in a journal and online within a month after being submitted to *EcoEvoRxiv*.
+We therefore assume any preprint that was published within a month of being submitted is also likely a postprint.
+
+```{r, fig-pubtime}
+#| label: fig-pubtime
+#| fig-cap: Time between submission and publication of preprints on *EcoEvoRxiv*. 'Preprints' that were published within a month of being submitted are considered postprints.
+
+preprints <- data2  %>% filter(time_between_preprint_and_pub_days >= 30)
+preprints %>% ggplot(aes(x = time_between_preprint_and_pub_days)) + geom_histogram(binwidth = 30) + labs(x = "Days", y = "Frequency") + theme_classic()
+
+# Summary of the data
+# what is the range
+sum_preprints <- preprints  %>% summarise(min = min(time_between_preprint_and_pub_days), max = max(time_between_preprint_and_pub_days), mean = mean(time_between_preprint_and_pub_days), median = median(time_between_preprint_and_pub_days), sd = sd(time_between_preprint_and_pub_days))
+```
+
+Overall, the maximum time between submission and publication was `r sum_preprints$max` days (@fig-pubtime).
+The median time to publication was `r sum_preprints$median` days (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days).
+
+## Preprint open access status when published
+
+```{r, oa}
+
+# Summary of the data
+sum_is_oa <- tabyl(preprints$is_oa)
+sum_oa_status <- tabyl(preprints$oa_status)
+```
+
+Preprints can be a useful way to ensure that research remains open and accessible to the research community as the paper is available online no matter what the published status of the preprint ends up being.
+Most of the published preprints ended up being open access(@fig-openaccess A), however, the status of many (i.e., `r sum_is_oa$n[3]` or `r sum_is_oa$percent[3]*100`%) were unknown, and `r sum_is_oa$n[1]` or `r sum_is_oa$percent[1]*100`% were not published in open access reserach journals.
+The open access status of the papers that were published in open access journals also varied widely (@fig-openaccess B).
+
+```{r, fig-openaccess}
+#| label: fig-openaccess
+#| fig-cap: Open access status of preprints when published.
+A) The number of papers pusblihed in open access journals compared to those not.
+Note that many journals could not be identified as open access (i.e, NA).
+B) The classification of open access status of the published preprints.
+
+########-------------------------###
+### What is the OA status of the published preprints?
+########-------------------------###
+
+# Lets first look only at the preprints. Then, we can look at the postprints. It's possible folks are putting up postprints because they are not OA journals and they want to share their work freely.
+
+p1 <- preprints  %>% ggplot(aes(x = is_oa)) + geom_bar() + labs(x = "Open Access", y = "Frequency") + theme_classic()
+
+p2 <- preprints  %>% ggplot(aes(x = oa_status)) + geom_bar() + labs(x = "Open Access Status", y = "Frequency") + theme_classic()
+
+(p1 + p2) + plot_annotation(tag_levels = 'A', tag_suffix=")")
+```

### 2024-03-16 supp/supp.qmd
Country breakdown

@@
 #install.packages("pacman")
-pacman::p_load(tidyverse, here, patchwork, readxl, googlesheets4, janitor)
+pacman::p_load(tidyverse, here, patchwork, readxl, googlesheets4, janitor, maps, forcats,RColorBrewer)
 
@@
 ```
+
+## What countries use preprints the most?
+
+Unsurprisingly, countries in North America and Europe use preprints more exstensively compared to other countries with countries in Africa, Central America and parts of Asia still slow to use *EcoEvoRxiv* for their preprints (@fig-countries).
+
+```{r, countries}
+#| label: fig-countries
+#| fig-cap: Percentage of preprints on *EcoEvoRxiv* across countries.
+
+# Create a global map with countried highlighted and shaded according to the frequency of preprints from that country
+# First, we need to get the country names and the number of preprints from each country
+  countries <- preprints  %>% tabyl(submitting_author_country)  %>% rename("country" = submitting_author_country, "n" = n)  %>% mutate(country = ifelse(country == "NA", "Unknown", country))  %>% arrange(desc(n))  %>% mutate(country=str_to_title(country))
+
+# Now we can plot the map, but before we do we need to make sure the names in the countries file match those in the region of the world map
+  world_map <- map_data(map = "world")
+
+# List unique countries
+  maps_country_name <- unique(world_map$region) # Names of regions in maps
+  countries[!countries$country %in% maps_country_name,] # Names of countries in our data that are not in the maps data, we need to fix these in countries
+
+# Fix names in countries
+replace = c("United States Of America" = "USA",  "United Kingdom" = "UK",  "Czechia" = "Czech Republic") 
+countries <- countries  %>% mutate(country = str_replace_all(country, replace))
+
+ggplot(countries) +
+  geom_map(aes(map_id = country, fill = valid_percent), map = world_map) +
+  geom_polygon(data = world_map, aes(x = long, y = lat, group = group), colour = 'black', fill = NA) +
+  expand_limits(x = world_map$long, y = world_map$lat) +
+  theme_void() +
+  coord_fixed() + labs(fill="%")
+
+  p1 <- countries  %>% ggplot(aes(map_id = country)) + geom_map(aes(fill = percent), map = map_data("world"), color = "black") + expand_limits(x = map_data("world")$long, y = map_data("world")$lat) + labs(fill = "Number of preprints", title = "Number of preprints by country") + theme_void() + theme(legend.position = "bottom")
+
+```

### 2024-03-16 supp/supp.qmd
Adding table for countries and a bit of writing

@@
 #install.packages("pacman")
-pacman::p_load(tidyverse, here, patchwork, readxl, googlesheets4, janitor, maps, forcats,RColorBrewer)
+pacman::p_load(tidyverse, here, patchwork, readxl, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable)
 
@@
 
-Unsurprisingly, countries in North America and Europe use preprints more exstensively compared to other countries with countries in Africa, Central America and parts of Asia still slow to use *EcoEvoRxiv* for their preprints (@fig-countries).
-
 ```{r, countries}
@@
   maps_country_name <- unique(world_map$region) # Names of regions in maps
-  countries[!countries$country %in% maps_country_name,] # Names of countries in our data that are not in the maps data, we need to fix these in countries
+  #countries[!countries$country %in% maps_country_name,] # Names of countries in our data that are not in the maps data, we need to fix these in countries
 
@@
 
+# Find the countries with 90% of the preprints
+
+most_use <- countries[cumsum(countries$valid_percent) <= 0.90, ]
+
 ```
+
+A total of `r length(unique(countries$country))-1` countries have used *EcoEvoRxiv* as a preprint server.
+Unsurprisingly, countries in North America and Europe use preprints more exstensively.
+Countries in Africa, Central America and parts of Asia are still slow to use *EcoEvoRxiv* for their preprints (@fig-countries).
+Overall, 90% of the preprints come from `r nrow(most_use)-1` countries (@tbl-countries).
+
+```{r}
+#| label: tbl-countries
+#| tbl-cap: Countries with 90% of the preprints on EcoEvoRxiv.
+
+tbl_most <- most_use %>% filter(!is.na(valid_percent)) %>% mutate(Percentage = valid_percent*100) %>% select(country, Percentage)  %>% rename("Country" = country)
+
+flextable(tbl_most) %>% bold(part = "header") %>% autofit()
+```

### 2024-03-16 supp/supp.qmd
chaneg layout of map

@@
 #install.packages("pacman")
-pacman::p_load(tidyverse, here, patchwork, readxl, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable)
+pacman::p_load(tidyverse, here, patchwork, readxl, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggimage, gt, performance, ggthemes, mapproj)
 
@@
 # Now we can plot the map, but before we do we need to make sure the names in the countries file match those in the region of the world map
-  world_map <- map_data(map = "world")
+  world_map <- map_data(map = "world") %>% 
+  filter(! long > 180)
 
@@
   expand_limits(x = world_map$long, y = world_map$lat) +
-  theme_void() +
-  coord_fixed() + labs(fill="%")
+  theme_void() + expand_limits(x = world_map$long, y = world_map$lat) +
+  coord_fixed() + labs(fill="%") + theme_map(base_size = 22) + coord_map("moll")
 

### 2024-03-16 supp/supp.qmd
change to html as it's cleaner looking and better res figs

@@
 format:
+  html:
+    highlight: pygments
+    theme: solarized-light
   docx:
@@
       text: '\usepackage{lineno}\linenumbers'
-  html:
-    highlight: pygments
-    theme: solarized-light
 editor_options: 

### 2024-03-17 supp/supp.qmd
formatting change to html

@@
   html:
-    highlight: pygments
-    theme: solarized-light
+    toc: true
+    toc-location: left
+    toc-depth: 3
+    toc-title: "**Table of Contents**"
+    theme: simplex
+    embed-resources: true
+    code-fold: show
+    code-tools: true
+    number-sections: true
+    fontsize: "12"
+    max-width: "10"
+    code-overflow: wrap
   docx:
@@
 *EcoEvoRxiv* accepts postprints which means that, technically, a 'preprint' can be published before being lodged on the preprint server.
-It is difficult to know exactly what would be a postprint because authors may have had the acceptance and then put the paper online as a preprint while they waited for it to go online in a research journal.
+Identifying postprints can be challenging because meta-data does not exist to tag such preprints on *EcoEvoRxiv*.
+In addition, authors may have lodged a postprint while waiting for an accepted article to be published online for a given research journal.
+
 In many cases, identifying a postprint is straightforward.
@@
 It seems highly unlikely for a paper to be accepted in a journal and online within a month after being submitted to *EcoEvoRxiv*.
-We therefore assume any preprint that was published within a month of being submitted is also likely a postprint.
+We therefore assume that any preprint that was published within a month of being submitted is likely a postprint.
 
@@
 ggplot(countries) +
-  geom_map(aes(map_id = country, fill = valid_percent), map = world_map) +
+  geom_map(aes(map_id = country, fill = valid_percent*100), map = world_map) +
   geom_polygon(data = world_map, aes(x = long, y = lat, group = group), colour = 'black', fill = NA) +

### 2024-03-18 supp/supp.qmd
Adding more to supp on unpublised preprints

@@
 
+# How many remain unpublished?
+unpub <- data2  %>% filter(is.na(publication_doi))  %>% nrow()
+
+# How many days between submission and publication
 preprints <- data2  %>% filter(time_between_preprint_and_pub_days >= 30)
@@
 
-Overall, the maximum time between submission and publication was `r sum_preprints$max` days (@fig-pubtime).
+Overall, `r unpub` papers were unpublished out of the `r nrow(data2)` (`r (unpub / nrow(data2))*100`%).
+The maximum time between submission and publication was `r sum_preprints$max` days (@fig-pubtime).
 The median time to publication was `r sum_preprints$median` days (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days).

### 2024-03-21 supp/supp.qmd
supp

@@
 Countries in Africa, Central America and parts of Asia are still slow to use *EcoEvoRxiv* for their preprints (@fig-countries).
-Overall, 90% of the preprints come from `r nrow(most_use)-1` countries (@tbl-countries).
+Overall, 90% of the preprints come from just `r nrow(most_use)-1` countries (@tbl-countries).
 
@@
 ```
+
+## Taxa studied in preprints
+
+```{r, taxa}
+cols <- c("plants", "algi", "fungi", "microorganisms", "invertebrates", "vertebrates")
+
+# Summary of the data
+sum_taxa <- data2  %>% select(all_of(cols))  %>% apply(., 2, sum, na.rm = TRUE)  %>% data.frame()   %>% rownames_to_column(var = "taxa")  %>% rename("n" = ".")
+
+blank_theme <- theme_minimal()+
+  theme(
+  axis.title.x = element_blank(),
+  axis.title.y = element_blank(),
+  panel.border = element_blank(),
+  panel.grid=element_blank(),
+  axis.ticks = element_blank(),
+  plot.title=element_text(size=14, face="bold")
+  )
+
+# Use data to create a pir chart and clean up colour palette
+
+pie <- sum_taxa  %>% ggplot(aes(x = "", y = n, fill = taxa)) + geom_bar(stat = "identity") + coord_polar("y", start=0) + blank_theme + labs(title = "Taxa studied in preprints") + theme(legend.position = "bottom")
+
+```

### 2024-03-22 supp/supp.qmd
Just updating README with where we are at and adding analysis for questions in supp

--- 2024-03-18 supp/supp.qmd
@@
 #install.packages("pacman")
-pacman::p_load(tidyverse, here, patchwork, readxl, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggimage, gt, performance, ggthemes, mapproj)
+pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, ggthemes, mapproj)
 
@@
 
-tbl_most <- most_use %>% filter(!is.na(valid_percent)) %>% mutate(Percentage = valid_percent*100) %>% select(country, Percentage)  %>% rename("Country" = country)
+tbl_most <- most_use %>% filter(!is.na(valid_percent)) %>% mutate(Percentage = valid_percent*100) %>% dplyr::select(country, Percentage)  %>% rename("Country" = country)
 
@@
 ```
+
+## Taxa studied in preprints
+
+```{r, fig-taxa}
+#| label: fig-taxa
+#| fig-cap: Taxa studied in preprints on *EcoEvoRxiv*.
+#| 
+cols <- c("plants", "algi", "fungi", "microorganisms", "invertebrates", "vertebrates")
+
+# Summary of the data
+sum_taxa <- data2  %>% dplyr::select(all_of(cols))  %>% apply(., 2, sum, na.rm = TRUE)  %>% data.frame()   %>% rownames_to_column(var = "taxa")  %>% rename("n" = ".")  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))
+
+# Use data to create a pir chart and clean up colour palette
+
+pie <- ggplot(sum_taxa, aes(x = "", y = perc, fill = taxa)) +
+  geom_col(color = "black") +
+  geom_label_repel(aes(label = labels),
+            position = position_stack(vjust = 0.6),
+           show.legend = FALSE) +
+  scale_fill_viridis_d() +
+  coord_polar(theta = "y") + 
+  theme_void() + labs(fill = "Taxa")
+pie
+```
+
+Preprints were published on all major taxomic groups, with the most common being plants (`r sum_taxa$perc[1]`%), vertebrates (`r sum_taxa$perc[6]`%), and invertebrates (`r sum_taxa$perc[5]`%) (@fig-taxa).
+
+## Preprint types
+
+```{r, fig-types}
+#| label: fig-types
+#| fig-cap: Types of papers posted on *EcoEvoRxiv*.
+
+# Summary of the data
+sum_types <- data2  %>% tabyl(type_of_preprint)  %>% rename("type" = type_of_preprint, "n" = n)  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))
+
+pie <- ggplot(sum_types, aes(x = "", y = perc, fill = type)) +
+  geom_col(color = "black") +
+  geom_label_repel(aes(label = labels),
+            position = position_stack(vjust = 0.6),
+           show.legend = FALSE) +
+  scale_fill_viridis_d() +
+  coord_polar(theta = "y") + 
+  theme_void() + labs(fill = "Article Type")
+pie
+```
+
+Preprints on *EcoEvoRxiv* were diverse in nature, with research articles (`r sum_types[sum_types$type == "research article",]$perc`%) being the most common, followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) (@fig-types).
+
+## How does career stage and gender impact preprint use?
+
+```{r, fig-career}
+#| label: fig-career
+#| fig-cap: Year of first publication for submitting authors of preprints on *EcoEvoRxiv*.
+
+ggplot(data2, aes(x = submitting_author_first_publication_year)) +
+  geom_histogram(binwidth = 1, fill = "grey", color = "black") +
+  labs(x = "Year of submitting authors first publication", y = "Number of preprints") +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+count_dat  <- data2  %>% group_by(submitting_author_first_publication_year)  %>% summarise(n = n())
+
+model <- glm.nb(n ~ submitting_author_first_publication_year, data = count_dat)
+res <- summary(model)$coefficients
+```
+
+We were interested in getting an understanding of whether career stage is related to preprint use.
+We used the first publication year of the submitting author as a proxy for career stage.
+We predicted that early career researchers would be more open to using preprints in Ecology and Evolution.
+
+Interestingly, there was strong evidence that the number of preprints posted decreases with later career stages (negative binomial glm: year slope = `r res[2, "Estimate"]`, SE: `r res[2, "Std.
+Error"]`, *p* < 0.001, N = `r nrow(count_dat[complete.cases(count_dat),])`).
+The majority of preprints were submitted by authors who published their first paper in the last 10 years (@fig-career), with the median year of first publication of submitting authors being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r round(mean(data2$submitting_author_first_publication_year, na.rm = TRUE),0)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`).

### 2024-03-22 supp/supp.qmd
genderize

@@
 #install.packages("pacman")
-pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, ggthemes, mapproj)
+pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, ggthemes, mapproj, DemografixeR)
 
@@
 The majority of preprints were submitted by authors who published their first paper in the last 10 years (@fig-career), with the median year of first publication of submitting authors being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r round(mean(data2$submitting_author_first_publication_year, na.rm = TRUE),0)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`).
+
+We cannot know gender of authors for certainty but we can use a data driven approach to suggest the probability a particular name is of a given gender (male or female).
+
+```{r}
+
+# First need to get the authors first name
+data2 <- data2 %>% mutate(submitting_author_firstname = str_split(submitting_author, " ") %>% map_chr(1))
+# Now we can use the first name and the country (that's important) to get an idea of the persons gender. 
+genders <- genderize(data2$submitting_author_firstname, country_id = data2$submitting_author_country, simplify = FALSE)
+
+```

### 2024-03-22 supp/supp.qmd
genderize and also countrycodes

--- 2024-03-22 supp/supp.qmd
@@
 #install.packages("pacman")
-pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, ggthemes, mapproj)
+pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, ggthemes, mapproj, DemografixeR, countrycode)
 
@@
 The majority of preprints were submitted by authors who published their first paper in the last 10 years (@fig-career), with the median year of first publication of submitting authors being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r round(mean(data2$submitting_author_first_publication_year, na.rm = TRUE),0)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`).
+
+Understanding gender publishing patterns is challenging.
+We cannot know the gender of authors for certainty but we can use a data driven approach to suggest the probability that a particular name is of a given gender (male or female).
+We used the R package *DemografixeR* (vers.
+`r utils::packageVersion("DemografixeR")`; @RJ-2016-002) to predict the most likely gender of the submitting author of a preprint.
+We incorperated information about the submitting authors country of affiliation to better account for differences across countries in naming .
+
+```{r, fig-gender}
+#| label: fig-gender
+#| fig-cap: Number of preprints published by male and female submitting authors. 
+#| 
+# First need to get the authors first name
+data2 <- data2 %>% mutate(submitting_author_firstname = str_split(submitting_author, " ") %>% map_chr(1))
+
+# In order to localise by country we need to get the country code
+data2 <- data2 %>% mutate(submitting_author_country_code = countrycode(data2$submitting_author_country, origin = "country.name", destination = "iso2c"))
+
+# Lets have a quick look at whether these are 'correct'
+data2 %>% dplyr::select(submitting_author_country_code, submitting_author_country)  %>% distinct()
+
+# This looks good, but lets see which two are NA. These are in fact NA, even though they shouldn't really be as affliations are not listed on preprint. Even the published paper isn't clear. 
+data2 %>% filter(is.na(submitting_author_country_code))  %>% data.frame()
+
+# Now we can use the first name and the country (that's important) to get an idea of the persons gender. 
+genders <- genderize(data2$submitting_author_firstname, country_id = data2$submitting_author_country_code, simplify = FALSE)
+
+```
+
+## References

### 2024-03-23 supp/supp.qmd
Adding citation results

@@
 #install.packages("pacman")
-pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, ggthemes, mapproj, DemografixeR, countrycode)
+pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, ggthemes, mapproj, DemografixeR, countrycode, see)
 
@@
 genders <- genderize(data2$submitting_author_firstname, country_id = data2$submitting_author_country_code, simplify = FALSE)
+write.csv(genders, here("data", "gender_dat.csv"))
 
@@
 
+## Preprint citations versus published article citations
+
+```{r, fig-citations}
+
+# First, we need to extract the published articles
+pubs <- data2  %>% filter(!is.na(time_between_preprint_and_pub_days))
+
+# We will need to re-oragnise the dataframe in long format for analysis.
+data_long_cites <- pubs  %>% dplyr::select(preprint_id, preprint_doi, publication_date, time_between_preprint_and_pub_days, number_of_citations_preprint, number_of_citations_article)  %>% pivot_longer(cols = c(number_of_citations_preprint, number_of_citations_article), names_to = "type", values_to = "citations")  %>% mutate(type = ifelse(type == "number_of_citations_preprint", "Preprint", "Published Article"))
+
+# Now we can plot the data
+ggplot(data_long_cites, aes(x = type, y = sqrt(citations))) +
+  geom_violinhalf(aes(fill = type), flip = 1) + geom_jitter(shape=16, position=position_jitter(0.01), alpha = 0.2) + geom_line(aes(group = preprint_id), alpha = 0.2, colour = "black") +
+  labs(x = "Paper Status", y = "Number of citations (sqrt transformed)") +
+  theme_bw() + theme(legend.position = "none")
+```
+
 ## References

### 2024-03-23 supp/supp.qmd
citatioons

@@
 #install.packages("pacman")
-pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, ggthemes, mapproj, DemografixeR, countrycode, see)
+pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot)
 
@@
 #| fig-cap: Number of preprints published by male and female submitting authors.
-#| 
+
 # First need to get the authors first name
@@
 
-# First, we need to extract the published articles
-pubs <- data2  %>% filter(!is.na(time_between_preprint_and_pub_days))
+# First, we need to extract the published articles, but we probably also need to remove postprints
+  pubs <- data2  %>% filter(!is.na(time_between_preprint_and_pub_days) & !time_between_preprint_and_pub_days <30)
 
@@
 # Now we can plot the data
-ggplot(data_long_cites, aes(x = type, y = sqrt(citations))) +
+  cites <- ggplot(data_long_cites, aes(x = type, y = sqrt(citations))) +
   geom_violinhalf(aes(fill = type), flip = 1) + geom_jitter(shape=16, position=position_jitter(0.01), alpha = 0.2) + geom_line(aes(group = preprint_id), alpha = 0.2, colour = "black") +
@@
   theme_bw() + theme(legend.position = "none")
+  cites
+
+  hist <- ggplot(data_long_cites, aes(x = sqrt(citations), group = type, fill = type)) + geom_histogram() + theme_bw() + labs(x = "Number of citations (sqrt transformed)", y = "Frequency") + labs(fill = "Paper Status") + theme(legend.position = "inside")
+
+  plot.with.inset <-
+    ggdraw() +
+    draw_plot(cites) +
+    draw_plot(hist, x = 0.07, y = .55, width = .45, height = .4)
+  plot.with.inset
+
+  # Have a look at relationship between preprint citations and publication citations
+  complete_pub_data <- pubs  %>% filter(!is.na(number_of_citations_preprint))  %>% filter(!is.na(number_of_citations_article))
+  spear <- cor.test(complete_pub_data$number_of_citations_preprint, complete_pub_data$number_of_citations_article, method = "spearman")
+
+# Model with ZI NBinom.
+NOt really sure this is worth properly analysing because we can't really discern much.
+Yes, they are cited more, but that's not surprising.
+We really want to know if those that peprinted are more likely to be cited.
+We could try comparing to 'postprints' papers that were posted after being published, but this could be a very small biased sample of already high ipact papers or biased towards certain research groups.
+Probably just a descriptive anlaysis is all we really need.
+ # model2 = glmmTMB(citations ~ type + time_between_preprint_and_pub_days + (1 | preprint_id), data = data_long_cites, 
+  #          family = nbinom2, zi = ~ 1)
+  #summary(model2)
+
+# Summary of the citation data. 
+  sum_cites <- data_long_cites  %>% group_by(type)  %>% summarise(mean = mean(citations, na.rm = TRUE), median = median(citations, na.rm = TRUE), sd = sd(citations, na.rm = TRUE), min = min(citations, na.rm = TRUE), max = max(citations, na.rm = TRUE))
+
+# Summary of frequency of papers in citation categories
+
+  sum_cites2 <- data_long_cites  %>% tabyl(type, citations)
+
 ```
 
+Papers that are preprinted have been shown to receive more citations compared to those that are not preprinted in other research fields.
+Testing if this is true in Ecology and Evolution is challenging and not possible using observational data from *EcoEvoRxiv*.
+However, we can compare the number of citations to preprints and the published articles that result from those preprints to give a sense of how many citations preprints are expected to potentially accumulate and whether highly cited preprints go on to also be highly cited published research papers.
+
+The vast majority of preprints were not cited before they became published (@fig-citations), with a total of `r sum_cites2[1,2]` papers receiving zero citations.
+The median number of citations to preprints were `r sum_cites[1,"median"]` (mean = `r round(sum_cites[1,"mean"], 1)`; SD = `r round(sum_cites[1,"sd"], 1)`), while the median number of citations to published articles was `r sum_cites[2,"median"]` (mean = `r round(sum_cites[2,"mean"], 1)`; SD = `r round(sum_cites[2,"sd"], 1)`).
+
+Notably, published articles with zero citations dropped dramatically (`r sum_cites2[2,2]` papers; a `r 1 - (sum_cites2[2,2]/ sum_cites2[1,2])*100`% reduction) compared to preprints with zero citations, suggesting that once published, only `r sum_cites2[2,2]/ sum_cites2[1,2]*100`% had no citations.
+
+Interestingly, highly a cited preprint did not necessarily become a highly cited published article over time, although some of this descrepency is related to whether and how preprints and articles are merged (Spearman Rank Correlation: `r spear$estimate`, S = `r spear$statistic`, *p* = `r spear$p.value`; @fig-citations).
+
+```{r}
+
 ## References

### 2024-03-23 supp/supp.qmd
Some changes to supp for rendering

@@
   theme_void() + expand_limits(x = world_map$long, y = world_map$lat) +
-  coord_fixed() + labs(fill="%") + theme_map(base_size = 22) + coord_map("moll")
+  coord_fixed() + labs(fill="%") +  coord_map("moll")
 
@@
 #| fig-cap: Number of preprints published by male and female submitting authors. 
+#| echo: false
+#| include: false
 
@@
 # Now we can use the first name and the country (that's important) to get an idea of the persons gender. 
-  genders <- genderize(data2$submitting_author_firstname, country_id = data2$submitting_author_country_code, simplify = FALSE)
-  write.csv(genders, here("data", "gender_dat.csv"))
+  #genders <- genderize(data2$submitting_author_firstname, country_id = data2$submitting_author_country_code, simplify = FALSE)
+ # write.csv(genders, here("data", "gender_dat.csv"))
 
@@
 ```{r, fig-citations} 
+#| label: fig-citations
+#| fig-cap: Number of citations to preprints and published articles that result from those preprints.
 
@@
   theme_bw() + theme(legend.position = "none")
-  cites
 
@@
   sum_cites2 <- data_long_cites  %>% tabyl(type, citations)
-
 ```
@@
 
-Notably, published articles with zero citations dropped dramatically (`r sum_cites2[2,2]` papers; a `r 1 - (sum_cites2[2,2]/ sum_cites2[1,2])*100`% reduction) compared to preprints with zero citations, suggesting that once published, only `r sum_cites2[2,2]/ sum_cites2[1,2]*100`% had no citations.
+Notably, published articles with zero citations dropped dramatically (`r sum_cites2[2,2]` papers; a `r (1 - (sum_cites2[2,2]/ sum_cites2[1,2]))*100`% reduction) compared to preprints with zero citations, suggesting that once published, only `r sum_cites2[2,2]/ sum_cites2[1,2]*100`% had no citations.
 
-Interestingly, highly a cited preprint did not necessarily become a highly cited published article over time, although some of this descrepency is related to whether and how preprints and articles are merged (Spearman Rank Correlation: `r spear$estimate`, S = `r spear$statistic`, *p* = `r spear$p.value`; @fig-citations).
+Interestingly, a highly cited preprint did not necessarily become a highly cited published article over time, although some of this descrepency is related to whether and how preprints and articles are linked through crossref (Spearman Rank Correlation: `r spear$estimate`, S = `r spear$statistic`, *p* = `r spear$p.value`; @fig-citations).
 
-```{r}
-
-## References
+# References

### 2024-03-24 supp/supp.qmd
Adding last few analyses

@@
 
+## Data and code sharing in preprints
+
+```{r, fig-data}
+#| label: fig-data
+#| fig-cap: Percentage of preprints on *EcoEvoRxiv* that have data and code available.
+
+# Summary of the data
+  preprint_data <- data2  %>% tabyl(data_link_preprint_cleaned) 
+  preprint_code <- data2  %>% tabyl(code_link_preprint_cleaned) 
+  article_data <- data2  %>% tabyl(data_link_article_cleaned) 
+  article_code <- data2  %>% tabyl(code_link_article_cleaned)
+
+# Check if it was shared not in preprint but then in article
+  pre_article_data <- data2   %>%  filter(!data_link_preprint_cleaned == "not applicable") %>% mutate(data_shared = ifelse(data_link_preprint_cleaned == "no" & data_link_article_cleaned == "yes", "yes", ifelse(code_link_preprint_cleaned == "yes" & code_link_article_cleaned == "yes", "always", "no")))  %>% tabyl(data_shared)
+  pre_article_code <- data2  %>%  filter(!data_link_preprint_cleaned == "not applicable") %>% mutate(code_shared = ifelse(code_link_preprint_cleaned == "no" & code_link_article_cleaned == "yes", "yes", ifelse(code_link_preprint_cleaned == "yes" & code_link_article_cleaned == "yes", "always", "no")))  %>% tabyl(code_shared)
+
+```
+
+Data and code sharing is a key component of open science.
+Despite this, we found that `r preprint_data[1,2]` (`r preprint_data[1,"percent"]*100`%) of relevant preprints on *EcoEvoRxiv* (i.e., only where data was generated) did not share data, while `r preprint_code[1,2]` (`r preprint_code[1,"percent"]*100`%) did not share code.
+
+Authors may be reluctant to share data in code for preprints because of the perceived concern that others may acquire and use such data and code without authors' consent.
+However, while we found that `r pre_article_data[3,2]` (`r pre_article_data[3,"percent"]*100`%) of preprints that did not share data at the preprint stage did in the published article, there were still `r pre_article_data[2,2]` (`r pre_article_data[2,"percent"]*100`%) that never ended up sharing data.
+The same was true for code.
+Overall, while `r pre_article_code[3,2]` (`r pre_article_code[3,"percent"]*100`%) of preprints that did not share code at the preprint stage did in the published article, there were still `r pre_article_code[2,2]` (`r pre_article_code[2,"percent"]*100`%) that never ended up sharing code.
+
+## Peer Community In recommendations
+
+```{r, fig-pci}
+#| label: fig-pci
+#| fig-cap: Number of preprints on *EcoEvoRxiv* that have been recommended by Peer Community In.
+
+# How many articles were PCI recomended
+  pci <- data2  %>% tabyl(pci_recommendation_preprint)  
+```
+
+Out of the `r nrow(data2)` preprints, only `r pci[2,2]` (`r pci[2,3]*100`%) used Peer Community In as a preprint peer-review service.
+
+## Title changes between preprint and published article
+
+```{r, fig-title} 
+titles <- data2 %>%  filter(!is.na(publication_doi)) %>% tabyl(publication_title_changed)
+```
+
+It was reasonably common for titles of preprints to change between the preprint and the published article (`r titles[2,2]` or `r titles[2,3]*100`%).
+This was a major contributer to preprints and published articles not being matched in Google Scholar as they were not picked up by crossref linking services.
+As such, we would recomend that authors make sure that, when preprints end up getting pusblished, that they update preprints with the publication DOI when it's available.
+This is quite easy for authors to do in *EcoEvoRxiv* and it will ensure that the preprint is linked to the published article and the citations are merged and the published paper is ultimately open access, allowing authors to save open access fees.
+
 # References

### 2024-03-28 supp/supp.qmd
Update to prevent messages
Added Losia's code in for gender analysis

@@
 #| label: setup
+#| echo: false
+#| include: false
 
@@
 
+ ##### ADDED BY ML"  
+install.packages("gender")
+install.packages("genderdata")
+library(gender)
+
+## testing - delete thi later
+#gender(c("Madison", "Hillary"), years = 2000, method = "ssa")
+#gender(c("Madison", "Hillary"), method = "genderize") #works ok until limit of 100 is reached
+#gender(data3$submitting_author_firstname, method = "genderize") #works ok until limit of 100 is reached
+
+# data3 <-  data2[1:100, ] #subset for testing
+# gender(data3$submitting_author_firstname) -> data3_genders
+# dim(data3_genders) #83 names assigned
+## EDN testing
+
+# Get gender using all unique first names from the data set
+data_genders <- data.frame(gender(unique(data2$submitting_author_firstname)))
+dim(data_genders) #514 assigned
+#names(data_genders)
+
+# Merge with main data frame
+#unique(data_genders$name)
+data_genders <- rename(data_genders, submitting_author_firstname = name)
+data3 <- left_join(data2, data_genders, by = c("submitting_author_firstname"))
+#names(data3)
+table(is.na(data3$proportion_male)) #157 missing
+
+# Plot probabilities of gender assignment
+ggplot(data3, aes(x = `proportion_male`)) +
+  geom_histogram(fill = "grey", color = "black") +
+  labs(x = "gender assignment probability (male)", y = "Number of preprints") +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+table(data3$proportion_male > 0.05 & data3$proportion_male < 0.95) #84 names bit unsure
+
+# Pull out records missing names
+#data3[is.na(data3$proportion_male), c("submitting_author", "submitting_author_country") ] #157 missing
+#data3[is.na(data3$proportion_male) == FALSE & data3$proportion_male > 0.05 & data3$proportion_male < 0.95, c("submitting_author", "submitting_author_country") ] # 84 missing a bit unsure
+
+#transliterate the non-ASCII characters using stringi package, e.g.: #stri_trans_general("Zażółć gęślą jaźń", "Latin-ASCII")
+data3$submitting_author_ASCII <- stringi::stri_trans_general(data3$submitting_author, "Latin-ASCII")
+
+data3 %>% 
+  filter(is.na(data3$proportion_male) == TRUE | (proportion_male > 0.05 & proportion_male < 0.95)) %>% dplyr::select(submitting_author_ASCII, submitting_author, submitting_author_country, preprint_title, gender) %>%
+  write.csv(file = here("data", "final_data3_fillin.csv")) #used to manually check and fill in gender data - then saved as final_data3_fillin_ML.csv
+
+# Load updated data	subset
+data3_update <- read_csv(here("data", "final_data3_fillin_ML.csv"))
+dim(data3_update)
+names(data3_update)
+
+data4 <- left_join(data3, data3_update, by = c("submitting_author_ASCII", "submitting_author", "submitting_author_country", "preprint_title"))
+#table(data4$gender.x, useNA = "always")
+#table(data4$gender.y, useNA = "always")
+data4$gender.x[is.na(data4$gender.x)] <- data4$gender.y[is.na(data4$gender.x)] #replace with correct values
+data4 <- rename(data4, gender = gender.x)
+table(data4$gender, useNA = "always") #more males than females, two NA ue to missing first name / collective authorship
+
 ```

### 2024-03-29 supp/supp.qmd
Adding some writing on gender section

@@
 
+Gender differences in preprint use have been established in a number of other research fields.
+It is hypothsised that such differences are driven by the larger childcare burden of female researchers, which limit their abilities to publish as frequently as their male counterparts [@ucar2022mind; @wehner2020comparison].
+Recent work has shown that COVID-19 exacerbated gender disparities in preprint publishing given the increased childcare burden during the pandemic [@wehner2020comparison].
 Understanding gender publishing patterns is challenging.
@@
 `r utils::packageVersion("DemografixeR")`; @RJ-2016-002) to predict the most likely gender of the submitting author of a preprint.
-We incorperated information about the submitting authors country of affiliation to better account for differences across countries in naming .
+We incorperated information about the submitting authors country of affiliation to better account for differences across countries in naming.
 

### 2024-03-29 supp/supp.qmd
Writs update

@@
 It is hypothsised that such differences are driven by the larger childcare burden of female researchers, which limit their abilities to publish as frequently as their male counterparts [@ucar2022mind; @wehner2020comparison].
-Recent work has shown that COVID-19 exacerbated gender disparities in preprint publishing given the increased childcare burden during the pandemic [@wehner2020comparison].
+Recent work has shown that COVID-19 exacerbated gender disparities in preprint publishing given the increased childcare burden during the pandemic associated with lockdowns and home schooling [@wehner2020comparison].
+
 Understanding gender publishing patterns is challenging.

### 2024-03-29 supp/supp.qmd
Move stuff around and add some supp updates

@@
 #install.packages("pacman")
-pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot)
+pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, genderdata, gender, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot)
 
@@
  ##### ADDED BY ML"  
-install.packages("gender")
-install.packages("genderdata")
-library(gender)
-
-## testing - delete thi later
+## testing - delhi later
 #gender(c("Madison", "Hillary"), years = 2000, method = "ssa")
@@
 
-data3 %>% 
-  filter(is.na(data3$proportion_male) == TRUE | (proportion_male > 0.05 & proportion_male < 0.95)) %>% dplyr::select(submitting_author_ASCII, submitting_author, submitting_author_country, preprint_title, gender) %>%
-  write.csv(file = here("data", "final_data3_fillin.csv")) #used to manually check and fill in gender data - then saved as final_data3_fillin_ML.csv
+#data3 %>% 
+  #filter(is.na(data3$proportion_male) == TRUE | (proportion_male > 0.05 & proportion_male < 0.95)) %>% dplyr::select(submitting_author_ASCII, submitting_author, submitting_author_country, preprint_title, gender) %>%
+ # write.csv(file = here("data", "final_data3_fillin.csv")) #used to manually check and fill in gender data - then saved as final_data3_fillin_ML.csv
 

### 2024-04-01 supp/supp.qmd
Adding gender plot and quick summary

@@
 
-Gender differences in preprint use have been established in a number of other research fields.
-It is hypothsised that such differences are driven by the larger childcare burden of female researchers, which limit their abilities to publish as frequently as their male counterparts [@ucar2022mind; @wehner2020comparison].
-Recent work has shown that COVID-19 exacerbated gender disparities in preprint publishing given the increased childcare burden during the pandemic associated with lockdowns and home schooling [@wehner2020comparison].
-
-Understanding gender publishing patterns is challenging.
-We cannot know the gender of authors for certainty but we can use a data driven approach to suggest the probability that a particular name is of a given gender (male or female).
-We used the R package *DemografixeR* (vers.
-`r utils::packageVersion("DemografixeR")`; @RJ-2016-002) to predict the most likely gender of the submitting author of a preprint.
-We incorperated information about the submitting authors country of affiliation to better account for differences across countries in naming.
-
 ```{r, fig-gender}
@@
 #unique(data_genders$name)
-data_genders <- rename(data_genders, submitting_author_firstname = name)
+#data_genders <- rename(data_genders, submitting_author_firstname = name)
 data3 <- left_join(data2, data_genders, by = c("submitting_author_firstname"))
@@
 
+# Plot the data
+data4 %>% filter(!is.na(gender))  %>% ggplot2::ggplot(aes(x = gender)) + geom_bar()
+
 ```
+
+Gender differences in preprint use have been established in a number of other research fields.
+It is hypothsised that such differences are driven by the larger childcare burden of female researchers, which limit their abilities to publish as frequently as their male counterparts [@ucar2022mind; @wehner2020comparison].
+Recent work has shown that COVID-19 exacerbated gender disparities in preprint publishing given the increased childcare burden during the pandemic associated with lockdowns and home schooling [@wehner2020comparison].
+
+Understanding gender publishing patterns is challenging.
+We cannot know the gender of authors for certainty but we can use a data driven approach to suggest the probability that a particular name is of a given gender (male or female).
+We used the R package *DemografixeR* (vers.
+`r utils::packageVersion("DemografixeR")`; @RJ-2016-002) to predict the most likely gender of the submitting author of a preprint.
+We incorperated information about the submitting authors country of affiliation to better account for differences across countries in naming.
+
+Overall, females were less likely to publish preprints on *EcoEvoRxiv* compared to males (females: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`% compared to males: `r (table(data4$gender)[2] / sum(table(data4$gender))*100)`%), which is likely a reflection of the broader publishing disparities between male and feamle scientists.
 

### 2024-04-03 ms/ms.qmd
Starting to integrate supp results

@@
 #install.packages("pacman")
-pacman::p_load(tidyverse, here, patchwork, readxl)
+pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, genderdata, gender, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot)
 
@@
 
+# Delegate details
+  delegates <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Delegate Details")
+
+  del_details <- delegates  %>% rename("attend" = "Attended hackathon (yes/no)") %>%
+			mutate(attend = str_to_title(attend))  %>% tabyl(attend)
+
+# Master preprint list
+  master_list <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Master List of Preprints") %>% clean_names()
+
+# Check allocation of papers
+		contr_extract <- master_list  %>%  tabyl(extractor_full_name)
+
+	# Check how many each person has done relative to their total
+		contr_extract2 <- master_list %>% group_by(extractor_full_name) %>% summarise(n = n(), yes = sum(completed_yes_no_extractor == "Yes"), no = sum(completed_yes_no_extractor == "No"), prop = yes/n)  %>% data.frame()  %>% arrange(n)
+
+# raw data. For analysis
+	data_coll <- read_sheet("https://docs.google.com/spreadsheets/d/1032gLryvtCNJ7eJjKBjrn7txxDRUGql9SoIG18QnFrQ/edit?resourcekey#gid=1062856014")
+
+# Final Processed data
+  data2 <- read_csv(here("data", "final_data2.csv"))
+
 ```
@@
 
-Here, we explore the first preprints uploaded to *EcoEvoRxiv* to understand preprint practices and use in our field, focusing our attention on understanding: 1) how long it takes for a preprint to become published, and how many preprints remain unpublished; 2) what countries make use of preprints; 3) how career stage and gender impact preprint use; 4) whether data and code are more likely to be shared in preprints; and 5) the extent to which authors make use of preprint servers for registered reports and community driven peer review.
+Here, we explore the first preprints uploaded to *EcoEvoRxiv*, one of the few community run preprint servers, to understand preprint practices and use in our field, focusing our attention on understanding: 1) how long it takes for a preprint to become published, and how many preprints remain unpublished; 2) what countries make use of preprints; 3) how career stage and gender impact preprint use; 4) whether data and code are more likely to be shared in preprints; and 5) the extent to which authors make use of preprint servers for registered reports and community driven peer review.
 
 We downloaded metadata on the preprints available on *EcoEvoRxiv* (as of the `r gsub("UTC", "", dates[2])`).
-After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissons for the same preprint rather than updating an existing submission – we had data for a total of `r pr` preprints with ~55-60 preprints published each month in the last two years (@fig-figdates).
+After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissons for the same preprint rather than updating an existing submission – we had data for a total of `r pr` preprints with ~55-60 preprints published each month in the last two years (@fig-summary).
 
-```{r, figdates}
-#| label: fig-figdates
+```{r, fig-summary}
+#| label: fig-summary
 #| fig-cap: Number of preprints published monthly to *EcoEvoRxiv* between 2018 and 2023.

### 2024-04-05 ms/ms.qmd
Updated MS with results and setting threshold to 60 days for postprints

@@
 #| label: setup
+
+# Set rounding options
+options(scipen = 1, digits = 2)
 
@@
 
-We downloaded metadata on the preprints available on *EcoEvoRxiv* (as of the `r gsub("UTC", "", dates[2])`).
-After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissons for the same preprint rather than updating an existing submission – we had data for a total of `r pr` preprints with ~55-60 preprints published each month in the last two years (@fig-summary).
-
 ```{r, fig-summary}
 #| label: fig-summary
-#| fig-cap: Number of preprints published monthly to *EcoEvoRxiv* between 2018 and 2023.
+#| fig-cap: Summary of preprints on *EcoEvoRxiv*. A) Number of preprints published monthly to *EcoEvoRxiv* between 2018 and 2023;
 
-ggplot(data, aes(x = `Published Date`)) +
+##---------------------##
+# Preprints over time
+##---------------------##
+
+p1 <- ggplot(data, aes(x = `Published Date`)) +
   geom_histogram(fill = "grey", color = "black") +
@@
 
+We downloaded metadata on the preprints available on *EcoEvoRxiv* (as of the `r gsub("UTC", "", dates[2])`).
+After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissons for the same preprint rather than updating an existing submission – we had data for a total of `r pr` preprints with ~55-60 preprints published each month in the last two years ([@fig-summary]A).
+
+```{r, fig-pubsummary}
+#| label: fig-pubsummary
+#| fig-cap: Summary of the publication status of preprints on *EcoEvoRxiv*.
+B) Time between submission and publication of preprints on *EcoEvoRxiv*.
+'Preprints' that were published within 2 months (60 days) of being submitted are considered postprints.
+
+##---------------------##
+# Publication times
+##---------------------##
+
+# How many remain unpublished?
+unpub <- data2  %>% filter(is.na(publication_doi))  %>% nrow()
+
+# How many days between submission and publication
+preprints <- data2  %>% filter(time_between_preprint_and_pub_days >= 60)
+
+p2 <- preprints %>% ggplot(aes(x = time_between_preprint_and_pub_days)) + geom_histogram(binwidth = 30) + labs(x = "Days", y = "Frequency") + theme_classic()
+
+# Summary of the data
+# what is the range
+sum_preprints <- preprints  %>% summarise(min = min(time_between_preprint_and_pub_days), max = max(time_between_preprint_and_pub_days), mean = mean(time_between_preprint_and_pub_days), median = median(time_between_preprint_and_pub_days), sd = sd(time_between_preprint_and_pub_days))
+
+```
+
+In total, `r unpub` papers were unpublished out of the `r nrow(data2)` (`r (unpub / nrow(data2))*100`%).
+The maximum time between submission and publication was `r sum_preprints$max` days (@fig-pubsummary A).
+The median time to publication was `r sum_preprints$median` days (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days).
+
 - figure timeline of EcoEvoRxiv, aims and future and current developments infographics mixed with the data.

### 2024-04-05 supp/supp.qmd
Updated MS with results and setting threshold to 60 days for postprints

@@
 # How many days between submission and publication
-preprints <- data2  %>% filter(time_between_preprint_and_pub_days >= 30)
+preprints <- data2  %>% filter(time_between_preprint_and_pub_days >= 60)
 preprints %>% ggplot(aes(x = time_between_preprint_and_pub_days)) + geom_histogram(binwidth = 30) + labs(x = "Days", y = "Frequency") + theme_classic()

### 2024-04-06 ms/ms.qmd
Fixing up worldmap with some more detail. and organising plot summary

@@
 
+  # Subset the preprints
+  preprints <- data2  %>% filter(time_between_preprint_and_pub_days >= 60)
+
 ##---------------------##
-# Preprints over time
+# Articles on EcoEvoRxiv over time
 ##---------------------##
 
-p1 <- ggplot(data, aes(x = `Published Date`)) +
+  p1 <- ggplot(data2, aes(x = preprint_published_date)) +
     geom_histogram(fill = "grey", color = "black") +
-  labs(x = "Published Date", y = "Number of preprints") +
+    labs(x = "Published Date", y = "Number of Papers") +
     theme_bw() +
     theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+##---------------------##
+# Countries using EcoEvoRxiv
+##---------------------##
+  # Create a global map with countried highlighted and shaded according to the frequency of preprints from that country
+  # First, we need to get the country names and the number of preprints from each country
+    countries <- data2  %>% tabyl(submitting_author_country)  %>% rename("country" = submitting_author_country, "n" = n)  %>% mutate(country = ifelse(country == "NA", "Unknown", country))  %>% arrange(desc(n))  %>% mutate(country=str_to_title(country))
+
+  # Now we can plot the map, but before we do we need to make sure the names in the countries file match those in the region of the world map
+    world_map <- map_data(map = "world") %>% 
+    filter(! long > 180)
+
+  # List unique countries
+    maps_country_name <- unique(world_map$region) # Names of regions in maps
+    #countries[!countries$country %in% maps_country_name,] # Names of countries in our data that are not in the maps data, we need to fix these in countries
+
+  # Fix names in countries
+      replace <- c("United States Of America" = "USA",  "United Kingdom" = "UK",  "Czechia" = "Czech Republic") 
+    countries <- countries  %>% mutate(country = str_replace_all(country, replace))  %>% filter(!is.na(valid_percent ))  %>% mutate(valid_percent_dis = factor(round(valid_percent, 3)*100, ordered = TRUE))
+
+  p2 <- ggplot(countries) +
+    geom_map(aes(map_id = country, fill = valid_percent_dis), map = world_map) +
+    geom_polygon(data = world_map, aes(x = long, y = lat, group = group), colour = 'black', fill = NA) +
+    expand_limits(x = world_map$long, y = world_map$lat) +
+    theme_void() + expand_limits(x = world_map$long, y = world_map$lat) + scale_fill_viridis(discrete = TRUE) + coord_fixed() + labs(fill="%") +  coord_map("moll")
+
+  # Find the countries with 90% of the preprints
+
+  most_use <- countries[cumsum(countries$valid_percent) <= 0.90, ]
+
+##---------------------##
+# Taxa
+##---------------------##
+  cols <- c("plants", "algi", "fungi", "microorganisms", "invertebrates", "vertebrates")
+
+  # Summary of the data
+  sum_taxa <- data2  %>% dplyr::select(all_of(cols))  %>% apply(., 2, sum, na.rm = TRUE)  %>% data.frame()   %>% rownames_to_column(var = "taxa")  %>% rename("n" = ".")  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))
+
+  # Use data to create a pir chart and clean up colour palette
+
+  p3 <- ggplot(sum_taxa, aes(x = "", y = perc, fill = taxa)) +
+    geom_col(color = "black") +
+    geom_label_repel(aes(label = labels),
+              position = position_stack(vjust = 0.6),
+            show.legend = FALSE) +
+    scale_fill_viridis_d() +
+    coord_polar(theta = "y") + 
+    theme_void() + labs(fill = "Taxa")
+
+##---------------------##
+# Types pf preprints
+##---------------------##
+# Summary of the data
+  sum_types <- preprints  %>% tabyl(type_of_preprint)  %>% rename("type" = type_of_preprint, "n" = n)  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))
+
+  p4 <- ggplot(sum_types, aes(x = "", y = perc, fill = type)) +
+    geom_col(color = "black") +
+    geom_label_repel(aes(label = labels),
+              position = position_stack(vjust = 0.6),
+            show.legend = FALSE) +
+    scale_fill_viridis_d() +
+    coord_polar(theta = "y") + 
+    theme_void() + labs(fill = "Article Type")
+
+## Final plot. World map in the middle with others around
+
+layout <- "
+##AA##
+BBBBBB
+BBBBBB
+BBBBBB
+CCCDDD
+CCCDDD 
+"
+
+p_summary <- p1+p2+p3+p4 + plot_layout(design = layout)+ plot_annotation(tag_levels = 'A', tag_suffix=")", theme = theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin"))
 
@@
 After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissons for the same preprint rather than updating an existing submission – we had data for a total of `r pr` preprints with ~55-60 preprints published each month in the last two years ([@fig-summary]A).
+Preprints were published on all major taxomic groups, with the most common being plants (`r sum_taxa$perc[1]`%), vertebrates (`r sum_taxa$perc[6]`%), and invertebrates (`r sum_taxa$perc[5]`%) ([@fig-summary]).
+A total of `r length(unique(countries$country))-1` countries have used *EcoEvoRxiv* as a preprint server.
+Unsurprisingly, countries in North America and Europe use preprints more exstensively.
+Countries in Africa, Central America and parts of Asia are still slow to use *EcoEvoRxiv* for their preprints ([@fig-summary]).
+Overall, 90% of the preprints come from just `r nrow(most_use)-1` countries ([@fig-summary]).
+
+Given that *EcoEvoRxiv* is a community driven preprint server it has managed to diversify the types of artciles accepted, including reports and books that are not easily accessible but may contain important data of relevance to research syntheses.
+Preprints on *EcoEvoRxiv* were diverse in nature, with research articles (`r sum_types[sum_types$type == "research article",]$perc`%) being the most common, followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]).
 
@@
 
-# How many days between submission and publication
-preprints <- data2  %>% filter(time_between_preprint_and_pub_days >= 60)
-
-p2 <- preprints %>% ggplot(aes(x = time_between_preprint_and_pub_days)) + geom_histogram(binwidth = 30) + labs(x = "Days", y = "Frequency") + theme_classic()
+p1 <- preprints %>% ggplot(aes(x = time_between_preprint_and_pub_days)) + geom_histogram(binwidth = 30) + labs(x = "Days", y = "Frequency") + theme_classic()
 
@@
 
+##-------------------##
+# Open access
+##-------------------##
+
+# Summary of the data
+sum_is_oa <- tabyl(preprints$is_oa)
+sum_oa_status <- tabyl(preprints$oa_status)
+
+p2 <- preprints  %>% ggplot(aes(x = is_oa)) + geom_bar() + labs(x = "Open Access", y = "Frequency") + theme_classic()
+
+p3 <- preprints  %>% ggplot(aes(x = oa_status)) + geom_bar() + labs(x = "Open Access Status", y = "Frequency") + theme_classic()
+
+p_pubsummary <- (p1 + p2) + plot_annotation(tag_levels = 'A', tag_suffix=")")
+
+##-------------------##
+# Career Stage & Gender
+##-------------------##
+
+p3 <- ggplot(preprints, aes(x = submitting_author_first_publication_year)) +
+  geom_histogram(binwidth = 1, fill = "grey", color = "black") +
+  labs(x = "Year of submitting authors first publication", y = "Number of preprints") +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+count_dat  <- preprints  %>% group_by(submitting_author_first_publication_year)  %>% summarise(n = n())
+
+model <- glm.nb(n ~ submitting_author_first_publication_year, data = count_dat)
+res <- summary(model)$coefficients
+
+# First need to get the authors first name
+  data2 <- data2 %>% mutate(submitting_author_firstname = str_split(submitting_author, " ") %>% map_chr(1))
+
+# In order to localise by country we need to get the country code
+  data2 <- data2 %>% mutate(submitting_author_country_code = countrycode(data2$submitting_author_country, origin = "country.name", destination = "iso2c"))
+
+# Lets have a quick look at whether these are 'correct'
+  data2 %>% dplyr::select(submitting_author_country_code, submitting_author_country)  %>% distinct()
+
+# This looks good, but lets see which two are NA. These are in fact NA, even though they shouldn't really be as affliations are not listed on preprint. Even the published paper isn't clear. 
+  data2 %>% filter(is.na(submitting_author_country_code))  %>% data.frame()
+
+# Get gender using all unique first names from the data set
+data_genders <- data.frame(gender(unique(preprints$submitting_author_firstname)))
+dim(data_genders) #514 assigned
+#names(data_genders)
+
+# Merge with main data frame
+#unique(data_genders$name)
+#data_genders <- rename(data_genders, submitting_author_firstname = name)
+data3 <- left_join(preprints, data_genders, by = c("submitting_author_firstname"))
+#names(data3)
+table(is.na(data3$proportion_male)) #157 missing
+
+# Pull out records missing names
+#data3[is.na(data3$proportion_male), c("submitting_author", "submitting_author_country") ] #157 missing
+#data3[is.na(data3$proportion_male) == FALSE & data3$proportion_male > 0.05 & data3$proportion_male < 0.95, c("submitting_author", "submitting_author_country") ] # 84 missing a bit unsure
+
+#transliterate the non-ASCII characters using stringi package, e.g.: #stri_trans_general("Zażółć gęślą jaźń", "Latin-ASCII")
+data3$submitting_author_ASCII <- stringi::stri_trans_general(data3$submitting_author, "Latin-ASCII")
+
+#data3 %>% 
+  #filter(is.na(data3$proportion_male) == TRUE | (proportion_male > 0.05 & proportion_male < 0.95)) %>% dplyr::select(submitting_author_ASCII, submitting_author, submitting_author_country, preprint_title, gender) %>%
+ # write.csv(file = here("data", "final_data3_fillin.csv")) #used to manually check and fill in gender data - then saved as final_data3_fillin_ML.csv
+
+# Load updated data	subset
+data3_update <- read_csv(here("data", "final_data3_fillin_ML.csv"))
+dim(data3_update)
+names(data3_update)
+
+data4 <- left_join(data3, data3_update, by = c("submitting_author_ASCII", "submitting_author", "submitting_author_country", "preprint_title"))
+#table(data4$gender.x, useNA = "always")
+#table(data4$gender.y, useNA = "always")
+data4$gender.x[is.na(data4$gender.x)] <- data4$gender.y[is.na(data4$gender.x)] #replace with correct values
+data4 <- rename(data4, gender = gender.x)
+table(data4$gender, useNA = "always") #more males than females, two NA ue to missing first name / collective authorship
+
+# Plot the data
+data4 %>% filter(!is.na(gender))  %>% ggplot2::ggplot(aes(x = gender)) + geom_bar()
+
+##-------------------##
+# Data and Code Sharing
+##-------------------##
+
+# Summary of the data
+  preprint_data <- preprints  %>% tabyl(data_link_preprint_cleaned) 
+  preprint_code <- preprints  %>% tabyl(code_link_preprint_cleaned) 
+  article_data <- preprints  %>% tabyl(data_link_article_cleaned) 
+  article_code <- preprints  %>% tabyl(code_link_article_cleaned)
+
+# Check if it was shared not in preprint but then in article
+  pre_article_data <- preprints   %>%  filter(!data_link_preprint_cleaned == "not applicable") %>% mutate(data_shared = ifelse(data_link_preprint_cleaned == "no" & data_link_article_cleaned == "yes", "yes", ifelse(code_link_preprint_cleaned == "yes" & code_link_article_cleaned == "yes", "always", "no")))  %>% tabyl(data_shared)
+  pre_article_code <- preprints  %>%  filter(!data_link_preprint_cleaned == "not applicable") %>% mutate(code_shared = ifelse(code_link_preprint_cleaned == "no" & code_link_article_cleaned == "yes", "yes", ifelse(code_link_preprint_cleaned == "yes" & code_link_article_cleaned == "yes", "always", "no")))  %>% tabyl(code_shared)
+
+##-------------------##
+# PCI Recommendations
+##-------------------##
+  # How many articles were PCI recomended
+  pci <- preprints  %>% tabyl(pci_recommendation_preprint)
+
+##-------------------##
+# Titel changes
+##-------------------##
+titles <- preprints %>%  filter(!is.na(publication_doi)) %>% tabyl(publication_title_changed)
 ```
@@
 
-- figure timeline of EcoEvoRxiv, aims and future and current developments infographics mixed with the data.
-- think about your preprint as workflow, continually evolving paper with support of the community. 
-- community driven peer review, can't update things with other preprints. 
-- our terms, we are not a journal, we are a preprint server. Cannot be company driven.
+Preprints can be a useful way to ensure that research remains open and accessible to the research community as the paper is available online no matter what the published status of the preprint ends up being.
+Most of the published preprints ended up being open access(@fig-pubsummary A), however, the status of many (i.e., `r sum_is_oa$n[3]` or `r sum_is_oa$percent[3]*100`%) were unknown, and `r sum_is_oa$n[1]` or `r sum_is_oa$percent[1]*100`% were not published in open access reserach journals.
+The open access status of the papers that were published in open access journals also varied widely (@fig-pubsummary B).
+
+We were interested in getting an understanding of whether career stage is related to preprint use.
+We used the first publication year of the submitting author as a proxy for career stage.
+We predicted that early career researchers would be more open to using preprints in Ecology and Evolution.
+Interestingly, there was strong evidence that the number of preprints posted decreases with later career stages (negative binomial glm: year slope = `r res[2, "Estimate"]`, SE: `r res[2, "Std.
+Error"]`, *p* < 0.001, N = `r nrow(count_dat[complete.cases(count_dat),])`).
+The majority of preprints were submitted by authors who published their first paper in the last 10 years (@fig-career), with the median year of first publication of submitting authors being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r round(mean(data2$submitting_author_first_publication_year, na.rm = TRUE),0)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`).
+
+Gender differences in preprint use have been established in a number of other research fields.
+It is hypothsised that such differences are driven by the larger childcare burden of female researchers, which limit their abilities to publish as frequently as their male counterparts [@ucar2022mind; @wehner2020comparison].
+Recent work has shown that COVID-19 exacerbated gender disparities in preprint publishing given the increased childcare burden during the pandemic associated with lockdowns and home schooling [@wehner2020comparison].
+
+Understanding gender publishing patterns is challenging.
+We cannot know the gender of authors for certainty but we can use a data driven approach to suggest the probability that a particular name is of a given gender (male or female).
+We used the R package *DemografixeR* (vers.
+`r utils::packageVersion("DemografixeR")`; @RJ-2016-002) to predict the most likely gender of the submitting author of a preprint.
+We incorperated information about the submitting authors country of affiliation to better account for differences across countries in naming.
+
+Overall, females were less likely to publish preprints on *EcoEvoRxiv* compared to males (females: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`% compared to males: `r (table(data4$gender)[2] / sum(table(data4$gender))*100)`%), which is likely a reflection of the broader publishing disparities between male and feamle scientists.
+
+Data and code sharing is a key component of open science.
+Despite this, we found that `r preprint_data[1,2]` (`r preprint_data[1,"percent"]*100`%) of relevant preprints on *EcoEvoRxiv* (i.e., only where data was generated) did not share data, while `r preprint_code[1,2]` (`r preprint_code[1,"percent"]*100`%) did not share code.
+
+Authors may be reluctant to share data in code for preprints because of the perceived concern that others may acquire and use such data and code without authors' consent.
+However, while we found that `r pre_article_data[3,2]` (`r pre_article_data[3,"percent"]*100`%) of preprints that did not share data at the preprint stage did in the published article, there were still `r pre_article_data[2,2]` (`r pre_article_data[2,"percent"]*100`%) that never ended up sharing data.
+The same was true for code.
+Overall, while `r pre_article_code[3,2]` (`r pre_article_code[3,"percent"]*100`%) of preprints that did not share code at the preprint stage did in the published article, there were still `r pre_article_code[2,2]` (`r pre_article_code[2,"percent"]*100`%) that never ended up sharing code.
+
+Out of the `r nrow(data2)` preprints, only `r pci[2,2]` (`r pci[2,3]*100`%) used Peer Community In as a preprint peer-review service.
+
+It was reasonably common for titles of preprints to change between the preprint and the published article (`r titles[2,2]` or `r titles[2,3]*100`%).
+This was a major contributer to preprints and published articles not being matched in Google Scholar as they were not picked up by crossref linking services.
+As such, we would recomend that authors make sure that, when preprints end up getting pusblished, that they update preprints with the publication DOI when it's available.
+This is quite easy for authors to do in *EcoEvoRxiv* and it will ensure that the preprint is linked to the published article and the citations are merged and the published paper is ultimately open access, allowing authors to save open access fees.
 

### 2024-04-06 ms/ms.qmd
Doing some writing and re-writing a few places

@@
 
-Authors: Daniel W.A. Noble, Malgorzata Lagisz, Hackathon Participants, Shinichi Nakagawa
+Authors: Daniel W.A. Noble, Shinichi Nakagawa, Hackathon Participants, Malgorzata Lagisz
 
@@
 
-Preprint servers, such as *EcoEvoRxiv*, can empower researchers to make their findings more accessible, open and transparent but only if they are used well.
+Preprint servers, such as *EcoEvoRxiv*, can empower researchers to make their findings more accessible, open and transparent but only if they are used well and initiatives are widely known.
 Significant barriers to preprint use still exist globally – from lack of clarity around preprint policies at journals [@Klebel2020] to a stigma that preprints are viewed by a research community to be of poor quality [@Chiarelli2019] (but see [@Faser2022]).
@@
 Here, we explore the first preprints uploaded to *EcoEvoRxiv*, one of the few community run preprint servers, to understand preprint practices and use in our field, focusing our attention on understanding: 1) how long it takes for a preprint to become published, and how many preprints remain unpublished; 2) what countries make use of preprints; 3) how career stage and gender impact preprint use; 4) whether data and code are more likely to be shared in preprints; and 5) the extent to which authors make use of preprint servers for registered reports and community driven peer review.
+In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other servers which we think will help further educate researchers globally of the benefits of using community driven preprint servers to post their research findings.
 
@@
 #| label: fig-summary
-#| fig-cap: Summary of preprints on *EcoEvoRxiv*. A) Number of preprints published monthly to *EcoEvoRxiv* between 2018 and 2023;
+#| fig-cap: Summary of articles posted to *EcoEvoRxiv*.
+A) Number of preprints published monthly to *EcoEvoRxiv* between 2018 and 2023; B) Countries that are posting artciles (preprpints and postprints) to *EcoEvoRxiv*; C) Taxa used / covered in the articles posted to *EcoEvoRxiv*; D) *EcoEvoRxiv* is a community-based preprint/postprint server and accepts a greater diversity of article types.
+The impetus behind greater inclusion is to help ensure non-typical publication types (e.g., government reports) are openly accessible.
 
@@
   p1 <- ggplot(data2, aes(x = preprint_published_date)) +
-    geom_histogram(fill = "grey", color = "black") +
+    geom_histogram(fill = "black", color = "black") +
     labs(x = "Published Date", y = "Number of Papers") +
     theme_bw() +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1))
+    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")
 
@@
     expand_limits(x = world_map$long, y = world_map$lat) +
-    theme_void() + expand_limits(x = world_map$long, y = world_map$lat) + scale_fill_viridis(discrete = TRUE) + coord_fixed() + labs(fill="%") +  coord_map("moll")
+    theme_void() + expand_limits(x = world_map$long, y = world_map$lat) + scale_fill_viridis(discrete = TRUE) + coord_fixed() + labs(fill="Precentage (%) of Total") +  coord_map("moll") + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")
 
@@
     coord_polar(theta = "y") + 
-    theme_void() + labs(fill = "Taxa")
+    theme_void() + labs(fill = "Taxa") + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")
 
@@
     coord_polar(theta = "y") + 
-    theme_void() + labs(fill = "Article Type")
+    theme_void() + labs(fill = "Article Type") + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")
 
@@
 
-p_summary <- p1+p2+p3+p4 + plot_layout(design = layout)+ plot_annotation(tag_levels = 'A', tag_suffix=")", theme = theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin"))
+p_summary <- p1+p2+p3+p4 + plot_layout(design = layout)+ plot_annotation(tag_levels = 'A', tag_suffix=")")
+ggsave(p_summary, filename = here("output", "figs", "summary.png"), width = 10.6, height = 9.7)
 
+p_summary
 ```
 
-We downloaded metadata on the preprints available on *EcoEvoRxiv* (as of the `r gsub("UTC", "", dates[2])`).
-After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissons for the same preprint rather than updating an existing submission – we had data for a total of `r pr` preprints with ~55-60 preprints published each month in the last two years ([@fig-summary]A).
-Preprints were published on all major taxomic groups, with the most common being plants (`r sum_taxa$perc[1]`%), vertebrates (`r sum_taxa$perc[6]`%), and invertebrates (`r sum_taxa$perc[5]`%) ([@fig-summary]).
+We downloaded metadata on the articles available on *EcoEvoRxiv* (as of the `r gsub("UTC", "", dates[2])`).
+*EcoEvoRxiv* accepts both preprints and postprints.
+Postprints are articles that are already published but are the final version of the published paper before typesetting for the research journal.
+Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication.
+For the purpose of summarising articles on *EcoEvoRxiv* we include these in our analysis.
+
+After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissons for the same preprint rather than updating an existing submission – we had data for a total of `r pr` articles with ~55-60 preprints published each month in the last two years ([@fig-summary]A).
+Articles covered all major taxomic groups, with the most common being plants (`r sum_taxa$perc[1]`%), vertebrates (`r sum_taxa$perc[6]`%), and invertebrates (`r sum_taxa$perc[5]`%) ([@fig-summary]).
 A total of `r length(unique(countries$country))-1` countries have used *EcoEvoRxiv* as a preprint server.
-Unsurprisingly, countries in North America and Europe use preprints more exstensively.
-Countries in Africa, Central America and parts of Asia are still slow to use *EcoEvoRxiv* for their preprints ([@fig-summary]).
-Overall, 90% of the preprints come from just `r nrow(most_use)-1` countries ([@fig-summary]).
+Unsurprisingly, countries in North America and Europe use articles more exstensively.
+Countries in Africa, Central America and parts of Asia are still slow to use *EcoEvoRxiv* ([@fig-summary]).
+Overall, 90% of the articles come from just `r nrow(most_use)-1` countries ([@fig-summary]).
 
-Given that *EcoEvoRxiv* is a community driven preprint server it has managed to diversify the types of artciles accepted, including reports and books that are not easily accessible but may contain important data of relevance to research syntheses.
-Preprints on *EcoEvoRxiv* were diverse in nature, with research articles (`r sum_types[sum_types$type == "research article",]$perc`%) being the most common, followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]).
+Given that *EcoEvoRxiv* is a community driven preprint server it has managed to diversify the types of articles accepted, including reports and books that are not easily accessible but may contain important data of relevance to research syntheses.
+Accepting a greater diversity of artciles types allows *EcoEvoRxiv* to begin dealing with the challenges of including 'grey literature'.
+As a result, articles on *EcoEvoRxiv* were diverse in nature, with research articles (`r sum_types[sum_types$type == "research article",]$perc`%) being the most common, followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]).
+Reports, parcticularly from government and industry research areas, are not yet common on *EcoEvoRxiv*, and we would encourage authors to consider posting these types of articles to ensure they are openly accessible.
+*EcoEvoRxiv* has already formed fruitful connections with the International Union for Conservation of Nature (IUCN) to be a place where their reports can be lodged to make them more easily accessible to the broader research community.
+For example, IUCN Red Ecosystem Reports will be lodged on *EcoEvoRxiv* .
 

### 2024-04-08 ms/ms.qmd
Some writing

@@
 #install.packages("pacman")
-pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, genderdata, gender, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot)
+pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, genderdata, gender, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot, viridis)
 
@@
 In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other servers which we think will help further educate researchers globally of the benefits of using community driven preprint servers to post their research findings.
+
+# *EcoEvoRxiv* as a community driven preprint server three years on: evaluating novel initiatives to improve open science and break down barriers to publishing
 
@@
 A total of `r length(unique(countries$country))-1` countries have used *EcoEvoRxiv* as a preprint server.
-Unsurprisingly, countries in North America and Europe use articles more exstensively.
+Unsurprisingly, countries in North America and Europe preprint more exstensively.
 Countries in Africa, Central America and parts of Asia are still slow to use *EcoEvoRxiv* ([@fig-summary]).
@@
 
-Given that *EcoEvoRxiv* is a community driven preprint server it has managed to diversify the types of articles accepted, including reports and books that are not easily accessible but may contain important data of relevance to research syntheses.
-Accepting a greater diversity of artciles types allows *EcoEvoRxiv* to begin dealing with the challenges of including 'grey literature'.
-As a result, articles on *EcoEvoRxiv* were diverse in nature, with research articles (`r sum_types[sum_types$type == "research article",]$perc`%) being the most common, followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]).
-Reports, parcticularly from government and industry research areas, are not yet common on *EcoEvoRxiv*, and we would encourage authors to consider posting these types of articles to ensure they are openly accessible.
-*EcoEvoRxiv* has already formed fruitful connections with the International Union for Conservation of Nature (IUCN) to be a place where their reports can be lodged to make them more easily accessible to the broader research community.
-For example, IUCN Red Ecosystem Reports will be lodged on *EcoEvoRxiv* .
+Given that *EcoEvoRxiv* is a community driven preprint server it has managed to diversify the types of articles accepted.
+It accepts reports and books that are not easily accessible but may contain important data of relevance to research syntheses.
+Accepting a greater diversity of article types allows *EcoEvoRxiv* to begin dealing with the challenges of finding 'grey literature'.
+As a result, articles on *EcoEvoRxiv* are diverse in nature, with the typical research articles (`r sum_types[sum_types$type == "research article",]$perc`%) being the most common, followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]).
+
+Reports, parcticularly from government and industry research areas, are not yet common on *EcoEvoRxiv*.
+We would encourage authors to consider posting these types of articles to ensure they are openly accessible.
+*EcoEvoRxiv* has already formed fruitful partnerships with the International Union for Conservation of Nature (IUCN) to be a place where their reports can be lodged to make them more easily accessible to the broader research community.
+For example, IUCN Red Ecosystem Reports will be posted on *EcoEvoRxiv* and *EcoEvoRxiv* has worked closely with the IUCN to ensure these reports meet the IUCN requirements.
+
+Multilingual initiatives have also been slow to take off on *EcoEvoRxiv*, with only a few Spanish preprints posted to date, and none in our other accepted langauges (e.g., French, and Portuguese).
+Part of the challenge in getting authors to submit multilingual preprints is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries; however, cultural differences in the perception of preprints and a strong reliance on traditional publishing models, which typically favour publishing in English, may also be contributing to the slow uptake.
+
+# Generational gaps of preprinting in ecology and evolution
+
+We were interested in getting an understanding of whether career stage is related to preprint use.
+We used the first publication year of the submitting author as a proxy for career stage.
+We predicted that early career researchers would be more open to using preprints in Ecology and Evolution.
+Interestingly, there was strong evidence that the number of preprints posted decreases with later career stages (negative binomial glm: year slope = `r res[2, "Estimate"]`, SE: `r res[2, "Std.
+Error"]`, *p* < 0.001, N = `r nrow(count_dat[complete.cases(count_dat),])`).
+The majority of preprints were submitted by authors who published their first paper in the last 10 years (@fig-career), with the median year of first publication of submitting authors being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r round(mean(data2$submitting_author_first_publication_year, na.rm = TRUE),0)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`).
+
+Gender differences in preprint use have been established in a number of other research fields.
+It is hypothsised that such differences are driven by the larger childcare burden of female researchers, which limit their abilities to publish as frequently as their male counterparts [@ucar2022mind; @wehner2020comparison].
+Recent work has shown that COVID-19 exacerbated gender disparities in preprint publishing given the increased childcare burden during the pandemic associated with lockdowns and home schooling [@wehner2020comparison].
+
+Understanding gender publishing patterns is challenging.
+We cannot know the gender of authors for certainty but we can use a data driven approach to suggest the probability that a particular name is of a given gender (male or female).
+We used the R package *DemografixeR* (vers.
+`r utils::packageVersion("DemografixeR")`; @RJ-2016-002) to predict the most likely gender of the submitting author of a preprint.
+We incorperated information about the submitting authors country of affiliation to better account for differences across countries in naming.
+
+Overall, females were less likely to publish preprints on *EcoEvoRxiv* compared to males (females: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`% compared to males: `r (table(data4$gender)[2] / sum(table(data4$gender))*100)`%), which is likely a reflection of the broader publishing disparities between male and feamle scientists.
+
+# Following the journey of a preprint on *EcoEvoRxiv*: from submission to publication, and beyond
 
@@
 
+It was reasonably common for titles of preprints to change between the preprint and the published article (`r titles[2,2]` or `r titles[2,3]*100`%).
+This was a major contributer to preprints and published articles not being matched in Google Scholar as they were not picked up by crossref linking services.
+As such, we would recomend that authors make sure that, when preprints end up getting pusblished, that they update preprints with the publication DOI when it's available.
+This is quite easy for authors to do in *EcoEvoRxiv* and it will ensure that the preprint is linked to the published article and the citations are merged and the published paper is ultimately open access, allowing authors to save open access fees.
+
 Preprints can be a useful way to ensure that research remains open and accessible to the research community as the paper is available online no matter what the published status of the preprint ends up being.
@@
 The open access status of the papers that were published in open access journals also varied widely (@fig-pubsummary B).
-
-We were interested in getting an understanding of whether career stage is related to preprint use.
-We used the first publication year of the submitting author as a proxy for career stage.
-We predicted that early career researchers would be more open to using preprints in Ecology and Evolution.
-Interestingly, there was strong evidence that the number of preprints posted decreases with later career stages (negative binomial glm: year slope = `r res[2, "Estimate"]`, SE: `r res[2, "Std.
-Error"]`, *p* < 0.001, N = `r nrow(count_dat[complete.cases(count_dat),])`).
-The majority of preprints were submitted by authors who published their first paper in the last 10 years (@fig-career), with the median year of first publication of submitting authors being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r round(mean(data2$submitting_author_first_publication_year, na.rm = TRUE),0)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`).
-
-Gender differences in preprint use have been established in a number of other research fields.
-It is hypothsised that such differences are driven by the larger childcare burden of female researchers, which limit their abilities to publish as frequently as their male counterparts [@ucar2022mind; @wehner2020comparison].
-Recent work has shown that COVID-19 exacerbated gender disparities in preprint publishing given the increased childcare burden during the pandemic associated with lockdowns and home schooling [@wehner2020comparison].
-
-Understanding gender publishing patterns is challenging.
-We cannot know the gender of authors for certainty but we can use a data driven approach to suggest the probability that a particular name is of a given gender (male or female).
-We used the R package *DemografixeR* (vers.
-`r utils::packageVersion("DemografixeR")`; @RJ-2016-002) to predict the most likely gender of the submitting author of a preprint.
-We incorperated information about the submitting authors country of affiliation to better account for differences across countries in naming.
-
-Overall, females were less likely to publish preprints on *EcoEvoRxiv* compared to males (females: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`% compared to males: `r (table(data4$gender)[2] / sum(table(data4$gender))*100)`%), which is likely a reflection of the broader publishing disparities between male and feamle scientists.
-
 Data and code sharing is a key component of open science.
@@
 
+# Paving *our* own future of open, transparent and community driven science
+
+Despite the early successes of new initiatives taken by *EcoEvoRxiv* it is still clear that much work needs to be done to improve authors' understanding of preprints (and postprints).
+Our community needs to work harder to help educate our colleagues in this space.
+We view this perspective piece as one small step in achieving that goal.
+Our data driven approach has allowed us to better understand some of the key elements of uncertainty surrounding preprints which provides us with opportunties to clarify our perspective and recommendations.
+First, authors need not be afraid of sharing data and code early in the publication process.
+Sharing data and code early can help improve the quality of research, establish precedence, and improve the transparency and computational reproducibility of scientific findings.
+If authors are worried about data being used unintentially, clear information surrounding its re-use and withholding some data or meta-data needed to understand the dataset may be options.
+Second, authors need to be aware of the benefits of posting preprints and postprints.
+Posting preprints can help establish precedence of research findings, ensure that research is open access, and help authors receive feedback on their research before it is published.
+Third, authors need to be aware of the benefits of using community driven preprint servers.
+Community driven preprint servers can help ensure that research is open access, that research is reviewed by experts in the field, and that research is disseminated quickly.
+
 Out of the `r nrow(data2)` preprints, only `r pci[2,2]` (`r pci[2,3]*100`%) used Peer Community In as a preprint peer-review service.
 
-It was reasonably common for titles of preprints to change between the preprint and the published article (`r titles[2,2]` or `r titles[2,3]*100`%).
-This was a major contributer to preprints and published articles not being matched in Google Scholar as they were not picked up by crossref linking services.
-As such, we would recomend that authors make sure that, when preprints end up getting pusblished, that they update preprints with the publication DOI when it's available.
-This is quite easy for authors to do in *EcoEvoRxiv* and it will ensure that the preprint is linked to the published article and the citations are merged and the published paper is ultimately open access, allowing authors to save open access fees.
-
 # References

### 2024-04-10 ms/ms.qmd
Update topic sentence
Small wording updates

@@
 
-We downloaded metadata on the articles available on *EcoEvoRxiv* (as of the `r gsub("UTC", "", dates[2])`).
+To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the articles available on *EcoEvoRxiv* as of `r gsub("UTC", "", dates[2])`.
 *EcoEvoRxiv* accepts both preprints and postprints.
@@
 Given that *EcoEvoRxiv* is a community driven preprint server it has managed to diversify the types of articles accepted.
-It accepts reports and books that are not easily accessible but may contain important data of relevance to research syntheses.
-Accepting a greater diversity of article types allows *EcoEvoRxiv* to begin dealing with the challenges of finding 'grey literature'.
+It accepts reports and books that are often not easily accessible, but may contain important data of relevance to research syntheses.
+Accepting a greater diversity of article types allows *EcoEvoRxiv* to begin dealing with the 'grey literature' problem.
 As a result, articles on *EcoEvoRxiv* are diverse in nature, with the typical research articles (`r sum_types[sum_types$type == "research article",]$perc`%) being the most common, followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]).

### 2024-04-12 ms/ms.qmd
chaneg subtitle
Fixing up the first plot to include summary of authors. These will be on the below part of the figure

@@
 
+##-------------------##
+# Career Stage & Gender
+##-------------------##
+
+p5 <- ggplot(preprints, aes(x = submitting_author_first_publication_year)) +
+  geom_histogram(binwidth = 1, fill = "grey", color = "black") +
+  labs(x = "Year of submitting authors first publication", y = "Number of preprints") +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+count_dat  <- preprints  %>% group_by(submitting_author_first_publication_year)  %>% summarise(n = n())
+
+model <- glm.nb(n ~ submitting_author_first_publication_year, data = count_dat)
+res <- summary(model)$coefficients
+
+# First need to get the authors first name
+  data2 <- data2 %>% mutate(submitting_author_firstname = str_split(submitting_author, " ") %>% map_chr(1))
+
+# In order to localise by country we need to get the country code
+  data2 <- data2 %>% mutate(submitting_author_country_code = countrycode(data2$submitting_author_country, origin = "country.name", destination = "iso2c"))
+
+# Lets have a quick look at whether these are 'correct'
+  data2 %>% dplyr::select(submitting_author_country_code, submitting_author_country)  %>% distinct()
+
+# This looks good, but lets see which two are NA. These are in fact NA, even though they shouldn't really be as affliations are not listed on preprint. Even the published paper isn't clear. 
+  data2 %>% filter(is.na(submitting_author_country_code))  %>% data.frame()
+
+# Get gender using all unique first names from the data set
+data_genders <- data.frame(gender(unique(data2$submitting_author_firstname)))
+dim(data_genders) #514 assigned
+#names(data_genders)
+colnames(data_genders)[1]  <- c("submitting_author_firstname")
+
+# Merge with main data frame
+data3 <- left_join(data2, data_genders, by = c("submitting_author_firstname"))
+#names(data3)
+table(is.na(data3$proportion_male)) #157 missing
+
+# Pull out records missing names
+#data3[is.na(data3$proportion_male), c("submitting_author", "submitting_author_country") ] #157 missing
+#data3[is.na(data3$proportion_male) == FALSE & data3$proportion_male > 0.05 & data3$proportion_male < 0.95, c("submitting_author", "submitting_author_country") ] # 84 missing a bit unsure
+
+#transliterate the non-ASCII characters using stringi package, e.g.: #stri_trans_general("Zażółć gęślą jaźń", "Latin-ASCII")
+data3$submitting_author_ASCII <- stringi::stri_trans_general(data3$submitting_author, "Latin-ASCII")
+
+#data3 %>% 
+  #filter(is.na(data3$proportion_male) == TRUE | (proportion_male > 0.05 & proportion_male < 0.95)) %>% dplyr::select(submitting_author_ASCII, submitting_author, submitting_author_country, preprint_title, gender) %>%
+ # write.csv(file = here("data", "final_data3_fillin.csv")) #used to manually check and fill in gender data - then saved as final_data3_fillin_ML.csv
+
+# Load updated data	subset
+data3_update <- read_csv(here("data", "final_data3_fillin_ML.csv"))
+dim(data3_update)
+names(data3_update)
+
+data4 <- left_join(data3, data3_update, by = c("submitting_author_ASCII", "submitting_author", "submitting_author_country", "preprint_title"))
+#table(data4$gender.x, useNA = "always")
+#table(data4$gender.y, useNA = "always")
+data4$gender.x[is.na(data4$gender.x)] <- data4$gender.y[is.na(data4$gender.x)] #replace with correct values
+data4 <- rename(data4, gender = gender.x)
+table(data4$gender, useNA = "always") #more males than females, two NA ue to missing first name / collective authorship
+
+# Plot the data
+p6 <- data4 %>% filter(!is.na(gender))  %>% tabyl(gender)  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))  %>%  ggplot(aes(x = "", y = percent, fill = gender)) +
+    geom_col(color = "black") +
+    geom_label_repel(aes(label = labels),
+              position = position_stack(vjust = 0.6),
+            show.legend = FALSE) +
+    scale_fill_viridis_d() +
+    coord_polar(theta = "y") + 
+    theme_void() + labs(fill = "Article Type") + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")
+
 ## Final plot. World map in the middle with others around
@@
 
-# Generational gaps of preprinting in ecology and evolution
+# Generational gaps in preprinting practices
 
@@
 ##-------------------##
-# Career Stage & Gender
-##-------------------##
-
-p3 <- ggplot(preprints, aes(x = submitting_author_first_publication_year)) +
-  geom_histogram(binwidth = 1, fill = "grey", color = "black") +
-  labs(x = "Year of submitting authors first publication", y = "Number of preprints") +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
-count_dat  <- preprints  %>% group_by(submitting_author_first_publication_year)  %>% summarise(n = n())
-
-model <- glm.nb(n ~ submitting_author_first_publication_year, data = count_dat)
-res <- summary(model)$coefficients
-
-# First need to get the authors first name
-  data2 <- data2 %>% mutate(submitting_author_firstname = str_split(submitting_author, " ") %>% map_chr(1))
-
-# In order to localise by country we need to get the country code
-  data2 <- data2 %>% mutate(submitting_author_country_code = countrycode(data2$submitting_author_country, origin = "country.name", destination = "iso2c"))
-
-# Lets have a quick look at whether these are 'correct'
-  data2 %>% dplyr::select(submitting_author_country_code, submitting_author_country)  %>% distinct()
-
-# This looks good, but lets see which two are NA. These are in fact NA, even though they shouldn't really be as affliations are not listed on preprint. Even the published paper isn't clear. 
-  data2 %>% filter(is.na(submitting_author_country_code))  %>% data.frame()
-
-# Get gender using all unique first names from the data set
-data_genders <- data.frame(gender(unique(preprints$submitting_author_firstname)))
-dim(data_genders) #514 assigned
-#names(data_genders)
-
-# Merge with main data frame
-#unique(data_genders$name)
-#data_genders <- rename(data_genders, submitting_author_firstname = name)
-data3 <- left_join(preprints, data_genders, by = c("submitting_author_firstname"))
-#names(data3)
-table(is.na(data3$proportion_male)) #157 missing
-
-# Pull out records missing names
-#data3[is.na(data3$proportion_male), c("submitting_author", "submitting_author_country") ] #157 missing
-#data3[is.na(data3$proportion_male) == FALSE & data3$proportion_male > 0.05 & data3$proportion_male < 0.95, c("submitting_author", "submitting_author_country") ] # 84 missing a bit unsure
-
-#transliterate the non-ASCII characters using stringi package, e.g.: #stri_trans_general("Zażółć gęślą jaźń", "Latin-ASCII")
-data3$submitting_author_ASCII <- stringi::stri_trans_general(data3$submitting_author, "Latin-ASCII")
-
-#data3 %>% 
-  #filter(is.na(data3$proportion_male) == TRUE | (proportion_male > 0.05 & proportion_male < 0.95)) %>% dplyr::select(submitting_author_ASCII, submitting_author, submitting_author_country, preprint_title, gender) %>%
- # write.csv(file = here("data", "final_data3_fillin.csv")) #used to manually check and fill in gender data - then saved as final_data3_fillin_ML.csv
-
-# Load updated data	subset
-data3_update <- read_csv(here("data", "final_data3_fillin_ML.csv"))
-dim(data3_update)
-names(data3_update)
-
-data4 <- left_join(data3, data3_update, by = c("submitting_author_ASCII", "submitting_author", "submitting_author_country", "preprint_title"))
-#table(data4$gender.x, useNA = "always")
-#table(data4$gender.y, useNA = "always")
-data4$gender.x[is.na(data4$gender.x)] <- data4$gender.y[is.na(data4$gender.x)] #replace with correct values
-data4 <- rename(data4, gender = gender.x)
-table(data4$gender, useNA = "always") #more males than females, two NA ue to missing first name / collective authorship
-
-# Plot the data
-data4 %>% filter(!is.na(gender))  %>% ggplot2::ggplot(aes(x = gender)) + geom_bar()
-
-##-------------------##
 # Data and Code Sharing
@@
 
-# Paving *our* own future of open, transparent and community driven science
+# Paving *our* future of open, transparent and community driven science
 

### 2024-04-13 ms/ms.qmd
Fix to fig 1

@@
 #install.packages("pacman")
-pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, genderdata, gender, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot, viridis)
+pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, genderdata, gender, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot, viridis, cowplot)
 
@@
             show.legend = FALSE) +
-    scale_fill_viridis_d() +
     coord_polar(theta = "y") + 
-    theme_void() + labs(fill = "Article Type") + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")
+    theme_void() + labs(fill = "Gender") + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")
 
+p7  <- ggdraw() + draw_plot(p5) + draw_plot(p6, x = 0.05, y = 0.40, width = 0.6, height = 0.6)
 ## Final plot. World map in the middle with others around
@@
 layout <- "
-##AA##
-BBBBBB
-BBBBBB
-BBBBBB
-CCCDDD
-CCCDDD 
+##AAAA##
+BBBBBBBB
+BBBBBBBB
+BBBBBBBB
+CCCCDDDD
+CCCCDDDD
+##EEEE##
+##EEEE##
 "
 
-p_summary <- p1+p2+p3+p4 + plot_layout(design = layout)+ plot_annotation(tag_levels = 'A', tag_suffix=")")
-ggsave(p_summary, filename = here("output", "figs", "summary.png"), width = 10.6, height = 9.7)
+p_summary <- p1+p2+p3+p4+p7 + plot_layout(design = layout)+ plot_annotation(tag_levels = 'A', tag_suffix=")") + theme(plot.tag = element_text(size = 16, face = "bold"))
+ggsave(p_summary, filename = here("output", "figs", "summary.png"), width = 11, height = 12)
 

### 2024-04-14 ms/ms.qmd
Fix fig 1

@@
 Error"]`, *p* < 0.001, N = `r nrow(count_dat[complete.cases(count_dat),])`).
-The majority of preprints were submitted by authors who published their first paper in the last 10 years (@fig-career), with the median year of first publication of submitting authors being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r round(mean(data2$submitting_author_first_publication_year, na.rm = TRUE),0)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`).
+The majority of preprints were submitted by authors who published their first paper in the last 10 years ([@fig-summary]E), with the median year of first publication of submitting authors being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r round(mean(data2$submitting_author_first_publication_year, na.rm = TRUE),0)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`).
 
@@
 It is hypothsised that such differences are driven by the larger childcare burden of female researchers, which limit their abilities to publish as frequently as their male counterparts [@ucar2022mind; @wehner2020comparison].
-Recent work has shown that COVID-19 exacerbated gender disparities in preprint publishing given the increased childcare burden during the pandemic associated with lockdowns and home schooling [@wehner2020comparison].
-
 Understanding gender publishing patterns is challenging.
@@
 
-Despite the early successes of new initiatives taken by *EcoEvoRxiv* it is still clear that much work needs to be done to improve authors' understanding of preprints (and postprints).
-Our community needs to work harder to help educate our colleagues in this space.
+Despite the early successes of new initiatives taken by *EcoEvoRxiv* it is still clear that much work needs to be done to improve our communities understanding of preprints (and postprints).
+Our community needs to work harder to help educate colleagues in this space.
 We view this perspective piece as one small step in achieving that goal.
+
 Our data driven approach has allowed us to better understand some of the key elements of uncertainty surrounding preprints which provides us with opportunties to clarify our perspective and recommendations.

### 2024-04-17 R/2_data_cleaning.R
No updates

@@ -103,7 +103,7 @@ data2 <- data2  %>% select(extractors_first_name, extractors_last_name, preprint
 		data3  <- data3  %>%  select(preprint_doi, publisher_doi, published_date, current_version, total_authors)  %>% rename("preprint_published_date" = "published_date" )
 
 # Join together and create time between preprint and pub
-	data2 <- left_join(data2, data3, by = c("preprint_doi" = "preprint_doi")) 
+	data2 <- left_join(data2, data3, by = c("preprint_id" = "preprint_id")) 
 
 # Fix one typo un the publication date
      data2$publication_date <- gsub("202-03-09", "2020-03-09", data2$publication_date) 

### 2024-04-17 ms/ms.qmd
Adding in the correct informatino for published date for preprints as the current column has misisng data, and that cannot be possible

@@
 # Delegate details
-  delegates <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Delegate Details")
+  #delegates <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Delegate Details")
 
-  del_details <- delegates  %>% rename("attend" = "Attended hackathon (yes/no)") %>%
+  #del_details <- delegates  %>% rename("attend" = "Attended hackathon (yes/no)") %>%
 			mutate(attend = str_to_title(attend))  %>% tabyl(attend)
@@
 # Master preprint list
-  master_list <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Master List of Preprints") %>% clean_names()
+  #master_list <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Master List of Preprints") %>% clean_names()
 
 # Check allocation of papers
-		contr_extract <- master_list  %>%  tabyl(extractor_full_name)
+		#contr_extract <- master_list  %>%  tabyl(extractor_full_name)
 
 	# Check how many each person has done relative to their total
-		contr_extract2 <- master_list %>% group_by(extractor_full_name) %>% summarise(n = n(), yes = sum(completed_yes_no_extractor == "Yes"), no = sum(completed_yes_no_extractor == "No"), prop = yes/n)  %>% data.frame()  %>% arrange(n)
+		#contr_extract2 <- master_list %>% group_by(extractor_full_name) %>% summarise(n = n(), yes = sum(completed_yes_no_extractor == "Yes"), no = sum(completed_yes_no_extractor == "No"), prop = yes/n)  %>% data.frame()  %>% arrange(n)
 
 # raw data. For analysis
-	data_coll <- read_sheet("https://docs.google.com/spreadsheets/d/1032gLryvtCNJ7eJjKBjrn7txxDRUGql9SoIG18QnFrQ/edit?resourcekey#gid=1062856014")
+	#data_coll <- read_sheet("https://docs.google.com/spreadsheets/d/1032gLryvtCNJ7eJjKBjrn7txxDRUGql9SoIG18QnFrQ/edit?resourcekey#gid=1062856014")
 
@@
   data2 <- read_csv(here("data", "final_data2.csv"))
+
+# Seem to be missing the publication date for preprints and this should ne known for all
+    data3 <- read_excel(here("data", "20231003_EER_preprints_metadata.xlsx"))  %>% clean_names()
+
+	# Subset the relevant rows
+		data3  <- data3  %>%  dplyr::select(preprint_id, preprint_doi, publisher_doi, published_date)  %>% rename("preprint_published_date" = "published_date" )
+
+  # Merge with the main data to make sure that the published data of the preprint is known for ALL papers
+    data2  <- left_join(data2, data3, by = c("preprint_id" = "preprint_id"))
 
@@
 
-  p1 <- ggplot(data2, aes(x = preprint_published_date)) +
+  p1 <- ggplot(data2, aes(x = preprint_published_date.y)) +
     geom_histogram(fill = "black", color = "black") +
@@
 Postprints are articles that are already published but are the final version of the published paper before typesetting for the research journal.
-Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication.
+Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication (assuming the journal has a preprint policy).
 For the purpose of summarising articles on *EcoEvoRxiv* we include these in our analysis.
@@
 It is hypothsised that such differences are driven by the larger childcare burden of female researchers, which limit their abilities to publish as frequently as their male counterparts [@ucar2022mind; @wehner2020comparison].
-Understanding gender publishing patterns is challenging.
-We cannot know the gender of authors for certainty but we can use a data driven approach to suggest the probability that a particular name is of a given gender (male or female).
+Understanding gender publishing patterns is challenging with observational data.
+We cannot know the gender of authors for certainty but we can use a data driven approach to ascertain the probability that a particular name is of a given gender (male or female).
 We used the R package *DemografixeR* (vers.
@@
 We incorperated information about the submitting authors country of affiliation to better account for differences across countries in naming.
+We only used names where the gender was identified with 95% certainty.
 

### 2024-04-17 ms/ms.qmd
Fixing some code and package issue

@@
 #install.packages("pacman")
-pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, genderdata, gender, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot, viridis, cowplot)
+remotes::install_github("lmullen/genderdata")
+pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, gender,genderdata, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot, viridis, cowplot)
 
@@
   #del_details <- delegates  %>% rename("attend" = "Attended hackathon (yes/no)") %>%
-			mutate(attend = str_to_title(attend))  %>% tabyl(attend)
+			#mutate(attend = str_to_title(attend))  %>% tabyl(attend)
 
@@
 
-# Seem to be missing the publication date for preprints and this should ne known for all
-    data3 <- read_excel(here("data", "20231003_EER_preprints_metadata.xlsx"))  %>% clean_names()
-
 # Subset the relevant rows
-		data3  <- data3  %>%  dplyr::select(preprint_id, preprint_doi, publisher_doi, published_date)  %>% rename("preprint_published_date" = "published_date" )
+		data3  <- data  %>%  dplyr::select(`Preprint ID`, `Preprint DOI`, `Published Date`)  %>% rename("preprint_pub_date" = "Published Date",
+                                                                                                      "preprint_id"  = "Preprint ID")
 
@@
 
-  p1 <- ggplot(data2, aes(x = preprint_published_date.y)) +
+  p1 <- ggplot(data2, aes(x = preprint_pub_date)) +
     geom_histogram(fill = "black", color = "black") +
@@
 
-p1 <- preprints %>% ggplot(aes(x = time_between_preprint_and_pub_days)) + geom_histogram(binwidth = 30) + labs(x = "Days", y = "Frequency") + theme_classic()
-
 # Summary of the data
@@
 sum_preprints <- preprints  %>% summarise(min = min(time_between_preprint_and_pub_days), max = max(time_between_preprint_and_pub_days), mean = mean(time_between_preprint_and_pub_days), median = median(time_between_preprint_and_pub_days), sd = sd(time_between_preprint_and_pub_days))
+
+p1_pub <- preprints %>% ggplot(aes(x = time_between_preprint_and_pub_days)) + geom_histogram(binwidth = 30) + geom_vline(aes(xintercept = sum_preprints$median), colour = "red", linetype = "dashed", linewidth = 1) + annotate("text", x = sum_preprints$median + 650, y = 60, label = paste0(sum_preprints$median, " days", "(~ ", sum_preprints$median/30, " months)"), size = 10, colour = "red") + labs(x = "Time to Publication (days)", y = "Number of Papers") + theme_classic() + theme(axis.title = element_text(size = 14))
 
@@
 
-p2 <- preprints  %>% ggplot(aes(x = is_oa)) + geom_bar() + labs(x = "Open Access", y = "Frequency") + theme_classic()
+p2_pub <- preprints  %>% ggplot(aes(x = is_oa)) + geom_bar() + labs(x = "Open Access", y = "Number of Papers") + theme_classic() + theme(axis.title = element_text(size = 14))
 
-p3 <- preprints  %>% ggplot(aes(x = oa_status)) + geom_bar() + labs(x = "Open Access Status", y = "Frequency") + theme_classic()
+p3_pub <- preprints  %>% ggplot(aes(x = oa_status)) + geom_bar() + labs(x = "Open Access Status", y = "Number of Papers") + theme_classic() + theme(axis.title = element_text(size = 14))
 
-p_pubsummary <- (p1 + p2) + plot_annotation(tag_levels = 'A', tag_suffix=")")
+p_pubsummary <- (p1_pub + p2_pub + p3_pub) + plot_annotation(tag_levels = 'A', tag_suffix=")")
+ggsave(p_pubsummary, filename = here("output", "figs", "pubsummary.png"), width = 20, height = 7)
 
@@
 ##-------------------##
-# Titel changes
+# Title changes
 ##-------------------##

### 2024-04-18 ms/ms.qmd
Updated MS

@@
 ---
-title: "Empowering the use of community driven preprints in ecology and evolution"
+title: "Encouraging the use of community driven preprints in ecology and evolution"
 bibliography: ../bib/refs.bib
@@
 remotes::install_github("lmullen/genderdata")
-pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, gender,genderdata, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot, viridis, cowplot)
+pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, gender,genderdata, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot, viridis, cowplot, magick)
 
@@
 While preprint use in biology has had a slower uptake [@Berg2016], in ecology and evolution, new discipline specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disseminate research findings.
-Such practices promote open science (e.g., ensuring papers are open access) and facilitate the rapid sharing of new discoveries that can have significant impacts on fundamental and applied knowledge globally.
+Such practices are expected to promote open science and facilitate the rapid sharing of new discoveries that can have significant impacts on fundamental and applied knowledge globally.
 
@@
 Here, we explore the first preprints uploaded to *EcoEvoRxiv*, one of the few community run preprint servers, to understand preprint practices and use in our field, focusing our attention on understanding: 1) how long it takes for a preprint to become published, and how many preprints remain unpublished; 2) what countries make use of preprints; 3) how career stage and gender impact preprint use; 4) whether data and code are more likely to be shared in preprints; and 5) the extent to which authors make use of preprint servers for registered reports and community driven peer review.
-In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other servers which we think will help further educate researchers globally of the benefits of using community driven preprint servers to post their research findings.
+In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other servers which we think will help further educate researchers about the benefits of using community driven preprint servers to post their research findings.
 
-# *EcoEvoRxiv* as a community driven preprint server three years on: evaluating novel initiatives to improve open science and break down barriers to publishing
+# Where we are now and where we want to go: a summary of the first preprints on *EcoEvoRxiv*
 
@@
 #| fig-cap: Summary of articles posted to *EcoEvoRxiv*.
-A) Number of preprints published monthly to *EcoEvoRxiv* between 2018 and 2023; B) Countries that are posting artciles (preprpints and postprints) to *EcoEvoRxiv*; C) Taxa used / covered in the articles posted to *EcoEvoRxiv*; D) *EcoEvoRxiv* is a community-based preprint/postprint server and accepts a greater diversity of article types.
-The impetus behind greater inclusion is to help ensure non-typical publication types (e.g., government reports) are openly accessible.
+A) Number of preprints and postprints published monthly to *EcoEvoRxiv* between 2018 and 2023; B) Countries that are posting articles (preprints and postprints) to *EcoEvoRxiv*; C) Taxa used / covered in the articles posted to *EcoEvoRxiv*; D) Types of articles accepted on *EcoEvoRxiv*.
+E) Career stage of authors posting to *EcoEvoRxiv* along with the gender of the submitting author.
+#| echo: false
+#| warning: false
+#| message: false
 
@@
 # Lets have a quick look at whether these are 'correct'
-  data2 %>% dplyr::select(submitting_author_country_code, submitting_author_country)  %>% distinct()
+  #data2 %>% dplyr::select(submitting_author_country_code, submitting_author_country)  %>% distinct()
 
 # This looks good, but lets see which two are NA. These are in fact NA, even though they shouldn't really be as affliations are not listed on preprint. Even the published paper isn't clear. 
-  data2 %>% filter(is.na(submitting_author_country_code))  %>% data.frame()
+  #data2 %>% filter(is.na(submitting_author_country_code))  %>% data.frame()
 
@@
 data_genders <- data.frame(gender(unique(data2$submitting_author_firstname)))
-dim(data_genders) #514 assigned
+#dim(data_genders) #514 assigned
 #names(data_genders)
@@
 #names(data3)
-table(is.na(data3$proportion_male)) #157 missing
+#table(is.na(data3$proportion_male)) #157 missing
 
@@
 data3_update <- read_csv(here("data", "final_data3_fillin_ML.csv"))
-dim(data3_update)
-names(data3_update)
+#dim(data3_update)
+#names(data3_update)
 
@@
 data4 <- rename(data4, gender = gender.x)
-table(data4$gender, useNA = "always") #more males than females, two NA ue to missing first name / collective authorship
+#table(data4$gender, useNA = "always") #more males than females, two NA ue to missing first name / collective authorship
 
@@
 p7  <- ggdraw() + draw_plot(p5) + draw_plot(p6, x = 0.05, y = 0.40, width = 0.6, height = 0.6)
+
 ## Final plot. World map in the middle with others around
@@
 
-p_summary
+fig1 <- image_read(here("output", "figs", "summary.png"))
+fig1
 ```
@@
 Postprints are articles that are already published but are the final version of the published paper before typesetting for the research journal.
-Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication (assuming the journal has a preprint policy).
-For the purpose of summarising articles on *EcoEvoRxiv* we include these in our analysis.
+Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication (assuming the journal has a preprint policy that recognised preprints - though most do).
+For the purpose of summarising articles on *EcoEvoRxiv* we include both preprints and postprints in our 'demographics' analysis.
 
-After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissons for the same preprint rather than updating an existing submission – we had data for a total of `r pr` articles with ~55-60 preprints published each month in the last two years ([@fig-summary]A).
-Articles covered all major taxomic groups, with the most common being plants (`r sum_taxa$perc[1]`%), vertebrates (`r sum_taxa$perc[6]`%), and invertebrates (`r sum_taxa$perc[5]`%) ([@fig-summary]).
+### *Demographics of **EcoEvoRxiv** preprints (and postprints)*
+
+After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissons for the same preprint rather than updating an existing submission – we had data for a total of `r pr` articles with ~55-60 preprints published each month in the last two years (@fig-summary A).
+Articles covered all major taxomic groups, with the most common being plants (`r sum_taxa$perc[1]`%), vertebrates (`r sum_taxa$perc[6]`%), and invertebrates (`r sum_taxa$perc[5]`%) (@fig-summary B).
 A total of `r length(unique(countries$country))-1` countries have used *EcoEvoRxiv* as a preprint server.
 Unsurprisingly, countries in North America and Europe preprint more exstensively.
-Countries in Africa, Central America and parts of Asia are still slow to use *EcoEvoRxiv* ([@fig-summary]).
-Overall, 90% of the articles come from just `r nrow(most_use)-1` countries ([@fig-summary]).
+Countries in Africa, Central America and parts of Asia are still slow to use *EcoEvoRxiv* (@fig-summary C).
+Overall, 90% of the articles come from just `r nrow(most_use)-1` countries.
+
+### *Diversifying articles types on **EcoEvoRxiv**: overcoming the 'grey literature' problem*
 
@@
 Accepting a greater diversity of article types allows *EcoEvoRxiv* to begin dealing with the 'grey literature' problem.
-As a result, articles on *EcoEvoRxiv* are diverse in nature, with the typical research articles (`r sum_types[sum_types$type == "research article",]$perc`%) being the most common, followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]).
+As a result, articles on *EcoEvoRxiv* are more diverse in nature than other preprint servers; nonetheless, typical research articles (`r sum_types[sum_types$type == "research article",]$perc`%)are still the most common type of preprint, followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) (@fig-summary).
 
-Reports, parcticularly from government and industry research areas, are not yet common on *EcoEvoRxiv*.
-We would encourage authors to consider posting these types of articles to ensure they are openly accessible.
+Reports, parcticularly from government and industry research areas exist but are not yet common on *EcoEvoRxiv*.
+We would encourage authors to consider posting these types of articles to ensure they are openly accessible and more easily found.
 *EcoEvoRxiv* has already formed fruitful partnerships with the International Union for Conservation of Nature (IUCN) to be a place where their reports can be lodged to make them more easily accessible to the broader research community.
-For example, IUCN Red Ecosystem Reports will be posted on *EcoEvoRxiv* and *EcoEvoRxiv* has worked closely with the IUCN to ensure these reports meet the IUCN requirements.
+For example, IUCN Red Ecosystem Reports are now posted to *EcoEvoRxiv* and our community has been able to work closely with the IUCN to ensure these reports meet the IUCN requirements.
 
-Multilingual initiatives have also been slow to take off on *EcoEvoRxiv*, with only a few Spanish preprints posted to date, and none in our other accepted langauges (e.g., French, and Portuguese).
-Part of the challenge in getting authors to submit multilingual preprints is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries; however, cultural differences in the perception of preprints and a strong reliance on traditional publishing models, which typically favour publishing in English, may also be contributing to the slow uptake.
+### *Breaking down language barriers to scientific communication: improving diversity and data representation globally*
 
-# Generational gaps in preprinting practices
+*EcoEvoRxiv* is the only preprint server that has worked hard to break down language barriers to scientific communication; currently accepting English, Spanish, Portuguese and French manuscripts.
+Such initiatives are incredible important if we are to Multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish preprints posted to date, and none in our other accepted langauges (e.g., French and Portuguese).
+Part of the challenge in getting authors to submit multilingual preprints is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries; cultural differences in the perception of preprints and a strong reliance on traditional publishing models, which typically favour publishing in English.
+
+### *Generational and gender-based gaps in preprinting practices*
 
@@
 titles <- preprints %>%  filter(!is.na(publication_doi)) %>% tabyl(publication_title_changed)
+
+fig2 <- image_read(here("output", "figs", "pubsummary.png"))
+fig2
 ```
@@
 The median time to publication was `r sum_preprints$median` days (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days).
-
-It was reasonably common for titles of preprints to change between the preprint and the published article (`r titles[2,2]` or `r titles[2,3]*100`%).
-This was a major contributer to preprints and published articles not being matched in Google Scholar as they were not picked up by crossref linking services.
-As such, we would recomend that authors make sure that, when preprints end up getting pusblished, that they update preprints with the publication DOI when it's available.
-This is quite easy for authors to do in *EcoEvoRxiv* and it will ensure that the preprint is linked to the published article and the citations are merged and the published paper is ultimately open access, allowing authors to save open access fees.
 
@@
 
-# Paving *our* future of open, transparent and community driven science
-
-Despite the early successes of new initiatives taken by *EcoEvoRxiv* it is still clear that much work needs to be done to improve our communities understanding of preprints (and postprints).
-Our community needs to work harder to help educate colleagues in this space.
-We view this perspective piece as one small step in achieving that goal.
+# Paving *our* own future of open, transparent and community driven science
 
@@
 Posting preprints can help establish precedence of research findings, ensure that research is open access, and help authors receive feedback on their research before it is published.
+It is notable that discussions around a preprints findings are still rare and its clear that we as a community need to provide better platforms that document discussions around a preprints findings.
 Third, authors need to be aware of the benefits of using community driven preprint servers.
-Community driven preprint servers can help ensure that research is open access, that research is reviewed by experts in the field, and that research is disseminated quickly.
+Community driven preprint servers are capable of setting their own agenda and are driven by the needs and disires of the community they would like their findings to be shared with.
+Supporting these initiatives should be a priority for all researchers.
+Lastly, it remains clear that the time between preprinting and publication is still quite long.
+One possible explanation is that preprints are not being sent to journals deemed suitable for the work.
+Interestingly, out of the `r nrow(data2)` preprints, only `r pci[2,2]` (`r pci[2,3]*100`%) used Peer Community In as a preprint peer-review service.
+Using PCI provides authors with quicker reviews of a paper and a more realistic recommendation of where such work is likely to be published.
+Many journals now also accept PCI reviews and recomendations when deciding to publish a paper.
+As such, we would encourage more authors to consider sending their preprints for PCI review to possibly speed up the publication process.
 
-Out of the `r nrow(data2)` preprints, only `r pci[2,2]` (`r pci[2,3]*100`%) used Peer Community In as a preprint peer-review service.
+Some authors have been frustrated by preprints and publications being disconnected in the digital world, with many instances where preprints and publications are not correctly recognised as the same paper that has developed over the peer review process.
+It was reasonably common for titles of preprints to change between the preprint and the published article (`r titles[2,2]` or `r titles[2,3]*100`%) and this was the major contributer to preprints and published articles not being matched.
+As such, we would recommend that authors make sure that, when preprints end up getting published, that they update preprints with the publication DOI when it's available.
+Particularly if their title has changed.
+This is quite easy for authors to do in *EcoEvoRxiv* and it will ensure that the preprint is linked to the published article and the citations are merged and the published paper is ultimately open access, allowing authors to save open access fees.
+
+Despite the early successes of the new initiatives taken by *EcoEvoRxiv* it is still clear that much work needs to be done to improve our communities understanding of preprints (and postprints).
+We view this perspective piece as one small step in achieving that goal.
 

### 2024-04-18 ms/ms.qmd
Updated MS. Close, but need more refs now

@@
 ---
-title: "Encouraging the use of community driven preprints in ecology and evolution"
+title: "The promise of community driven preprints in ecology and evolution"
 bibliography: ../bib/refs.bib
@@
 Postprints are articles that are already published but are the final version of the published paper before typesetting for the research journal.
-Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication (assuming the journal has a preprint policy that recognised preprints - though most do).
+Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication (assuming the journal has a preprint policy that recognises preprints - though most do).
 For the purpose of summarising articles on *EcoEvoRxiv* we include both preprints and postprints in our 'demographics' analysis.
@@
 
-After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissons for the same preprint rather than updating an existing submission – we had data for a total of `r pr` articles with ~55-60 preprints published each month in the last two years (@fig-summary A).
-Articles covered all major taxomic groups, with the most common being plants (`r sum_taxa$perc[1]`%), vertebrates (`r sum_taxa$perc[6]`%), and invertebrates (`r sum_taxa$perc[5]`%) (@fig-summary B).
+After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissons for the same preprint rather than updating an existing submission – we had data for a total of `r pr` articles with ~55-60 preprints published each month in the last two years ([@fig-summary]A).
 A total of `r length(unique(countries$country))-1` countries have used *EcoEvoRxiv* as a preprint server.
 Unsurprisingly, countries in North America and Europe preprint more exstensively.
-Countries in Africa, Central America and parts of Asia are still slow to use *EcoEvoRxiv* (@fig-summary C).
+Countries in Africa, Central America and parts of Asia are still slow to use *EcoEvoRxiv* ([@fig-summary]B).
 Overall, 90% of the articles come from just `r nrow(most_use)-1` countries.
+Articles covered all major taxomic groups, with the most common being vertebrates (`r sum_taxa$perc[6]`%), plants (`r sum_taxa$perc[1]`%) and invertebrates (`r sum_taxa$perc[5]`%) ([@fig-summary]C).
 
@@
 Accepting a greater diversity of article types allows *EcoEvoRxiv* to begin dealing with the 'grey literature' problem.
-As a result, articles on *EcoEvoRxiv* are more diverse in nature than other preprint servers; nonetheless, typical research articles (`r sum_types[sum_types$type == "research article",]$perc`%)are still the most common type of preprint, followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) (@fig-summary).
+As a result, articles on *EcoEvoRxiv* are more diverse in nature than other preprint servers; nonetheless, typical research articles (`r sum_types[sum_types$type == "research article",]$perc`%) are still the most common type of preprint, followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) (@fig-summary).
 
@@
 For example, IUCN Red Ecosystem Reports are now posted to *EcoEvoRxiv* and our community has been able to work closely with the IUCN to ensure these reports meet the IUCN requirements.
+Such reports often contain important data that can be leveraged for research syntheses and meta-analyses.
 
@@
 *EcoEvoRxiv* is the only preprint server that has worked hard to break down language barriers to scientific communication; currently accepting English, Spanish, Portuguese and French manuscripts.
-Such initiatives are incredible important if we are to Multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish preprints posted to date, and none in our other accepted langauges (e.g., French and Portuguese).
+Such initiatives are incredibly important if we are to begin filling global voids of scientitic knowledge, Multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish preprints posted to date, and none in our other accepted langauges (e.g., French and Portuguese).
 Part of the challenge in getting authors to submit multilingual preprints is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries; cultural differences in the perception of preprints and a strong reliance on traditional publishing models, which typically favour publishing in English.
@@
 
-Our data driven approach has allowed us to better understand some of the key elements of uncertainty surrounding preprints which provides us with opportunties to clarify our perspective and recommendations.
-First, authors need not be afraid of sharing data and code early in the publication process.
+Our data driven approach has allowed us to better understand some of the key elements of uncertainty surrounding preprints and identify shortcomings and areas needing greater clarity to authors.
+A number of key insights can be gleaned upon from an analysis of the first *EcoEvoRxiv* preprints.
+
+- First, authors need not be afraid of sharing data and code early in the publication process.
 Sharing data and code early can help improve the quality of research, establish precedence, and improve the transparency and computational reproducibility of scientific findings.
 If authors are worried about data being used unintentially, clear information surrounding its re-use and withholding some data or meta-data needed to understand the dataset may be options.
-Second, authors need to be aware of the benefits of posting preprints and postprints.
-Posting preprints can help establish precedence of research findings, ensure that research is open access, and help authors receive feedback on their research before it is published.
-It is notable that discussions around a preprints findings are still rare and its clear that we as a community need to provide better platforms that document discussions around a preprints findings.
-Third, authors need to be aware of the benefits of using community driven preprint servers.
+- Second, authors need to be aware of the benefits of posting preprints and postprints.
+Posting preprints is expected to help: 1) establish precedence of research findings; 2) ensure that research is open access and 3) authors receive feedback on their research before it is published.
+While it is clear points 1 and 2 have already been achived discussions around a preprints findings are still rare.
+It is clear that we, as a community, need to provide better platforms that document discussions around a preprint findings.
+Such discussions are useful for the authors to help improve their work and communicate their findings more effectively (when done constructively, of course).
+- Third, authors need to be aware of the benefits of using community driven preprint servers.
 Community driven preprint servers are capable of setting their own agenda and are driven by the needs and disires of the community they would like their findings to be shared with.
 Supporting these initiatives should be a priority for all researchers.
-Lastly, it remains clear that the time between preprinting and publication is still quite long.
+- Lastly, it remains clear that the time between preprinting and publication is still quite long.
 One possible explanation is that preprints are not being sent to journals deemed suitable for the work.
-Interestingly, out of the `r nrow(data2)` preprints, only `r pci[2,2]` (`r pci[2,3]*100`%) used Peer Community In as a preprint peer-review service.
+Interestingly, out of the `r nrow(data2)` preprints, only `r pci[2,2]` (`r pci[2,3]*100`%) used Peer Community In (PCI) as a preprint peer-review service.
 Using PCI provides authors with quicker reviews of a paper and a more realistic recommendation of where such work is likely to be published.
@@
 
-Some authors have been frustrated by preprints and publications being disconnected in the digital world, with many instances where preprints and publications are not correctly recognised as the same paper that has developed over the peer review process.
-It was reasonably common for titles of preprints to change between the preprint and the published article (`r titles[2,2]` or `r titles[2,3]*100`%) and this was the major contributer to preprints and published articles not being matched.
-As such, we would recommend that authors make sure that, when preprints end up getting published, that they update preprints with the publication DOI when it's available.
+While most preprints seemlessly get connected with their published version and merged together often they can remain disconnected making it unclear how to associate the preprint and published version, creating confusion in the findings and leading to frustration from authors.
+Cross-refererencing problems do occur and are the major reason for why preprints are not always connected automatically.
+Thanksfully, the reasons are fairly well understood and easily rectified.
+They often result from a mismatch between titles or authors in preprint and published metadata.
+In fact, it was reasonably common for titles of preprints to change between the preprint and the published article (`r titles[2,2]` or `r titles[2,3]*100`%) and this was the major contributer to preprints and published articles not being matched automatically in Google Scholar during our data collection.
+As such, we would recommend that authors make sure that, when preprints end up getting published, that they update their preprint with the publication DOI when it's available.
 Particularly if their title has changed.
@@
 We view this perspective piece as one small step in achieving that goal.
+We believe that the future of preprints is bright and community driven initiatives, such as *EcoEvoRxiv*, are set to play a key role in the future of scientific publishing.
 

### 2024-04-18 ms/ms.qmd
awknowledgemets

@@
 
-Authors: Daniel W.A. Noble, Shinichi Nakagawa, Hackathon Participants, Malgorzata Lagisz
+Authors: Daniel W.A. Noble ^1^ $\ddagger$, Shinichi Nakagawa^2^, Hackathon Participants, Malgorzata Lagisz^2^
+
+Affiliations:
+^1^ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia &NewLine;  
+^2^ Ecology and Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia &NewLine;
+
+$\ddagger$ corresponding author, daniel.noble@anu.edu.au &NewLine;
 
@@
 
+# Awknowledgements
+We would like to thank the California Digitial Library (CDL) and the CDL team (particularly Alainna Wrigley) for their support in hosting and maintaining *EcoEvoRxiv* for the Society for Open, Reliable, and Transparent Ecology and Evolution (SORTEE).
+We would also like to thank Gabriela Hidalgo, Daisy Larios
+for helping connect us with the IUCN and facilitating discussions to make *EcoEvoRxiv* a place where IUCN reports can be posted.
+Finally, we would also like to thank the endless number of SORTEE volunteers, and those especially on the *EcoEvoRxiv* Commitee, who have helped to make *EcoEvoRxiv* a success.
+This paper emerged from a hackathon at the 2022 SORTEE conference, and we thank delegates who attended the session but could not be part of this paper.
+DWAN would also like to thank the Australian Research Council Future Fellowship support (FT220100276).
+
 # References

### 2024-04-19 ms/ms.qmd
Updated paper

@@
 
-Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed, visibility and output of research findings; 2) encouraging constructive and critical feedback from a research community; 3) helping establish precedence of research findings; and 4) removing financial barriers to publication [e.g., @Proulx2013].
+Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed, visibility and output of research findings; 2) encouraging constructive and critical feedback from a research community; 3) helping establish precedence of research findings; and 4) removing financial barriers to publication [@Proulx2013; @bourne2017ten; @vale2015accelerating].
 *EcoEvoRxiv* is a community driven preprint server that has paved the way for new initiatives, including accepting multilingual preprints, recognising and accepting registered reports and non-traditional research reports, and promoting peer review and community discussion to improve the quality of preprints and speed up their peer-reviewed publication (e.g., Peer Community In -- PCI).
@@
 Significant barriers to preprint use still exist globally – from lack of clarity around preprint policies at journals [@Klebel2020] to a stigma that preprints are viewed by a research community to be of poor quality [@Chiarelli2019] (but see [@Faser2022]).
-Nonetheless, we lack a systematic understanding of the factors that influence preprint use in ecology and evolution which can help inform future initiatives and allow us to begin to break down barriers to their use in our field.
+Nonetheless, we lack a systematic understanding of the factors that influence preprint use in ecology and evolution which can help inform future initiatives, improve others, and allow us to work harder in further breaking down barriers to their use in our field.
 
-Here, we explore the first preprints uploaded to *EcoEvoRxiv*, one of the few community run preprint servers, to understand preprint practices and use in our field, focusing our attention on understanding: 1) how long it takes for a preprint to become published, and how many preprints remain unpublished; 2) what countries make use of preprints; 3) how career stage and gender impact preprint use; 4) whether data and code are more likely to be shared in preprints; and 5) the extent to which authors make use of preprint servers for registered reports and community driven peer review.
+Here, we explore the first preprints uploaded to *EcoEvoRxiv*, one of the few community run preprint servers, to understand preprint practices and use in ecology and evolution.
+We focus our attention on understanding better: 1) how long it takes for a preprint to become published, and how many preprints remain unpublished; 2) what countries make use of preprints; 3) how career stage and gender impact preprint use; 4) whether data and code are more likely to be shared in preprints; and 5) the extent to which authors make use of preprint servers for registered reports and community driven peer review.
 In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other servers which we think will help further educate researchers about the benefits of using community driven preprint servers to post their research findings.
@@
 It accepts reports and books that are often not easily accessible, but may contain important data of relevance to research syntheses.
-Accepting a greater diversity of article types allows *EcoEvoRxiv* to begin dealing with the 'grey literature' problem.
+Accepting a greater diversity of article types allows *EcoEvoRxiv* to begin dealing with the 'grey literature' problem [@haddaway2015shades; @haddaway2020eight].
 As a result, articles on *EcoEvoRxiv* are more diverse in nature than other preprint servers; nonetheless, typical research articles (`r sum_types[sum_types$type == "research article",]$perc`%) are still the most common type of preprint, followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) (@fig-summary).
@@
 
-*EcoEvoRxiv* is the only preprint server that has worked hard to break down language barriers to scientific communication; currently accepting English, Spanish, Portuguese and French manuscripts.
-Such initiatives are incredibly important if we are to begin filling global voids of scientitic knowledge, Multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish preprints posted to date, and none in our other accepted langauges (e.g., French and Portuguese).
-Part of the challenge in getting authors to submit multilingual preprints is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries; cultural differences in the perception of preprints and a strong reliance on traditional publishing models, which typically favour publishing in English.
+A significant barrier to the communication of research findings is due to the fact that they are primarily communicated in English [@amano2016languages; @amano2013four; @amano2021ten].
+Communication of research through a single language has major consequences for the global distribution of knowledge resulting in knowledge gaps in some of the most biodiverse and threatened regions in the world [@amano2023role; @zenni2023multi].
+Such gaps also have flow on effects for research syntheses and meta-analyses because it creates a distorted picture of our knowledge base that can lead to bias and inadequate sampling that affects policy development and decision making [@hannah2024language; @zenni2023multi; @white2021geographical; @konno2020ignoring].
+
+*EcoEvoRxiv* is the only preprint server breaking down language barriers to scientific communication; currently accepting English, Spanish, Portuguese and French manuscripts.
+Such initiatives are incredibly important if we are to begin filling global voids of scientitic knowledge.
+Multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish preprints posted to date, and none in other accepted langauges (e.g., French and Portuguese).
+Part of the challenge in getting authors to submit multilingual preprints is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries and the fact that it accepts preprints in different languages, cultural differences in the perception of preprints and a strong reliance on traditional publishing models, which typically favour publishing in English.
 
@@
 
-We were interested in getting an understanding of whether career stage is related to preprint use.
-We used the first publication year of the submitting author as a proxy for career stage.
-We predicted that early career researchers would be more open to using preprints in Ecology and Evolution.
-Interestingly, there was strong evidence that the number of preprints posted decreases with later career stages (negative binomial glm: year slope = `r res[2, "Estimate"]`, SE: `r res[2, "Std.
+Research papers take time to be published (see below).
+Early and mid career researchers (ECMRs) need their research to come out quickly for job applications, promotion and obtaining grants to accerate their careers [@vale2015accelerating; @sarabipour2019value].
+Preprints are one way ECMRs can acheive faster dissemination and greater visibility.
+As such, we expect ECMRs to accept and adopt preprints more than later career colleagues.
+At the same time, gender differences in preprint use and publication outcomes  have been established in a number of other research fields, including in ecology and evolution [@fox2019gender; @wehner2020comparison].
+We therefore expect such discrepencies to manifest in preprint use on *EcoEvoRxiv*, but it is unclear to what extent.
+Understanding gender publishing patterns is challenging with observational data such as ours because we cannot know the gender of authors for certainty but we can use a data driven approach to ascertain the probability that a particular name is of a given gender (male or female).
+To obtain an idea of an authors' gender, we used the R package *DemografixeR* (vers.
+`r utils::packageVersion("DemografixeR")`; @RJ-2016-002) to predict the most likely gender of the submitting author of a preprint.
+We incorperated information about the submitting authors country of affiliation to better account for differences across countries.
+We only used names where the gender was identified with 95% certainty.
+
+Overall, females were less likely to publish preprints on *EcoEvoRxiv* compared to males (females: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`% compared to males: `r (table(data4$gender)[2] / sum(table(data4$gender))*100)`%), which is likely a reflection of the broader publishing disparities between male and female scientists [@fox2019gender].
+There was also strong evidence that the number of preprints posted decreases with later career stages (negative binomial glm: year slope = `r res[2, "Estimate"]`, SE: `r res[2, "Std.
 Error"]`, *p* < 0.001, N = `r nrow(count_dat[complete.cases(count_dat),])`).
 The majority of preprints were submitted by authors who published their first paper in the last 10 years ([@fig-summary]E), with the median year of first publication of submitting authors being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r round(mean(data2$submitting_author_first_publication_year, na.rm = TRUE),0)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`).
+These preprinting practices support the idea that ECMRs may value preprints as a way to make their work more visible and disseminate tehir finding more quickly.
 
-Gender differences in preprint use have been established in a number of other research fields.
-It is hypothsised that such differences are driven by the larger childcare burden of female researchers, which limit their abilities to publish as frequently as their male counterparts [@ucar2022mind; @wehner2020comparison].
-Understanding gender publishing patterns is challenging with observational data.
-We cannot know the gender of authors for certainty but we can use a data driven approach to ascertain the probability that a particular name is of a given gender (male or female).
-We used the R package *DemografixeR* (vers.
-`r utils::packageVersion("DemografixeR")`; @RJ-2016-002) to predict the most likely gender of the submitting author of a preprint.
-We incorperated information about the submitting authors country of affiliation to better account for differences across countries in naming.
-We only used names where the gender was identified with 95% certainty.
-
-Overall, females were less likely to publish preprints on *EcoEvoRxiv* compared to males (females: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`% compared to males: `r (table(data4$gender)[2] / sum(table(data4$gender))*100)`%), which is likely a reflection of the broader publishing disparities between male and feamle scientists.
-
-# Following the journey of a preprint on *EcoEvoRxiv*: from submission to publication, and beyond
-
+# Following the journey of a preprint on *EcoEvoRxiv*: from submission to publication
 ```{r, fig-pubsummary}
@@
 #| fig-cap: Summary of the publication status of preprints on *EcoEvoRxiv*.
-B) Time between submission and publication of preprints on *EcoEvoRxiv*.
+A) Time between submission and publication of preprints on *EcoEvoRxiv*.
 'Preprints' that were published within 2 months (60 days) of being submitted are considered postprints.
+B) Number of preprints that were published in open access journals.
+C) Open access status of preprints published on *EcoEvoRxiv*.
 
@@
 
-In total, `r unpub` papers were unpublished out of the `r nrow(data2)` (`r (unpub / nrow(data2))*100`%).
-The maximum time between submission and publication was `r sum_preprints$max` days (@fig-pubsummary A).
-The median time to publication was `r sum_preprints$median` days (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days).
+### **Science takes time, but publication takes longer**
+Increased competition in science has resulted in the bar being raised with respect to the amount of data required for publication [@vale2015accelerating].
+This is a good outcome if it results in higher impact research that better clarifies our understadning of the natural world, but it does come at a cost for the rate at which research findings can be disseminated [@vale2015accelerating].
+Preprinting has been proposed as a way research can be disseminated more quickly as it can take a long time before results are ultimately published [@bourne2017ten; @vale2015accelerating].
+However, data on the time to publication is sparse, and the real benefit of preprints in this context would be reinforced if preprinting is able to dramatically speed up dissemination.
+We evaluated just how much time it takes to publish a research paper in ecology and evolution by ascertaining the time between when a preprint was first posted to when it was finally accepted in a research journal.
+In total, `r unpub` papers were still unpublished out of the `r nrow(data2)` (`r (unpub / nrow(data2))*100`%) at the time these data were collected.
+Astonishingly, the maximum time between submission and publication was `r sum_preprints$max` days ([@fig-pubsummary]A), and the median time to publication was `r sum_preprints$median` days (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days).
+Our results largely confirm the long timespans most authors are dealing with to get their research published after the paper is written.
 
-Preprints can be a useful way to ensure that research remains open and accessible to the research community as the paper is available online no matter what the published status of the preprint ends up being.
-Most of the published preprints ended up being open access(@fig-pubsummary A), however, the status of many (i.e., `r sum_is_oa$n[3]` or `r sum_is_oa$percent[3]*100`%) were unknown, and `r sum_is_oa$n[1]` or `r sum_is_oa$percent[1]*100`% were not published in open access reserach journals.
-The open access status of the papers that were published in open access journals also varied widely (@fig-pubsummary B).
-Data and code sharing is a key component of open science.
+### **Catious 'open'-mindedness of research findings in preprints**
+In additon to speeding up dissemination, preprints can also be a useful way to ensure that research remains open and accessible to the research community because the paper is available online no matter what the open access status of the publication ends up being [@bourne2017ten; @vale2015accelerating].
+Using the published articles on *EcoEvoRxiv*, we evaluated the open access status of each paper using....LOSIA?.
+Most of the published preprints ended up being open access([@fig-pubsummary]A), however, the status of many (i.e., `r sum_is_oa$n[3]` or `r sum_is_oa$percent[3]*100`%) were unknown, and `r sum_is_oa$n[1]` or `r sum_is_oa$percent[1]*100`% were not published in open access reserach journals.
+The level of open access for a paper published in an open access journal also varied widely ([@fig-pubsummary]B).
+
+Data and code sharing is also a key component of open science [@roche2015public].
+In the spirit of 'openness' we expected data and code sharing among preprints to be better than many papers published in research journals [@roche2015public; @o2021preferred].
 Despite this, we found that `r preprint_data[1,2]` (`r preprint_data[1,"percent"]*100`%) of relevant preprints on *EcoEvoRxiv* (i.e., only where data was generated) did not share data, while `r preprint_code[1,2]` (`r preprint_code[1,"percent"]*100`%) did not share code.
-
 Authors may be reluctant to share data in code for preprints because of the perceived concern that others may acquire and use such data and code without authors' consent.
-However, while we found that `r pre_article_data[3,2]` (`r pre_article_data[3,"percent"]*100`%) of preprints that did not share data at the preprint stage did in the published article, there were still `r pre_article_data[2,2]` (`r pre_article_data[2,"percent"]*100`%) that never ended up sharing data.
+However, while `r pre_article_data[3,2]` (`r pre_article_data[3,"percent"]*100`%) of preprints that did not share data at the preprint stage did ultimately share data in the published article, there were still `r pre_article_data[2,2]` (`r pre_article_data[2,"percent"]*100`%) that never ended up sharing data.
 The same was true for code.
-Overall, while `r pre_article_code[3,2]` (`r pre_article_code[3,"percent"]*100`%) of preprints that did not share code at the preprint stage did in the published article, there were still `r pre_article_code[2,2]` (`r pre_article_code[2,"percent"]*100`%) that never ended up sharing code.
+Overall, `r pre_article_code[3,2]` (`r pre_article_code[3,"percent"]*100`%) of preprints did not share code at the preprint stage but did in the published article, however, there were still `r pre_article_code[2,2]` (`r pre_article_code[2,"percent"]*100`%) that never ended up sharing code.
+Code and data sharing patterns in our sample of preprints is consistent with other analyses looking at code and data sharing in published articles (e.g., [@o2021preferred]), even for journals that have strict public data archiving policies [@roche2015public].
 
@@
 - First, authors need not be afraid of sharing data and code early in the publication process.
-Sharing data and code early can help improve the quality of research, establish precedence, and improve the transparency and computational reproducibility of scientific findings.
+Sharing data and code early can help improve the quality of research, establish precedence, and improve the transparency and computational reproducibility of scientific findings [@sarabipour2019value].
 If authors are worried about data being used unintentially, clear information surrounding its re-use and withholding some data or meta-data needed to understand the dataset may be options.
 - Second, authors need to be aware of the benefits of posting preprints and postprints.
-Posting preprints is expected to help: 1) establish precedence of research findings; 2) ensure that research is open access and 3) authors receive feedback on their research before it is published.
-While it is clear points 1 and 2 have already been achived discussions around a preprints findings are still rare.
+Posting preprints is expected to help: 1) establish precedence of research findings; 2) ensure that research is open access and 3) authors receive feedback on their research before it is published [@bourne2017ten].
+While it is clear points 1 and 2 have already been achived discussions around a preprints findings are still rare, which is consistent with findings on other preprint servers (e.g.
+BioRxiv [@anderson2020biorxiv]).
 It is clear that we, as a community, need to provide better platforms that document discussions around a preprint findings.
 Such discussions are useful for the authors to help improve their work and communicate their findings more effectively (when done constructively, of course).
-- Third, authors need to be aware of the benefits of using community driven preprint servers.
+- Third, authors need to be aware of the benefits of using community driven preprint servers and the unique initiatives being pursued.
 Community driven preprint servers are capable of setting their own agenda and are driven by the needs and disires of the community they would like their findings to be shared with.
-Supporting these initiatives should be a priority for all researchers.
+Supporting these initiatives should be a priority for all researchers and those volunteering their time at *EcoEvoRxiv* remain open to new and innovative ways to improve publication and open science practices.
 - Lastly, it remains clear that the time between preprinting and publication is still quite long.
@@
 
-While most preprints seemlessly get connected with their published version and merged together often they can remain disconnected making it unclear how to associate the preprint and published version, creating confusion in the findings and leading to frustration from authors.
-Cross-refererencing problems do occur and are the major reason for why preprints are not always connected automatically.
-Thanksfully, the reasons are fairly well understood and easily rectified.
+While most preprints get seemlessly connected with and merged with their published version some remain disconnected.
+Incorrect cross-linking can create confusion in research findings and lead to frustration from authors.
+Thankfully, the reasons for unmatched preprints and publications are fairly well understood and easily rectified.
 They often result from a mismatch between titles or authors in preprint and published metadata.
-In fact, it was reasonably common for titles of preprints to change between the preprint and the published article (`r titles[2,2]` or `r titles[2,3]*100`%) and this was the major contributer to preprints and published articles not being matched automatically in Google Scholar during our data collection.
-As such, we would recommend that authors make sure that, when preprints end up getting published, that they update their preprint with the publication DOI when it's available.
+In fact, it was reasonably common for titles of preprints to change between the preprint and the published article (`r titles[2,2]` or `r titles[2,3]*100`%).
+Mismatched metadata was the almost always the contributer to preprints and published articles not being matched automatically in Google Scholar during our data collection.
+As such, we would recommend that authors make sure that, when preprints end up getting published, that they update their preprint with the publication DOI when it is available.
 Particularly if their title has changed.
-This is quite easy for authors to do in *EcoEvoRxiv* and it will ensure that the preprint is linked to the published article and the citations are merged and the published paper is ultimately open access, allowing authors to save open access fees.
+This is quite easy for authors to do in *EcoEvoRxiv* and it will ensure that the preprint is linked to the published article and the citations are merged.
+It will also create a link between the final preprint and the published paper so that, no matter the open access status of the publication, the reserach findings will remain openly accessible, saving costs for authors and improving the visibility and use of research.
 

### 2024-04-19 ms/ms.qmd
First draft. Off to Shin and Losia

@@
 Significant barriers to preprint use still exist globally – from lack of clarity around preprint policies at journals [@Klebel2020] to a stigma that preprints are viewed by a research community to be of poor quality [@Chiarelli2019] (but see [@Faser2022]).
-Nonetheless, we lack a systematic understanding of the factors that influence preprint use in ecology and evolution which can help inform future initiatives, improve others, and allow us to work harder in further breaking down barriers to their use in our field.
+Nonetheless, we lack a systematic understanding of the factors that influence preprint use in ecology and evolution which can help inform future initiatives, improve others, and allow us to work harder in further break down barriers to their use in our field.
 
@@
 
-### **Science takes time, but publication takes longer**
+### *Science takes time, but publication could take longer*
 Increased competition in science has resulted in the bar being raised with respect to the amount of data required for publication [@vale2015accelerating].
-This is a good outcome if it results in higher impact research that better clarifies our understadning of the natural world, but it does come at a cost for the rate at which research findings can be disseminated [@vale2015accelerating].
+This is a good outcome if it results in higher impact research that better clarifies our understanding of the natural world, but it does come at a cost for the rate at which research findings can be disseminated [@vale2015accelerating].
 Preprinting has been proposed as a way research can be disseminated more quickly as it can take a long time before results are ultimately published [@bourne2017ten; @vale2015accelerating].
@@
 
-### **Catious 'open'-mindedness of research findings in preprints**
+### *Catious 'open'-mindedness of research findings in preprints*
 In additon to speeding up dissemination, preprints can also be a useful way to ensure that research remains open and accessible to the research community because the paper is available online no matter what the open access status of the publication ends up being [@bourne2017ten; @vale2015accelerating].
@@
 
-- First, authors need not be afraid of sharing data and code early in the publication process.
+- First, authors need not be afraid of sharing data and code early in the preprint stage.
 Sharing data and code early can help improve the quality of research, establish precedence, and improve the transparency and computational reproducibility of scientific findings [@sarabipour2019value].
 If authors are worried about data being used unintentially, clear information surrounding its re-use and withholding some data or meta-data needed to understand the dataset may be options.
-- Second, authors need to be aware of the benefits of posting preprints and postprints.
-Posting preprints is expected to help: 1) establish precedence of research findings; 2) ensure that research is open access and 3) authors receive feedback on their research before it is published [@bourne2017ten].
-While it is clear points 1 and 2 have already been achived discussions around a preprints findings are still rare, which is consistent with findings on other preprint servers (e.g.
+- Second, authors need to be aware of the benefits of posting preprints and postprints for constructive feedback [@bourne2017ten].
+While it is clear preprints help establish precedence and allow findings to be openly accessible it is still rare that constructive discussions form around preprints in an open form, which is consistent with findings on other preprint servers (e.g.
 BioRxiv [@anderson2020biorxiv]).
@@
 Such discussions are useful for the authors to help improve their work and communicate their findings more effectively (when done constructively, of course).
-- Third, authors need to be aware of the benefits of using community driven preprint servers and the unique initiatives being pursued.
-Community driven preprint servers are capable of setting their own agenda and are driven by the needs and disires of the community they would like their findings to be shared with.
-Supporting these initiatives should be a priority for all researchers and those volunteering their time at *EcoEvoRxiv* remain open to new and innovative ways to improve publication and open science practices.
-- Lastly, it remains clear that the time between preprinting and publication is still quite long.
+One way to facilitate such discussions may be to use open peer reviewing serves such as *Peer Community In* (PCI) or *PubPeer* to provide feedback on preprints that ultimately are associated with a preprint.
+- Third, it remains clear that the time between preprinting and publication is still quite long.
 One possible explanation is that preprints are not being sent to journals deemed suitable for the work.
@@
 As such, we would encourage more authors to consider sending their preprints for PCI review to possibly speed up the publication process.
-
-While most preprints get seemlessly connected with and merged with their published version some remain disconnected.
-Incorrect cross-linking can create confusion in research findings and lead to frustration from authors.
+- Finally, while most preprints get seemlessly connected with and merged with their published version some remain disconnected.
+Incorrect cross-linking can create confusion and lead to frustration among authors.
 Thankfully, the reasons for unmatched preprints and publications are fairly well understood and easily rectified.
@@
 In fact, it was reasonably common for titles of preprints to change between the preprint and the published article (`r titles[2,2]` or `r titles[2,3]*100`%).
-Mismatched metadata was the almost always the contributer to preprints and published articles not being matched automatically in Google Scholar during our data collection.
-As such, we would recommend that authors make sure that, when preprints end up getting published, that they update their preprint with the publication DOI when it is available.
+Mismatched metadata was almost always the main contributer to preprints and published articles not being matched automatically in Google Scholar during our data collection.
+We recommend that authors make sure that, when preprints end up getting published, they update their preprint with the publication DOI when it is available.
 Particularly if their title has changed.
@@
 We view this perspective piece as one small step in achieving that goal.
+Authors also need to be aware of the benefits of using community driven preprint servers and the unique initiatives being pursued.
+Community driven preprint servers are capable of setting their own agenda and are driven by the needs and disires of the community they would like their findings to be shared with.
+Supporting these initiatives should be a priority for all researchers and those volunteering their time at *EcoEvoRxiv* remain open to new and innovative ways to improve publication and open science practices.
 We believe that the future of preprints is bright and community driven initiatives, such as *EcoEvoRxiv*, are set to play a key role in the future of scientific publishing.

### 2024-04-19 ms/ms.qmd
Spelling error

@@
 
-### *Catious 'open'-mindedness of research findings in preprints*
+### *Cautious 'open'-mindedness of research findings in preprints*
 In additon to speeding up dissemination, preprints can also be a useful way to ensure that research remains open and accessible to the research community because the paper is available online no matter what the open access status of the publication ends up being [@bourne2017ten; @vale2015accelerating].

### 2024-04-19 ms/ms.qmd
Updated ms to fix a few things and streamline text

--- 2024-04-19 ms/ms.qmd
@@
 Affiliations:
+
 ^1^ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia &NewLine;  
@@
 Here, we explore the first preprints uploaded to *EcoEvoRxiv*, one of the few community run preprint servers, to understand preprint practices and use in ecology and evolution.
-We focus our attention on understanding better: 1) how long it takes for a preprint to become published, and how many preprints remain unpublished; 2) what countries make use of preprints; 3) how career stage and gender impact preprint use; 4) whether data and code are more likely to be shared in preprints; and 5) the extent to which authors make use of preprint servers for registered reports and community driven peer review.
+We focus our attention on understanding better: 1) what countries make use of preprints; 2) the extent to which authors make use of preprint servers for registered reports and community driven peer review  3) how career stage and gender impact preprint use; 4) whether data and code are more likely to be shared in preprints; and 5) how long it takes for a preprint to become published, and how many preprints remain unpublished.
 In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other servers which we think will help further educate researchers about the benefits of using community driven preprint servers to post their research findings.
 
-# Where we are now and where we want to go: a summary of the first preprints on *EcoEvoRxiv*
+# Getting to know your *EcoEvoRxiv* preprint server
+
+*EcoEvoRxiv* is run by the Society for Open, Reliable, and Transparent Ecology and Evolution (SORTEE).
+Editors are researchers across the globe in the fields of ecology and evolution who volunteer their time to screen papers and push new initiatives in the preprint space.
+To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the articles available on *EcoEvoRxiv* as of `r gsub("UTC", "", dates[2])`.
+*EcoEvoRxiv* accepts both preprints and postprints.
+Postprints are articles that are already published but are the final version of the published paper before typesetting for the research journal.
+Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication (assuming the journal has a preprint policy that recognises preprints - though most do).
+For the purpose of summarising articles on *EcoEvoRxiv* we include both preprints and postprints in our 'demographics' analysis.
 
@@
 
-To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the articles available on *EcoEvoRxiv* as of `r gsub("UTC", "", dates[2])`.
-*EcoEvoRxiv* accepts both preprints and postprints.
-Postprints are articles that are already published but are the final version of the published paper before typesetting for the research journal.
-Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication (assuming the journal has a preprint policy that recognises preprints - though most do).
-For the purpose of summarising articles on *EcoEvoRxiv* we include both preprints and postprints in our 'demographics' analysis.
-
 ### *Demographics of **EcoEvoRxiv** preprints (and postprints)*
@@
 Accepting a greater diversity of article types allows *EcoEvoRxiv* to begin dealing with the 'grey literature' problem [@haddaway2015shades; @haddaway2020eight].
-As a result, articles on *EcoEvoRxiv* are more diverse in nature than other preprint servers; nonetheless, typical research articles (`r sum_types[sum_types$type == "research article",]$perc`%) are still the most common type of preprint, followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) (@fig-summary).
+As a result, articles on *EcoEvoRxiv* are more diverse in nature than other preprint servers; nonetheless, typical research articles (`r sum_types[sum_types$type == "research article",]$perc`%) are still the most common type of preprint, followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]D).
 
@@
 Multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish preprints posted to date, and none in other accepted langauges (e.g., French and Portuguese).
-Part of the challenge in getting authors to submit multilingual preprints is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries and the fact that it accepts preprints in different languages, cultural differences in the perception of preprints and a strong reliance on traditional publishing models, which typically favour publishing in English.
+Part of the challenge in getting authors to submit non-English preprints is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries and the fact that it accepts preprints in different languages, cultural differences in the perception of preprints and a strong reliance on traditional publishing models, which typically favour publishing in English.
 
@@
 The majority of preprints were submitted by authors who published their first paper in the last 10 years ([@fig-summary]E), with the median year of first publication of submitting authors being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r round(mean(data2$submitting_author_first_publication_year, na.rm = TRUE),0)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`).
-These preprinting practices support the idea that ECMRs may value preprints as a way to make their work more visible and disseminate tehir finding more quickly.
+These preprinting practices support the idea that ECMRs may value preprints as a way to make their work more visible and disseminate their finding more quickly.
 
@@
 
-### *Catious 'open'-mindedness of research findings in preprints*
+### *Cautious 'open'-mindedness of research in preprints*
 In additon to speeding up dissemination, preprints can also be a useful way to ensure that research remains open and accessible to the research community because the paper is available online no matter what the open access status of the publication ends up being [@bourne2017ten; @vale2015accelerating].
@@
 We would like to thank the California Digitial Library (CDL) and the CDL team (particularly Alainna Wrigley) for their support in hosting and maintaining *EcoEvoRxiv* for the Society for Open, Reliable, and Transparent Ecology and Evolution (SORTEE).
-We would also like to thank Gabriela Hidalgo, Daisy Larios
-for helping connect us with the IUCN and facilitating discussions to make *EcoEvoRxiv* a place where IUCN reports can be posted.
+We would also like to thank Gabriela Hidalgo and Daisy Larios for helping connect us with the IUCN and facilitating discussions to make *EcoEvoRxiv* a place where IUCN reports can be posted.
 Finally, we would also like to thank the endless number of SORTEE volunteers, and those especially on the *EcoEvoRxiv* Commitee, who have helped to make *EcoEvoRxiv* a success.
 This paper emerged from a hackathon at the 2022 SORTEE conference, and we thank delegates who attended the session but could not be part of this paper.
-DWAN would also like to thank the Australian Research Council Future Fellowship support (FT220100276).
+DWAN would also like to thank the Australian Research Council for a Future Fellowship (FT220100276).
+
+# Data and Code Availability
+All data and code can be found on GitHub at: https://github.com/daniel1noble/ecoevo_1000
 

### 2024-04-19 ms/ms.qmd
nothing much

@@
 Using the published articles on *EcoEvoRxiv*, we evaluated the open access status of each paper using....LOSIA?.
-Most of the published preprints ended up being open access([@fig-pubsummary]A), however, the status of many (i.e., `r sum_is_oa$n[3]` or `r sum_is_oa$percent[3]*100`%) were unknown, and `r sum_is_oa$n[1]` or `r sum_is_oa$percent[1]*100`% were not published in open access reserach journals.
+Most of the published preprints ended up being open access ([@fig-pubsummary]A), however, the status of many (i.e., `r sum_is_oa$n[3]` or `r sum_is_oa$percent[3]*100`%) were unknown, and `r sum_is_oa$n[1]` or `r sum_is_oa$percent[1]*100`% were not published in open access reserach journals.
 The level of open access for a paper published in an open access journal also varied widely ([@fig-pubsummary]B).

### 2024-04-20 supp/supp.qmd
Clean up supp as most have been moved into main MS

--- 2024-03-29 supp/supp.qmd
@@
 
-## Preprint submission and publication dates over time
-*EcoEvoRxiv* was established in 2018 and there has been a steady increase in preprints (and postprints) to the journal since that time (@fig-figdates).
-
-```{r, figdates}
-#| label: fig-figdates
-#| fig-cap: Number of preprints published monthly to *EcoEvoRxiv* between 2018 and 2023.
-
-ggplot(data, aes(x = `Published Date`)) +
-  geom_histogram(fill = "grey", color = "black") +
-  labs(x = "Published Date", y = "Number of preprints") +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
-```
-
-## Publication time of preprints
-*EcoEvoRxiv* accepts postprints which means that, technically, a 'preprint' can be published before being lodged on the preprint server.
-Identifying postprints can be challenging because meta-data does not exist to tag such preprints on *EcoEvoRxiv*.
-In addition, authors may have lodged a postprint while waiting for an accepted article to be published online for a given research journal.
-
-In many cases, identifying a postprint is straightforward.
-These are papers that have preprint publication dates that are later than the journal publication date.
-However, papers that were 'quick' to be accepted could also be postprints, as mentioned above.
-It seems highly unlikely for a paper to be accepted in a journal and online within a month after being submitted to *EcoEvoRxiv*.
-We therefore assume that any preprint that was published within a month of being submitted is likely a postprint.
-
-```{r, fig-pubtime}
-#| label: fig-pubtime
-#| fig-cap: Time between submission and publication of preprints on *EcoEvoRxiv*. 'Preprints' that were published within a month of being submitted are considered postprints.
-
-# How many remain unpublished?
-unpub <- data2  %>% filter(is.na(publication_doi))  %>% nrow()
-
-# How many days between submission and publication
-preprints <- data2  %>% filter(time_between_preprint_and_pub_days >= 30)
-preprints %>% ggplot(aes(x = time_between_preprint_and_pub_days)) + geom_histogram(binwidth = 30) + labs(x = "Days", y = "Frequency") + theme_classic()
-
-# Summary of the data
-# what is the range
-sum_preprints <- preprints  %>% summarise(min = min(time_between_preprint_and_pub_days), max = max(time_between_preprint_and_pub_days), mean = mean(time_between_preprint_and_pub_days), median = median(time_between_preprint_and_pub_days), sd = sd(time_between_preprint_and_pub_days))
-```
-
-Overall, `r unpub` papers were unpublished out of the `r nrow(data2)` (`r (unpub / nrow(data2))*100`%).
-The maximum time between submission and publication was `r sum_preprints$max` days (@fig-pubtime).
-The median time to publication was `r sum_preprints$median` days (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days).
-
-## Preprint open access status when published
-
-```{r, oa}
-
-# Summary of the data
-sum_is_oa <- tabyl(preprints$is_oa)
-sum_oa_status <- tabyl(preprints$oa_status)
-```
-
-Preprints can be a useful way to ensure that research remains open and accessible to the research community as the paper is available online no matter what the published status of the preprint ends up being.
-Most of the published preprints ended up being open access(@fig-openaccess A), however, the status of many (i.e., `r sum_is_oa$n[3]` or `r sum_is_oa$percent[3]*100`%) were unknown, and `r sum_is_oa$n[1]` or `r sum_is_oa$percent[1]*100`% were not published in open access reserach journals.
-The open access status of the papers that were published in open access journals also varied widely (@fig-openaccess B).
-
-```{r, fig-openaccess}
-#| label: fig-openaccess
-#| fig-cap: Open access status of preprints when published.
-A) The number of papers pusblihed in open access journals compared to those not.
-Note that many journals could not be identified as open access (i.e, NA).
-B) The classification of open access status of the published preprints.
-
-########-------------------------###
-### What is the OA status of the published preprints?
-########-------------------------###
-
-# Lets first look only at the preprints. Then, we can look at the postprints. It's possible folks are putting up postprints because they are not OA journals and they want to share their work freely.
-
-p1 <- preprints  %>% ggplot(aes(x = is_oa)) + geom_bar() + labs(x = "Open Access", y = "Frequency") + theme_classic()
-
-p2 <- preprints  %>% ggplot(aes(x = oa_status)) + geom_bar() + labs(x = "Open Access Status", y = "Frequency") + theme_classic()
-
-(p1 + p2) + plot_annotation(tag_levels = 'A', tag_suffix=")")
-```
-
-## What countries use preprints the most?
-
-```{r, countries}
-#| label: fig-countries
-#| fig-cap: Percentage of preprints on *EcoEvoRxiv* across countries.
-
-# Create a global map with countried highlighted and shaded according to the frequency of preprints from that country
-# First, we need to get the country names and the number of preprints from each country
-  countries <- preprints  %>% tabyl(submitting_author_country)  %>% rename("country" = submitting_author_country, "n" = n)  %>% mutate(country = ifelse(country == "NA", "Unknown", country))  %>% arrange(desc(n))  %>% mutate(country=str_to_title(country))
-
-# Now we can plot the map, but before we do we need to make sure the names in the countries file match those in the region of the world map
-  world_map <- map_data(map = "world") %>% 
-  filter(! long > 180)
-
-# List unique countries
-  maps_country_name <- unique(world_map$region) # Names of regions in maps
-  #countries[!countries$country %in% maps_country_name,] # Names of countries in our data that are not in the maps data, we need to fix these in countries
-
-# Fix names in countries
-replace = c("United States Of America" = "USA",  "United Kingdom" = "UK",  "Czechia" = "Czech Republic") 
-countries <- countries  %>% mutate(country = str_replace_all(country, replace))
-
-ggplot(countries) +
-  geom_map(aes(map_id = country, fill = valid_percent*100), map = world_map) +
-  geom_polygon(data = world_map, aes(x = long, y = lat, group = group), colour = 'black', fill = NA) +
-  expand_limits(x = world_map$long, y = world_map$lat) +
-  theme_void() + expand_limits(x = world_map$long, y = world_map$lat) +
-  coord_fixed() + labs(fill="%") +  coord_map("moll")
-
-  p1 <- countries  %>% ggplot(aes(map_id = country)) + geom_map(aes(fill = percent), map = map_data("world"), color = "black") + expand_limits(x = map_data("world")$long, y = map_data("world")$lat) + labs(fill = "Number of preprints", title = "Number of preprints by country") + theme_void() + theme(legend.position = "bottom")
-
-# Find the countries with 90% of the preprints
-
-most_use <- countries[cumsum(countries$valid_percent) <= 0.90, ]
-
-```
-
-A total of `r length(unique(countries$country))-1` countries have used *EcoEvoRxiv* as a preprint server.
-Unsurprisingly, countries in North America and Europe use preprints more exstensively.
-Countries in Africa, Central America and parts of Asia are still slow to use *EcoEvoRxiv* for their preprints (@fig-countries).
-Overall, 90% of the preprints come from just `r nrow(most_use)-1` countries (@tbl-countries).
-
-```{r}
-#| label: tbl-countries
-#| tbl-cap: Countries with 90% of the preprints on EcoEvoRxiv.
-
-tbl_most <- most_use %>% filter(!is.na(valid_percent)) %>% mutate(Percentage = valid_percent*100) %>% dplyr::select(country, Percentage)  %>% rename("Country" = country)
-
-flextable(tbl_most) %>% bold(part = "header") %>% autofit()
-```
-
-## Taxa studied in preprints
-
-```{r, fig-taxa}
-#| label: fig-taxa
-#| fig-cap: Taxa studied in preprints on *EcoEvoRxiv*.
-#| 
-cols <- c("plants", "algi", "fungi", "microorganisms", "invertebrates", "vertebrates")
-
-# Summary of the data
-sum_taxa <- data2  %>% dplyr::select(all_of(cols))  %>% apply(., 2, sum, na.rm = TRUE)  %>% data.frame()   %>% rownames_to_column(var = "taxa")  %>% rename("n" = ".")  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))
-
-# Use data to create a pir chart and clean up colour palette
-
-pie <- ggplot(sum_taxa, aes(x = "", y = perc, fill = taxa)) +
-  geom_col(color = "black") +
-  geom_label_repel(aes(label = labels),
-            position = position_stack(vjust = 0.6),
-           show.legend = FALSE) +
-  scale_fill_viridis_d() +
-  coord_polar(theta = "y") + 
-  theme_void() + labs(fill = "Taxa")
-pie
-```
-
-Preprints were published on all major taxomic groups, with the most common being plants (`r sum_taxa$perc[1]`%), vertebrates (`r sum_taxa$perc[6]`%), and invertebrates (`r sum_taxa$perc[5]`%) (@fig-taxa).
-
-## Preprint types
-
-```{r, fig-types}
-#| label: fig-types
-#| fig-cap: Types of papers posted on *EcoEvoRxiv*.
-
-# Summary of the data
-sum_types <- data2  %>% tabyl(type_of_preprint)  %>% rename("type" = type_of_preprint, "n" = n)  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))
-
-pie <- ggplot(sum_types, aes(x = "", y = perc, fill = type)) +
-  geom_col(color = "black") +
-  geom_label_repel(aes(label = labels),
-            position = position_stack(vjust = 0.6),
-           show.legend = FALSE) +
-  scale_fill_viridis_d() +
-  coord_polar(theta = "y") + 
-  theme_void() + labs(fill = "Article Type")
-pie
-```
-
-Preprints on *EcoEvoRxiv* were diverse in nature, with research articles (`r sum_types[sum_types$type == "research article",]$perc`%) being the most common, followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) (@fig-types).
-
-## How does career stage and gender impact preprint use?
-
-```{r, fig-career}
-#| label: fig-career
-#| fig-cap: Year of first publication for submitting authors of preprints on *EcoEvoRxiv*.
-
-ggplot(data2, aes(x = submitting_author_first_publication_year)) +
-  geom_histogram(binwidth = 1, fill = "grey", color = "black") +
-  labs(x = "Year of submitting authors first publication", y = "Number of preprints") +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
-count_dat  <- data2  %>% group_by(submitting_author_first_publication_year)  %>% summarise(n = n())
-
-model <- glm.nb(n ~ submitting_author_first_publication_year, data = count_dat)
-res <- summary(model)$coefficients
-```
-
-We were interested in getting an understanding of whether career stage is related to preprint use.
-We used the first publication year of the submitting author as a proxy for career stage.
-We predicted that early career researchers would be more open to using preprints in Ecology and Evolution.
-
-Interestingly, there was strong evidence that the number of preprints posted decreases with later career stages (negative binomial glm: year slope = `r res[2, "Estimate"]`, SE: `r res[2, "Std.
-Error"]`, *p* < 0.001, N = `r nrow(count_dat[complete.cases(count_dat),])`).
-The majority of preprints were submitted by authors who published their first paper in the last 10 years (@fig-career), with the median year of first publication of submitting authors being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r round(mean(data2$submitting_author_first_publication_year, na.rm = TRUE),0)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`).
-
-Gender differences in preprint use have been established in a number of other research fields.
-It is hypothsised that such differences are driven by the larger childcare burden of female researchers, which limit their abilities to publish as frequently as their male counterparts [@ucar2022mind; @wehner2020comparison].
-Recent work has shown that COVID-19 exacerbated gender disparities in preprint publishing given the increased childcare burden during the pandemic associated with lockdowns and home schooling [@wehner2020comparison].
-
-Understanding gender publishing patterns is challenging.
-We cannot know the gender of authors for certainty but we can use a data driven approach to suggest the probability that a particular name is of a given gender (male or female).
-We used the R package *DemografixeR* (vers.
-`r utils::packageVersion("DemografixeR")`; @RJ-2016-002) to predict the most likely gender of the submitting author of a preprint.
-We incorperated information about the submitting authors country of affiliation to better account for differences across countries in naming.
-
-```{r, fig-gender}
-#| label: fig-gender
-#| fig-cap: Number of preprints published by male and female submitting authors. 
-#| echo: false
-#| include: false
-
-# First need to get the authors first name
-  data2 <- data2 %>% mutate(submitting_author_firstname = str_split(submitting_author, " ") %>% map_chr(1))
-
-# In order to localise by country we need to get the country code
-  data2 <- data2 %>% mutate(submitting_author_country_code = countrycode(data2$submitting_author_country, origin = "country.name", destination = "iso2c"))
-
-# Lets have a quick look at whether these are 'correct'
-  data2 %>% dplyr::select(submitting_author_country_code, submitting_author_country)  %>% distinct()
-
-# This looks good, but lets see which two are NA. These are in fact NA, even though they shouldn't really be as affliations are not listed on preprint. Even the published paper isn't clear. 
-  data2 %>% filter(is.na(submitting_author_country_code))  %>% data.frame()
-
-# Now we can use the first name and the country (that's important) to get an idea of the persons gender. 
-  #genders <- genderize(data2$submitting_author_firstname, country_id = data2$submitting_author_country_code, simplify = FALSE)
- # write.csv(genders, here("data", "gender_dat.csv"))
-
- ##### ADDED BY ML"  
-## testing - delhi later
-#gender(c("Madison", "Hillary"), years = 2000, method = "ssa")
-#gender(c("Madison", "Hillary"), method = "genderize") #works ok until limit of 100 is reached
-#gender(data3$submitting_author_firstname, method = "genderize") #works ok until limit of 100 is reached
-
-# data3 <-  data2[1:100, ] #subset for testing
-# gender(data3$submitting_author_firstname) -> data3_genders
-# dim(data3_genders) #83 names assigned
-## EDN testing
-
-# Get gender using all unique first names from the data set
-data_genders <- data.frame(gender(unique(data2$submitting_author_firstname)))
-dim(data_genders) #514 assigned
-#names(data_genders)
-
-# Merge with main data frame
-#unique(data_genders$name)
-data_genders <- rename(data_genders, submitting_author_firstname = name)
-data3 <- left_join(data2, data_genders, by = c("submitting_author_firstname"))
-#names(data3)
-table(is.na(data3$proportion_male)) #157 missing
-
-# Plot probabilities of gender assignment
-ggplot(data3, aes(x = `proportion_male`)) +
-  geom_histogram(fill = "grey", color = "black") +
-  labs(x = "gender assignment probability (male)", y = "Number of preprints") +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
-table(data3$proportion_male > 0.05 & data3$proportion_male < 0.95) #84 names bit unsure
-
-# Pull out records missing names
-#data3[is.na(data3$proportion_male), c("submitting_author", "submitting_author_country") ] #157 missing
-#data3[is.na(data3$proportion_male) == FALSE & data3$proportion_male > 0.05 & data3$proportion_male < 0.95, c("submitting_author", "submitting_author_country") ] # 84 missing a bit unsure
-
-#transliterate the non-ASCII characters using stringi package, e.g.: #stri_trans_general("Zażółć gęślą jaźń", "Latin-ASCII")
-data3$submitting_author_ASCII <- stringi::stri_trans_general(data3$submitting_author, "Latin-ASCII")
-
-#data3 %>% 
-  #filter(is.na(data3$proportion_male) == TRUE | (proportion_male > 0.05 & proportion_male < 0.95)) %>% dplyr::select(submitting_author_ASCII, submitting_author, submitting_author_country, preprint_title, gender) %>%
- # write.csv(file = here("data", "final_data3_fillin.csv")) #used to manually check and fill in gender data - then saved as final_data3_fillin_ML.csv
-
-# Load updated data	subset
-data3_update <- read_csv(here("data", "final_data3_fillin_ML.csv"))
-dim(data3_update)
-names(data3_update)
-
-data4 <- left_join(data3, data3_update, by = c("submitting_author_ASCII", "submitting_author", "submitting_author_country", "preprint_title"))
-#table(data4$gender.x, useNA = "always")
-#table(data4$gender.y, useNA = "always")
-data4$gender.x[is.na(data4$gender.x)] <- data4$gender.y[is.na(data4$gender.x)] #replace with correct values
-data4 <- rename(data4, gender = gender.x)
-table(data4$gender, useNA = "always") #more males than females, two NA ue to missing first name / collective authorship
-
-```
-
 ## Preprint citations versus published article citations
@@
 Interestingly, a highly cited preprint did not necessarily become a highly cited published article over time, although some of this descrepency is related to whether and how preprints and articles are linked through crossref (Spearman Rank Correlation: `r spear$estimate`, S = `r spear$statistic`, *p* = `r spear$p.value`; @fig-citations).
-
-## Data and code sharing in preprints
-
-```{r, fig-data}
-#| label: fig-data
-#| fig-cap: Percentage of preprints on *EcoEvoRxiv* that have data and code available.
-
-# Summary of the data
-  preprint_data <- data2  %>% tabyl(data_link_preprint_cleaned) 
-  preprint_code <- data2  %>% tabyl(code_link_preprint_cleaned) 
-  article_data <- data2  %>% tabyl(data_link_article_cleaned) 
-  article_code <- data2  %>% tabyl(code_link_article_cleaned)
-
-# Check if it was shared not in preprint but then in article
-  pre_article_data <- data2   %>%  filter(!data_link_preprint_cleaned == "not applicable") %>% mutate(data_shared = ifelse(data_link_preprint_cleaned == "no" & data_link_article_cleaned == "yes", "yes", ifelse(code_link_preprint_cleaned == "yes" & code_link_article_cleaned == "yes", "always", "no")))  %>% tabyl(data_shared)
-  pre_article_code <- data2  %>%  filter(!data_link_preprint_cleaned == "not applicable") %>% mutate(code_shared = ifelse(code_link_preprint_cleaned == "no" & code_link_article_cleaned == "yes", "yes", ifelse(code_link_preprint_cleaned == "yes" & code_link_article_cleaned == "yes", "always", "no")))  %>% tabyl(code_shared)
-
-```
-
-Data and code sharing is a key component of open science.
-Despite this, we found that `r preprint_data[1,2]` (`r preprint_data[1,"percent"]*100`%) of relevant preprints on *EcoEvoRxiv* (i.e., only where data was generated) did not share data, while `r preprint_code[1,2]` (`r preprint_code[1,"percent"]*100`%) did not share code.
-
-Authors may be reluctant to share data in code for preprints because of the perceived concern that others may acquire and use such data and code without authors' consent.
-However, while we found that `r pre_article_data[3,2]` (`r pre_article_data[3,"percent"]*100`%) of preprints that did not share data at the preprint stage did in the published article, there were still `r pre_article_data[2,2]` (`r pre_article_data[2,"percent"]*100`%) that never ended up sharing data.
-The same was true for code.
-Overall, while `r pre_article_code[3,2]` (`r pre_article_code[3,"percent"]*100`%) of preprints that did not share code at the preprint stage did in the published article, there were still `r pre_article_code[2,2]` (`r pre_article_code[2,"percent"]*100`%) that never ended up sharing code.
-
-## Peer Community In recommendations
-
-```{r, fig-pci}
-#| label: fig-pci
-#| fig-cap: Number of preprints on *EcoEvoRxiv* that have been recommended by Peer Community In.
-
-# How many articles were PCI recomended
-  pci <- data2  %>% tabyl(pci_recommendation_preprint)  
-```
-
-Out of the `r nrow(data2)` preprints, only `r pci[2,2]` (`r pci[2,3]*100`%) used Peer Community In as a preprint peer-review service.
-
-## Title changes between preprint and published article
-
-```{r, fig-title} 
-titles <- data2 %>%  filter(!is.na(publication_doi)) %>% tabyl(publication_title_changed)
-```
-
-It was reasonably common for titles of preprints to change between the preprint and the published article (`r titles[2,2]` or `r titles[2,3]*100`%).
-This was a major contributer to preprints and published articles not being matched in Google Scholar as they were not picked up by crossref linking services.
-As such, we would recomend that authors make sure that, when preprints end up getting pusblished, that they update preprints with the publication DOI when it's available.
-This is quite easy for authors to do in *EcoEvoRxiv* and it will ensure that the preprint is linked to the published article and the citations are merged and the published paper is ultimately open access, allowing authors to save open access fees.
-
-# References

### 2024-04-29 ms/ms.qmd
Fixing up comments from Losia and Shinichi. Need to work on figures, conclusion and reporting a few numbers..just check

--- 2024-04-19 ms/ms.qmd
@@
 
-Authors: Daniel W.A. Noble ^1^ $\ddagger$, Shinichi Nakagawa^2^, Hackathon Participants, Malgorzata Lagisz^2^
+Authors: Daniel W.A. Noble ^1^, $\ddagger$, Hackathon Participants, Shinichi Nakagawa^2,\*^,Malgorzata Lagisz^2,\*^
 
@@
 
+\* equal contribution
+
 # Introduction
@@
 Publishing preprints -- papers communicating non-peer-reviewed research findings -- is now an entrenched practice across a multitude of scientific disciplines [@Ginsparg2011].
-While preprint use in biology has had a slower uptake [@Berg2016], in ecology and evolution, new discipline specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disseminate research findings.
-Such practices are expected to promote open science and facilitate the rapid sharing of new discoveries that can have significant impacts on fundamental and applied knowledge globally.
+While preprint use in biology has had a slower uptake [@Berg2016], in ecology and evolution, new discipline-specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disseminate research findings.
+Preprints are expected to promote open science and facilitate the rapid sharing of new discoveries that can have significant impacts on fundamental and applied knowledge globally.
+Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed, visibility and output of research findings; 2) helping establish precedence of research findings; 3) removing financial barriers to publication; and 4) encouraging constructive and critical feedback from a research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
 
-Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed, visibility and output of research findings; 2) encouraging constructive and critical feedback from a research community; 3) helping establish precedence of research findings; and 4) removing financial barriers to publication [@Proulx2013; @bourne2017ten; @vale2015accelerating].
-*EcoEvoRxiv* is a community driven preprint server that has paved the way for new initiatives, including accepting multilingual preprints, recognising and accepting registered reports and non-traditional research reports, and promoting peer review and community discussion to improve the quality of preprints and speed up their peer-reviewed publication (e.g., Peer Community In -- PCI).
+Preprint servers can empower researchers to make their findings more accessible, open and transparent but only if they are used well and initiatives are widely known.
+Significant barriers to preprint use still exist globally – from lack of clarity around preprint policies at journals [@Klebel2020] to a stigma that preprints are viewed by a research community to be of poor quality [@Chiarelli2019] (but see [@Faser2022]).
+Nonetheless, we lack a systematic understanding of the factors that influence preprint use in ecology and evolution which can help inform future initiatives, improve others, and allow us to work harder in further breaking down barriers to their use in our field.
 
-Preprint servers, such as *EcoEvoRxiv*, can empower researchers to make their findings more accessible, open and transparent but only if they are used well and initiatives are widely known.
-Significant barriers to preprint use still exist globally – from lack of clarity around preprint policies at journals [@Klebel2020] to a stigma that preprints are viewed by a research community to be of poor quality [@Chiarelli2019] (but see [@Faser2022]).
-Nonetheless, we lack a systematic understanding of the factors that influence preprint use in ecology and evolution which can help inform future initiatives, improve others, and allow us to work harder in further break down barriers to their use in our field.
+*EcoEvoRxiv* is one of the few community driven preprint servers that has paved the way for new initiatives, including accepting multilingual preprints, recognising and accepting registered reports and non-traditional research reports, and promoting peer review and community discussion to improve the quality of preprints and speed up their peer-reviewed publication (e.g., Peer Community In -- PCI).
 
-Here, we explore the first preprints uploaded to *EcoEvoRxiv*, one of the few community run preprint servers, to understand preprint practices and use in ecology and evolution.
-We focus our attention on understanding better: 1) what countries make use of preprints; 2) the extent to which authors make use of preprint servers for registered reports and community driven peer review  3) how career stage and gender impact preprint use; 4) whether data and code are more likely to be shared in preprints; and 5) how long it takes for a preprint to become published, and how many preprints remain unpublished.
+Here, we explore the first preprints uploaded to *EcoEvoRxiv* to understand preprint practices and use in ecology and evolution.
+We focus our attention on understanding better: 1) what countries authors that preprint are located; 2) how career stage and gender impact preprint use; 3) the extent to which authors make use of preprint servers for registered reports and community-driven peer review; 4) whether data and code are more likely to be shared in preprints; and 5) how long it takes for a preprint to become published, and how many preprints remain unpublished.
 In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other servers which we think will help further educate researchers about the benefits of using community driven preprint servers to post their research findings.
@@
 *EcoEvoRxiv* is run by the Society for Open, Reliable, and Transparent Ecology and Evolution (SORTEE).
+Originally launched in 2018 on the Center for Open Science preprint platforms, *EcoEvoRxiv* has grown to become a popular preprint server for researchers in ecology and evolution.
+It has since been adopted by the California Digital Library (CDL) to be hosted in perpetuity without fees.
 Editors are researchers across the globe in the fields of ecology and evolution who volunteer their time to screen papers and push new initiatives in the preprint space.
-To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the articles available on *EcoEvoRxiv* as of `r gsub("UTC", "", dates[2])`.
 *EcoEvoRxiv* accepts both preprints and postprints.
@@
 Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication (assuming the journal has a preprint policy that recognises preprints - though most do).
-For the purpose of summarising articles on *EcoEvoRxiv* we include both preprints and postprints in our 'demographics' analysis.
+To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the articles available on *EcoEvoRxiv* as of `r gsub("UTC", "", dates[2])`.
+For the purpose of summarising articles on *EcoEvoRxiv* we include both preprints and postprints as 'articles' in our overview analysis.
 
@@
 #| fig-cap: Summary of articles posted to *EcoEvoRxiv*.
-A) Number of preprints and postprints published monthly to *EcoEvoRxiv* between 2018 and 2023; B) Countries that are posting articles (preprints and postprints) to *EcoEvoRxiv*; C) Taxa used / covered in the articles posted to *EcoEvoRxiv*; D) Types of articles accepted on *EcoEvoRxiv*.
+A) Number of articles (preprints and postprints) published monthly to *EcoEvoRxiv* between 2018 and 2023; B) Countries that are posting articles (preprints and postprints) to *EcoEvoRxiv* as inferred from the country of affiliation of the submitting author; C) Taxa used / covered in the articles posted to *EcoEvoRxiv*; D) Types of articles accepted on *EcoEvoRxiv*.
 E) Career stage of authors posting to *EcoEvoRxiv* along with the gender of the submitting author.
@@
     theme_void() + labs(fill = "Article Type") + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")
+
+nt <- sum_types  %>% filter(type %in% c("book", "report", "book chapter", "other"))  %>% summarise(perc = sum(perc))
 
@@
 
-### *Demographics of **EcoEvoRxiv** preprints (and postprints)*
+### *Overview of **EcoEvoRxiv** preprints (and postprints)*
 
-After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissons for the same preprint rather than updating an existing submission – we had data for a total of `r pr` articles with ~55-60 preprints published each month in the last two years ([@fig-summary]A).
-A total of `r length(unique(countries$country))-1` countries have used *EcoEvoRxiv* as a preprint server.
-Unsurprisingly, countries in North America and Europe preprint more exstensively.
-Countries in Africa, Central America and parts of Asia are still slow to use *EcoEvoRxiv* ([@fig-summary]B).
+After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissions for the same preprint rather than updating an existing submission – we had data for a total of `r pr` articles with ~55-60 preprints published each month in the last two years ([@fig-summary]A).
+Authors from a total of `r length(unique(countries$country))-1` countries have used *EcoEvoRxiv* as a preprint server.
+Unsurprisingly, authors from countries in North America and Europe upload the most preprints.
+Authors from countries in Africa, Central America and parts of Asia still do not use *EcoEvoRxiv* much ([@fig-summary]B).
 Overall, 90% of the articles come from just `r nrow(most_use)-1` countries.
-Articles covered all major taxomic groups, with the most common being vertebrates (`r sum_taxa$perc[6]`%), plants (`r sum_taxa$perc[1]`%) and invertebrates (`r sum_taxa$perc[5]`%) ([@fig-summary]C).
+Articles covered all major taxonomic groups, with the most common being vertebrates (`r sum_taxa$perc[6]`%), plants (`r sum_taxa$perc[1]`%) and invertebrates (`r sum_taxa$perc[5]`%) ([@fig-summary]C).
 
@@
 
-Given that *EcoEvoRxiv* is a community driven preprint server it has managed to diversify the types of articles accepted.
-It accepts reports and books that are often not easily accessible, but may contain important data of relevance to research syntheses.
-Accepting a greater diversity of article types allows *EcoEvoRxiv* to begin dealing with the 'grey literature' problem [@haddaway2015shades; @haddaway2020eight].
-As a result, articles on *EcoEvoRxiv* are more diverse in nature than other preprint servers; nonetheless, typical research articles (`r sum_types[sum_types$type == "research article",]$perc`%) are still the most common type of preprint, followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]D).
+Given that *EcoEvoRxiv* is a community-driven preprint server it has managed to diversify the types of articles accepted.
+It accepts reports and books that are often not easily accessible, but may contain important data of relevance to research syntheses or for practitioners.
+As a result, articles on *EcoEvoRxiv* are more diverse in nature than those on other preprint servers; nonetheless, typical research articles (`r sum_types[sum_types$type == "research article",]$perc`%) are still the most common type of preprint, followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]D).
 
-Reports, parcticularly from government and industry research areas exist but are not yet common on *EcoEvoRxiv*.
+Accepting a greater diversity of article types allows *EcoEvoRxiv* to begin dealing with the 'grey literature' problem whereby data that are relevant for research syntheses are not published in typical peer-reviewed journals[@haddaway2015shades; @haddaway2020eight].
+This is reflected by `r nt`% of articles that could be considered ‘grey literature’ in ecology and evolutionary biology: books, book chapters, reports, and other research output types.
+Currently, *EcoEvoRxiv* does not host many reports (`r sum_types[sum_types$type == "report", "perc"]`%), particularly from government and industry.
 We would encourage authors to consider posting these types of articles to ensure they are openly accessible and more easily found.
 *EcoEvoRxiv* has already formed fruitful partnerships with the International Union for Conservation of Nature (IUCN) to be a place where their reports can be lodged to make them more easily accessible to the broader research community.
-For example, IUCN Red Ecosystem Reports are now posted to *EcoEvoRxiv* and our community has been able to work closely with the IUCN to ensure these reports meet the IUCN requirements.
-Such reports often contain important data that can be leveraged for research syntheses and meta-analyses.
+For example, IUCN Red Ecosystem Reports are now posted to *EcoEvoRxiv* and our community has been able to work closely with the IUCN to ensure these documents meet the IUCN requirements.
 
@@
 Communication of research through a single language has major consequences for the global distribution of knowledge resulting in knowledge gaps in some of the most biodiverse and threatened regions in the world [@amano2023role; @zenni2023multi].
-Such gaps also have flow on effects for research syntheses and meta-analyses because it creates a distorted picture of our knowledge base that can lead to bias and inadequate sampling that affects policy development and decision making [@hannah2024language; @zenni2023multi; @white2021geographical; @konno2020ignoring].
+Such gaps also have flow on effects for research syntheses and meta-analyses because they create a distorted picture of our knowledge base that can lead to bias and inadequate sampling that affects policy development and decision making [@hannah2024language; @zenni2023multi; @white2021geographical; @konno2020ignoring].
 
 *EcoEvoRxiv* is the only preprint server breaking down language barriers to scientific communication; currently accepting English, Spanish, Portuguese and French manuscripts.
-Such initiatives are incredibly important if we are to begin filling global voids of scientitic knowledge.
-Multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish preprints posted to date, and none in other accepted langauges (e.g., French and Portuguese).
+Such initiatives are incredibly important if we are to begin filling global voids of scientific knowledge.
+Multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish preprints posted to date, and none in other accepted languages (e.g., French and Portuguese).
 Part of the challenge in getting authors to submit non-English preprints is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries and the fact that it accepts preprints in different languages, cultural differences in the perception of preprints and a strong reliance on traditional publishing models, which typically favour publishing in English.
@@
 Research papers take time to be published (see below).
-Early and mid career researchers (ECMRs) need their research to come out quickly for job applications, promotion and obtaining grants to accerate their careers [@vale2015accelerating; @sarabipour2019value].
-Preprints are one way ECMRs can acheive faster dissemination and greater visibility.
-As such, we expect ECMRs to accept and adopt preprints more than later career colleagues.
-At the same time, gender differences in preprint use and publication outcomes  have been established in a number of other research fields, including in ecology and evolution [@fox2019gender; @wehner2020comparison].
-We therefore expect such discrepencies to manifest in preprint use on *EcoEvoRxiv*, but it is unclear to what extent.
-Understanding gender publishing patterns is challenging with observational data such as ours because we cannot know the gender of authors for certainty but we can use a data driven approach to ascertain the probability that a particular name is of a given gender (male or female).
-To obtain an idea of an authors' gender, we used the R package *DemografixeR* (vers.
-`r utils::packageVersion("DemografixeR")`; @RJ-2016-002) to predict the most likely gender of the submitting author of a preprint.
-We incorperated information about the submitting authors country of affiliation to better account for differences across countries.
-We only used names where the gender was identified with 95% certainty.
+Early and mid-career researchers (ECMRs) need their research to come out quickly for job applications, promotion and obtaining grants to accelerate their careers [@vale2015accelerating; @sarabipour2019value].
+Preprints are one way ECMRs can achieve faster dissemination and greater visibility.
+As such, we expect ECMRs to accept and adopt preprints more than colleagues at later career stages.
+At the same time, gender differences in preprint use and publication outcomes  have been observed in a number of other research fields, including ecology and evolution [@fox2019gender; @wehner2020comparison].
+We therefore expect such discrepancies to manifest in preprint use on *EcoEvoRxiv*, but it is unclear to what extent.
+Understanding gender publishing patterns is challenging with observational data such as ours because we cannot know the gender of authors for certainty but we can use a data-driven approach to ascertain the probability that a particular name is of a given gender (male or female).
+To obtain an idea of an author's gender, we used the R package *gender* (vers.
+`r utils::packageVersion("gender")`; @mullen2021predict) to predict the most likely gender of the submitting author of a preprint.
+We only used algorithm-assigned names where the gender was identified with 95% certainty.
+For the remaining names, we performed manual searches to determine gender based on the pronouns and photographs from professional and personal websites (we acknowledge that our approach does not capture self-assigned and non-binary genders).
+Our data on gender has only two missing values – one where the first name of the submitting author was missing and the other one for a collective submission.
 
@@
 The majority of preprints were submitted by authors who published their first paper in the last 10 years ([@fig-summary]E), with the median year of first publication of submitting authors being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r round(mean(data2$submitting_author_first_publication_year, na.rm = TRUE),0)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`).
-These preprinting practices support the idea that ECMRs may value preprints as a way to make their work more visible and disseminate their finding more quickly.
+These patterns support the expectation that ECMRs may value preprints as a way to make their work more visible and disseminate their finding more quickly.
 
@@
 ### *Science takes time, but publication could take longer*
-Increased competition in science has resulted in the bar being raised with respect to the amount of data required for publication [@vale2015accelerating].
+Increased competition in science has raised the bar with respect to the amount of data required for publication [@vale2015accelerating].
 This is a good outcome if it results in higher impact research that better clarifies our understanding of the natural world, but it does come at a cost for the rate at which research findings can be disseminated [@vale2015accelerating].
-Preprinting has been proposed as a way research can be disseminated more quickly as it can take a long time before results are ultimately published [@bourne2017ten; @vale2015accelerating].
-However, data on the time to publication is sparse, and the real benefit of preprints in this context would be reinforced if preprinting is able to dramatically speed up dissemination.
-We evaluated just how much time it takes to publish a research paper in ecology and evolution by ascertaining the time between when a preprint was first posted to when it was finally accepted in a research journal.
-In total, `r unpub` papers were still unpublished out of the `r nrow(data2)` (`r (unpub / nrow(data2))*100`%) at the time these data were collected.
-Astonishingly, the maximum time between submission and publication was `r sum_preprints$max` days ([@fig-pubsummary]A), and the median time to publication was `r sum_preprints$median` days (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days).
+Preprinting has been proposed as a way to disseminate research more quickly as it can take a long time before results are ultimately published [@bourne2017ten; @vale2015accelerating].
+However, data on the time to publication is sparse, and the real benefit of preprints in this context would be reinforced if preprinting can dramatically speed up dissemination.
+We evaluated how long it takes to publish a research paper in ecology and evolution by ascertaining the time between when a preprint was first posted and finally accepted in a research journal.
+In total, `r unpub` papers were still unpublished out of the `r nrow(data2)` (`r (unpub / nrow(data2))*100`%) when these data were collected.
+Astonishingly, the maximum time between preprint submission and publication was `r sum_preprints$max` days or `r sum_preprints$max/365` years ([@fig-pubsummary]A), and the median time to publication was `r sum_preprints$median` days (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days).
 Our results largely confirm the long timespans most authors are dealing with to get their research published after the paper is written.
@@
 ### *Cautious 'open'-mindedness of research in preprints*
-In additon to speeding up dissemination, preprints can also be a useful way to ensure that research remains open and accessible to the research community because the paper is available online no matter what the open access status of the publication ends up being [@bourne2017ten; @vale2015accelerating].
-Using the published articles on *EcoEvoRxiv*, we evaluated the open access status of each paper using....LOSIA?.
-Most of the published preprints ended up being open access([@fig-pubsummary]A), however, the status of many (i.e., `r sum_is_oa$n[3]` or `r sum_is_oa$percent[3]*100`%) were unknown, and `r sum_is_oa$n[1]` or `r sum_is_oa$percent[1]*100`% were not published in open access reserach journals.
-The level of open access for a paper published in an open access journal also varied widely ([@fig-pubsummary]B).
+In addition to speeding up dissemination, preprints can also be a useful way to ensure that research remains open and accessible to the research community because the paper is available online no matter what the open access status of the publication ends up being [@bourne2017ten; @vale2015accelerating].
+Using the published articles on *EcoEvoRxiv*, we evaluated the open access status of each paper using the R package *roadoi* to connect to Unpaywall platform [@jahn2024].
+Most of the published preprints ended up being open access ([@fig-pubsummary]A), however, the status of many `r sum_is_oa$n[3]` (`r sum_is_oa$percent[3]*100`%) were unknown, and `r sum_is_oa$n[1]` (`r sum_is_oa$percent[1]*100`%) were not published in open access research journals.
+The level of open access for a paper published in an open-access journal also varied widely ([@fig-pubsummary]B).
 
-Data and code sharing is also a key component of open science [@roche2015public].
-In the spirit of 'openness' we expected data and code sharing among preprints to be better than many papers published in research journals [@roche2015public; @o2021preferred].
+Data and code sharing are also key components of open science [@roche2015public].
+In the spirit of 'openness' we expected data and code sharing among preprints to be better than in many papers published in research journals [@roche2015public; @o2021preferred].
 Despite this, we found that `r preprint_data[1,2]` (`r preprint_data[1,"percent"]*100`%) of relevant preprints on *EcoEvoRxiv* (i.e., only where data was generated) did not share data, while `r preprint_code[1,2]` (`r preprint_code[1,"percent"]*100`%) did not share code.
-Authors may be reluctant to share data in code for preprints because of the perceived concern that others may acquire and use such data and code without authors' consent.
-However, while `r pre_article_data[3,2]` (`r pre_article_data[3,"percent"]*100`%) of preprints that did not share data at the preprint stage did ultimately share data in the published article, there were still `r pre_article_data[2,2]` (`r pre_article_data[2,"percent"]*100`%) that never ended up sharing data.
+Authors may be reluctant to share data and code for preprints because of the perceived concern that others may acquire and use such data and code without authors' consent.
+However, while `r pre_article_data[3,2]` (`r pre_article_data[3,"percent"]*100`%) of preprints that did not share data at the preprint stage did ultimately share data in the published article, there were still `r pre_article_data[2,2]` (`r pre_article_data[2,"percent"]*100`%) that never shared data.
 The same was true for code.
-Overall, `r pre_article_code[3,2]` (`r pre_article_code[3,"percent"]*100`%) of preprints did not share code at the preprint stage but did in the published article, however, there were still `r pre_article_code[2,2]` (`r pre_article_code[2,"percent"]*100`%) that never ended up sharing code.
-Code and data sharing patterns in our sample of preprints is consistent with other analyses looking at code and data sharing in published articles (e.g., [@o2021preferred]), even for journals that have strict public data archiving policies [@roche2015public].
+Overall, `r pre_article_code[3,2]` (`r pre_article_code[3,"percent"]*100`%) of preprints did not share code at the preprint stage but did in the published article; however, `r pre_article_code[2,2]` (`r pre_article_code[2,"percent"]*100`%) never shared code.
+Code and data- sharing patterns in our sample of preprints are consistent with analyses of published articles (e.g., [@o2021preferred]), even for journals with strict public data archiving policies [@roche2015public].
 
-# Paving *our* own future of open, transparent and community driven science
+# Paving *our* own future of open, transparent and community-driven science
 
-Our data driven approach has allowed us to better understand some of the key elements of uncertainty surrounding preprints and identify shortcomings and areas needing greater clarity to authors.
-A number of key insights can be gleaned upon from an analysis of the first *EcoEvoRxiv* preprints.
+Our data-driven approach has allowed us to better understand some of the key elements of uncertainty surrounding preprints and identify shortcomings and areas needing greater clarity to authors.
+Several key insights follow from our analysis of the first *EcoEvoRxiv* preprints.
 
@@
 Sharing data and code early can help improve the quality of research, establish precedence, and improve the transparency and computational reproducibility of scientific findings [@sarabipour2019value].
-If authors are worried about data being used unintentially, clear information surrounding its re-use and withholding some data or meta-data needed to understand the dataset may be options.
-- Second, authors need to be aware of the benefits of posting preprints and postprints for constructive feedback [@bourne2017ten].
-While it is clear preprints help establish precedence and allow findings to be openly accessible it is still rare that constructive discussions form around preprints in an open form, which is consistent with findings on other preprint servers (e.g.
-BioRxiv [@anderson2020biorxiv]).
-It is clear that we, as a community, need to provide better platforms that document discussions around a preprint findings.
-Such discussions are useful for the authors to help improve their work and communicate their findings more effectively (when done constructively, of course).
-One way to facilitate such discussions may be to use open peer reviewing serves such as *Peer Community In* (PCI) or *PubPeer* to provide feedback on preprints that ultimately are associated with a preprint.
+If authors are worried about data being used unintentionally, clear information surrounding its reuse and withholding some data or meta-data needed to understand the dataset may be options.
+- Second, authors need to be aware of the benefits of posting preprints and post-prints for constructive feedback [@bourne2017ten].
+While it is clear preprints help establish precedence and allow findings to be openly accessible, it is still rare that constructive discussions form around preprints in an open form, which is consistent with findings on other preprint servers (e.g.
+bioRxiv [@anderson2020biorxiv]).
+Clearly, as a community, we need to provide better platforms that document discussions around preprint findings.
+Such discussions help the authors improve their work and communicate their findings more effectively (when done constructively, of course).
+One way to facilitate such discussions may be to use open peer reviewing services such as *Peer Community In* (PCI) or *PubPeer* to provide feedback on preprints that ultimately is associated with a preprint.
 - Third, it remains clear that the time between preprinting and publication is still quite long.
-One possible explanation is that preprints are not being sent to journals deemed suitable for the work.
+One possible explanation is that preprints are not being sent to suitable journals.
 Interestingly, out of the `r nrow(data2)` preprints, only `r pci[2,2]` (`r pci[2,3]*100`%) used Peer Community In (PCI) as a preprint peer-review service.
 Using PCI provides authors with quicker reviews of a paper and a more realistic recommendation of where such work is likely to be published.
-Many journals now also accept PCI reviews and recomendations when deciding to publish a paper.
+Many journals now also accept PCI reviews and recommendations when publishing a paper.
 As such, we would encourage more authors to consider sending their preprints for PCI review to possibly speed up the publication process.
-- Finally, while most preprints get seemlessly connected with and merged with their published version some remain disconnected.
+- Finally, while most preprints get seamlessly connected with and merged with their published version some remain disconnected.
 Incorrect cross-linking can create confusion and lead to frustration among authors.
-Thankfully, the reasons for unmatched preprints and publications are fairly well understood and easily rectified.
-They often result from a mismatch between titles or authors in preprint and published metadata.
+Thankfully, the reasons for unmatched preprints and publications are well understood and easily rectified.
+They often result from a mismatch between preprint and published metadata (e.g., titles and author details).
 In fact, it was reasonably common for titles of preprints to change between the preprint and the published article (`r titles[2,2]` or `r titles[2,3]*100`%).
-Mismatched metadata was almost always the main contributer to preprints and published articles not being matched automatically in Google Scholar during our data collection.
-We recommend that authors make sure that, when preprints end up getting published, they update their preprint with the publication DOI when it is available.
-Particularly if their title has changed.
-This is quite easy for authors to do in *EcoEvoRxiv* and it will ensure that the preprint is linked to the published article and the citations are merged.
-It will also create a link between the final preprint and the published paper so that, no matter the open access status of the publication, the reserach findings will remain openly accessible, saving costs for authors and improving the visibility and use of research.
+We found that mismatched metadata almost always contributed to preprints and published articles not being matched automatically in Google Scholar.
+We recommend that authors ensure that, when preprints are published in a journal, they update their preprint with the publication DOI.
+Especially if their title has changed, this is quite easy for authors to do on *EcoEvoRxiv*, and it will ensure that the preprint is linked to the published article and that the citations are merged.
+It will also create a link between the final preprint and the published paper so that, no matter the open access status of the publication, the research findings will remain openly accessible, saving costs for authors and improving the visibility and use of research.
 
-Despite the early successes of the new initiatives taken by *EcoEvoRxiv* it is still clear that much work needs to be done to improve our communities understanding of preprints (and postprints).
+Despite the early successes of the new initiatives taken by *EcoEvoRxiv*, much work needs to be done to improve our community’s understanding and use of preprints (and post-prints).
 We view this perspective piece as one small step in achieving that goal.
-Authors also need to be aware of the benefits of using community driven preprint servers and the unique initiatives being pursued.
-Community driven preprint servers are capable of setting their own agenda and are driven by the needs and disires of the community they would like their findings to be shared with.
-Supporting these initiatives should be a priority for all researchers and those volunteering their time at *EcoEvoRxiv* remain open to new and innovative ways to improve publication and open science practices.
-We believe that the future of preprints is bright and community driven initiatives, such as *EcoEvoRxiv*, are set to play a key role in the future of scientific publishing.
+Authors must also be aware of the benefits of using community-driven preprint servers and the unique initiatives being pursued.
+Community-driven preprint servers are capable of setting their own agenda and are driven by the needs and desires of the community.
+Supporting these initiatives should be a priority for all researchers.
+Volunteers at *EcoEvoRxiv* should remain open to new and innovative ways to improve publication and open science practices.
+We believe that the future of preprints is bright, and community-driven initiatives, such as *EcoEvoRxiv*, are set to play a crucial role in the future of scientific publishing.
 
-# Awknowledgements
-We would like to thank the California Digitial Library (CDL) and the CDL team (particularly Alainna Wrigley) for their support in hosting and maintaining *EcoEvoRxiv* for the Society for Open, Reliable, and Transparent Ecology and Evolution (SORTEE).
+# Acknowledgements
+We would like to thank the California Digital Library (CDL) and the CDL team (particularly Alainna Wrigley) for their support in hosting and maintaining *EcoEvoRxiv* for the Society for Open, Reliable, and Transparent Ecology and Evolution (SORTEE).
 We would also like to thank Gabriela Hidalgo and Daisy Larios for helping connect us with the IUCN and facilitating discussions to make *EcoEvoRxiv* a place where IUCN reports can be posted.
-Finally, we would also like to thank the endless number of SORTEE volunteers, and those especially on the *EcoEvoRxiv* Commitee, who have helped to make *EcoEvoRxiv* a success.
+Finally, we would also like to thank the endless number of SORTEE volunteers, and those especially on the *EcoEvoRxiv* Committee, who have helped to make *EcoEvoRxiv* a success.
 This paper emerged from a hackathon at the 2022 SORTEE conference, and we thank delegates who attended the session but could not be part of this paper.

### 2024-04-30 ms/ms.qmd
Fix fig 2 to have some colour

@@
 #install.packages("pacman")
-remotes::install_github("lmullen/genderdata")
+#remotes::install_github("lmullen/genderdata")
 pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, gender,genderdata, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot, viridis, cowplot, magick)
@@
 
+  dates_preprints <- range(preprints$preprint_published_date)
 ##---------------------##
@@
 
-p3_pub <- preprints  %>% ggplot(aes(x = oa_status)) + geom_bar() + labs(x = "Open Access Status", y = "Number of Papers") + theme_classic() + theme(axis.title = element_text(size = 14))
+p3_pub <- preprints  %>% ggplot(aes(x = oa_status, fill = oa_status)) + geom_bar() + labs(x = "Open Access Status", y = "Number of Papers") + theme_classic() + theme(axis.title = element_text(size = 14)) + scale_fill_manual(values = c("bronze" = "#9b6023", "gold" = "#ffd700", "green" = "#008000", "hybrid" = "#6fa8dc", "NA" = "grey", "closed" = "black"))
 

### 2024-04-30 ms/ms.qmd
Update to figs

@@
 *EcoEvoRxiv* is run by the Society for Open, Reliable, and Transparent Ecology and Evolution (SORTEE).
-Originally launched in 2018 on the Center for Open Science preprint platforms, *EcoEvoRxiv* has grown to become a popular preprint server for researchers in ecology and evolution.
+Originally launched in 2018 on the Center for Open Science preprint platform, *EcoEvoRxiv* has grown to become a popular preprint server for researchers in ecology and evolution.
 It has since been adopted by the California Digital Library (CDL) to be hosted in perpetuity without fees.
@@
 #| fig-cap: Summary of articles posted to *EcoEvoRxiv*.
-A) Number of articles (preprints and postprints) published monthly to *EcoEvoRxiv* between 2018 and 2023; B) Countries that are posting articles (preprints and postprints) to *EcoEvoRxiv* as inferred from the country of affiliation of the submitting author; C) Taxa used / covered in the articles posted to *EcoEvoRxiv*; D) Types of articles accepted on *EcoEvoRxiv*.
+A) Number of articles (preprints and postprints) published monthly to *EcoEvoRxiv* between 2018 and 2023.
+*EcoEvoRxiv* was established in June 2018 before the soft launch in November 2018; B) Countries that are posting articles (preprints and postprints) to *EcoEvoRxiv* as inferred from the country of affiliation of the submitting author; C) Taxa used / covered in the articles posted to *EcoEvoRxiv*; D) Types of articles accepted on *EcoEvoRxiv*.
 E) Career stage of authors posting to *EcoEvoRxiv* along with the gender of the submitting author.
@@
 ##---------------------##
-
+  angle = 45
   p1 <- ggplot(data2, aes(x = preprint_pub_date)) +
@@
     theme_bw() +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")
-
+    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin") + ylim(0, 130) + 
+      # Soft Launch of EcoEvoRxiv
+    annotate( "segment", x = as.POSIXct("2018-07-01"),  xend = as.POSIXct("2018-07-01"), y = 0, yend = 82, color = "#ffd966", linetype = "dashed", size = 1.5) + 
+    annotate("text", x = as.POSIXct("2018-07-01"), y = 85, label = "Soft Launch", color = "#ffd966", size = 4, angle = angle, hjust = 0) +
+    # Launch of EcoEvoRxiv
+    annotate( "segment", x = as.POSIXct("2018-11-11"),  xend = as.POSIXct("2018-11-11"), y = 0, yend = 82, color = "#2986cc", linetype = "dashed", size = 1.5) + 
+    annotate("text", x = as.POSIXct("2018-11-11"), y = 85, label = "Launch", color = "#2986cc", size = 4, angle = angle, hjust = 0) +
+    # Spanish and Port
+    annotate( "segment", x = as.POSIXct("2023-02-14"),  xend = as.POSIXct("2023-02-14"), y = 0, yend = 82, color = "#3d85c6", linetype = "dashed", size = 1.5) + 
+    annotate("text", x = as.POSIXct("2022-11-14"), y = 85, label = "Spanish and Portug.", color = "#3d85c6", size = 4, angle = angle, hjust = 0) +
+    # Transition to CDL
+    annotate( "segment", x = as.POSIXct("2022-09-14"),  xend = as.POSIXct("2022-09-14"), y = 0, yend = 82, color = "#008000", linetype = "dashed", size = 1.5) + 
+    annotate("text", x = as.POSIXct("2022-07-14"), y = 85, label = "CDL", color = "#008000", size = 4, angle = angle, hjust = 0) +
+   # IUCN Red Eco submission 29 August 2023
+   # 1000 preprints
+    annotate( "segment", x = as.POSIXct("2023-08-29"),  xend = as.POSIXct("2023-08-29"), y = 0, yend = 82, color = "#cc0000", linetype = "dashed", size = 1.5) + 
+    annotate("text", x = as.POSIXct("2023-04-29"), y = 85, label = "IUCN Report", color = "#cc0000", size = 4, angle = angle, hjust = 0) 
 ##---------------------##
@@
 layout <- "
-##AAAA##
+#AAAAAA#
+#AAAAAA#
+#AAAAAA#
 BBBBBBBB
@@
 
-p3_pub <- preprints  %>% ggplot(aes(x = oa_status, fill = oa_status)) + geom_bar() + labs(x = "Open Access Status", y = "Number of Papers") + theme_classic() + theme(axis.title = element_text(size = 14)) + scale_fill_manual(values = c("bronze" = "#9b6023", "gold" = "#ffd700", "green" = "#008000", "hybrid" = "#6fa8dc", "NA" = "grey", "closed" = "black"))
+p3_pub <- preprints  %>% ggplot(aes(x = oa_status, fill = oa_status)) + geom_bar() + labs(x = "Open Access Status", y = "Number of Papers") + theme_classic() + theme(axis.title = element_text(size = 14), legend.position = "none") + scale_fill_manual(values = c("bronze" = "#9b6023", "gold" = "#ffd700", "green" = "#008000", "hybrid" = "#6fa8dc", "NA" = "grey", "closed" = "black"))
 

### 2024-04-30 R/4_author_affli.R
Add some code to avoid painful author details

@@ -1,0 +1,30 @@
+###–––––––––––––––––––––––––––––––––––––––––––––––––###
+# Purpose: Creating afffiliations and authors
+###–––––––––––––––––––––––––––––––––––––––––––––––––###
+###-------------------------###
+# Load packages
+###-------------------------###
+	pacman::p_load(tidyverse, googlesheets4, janitor, here)
+
+###-------------------------###
+# Load data from Google Sheets 
+# and save raw files
+###-------------------------###
+
+delegates <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Delegate Details")  %>%  clean_names()   %>% mutate(fullname = paste(firstname, lastname, sep = " "))  %>% arrange(lastname)  %>% filter(!is.na(fullname) & !fullname %in% c("Shinichi Nakagawa", "Daniel Noble", "Malgorzata Lagisz"))
+
+# Now that we have all the details lets create a markdown file that writes the authors and the afflitions
+yaml <- "---
+title: ""
+format:
+  docx:
+    reference-doc: ./bib/template.docx
+---"
+nums <- 1:length(delegates$fullname)
+sink("authors.qmd")
+writeLines(paste0(paste0(delegates$fullname, "^", nums,"^", collapse = ", ")), fileConn)
+cat("\n")
+writeLines(paste0(paste0("^", nums,"^", delegates$affiliation_school_department_organisation, sep = "\n", collapse = "\n")), fileConn)
+sink()
+
+

### 2024-04-30 ms/ms.qmd
updates

@@
 Finally, we would also like to thank the endless number of SORTEE volunteers, and those especially on the *EcoEvoRxiv* Committee, who have helped to make *EcoEvoRxiv* a success.
-This paper emerged from a hackathon at the 2022 SORTEE conference, and we thank delegates who attended the session but could not be part of this paper.
+This paper emerged from a hackathon at the 2023 SORTEE conference, and we thank delegates who attended the session but could not be part of this paper.
 DWAN would also like to thank the Australian Research Council for a Future Fellowship (FT220100276).

### 2024-04-30 ms/ms.qmd
Some fixes

@@
 #remotes::install_github("lmullen/genderdata")
-pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, gender,genderdata, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot, viridis, cowplot, magick)
+pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, gender,genderdata, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot, viridis, cowplot, magick, lme4, lmerTest)
 

### 2024-05-01 ms/ms.qmd
Starting a bit of clean up of the MS

@@
 ---
-title: "The promise of community driven preprints in ecology and evolution"
+title: "The promise of community-driven preprints in ecology and evolution"
 bibliography: ../bib/refs.bib
@@
 Preprints are expected to promote open science and facilitate the rapid sharing of new discoveries that can have significant impacts on fundamental and applied knowledge globally.
-Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed, visibility and output of research findings; 2) helping establish precedence of research findings; 3) removing financial barriers to publication; and 4) encouraging constructive and critical feedback from a research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
+Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed, visibility and output of research findings; 2) helping establish precedence of research findings; 3) removing financial barriers to publication; and 4) encouraging constructive and critical feedback from the research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
 
-Preprint servers can empower researchers to make their findings more accessible, open and transparent but only if they are used well and initiatives are widely known.
+Preprint servers can empower researchers to make their findings more accessible, open, and transparent but only if they are used well and initiatives are widely known.
 Significant barriers to preprint use still exist globally – from lack of clarity around preprint policies at journals [@Klebel2020] to a stigma that preprints are viewed by a research community to be of poor quality [@Chiarelli2019] (but see [@Faser2022]).

### 2024-05-01 ms/ms.qmd
Add a few refs and fix up intro

@@
 While preprint use in biology has had a slower uptake [@Berg2016], in ecology and evolution, new discipline-specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disseminate research findings.
-Preprints are expected to promote open science and facilitate the rapid sharing of new discoveries that can have significant impacts on fundamental and applied knowledge globally.
+Preprints are expected to promote open science, increase the visibility of research (e.g., [fu2019releasing]), and facilitate the rapid sharing of new discoveries that can have significant impacts on fundamental and applied knowledge globally.
 Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed, visibility and output of research findings; 2) helping establish precedence of research findings; 3) removing financial barriers to publication; and 4) encouraging constructive and critical feedback from the research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
 
-Preprint servers can empower researchers to make their findings more accessible, open, and transparent but only if they are used well and initiatives are widely known.
-Significant barriers to preprint use still exist globally – from lack of clarity around preprint policies at journals [@Klebel2020] to a stigma that preprints are viewed by a research community to be of poor quality [@Chiarelli2019] (but see [@Faser2022]).
-Nonetheless, we lack a systematic understanding of the factors that influence preprint use in ecology and evolution which can help inform future initiatives, improve others, and allow us to work harder in further breaking down barriers to their use in our field.
+Preprint servers can empower researchers to make their findings more accessible, open, and transparent but only if they are used as forums for spreading and discussing findings within a research community.
+Significant barriers to preprint use still exist globally – from a lack of clarity around preprint policies at journals [@Klebel2020] to a stigma that preprints are viewed by the research community to be of poor quality [@Chiarelli2019] (but see [@Faser2022]).
+Nonetheless, we lack a systematic understanding of the factors that influence preprint use in ecology and evolution that can help inform future initiatives and allow us to work harder in further breaking down barriers to preprint use in our field.
 
-*EcoEvoRxiv* is one of the few community driven preprint servers that has paved the way for new initiatives, including accepting multilingual preprints, recognising and accepting registered reports and non-traditional research reports, and promoting peer review and community discussion to improve the quality of preprints and speed up their peer-reviewed publication (e.g., Peer Community In -- PCI).
+*EcoEvoRxiv* is one of the few community-driven preprint servers that has paved the way for new initiatives, including by accepting multilingual preprints, recognising registered reports and non-traditional research reports, and promoting peer review and community discussion to improve the quality of preprints and speed up their peer-reviewed publication (e.g., Peer Community In -- PCI [@guillemaud2019peer]).
+Peer Community In allows for fast constructive peer review around a preprint.
+Peer reviews are transparent and published online and the community makes a recommendation on where the reasearch findings should be published [@guillemaud2019peer].
 
-Here, we explore the first preprints uploaded to *EcoEvoRxiv* to understand preprint practices and use in ecology and evolution.
-We focus our attention on understanding better: 1) what countries authors that preprint are located; 2) how career stage and gender impact preprint use; 3) the extent to which authors make use of preprint servers for registered reports and community-driven peer review; 4) whether data and code are more likely to be shared in preprints; and 5) how long it takes for a preprint to become published, and how many preprints remain unpublished.
-In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other servers which we think will help further educate researchers about the benefits of using community driven preprint servers to post their research findings.
+Here, we explore the first preprints uploaded to *EcoEvoRxiv* to understand preprint practices and uses in ecology and evolution.
+We focus our attention on better understanding: 1) what countries authors who use *EcoEvoRxiv* are located; 2) how career stage and gender impact preprint server use; 3) the extent to which authors make use of preprint servers for registered reports and community-driven peer review; 4) the extent to which data and code are shared in preprints; and 5) how many preprints remain unpublished, and for those that are published, how long it took them to become published.
+In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other preprint servers to help further educate researchers about the benefits of using community-driven preprint servers to post their research findings.
 

### 2024-05-02 ms/ms.qmd
Adding refs and adding in some corrections to text

@@
 
-*EcoEvoRxiv* is run by the Society for Open, Reliable, and Transparent Ecology and Evolution (SORTEE).
-Originally launched in 2018 on the Center for Open Science preprint platform, *EcoEvoRxiv* has grown to become a popular preprint server for researchers in ecology and evolution.
+*EcoEvoRxiv* is run by the Society for Open, Reliable, and Transparent Ecology and Evolutionary biology (SORTEE)[@o2021towards].
+Originally launched in 2018 on the Center for Open Science preprint platform, *EcoEvoRxiv* has grown to become a popular preprint server for researchers in ecology and evolutionary biology.
 It has since been adopted by the California Digital Library (CDL) to be hosted in perpetuity without fees.
-Editors are researchers across the globe in the fields of ecology and evolution who volunteer their time to screen papers and push new initiatives in the preprint space.
-*EcoEvoRxiv* accepts both preprints and postprints.
-Postprints are articles that are already published but are the final version of the published paper before typesetting for the research journal.
-Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication (assuming the journal has a preprint policy that recognises preprints - though most do).
-To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the articles available on *EcoEvoRxiv* as of `r gsub("UTC", "", dates[2])`.
+Editors are researchers from across the globe (currently eight different countries) in the fields of ecology and evolutionary biology who volunteer their time to screen papers and push new initiatives in the preprint space.
+*EcoEvoRxiv* accepts both preprints and postprints, or author-accepted manuscripts (AAM) -  a version of an accepted or published article without typesetting and formatting by a journal.
+Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication (assuming the journal has a preprint policy that recognises preprints-- though most do; see https://www.sherpa.ac.uk/romeo/).
+To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the articles available on *EcoEvoRxiv* as of `r gsub("UTC", "", dates[2])` (see Supplement for more details on methods).
 For the purpose of summarising articles on *EcoEvoRxiv* we include both preprints and postprints as 'articles' in our overview analysis.

### 2024-05-02 ms/ms.qmd
Added some numbers and details to legend fig 1

@@
 A) Number of articles (preprints and postprints) published monthly to *EcoEvoRxiv* between 2018 and 2023.
-*EcoEvoRxiv* was established in June 2018 before the soft launch in November 2018; B) Countries that are posting articles (preprints and postprints) to *EcoEvoRxiv* as inferred from the country of affiliation of the submitting author; C) Taxa used / covered in the articles posted to *EcoEvoRxiv*; D) Types of articles accepted on *EcoEvoRxiv*.
+*EcoEvoRxiv* was established in June 2018 before the soft launch in November 2018.
+Notable milestones include when *EcoEvoRxiv* transitioned to the California Digitial Library (CDL), the acceptance of Spanish and Portuguese preprints and postprints and when the first IUCN Redlist Ecosystem report was accepted; B) Countries that are posting articles (preprints and postprints) to *EcoEvoRxiv* as inferred from the country of affiliation of the submitting author; C) Taxa used / covered in the articles posted to *EcoEvoRxiv* (*n* = 1080); D) Types of preprints accepted on *EcoEvoRxiv* (*n* = 620).
 E) Career stage of authors posting to *EcoEvoRxiv* along with the gender of the submitting author.
@@
   sum_taxa <- data2  %>% dplyr::select(all_of(cols))  %>% apply(., 2, sum, na.rm = TRUE)  %>% data.frame()   %>% rownames_to_column(var = "taxa")  %>% rename("n" = ".")  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))
-
+  #sum(sum_taxa$n) #1080
   # Use data to create a pir chart and clean up colour palette
@@
   sum_types <- preprints  %>% tabyl(type_of_preprint)  %>% rename("type" = type_of_preprint, "n" = n)  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))
-
+  sum(sum_types$n) #620
   p4 <- ggplot(sum_types, aes(x = "", y = perc, fill = type)) +

### 2024-05-02 ms/ms.qmd
Chnages text to incorperate suggestions

@@
 While preprint use in biology has had a slower uptake [@Berg2016], in ecology and evolution, new discipline-specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disseminate research findings.
-Preprints are expected to promote open science, increase the visibility of research (e.g., [fu2019releasing]), and facilitate the rapid sharing of new discoveries that can have significant impacts on fundamental and applied knowledge globally.
+Preprints are expected to promote open science, increase the visibility of research (e.g., [@fu2019releasing]), and facilitate the rapid sharing of new discoveries that can have significant impacts on fundamental and applied knowledge globally.
 Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed, visibility and output of research findings; 2) helping establish precedence of research findings; 3) removing financial barriers to publication; and 4) encouraging constructive and critical feedback from the research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
@@
 *EcoEvoRxiv* was established in June 2018 before the soft launch in November 2018.
-Notable milestones include when *EcoEvoRxiv* transitioned to the California Digitial Library (CDL), the acceptance of Spanish and Portuguese preprints and postprints and when the first IUCN Redlist Ecosystem report was accepted; B) Countries that are posting articles (preprints and postprints) to *EcoEvoRxiv* as inferred from the country of affiliation of the submitting author; C) Taxa used / covered in the articles posted to *EcoEvoRxiv* (*n* = 1080); D) Types of preprints accepted on *EcoEvoRxiv* (*n* = 620).
+Notable milestones include when *EcoEvoRxiv* transitioned to the California Digital Library (CDL), the acceptance of Spanish and Portuguese preprints and postprints and when the first IUCN Red list Ecosystem report was accepted; B) Countries that are posting articles (preprints and postprints) to *EcoEvoRxiv* as inferred from the country of affiliation of the submitting author; C) Taxa used / covered in the articles posted to *EcoEvoRxiv* (*n* = 1080); D) Types of preprints accepted on *EcoEvoRxiv* (*n* = 620).
 E) Career stage of authors posting to *EcoEvoRxiv* along with the gender of the submitting author.
@@
       # Soft Launch of EcoEvoRxiv
-    annotate( "segment", x = as.POSIXct("2018-07-01"),  xend = as.POSIXct("2018-07-01"), y = 0, yend = 82, color = "#ffd966", linetype = "dashed", size = 1.5) + 
-    annotate("text", x = as.POSIXct("2018-07-01"), y = 85, label = "Soft Launch", color = "#ffd966", size = 4, angle = angle, hjust = 0) +
+    annotate( "segment", x = as.POSIXct("2018-06-01"),  xend = as.POSIXct("2018-07-01"), y = 0, yend = 82, color = "#ffd966", linetype = "dashed", size = 1.5) + 
+    annotate("text", x = as.POSIXct("2018-06-01"), y = 85, label = "Soft Launch", color = "#ffd966", size = 4, angle = angle, hjust = 0) +
     # Launch of EcoEvoRxiv
@@
 
-After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissions for the same preprint rather than updating an existing submission – we had data for a total of `r pr` articles with ~55-60 preprints published each month in the last two years ([@fig-summary]A).
-Authors from a total of `r length(unique(countries$country))-1` countries have used *EcoEvoRxiv* as a preprint server.
-Unsurprisingly, authors from countries in North America and Europe upload the most preprints.
-Authors from countries in Africa, Central America and parts of Asia still do not use *EcoEvoRxiv* much ([@fig-summary]B).
-Overall, 90% of the articles come from just `r nrow(most_use)-1` countries.
+After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissions for the same preprint rather than updating an existing submission – we had data for a total of `r pr` articles with ~55--60 preprints published each month in the last two years ([@fig-summary]A).
+*EcoEvoRxiv* hosts papers from authors based in `r length(unique(countries$country))-1` countries, with 90% of the articles coming from just `r nrow(most_use)-1` countries.
+North America, Australia, and Europe upload the most preprints with much fewer coming from countries in Africa, Central America and parts of Asia ([@fig-summary]B).
 Articles covered all major taxonomic groups, with the most common being vertebrates (`r sum_taxa$perc[6]`%), plants (`r sum_taxa$perc[1]`%) and invertebrates (`r sum_taxa$perc[5]`%) ([@fig-summary]C).
@@
 It accepts reports and books that are often not easily accessible, but may contain important data of relevance to research syntheses or for practitioners.
-As a result, articles on *EcoEvoRxiv* are more diverse in nature than those on other preprint servers; nonetheless, typical research articles (`r sum_types[sum_types$type == "research article",]$perc`%) are still the most common type of preprint, followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]D).
+As a result, articles on *EcoEvoRxiv* are more diverse than those on preprint servers that have more restrictive submission policies; nonetheless, typical research articles are still the most common type of preprint (`r sum_types[sum_types$type == "research article",]$perc`%), followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]D).
 
 Accepting a greater diversity of article types allows *EcoEvoRxiv* to begin dealing with the 'grey literature' problem whereby data that are relevant for research syntheses are not published in typical peer-reviewed journals[@haddaway2015shades; @haddaway2020eight].
-This is reflected by `r nt`% of articles that could be considered ‘grey literature’ in ecology and evolutionary biology: books, book chapters, reports, and other research output types.
-Currently, *EcoEvoRxiv* does not host many reports (`r sum_types[sum_types$type == "report", "perc"]`%), particularly from government and industry.
+This is reflected by `r nt`% of articles on *EcoEvoRxiv* that could be considered ‘grey literature’ in ecology and evolutionary biology: books, book chapters, reports, and other research output types.
+Currently, *EcoEvoRxiv* does not host many reports (`r sum_types[sum_types$type == "report", "perc"]`%), particularly from government or industry.
 We would encourage authors to consider posting these types of articles to ensure they are openly accessible and more easily found.
-*EcoEvoRxiv* has already formed fruitful partnerships with the International Union for Conservation of Nature (IUCN) to be a place where their reports can be lodged to make them more easily accessible to the broader research community.
+*EcoEvoRxiv* articles are given a unique DOI and indexed on Google Scholar.
+*EcoEvoRxiv* has already formed fruitful partnerships with the International Union for Conservation of Nature (IUCN) as a place where IUCN reports can be hosted to make them more easily accessible to the broader research community.
 For example, IUCN Red Ecosystem Reports are now posted to *EcoEvoRxiv* and our community has been able to work closely with the IUCN to ensure these documents meet the IUCN requirements.
@@
 A significant barrier to the communication of research findings is due to the fact that they are primarily communicated in English [@amano2016languages; @amano2013four; @amano2021ten].
-Communication of research through a single language has major consequences for the global distribution of knowledge resulting in knowledge gaps in some of the most biodiverse and threatened regions in the world [@amano2023role; @zenni2023multi].
-Such gaps also have flow on effects for research syntheses and meta-analyses because they create a distorted picture of our knowledge base that can lead to bias and inadequate sampling that affects policy development and decision making [@hannah2024language; @zenni2023multi; @white2021geographical; @konno2020ignoring].
+Communication of research through a single language has major consequences for the global distribution of knowledge resulting in knowledge gaps across some of the most biodiverse and threatened regions in the world [@amano2023role; @zenni2023multi].
+Such gaps also have flow on effects for research syntheses and meta-analyses because they create a distorted picture of our knowledge base that can lead to bias and inadequate sampling that affects policy development and decision-making [@hannah2024language; @zenni2023multi; @white2021geographical; @konno2020ignoring].
 
-*EcoEvoRxiv* is the only preprint server breaking down language barriers to scientific communication; currently accepting English, Spanish, Portuguese and French manuscripts.
+*EcoEvoRxiv* is the only preprint server to date breaking down language barriers to scientific communication; currently accepting English, Spanish, Portuguese and French manuscripts.
 Such initiatives are incredibly important if we are to begin filling global voids of scientific knowledge.
-Multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish preprints posted to date, and none in other accepted languages (e.g., French and Portuguese).
-Part of the challenge in getting authors to submit non-English preprints is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries and the fact that it accepts preprints in different languages, cultural differences in the perception of preprints and a strong reliance on traditional publishing models, which typically favour publishing in English.
+However, multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish preprints posted to date, and none in other accepted languages (e.g., French and Portuguese).
+Part of the challenge in getting authors to submit non-English preprints is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries and the fact that it accepts preprints in different languages, cultural differences in the perception of preprints, and a strong reliance on traditional publishing models which typically mandate publishing in English.
 
@@
 
-Research papers take time to be published (see below).
-Early and mid-career researchers (ECMRs) need their research to come out quickly for job applications, promotion and obtaining grants to accelerate their careers [@vale2015accelerating; @sarabipour2019value].
-Preprints are one way ECMRs can achieve faster dissemination and greater visibility.
-As such, we expect ECMRs to accept and adopt preprints more than colleagues at later career stages.
-At the same time, gender differences in preprint use and publication outcomes  have been observed in a number of other research fields, including ecology and evolution [@fox2019gender; @wehner2020comparison].
-We therefore expect such discrepancies to manifest in preprint use on *EcoEvoRxiv*, but it is unclear to what extent.
-Understanding gender publishing patterns is challenging with observational data such as ours because we cannot know the gender of authors for certainty but we can use a data-driven approach to ascertain the probability that a particular name is of a given gender (male or female).
+Research papers can take long periods of time to become published (see below).
+However, Early and Mid-Career Researchers (EMCRs) are under pressure to publish rapidly to be competitive in job applications, promotions, and obtaining grants to accelerate their careers [@vale2015accelerating; @sarabipour2019value].
+Preprints are one way EMCRs can achieve faster dissemination and greater visibility [@fu2019releasing].
+As such, we expect EMCRs to accept and adopt preprints more than colleagues at later career stages.
+At the same time, gender differences in preprint use and publication outcomes  have been observed in a number of other research fields, including ecology and evolutionary biology [@fox2019gender; @wehner2020comparison].
+Therefore such discrepancies are expected to manifest in preprint use on *EcoEvoRxiv*, but it is unclear to what extent.
+Understanding gender publishing patterns is challenging with observational data such as ours because we cannot know the gender of authors for certain but we can use a data-driven approach to ascertain the probability that a particular name is of a given gender (man or women).
 To obtain an idea of an author's gender, we used the R package *gender* (vers.

### 2024-05-03 ms/ms.qmd
Fixing grammar in gender section. Some comments to dela with still

@@
 At the same time, gender differences in preprint use and publication outcomes  have been observed in a number of other research fields, including ecology and evolutionary biology [@fox2019gender; @wehner2020comparison].
-Therefore such discrepancies are expected to manifest in preprint use on *EcoEvoRxiv*, but it is unclear to what extent.
+Therefore, such discrepancies are expected to manifest in preprint use on *EcoEvoRxiv*, but it is unclear to what extent.
 Understanding gender publishing patterns is challenging with observational data such as ours because we cannot know the gender of authors for certain but we can use a data-driven approach to ascertain the probability that a particular name is of a given gender (man or women).
@@
 `r utils::packageVersion("gender")`; @mullen2021predict) to predict the most likely gender of the submitting author of a preprint.
+We acknowledge that our approach does not capture self-assigned and non-binary genders.
 We only used algorithm-assigned names where the gender was identified with 95% certainty.
-For the remaining names, we performed manual searches to determine gender based on the pronouns and photographs from professional and personal websites (we acknowledge that our approach does not capture self-assigned and non-binary genders).
-Our data on gender has only two missing values – one where the first name of the submitting author was missing and the other one for a collective submission.
+For the remaining names, we performed manual searches to determine gender based on the pronouns and photographs from professional and personal websites.
+Our data on gender has only two missing values--one where the first name of the submitting author was missing and the other one for a collective submission.
 
-Overall, females were less likely to publish preprints on *EcoEvoRxiv* compared to males (females: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`% compared to males: `r (table(data4$gender)[2] / sum(table(data4$gender))*100)`%), which is likely a reflection of the broader publishing disparities between male and female scientists [@fox2019gender].
+Overall, women were less likely to publish preprints on *EcoEvoRxiv* compared to men (women: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`% compared to men: `r (table(data4$gender)[2] / sum(table(data4$gender))*100)`%), which is likely a reflection of the broader publishing disparities between male and female scientists [@fox2019gender].
 There was also strong evidence that the number of preprints posted decreases with later career stages (negative binomial glm: year slope = `r res[2, "Estimate"]`, SE: `r res[2, "Std.
@@
 The majority of preprints were submitted by authors who published their first paper in the last 10 years ([@fig-summary]E), with the median year of first publication of submitting authors being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r round(mean(data2$submitting_author_first_publication_year, na.rm = TRUE),0)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`).
-These patterns support the expectation that ECMRs may value preprints as a way to make their work more visible and disseminate their finding more quickly.
+These patterns support the expectation that EMCRs may value preprints as a way to make their work more visible and disseminate their findings more quickly.
 

### 2024-05-03 ms/ms.qmd
Small fixes

@@
 Editors are researchers from across the globe (currently eight different countries) in the fields of ecology and evolutionary biology who volunteer their time to screen papers and push new initiatives in the preprint space.
-*EcoEvoRxiv* accepts both preprints and postprints, or author-accepted manuscripts (AAM) -  a version of an accepted or published article without typesetting and formatting by a journal.
+*EcoEvoRxiv* allows authors to post both preprints and postprints, or author-accepted manuscripts -  a version of an accepted or published article without typesetting and formatting by a journal.
 Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication (assuming the journal has a preprint policy that recognises preprints-- though most do; see https://www.sherpa.ac.uk/romeo/).

### 2024-05-03 ms/ms.qmd
Addeding a sentence about gender caveat

@@
 Research papers can take long periods of time to become published (see below).
-However, Early and Mid-Career Researchers (EMCRs) are under pressure to publish rapidly to be competitive in job applications, promotions, and obtaining grants to accelerate their careers [@vale2015accelerating; @sarabipour2019value].
+However, Early and Mid-Career Researchers (EMCRs) (~10 years post-PhD) are under pressure to publish rapidly to be competitive in job applications, promotions, and obtaining grants to accelerate their careers [@vale2015accelerating; @sarabipour2019value].
 Preprints are one way EMCRs can achieve faster dissemination and greater visibility [@fu2019releasing].
@@
 We acknowledge that our approach does not capture self-assigned and non-binary genders.
+As such, our assumptions about an authors gender idendity could be incorrect.
 We only used algorithm-assigned names where the gender was identified with 95% certainty.

### 2024-05-03 ms/ms.qmd
More corrections

@@
 *EcoEvoRxiv* was established in June 2018 before the soft launch in November 2018.
-Notable milestones include when *EcoEvoRxiv* transitioned to the California Digital Library (CDL), the acceptance of Spanish and Portuguese preprints and postprints and when the first IUCN Red list Ecosystem report was accepted; B) Countries that are posting articles (preprints and postprints) to *EcoEvoRxiv* as inferred from the country of affiliation of the submitting author; C) Taxa used / covered in the articles posted to *EcoEvoRxiv* (*n* = 1080); D) Types of preprints accepted on *EcoEvoRxiv* (*n* = 620).
+Notable milestones include when *EcoEvoRxiv* transitioned to the California Digital Library (CDL), the acceptance of Spanish and Portuguese preprints and postprints and when the first IUCN Red list Ecosystem report was accepted; B) Countries that are posting articles (preprints and postprints) to *EcoEvoRxiv* as inferred from the country of affiliation of the submitting author; C) Taxa used / covered in the articles posted to *EcoEvoRxiv* (*n* = 1080 papers); D) Types of preprints accepted on *EcoEvoRxiv* (*n* = 620 papers).
 E) Career stage of authors posting to *EcoEvoRxiv* along with the gender of the submitting author.
@@
 
-After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissions for the same preprint rather than updating an existing submission – we had data for a total of `r pr` articles with ~55--60 preprints published each month in the last two years ([@fig-summary]A).
+After removing five duplicate titles – suggesting a few authors created multiple submissions for the same preprint rather than updating an existing submission – we had data for a total of `r pr` articles with ~55--60 preprints published each month in the last two years ([@fig-summary]A).
 *EcoEvoRxiv* hosts papers from authors based in `r length(unique(countries$country))-1` countries, with 90% of the articles coming from just `r nrow(most_use)-1` countries.
-North America, Australia, and Europe upload the most preprints with much fewer coming from countries in Africa, Central America and parts of Asia ([@fig-summary]B).
-Articles covered all major taxonomic groups, with the most common being vertebrates (`r sum_taxa$perc[6]`%), plants (`r sum_taxa$perc[1]`%) and invertebrates (`r sum_taxa$perc[5]`%) ([@fig-summary]C).
+North America, Australia, and European countries upload the most preprints with much fewer coming from countries in Africa, Central America, and parts of Asia ([@fig-summary]B).
+Articles covered all major taxonomic groups, with the most common being vertebrates (`r sum_taxa$perc[6]`%), plants (`r sum_taxa$perc[1]`%), and invertebrates (`r sum_taxa$perc[5]`%) ([@fig-summary]C).
 
-### *Diversifying articles types on **EcoEvoRxiv**: overcoming the 'grey literature' problem*
+### *Diversifying article types on **EcoEvoRxiv**: overcoming the 'grey literature' problem*
 
@@
 This is reflected by `r nt`% of articles on *EcoEvoRxiv* that could be considered ‘grey literature’ in ecology and evolutionary biology: books, book chapters, reports, and other research output types.
-Currently, *EcoEvoRxiv* does not host many reports (`r sum_types[sum_types$type == "report", "perc"]`%), particularly from government or industry.
-We would encourage authors to consider posting these types of articles to ensure they are openly accessible and more easily found.
+Currently, *EcoEvoRxiv* does not host many reports (`r sum_types[sum_types$type == "report", "perc"]`%), particularly from governments or industry.
+We would encourage authors to consider posting books, book chapters and reports to ensure they are openly accessible and more easily found.
 *EcoEvoRxiv* articles are given a unique DOI and indexed on Google Scholar.
@@
 Such initiatives are incredibly important if we are to begin filling global voids of scientific knowledge.
-However, multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish preprints posted to date, and none in other accepted languages (e.g., French and Portuguese).
+However, multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish preprints and a single Portuguese preprint posted to date.
 Part of the challenge in getting authors to submit non-English preprints is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries and the fact that it accepts preprints in different languages, cultural differences in the perception of preprints, and a strong reliance on traditional publishing models which typically mandate publishing in English.
@@
 Increased competition in science has raised the bar with respect to the amount of data required for publication [@vale2015accelerating].
-This is a good outcome if it results in higher impact research that better clarifies our understanding of the natural world, but it does come at a cost for the rate at which research findings can be disseminated [@vale2015accelerating].
-Preprinting has been proposed as a way to disseminate research more quickly as it can take a long time before results are ultimately published [@bourne2017ten; @vale2015accelerating].
+This is a good outcome if it results in more comprehensive research that better clarifies our understanding of the natural world, but it does come at a cost for the rate at which research findings can be disseminated [@vale2015accelerating].
+Preprints have been proposed as a way to disseminate research more quickly as it can take a long time before results are ultimately published [@bourne2017ten; @vale2015accelerating].
 However, data on the time to publication is sparse, and the real benefit of preprints in this context would be reinforced if preprinting can dramatically speed up dissemination.
-We evaluated how long it takes to publish a research paper in ecology and evolution by ascertaining the time between when a preprint was first posted and finally accepted in a research journal.
+We evaluated how long it takes to publish a research paper in ecology and evolution by ascertaining the time between when a preprint was first posted and finally accepted in a peer-reviewed journal.
 In total, `r unpub` papers were still unpublished out of the `r nrow(data2)` (`r (unpub / nrow(data2))*100`%) when these data were collected.
-Astonishingly, the maximum time between preprint submission and publication was `r sum_preprints$max` days or `r sum_preprints$max/365` years ([@fig-pubsummary]A), and the median time to publication was `r sum_preprints$median` days (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days).
-Our results largely confirm the long timespans most authors are dealing with to get their research published after the paper is written.
+Not all of these papers, however, are anticipated to be published in a peer-reviewed journal (e.g., reports).
+The maximum time between preprint submission and publication was `r sum_preprints$max` days or `r sum_preprints$max/365` years ([@fig-pubsummary]A), and the median time to publication was `r sum_preprints$median` days (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days).
+Our results largely confirm the extended timeframes that most authors experience between writing their research papers and their publication.
 

### 2024-05-04 ms/ms.qmd
Fixing up last few sections

@@
 Preprints are expected to promote open science, increase the visibility of research (e.g., [@fu2019releasing]), and facilitate the rapid sharing of new discoveries that can have significant impacts on fundamental and applied knowledge globally.
-Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed, visibility and output of research findings; 2) helping establish precedence of research findings; 3) removing financial barriers to publication; and 4) encouraging constructive and critical feedback from the research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
+Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed, visibility and output of research findings which can lead to more citations [e.g., @colavizza2024analysis]; 2) helping establish precedence of research findings; 3) removing financial barriers to publication; and 4) encouraging constructive and critical feedback from the research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
 
@@
 Significant barriers to preprint use still exist globally – from a lack of clarity around preprint policies at journals [@Klebel2020] to a stigma that preprints are viewed by the research community to be of poor quality [@Chiarelli2019] (but see [@Faser2022]).
-Nonetheless, we lack a systematic understanding of the factors that influence preprint use in ecology and evolution that can help inform future initiatives and allow us to work harder in further breaking down barriers to preprint use in our field.
+Nonetheless, we lack a systematic understanding of the factors that influence preprint use in ecology and evolution.
+Such an understanding can help inform future initiatives and allow us to work harder in further breaking down barriers to scientific publishing.
 
-*EcoEvoRxiv* is one of the few community-driven preprint servers that has paved the way for new initiatives, including by accepting multilingual preprints, recognising registered reports and non-traditional research reports, and promoting peer review and community discussion to improve the quality of preprints and speed up their peer-reviewed publication (e.g., Peer Community In -- PCI [@guillemaud2019peer]).
+*EcoEvoRxiv* is one of the few community-driven preprint servers that has paved the way for new initiatives, by accepting multilingual preprints, recognising registered reports and non-traditional research reports, and promoting peer review and community discussion which we hope will improve the quality of preprints and speed up their peer-reviewed publication (e.g., Peer Community In -- PCI [@guillemaud2019peer]).
 Peer Community In allows for fast constructive peer review around a preprint.
@@
 
-Here, we explore the first preprints uploaded to *EcoEvoRxiv* to understand preprint practices and uses in ecology and evolution.
-We focus our attention on better understanding: 1) what countries authors who use *EcoEvoRxiv* are located; 2) how career stage and gender impact preprint server use; 3) the extent to which authors make use of preprint servers for registered reports and community-driven peer review; 4) the extent to which data and code are shared in preprints; and 5) how many preprints remain unpublished, and for those that are published, how long it took them to become published.
+Here, we explore the first 1000+ preprints uploaded to *EcoEvoRxiv* to understand preprint practices and uses in ecology and evolution.
+We focus our attention on better understanding: 1) in what countries authors who use *EcoEvoRxiv* are located; 2) how career stage and gender impact preprint server use; 3) the extent to which authors make use of preprint servers for registered reports and community-driven peer review; 4) the extent to which data and code are shared in preprints; and 5) how many preprints remain unpublished, and for those that are published, how long it took them to become published.
 In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other preprint servers to help further educate researchers about the benefits of using community-driven preprint servers to post their research findings.
@@
 *EcoEvoRxiv* allows authors to post both preprints and postprints, or author-accepted manuscripts -  a version of an accepted or published article without typesetting and formatting by a journal.
-Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication (assuming the journal has a preprint policy that recognises preprints-- though most do; see https://www.sherpa.ac.uk/romeo/).
+Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication (assuming the journal has a policy that recognises pre- and post-prints -- though most do; see https://www.sherpa.ac.uk/romeo/).
 To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the articles available on *EcoEvoRxiv* as of `r gsub("UTC", "", dates[2])` (see Supplement for more details on methods).
@@
 In addition to speeding up dissemination, preprints can also be a useful way to ensure that research remains open and accessible to the research community because the paper is available online no matter what the open access status of the publication ends up being [@bourne2017ten; @vale2015accelerating].
-Using the published articles on *EcoEvoRxiv*, we evaluated the open access status of each paper using the R package *roadoi* to connect to Unpaywall platform [@jahn2024].
-Most of the published preprints ended up being open access ([@fig-pubsummary]A), however, the status of many `r sum_is_oa$n[3]` (`r sum_is_oa$percent[3]*100`%) were unknown, and `r sum_is_oa$n[1]` (`r sum_is_oa$percent[1]*100`%) were not published in open access research journals.
-The level of open access for a paper published in an open-access journal also varied widely ([@fig-pubsummary]B).
+Using the published articles on *EcoEvoRxiv*, we evaluated the open access status of each paper using the R package *roadoi* (vers.
+`r utils::packageVersion("roadoi")`) to connect to the Unpaywall platform [@jahn2024].
+Most of the published articles arising from preprints were open access [`r sum_is_oa$n[2]` (`r sum_is_oa$percent[2]*100`%) [@fig-pubsummary]A]; however, the status of many were unknown [`r sum_is_oa$n[3]` (`r sum_is_oa$percent[3]*100`%)], and `r sum_is_oa$n[1]` (`r sum_is_oa$percent[1]*100`%) were published behind paywalls.
+The type of open access for a published paper in an open-access journal also varied widely ([@fig-pubsummary]B).
 
 Data and code sharing are also key components of open science [@roche2015public].
-In the spirit of 'openness' we expected data and code sharing among preprints to be better than in many papers published in research journals [@roche2015public; @o2021preferred].
-Despite this, we found that `r preprint_data[1,2]` (`r preprint_data[1,"percent"]*100`%) of relevant preprints on *EcoEvoRxiv* (i.e., only where data was generated) did not share data, while `r preprint_code[1,2]` (`r preprint_code[1,"percent"]*100`%) did not share code.
-Authors may be reluctant to share data and code for preprints because of the perceived concern that others may acquire and use such data and code without authors' consent.
-However, while `r pre_article_data[3,2]` (`r pre_article_data[3,"percent"]*100`%) of preprints that did not share data at the preprint stage did ultimately share data in the published article, there were still `r pre_article_data[2,2]` (`r pre_article_data[2,"percent"]*100`%) that never shared data.
+In the spirit of 'openness', we expected data and code sharing among preprints to be greater than in many papers published in research journals [@roche2015public; @o2021preferred].
+Despite this, we found that `r preprint_data[1,2]` (`r preprint_data[1,"percent"]*100`%) of preprints relying on data on *EcoEvoRxiv* did not share data, and `r preprint_code[1,2]` (`r preprint_code[1,"percent"]*100`%) did not share code.
+Authors may be reluctant to share data and code for preprints because of the perceived concern that others may acquire and use such data and code prior to publication in a journal.
+Notably, authors of `r pre_article_data[3,2]` (`r pre_article_data[3,"percent"]*100`%) preprints that did not share data at the preprint stage ultimately did share data when the article was published; authors for `r pre_article_data[2,2]` (`r pre_article_data[2,"percent"]*100`%) preprints never shared data.
 The same was true for code.
-Overall, `r pre_article_code[3,2]` (`r pre_article_code[3,"percent"]*100`%) of preprints did not share code at the preprint stage but did in the published article; however, `r pre_article_code[2,2]` (`r pre_article_code[2,"percent"]*100`%) never shared code.
-Code and data- sharing patterns in our sample of preprints are consistent with analyses of published articles (e.g., [@o2021preferred]), even for journals with strict public data archiving policies [@roche2015public].
+Overall, `r pre_article_code[3,2]` (`r pre_article_code[3,"percent"]*100`%) preprints had no open code at the preprint stage but did at the published article stage; authors of `r pre_article_code[2,2]` (`r pre_article_code[2,"percent"]*100`%) preprints did not share code on publication.
+Code and data-sharing patterns in our sample of preprints are consistent with analyses sharing practices for published articles (e.g., [@o2021preferred]), even for journals with strict public data archiving policies [@roche2015public].
 
@@
 
-Our data-driven approach has allowed us to better understand some of the key elements of uncertainty surrounding preprints and identify shortcomings and areas needing greater clarity to authors.
-Several key insights follow from our analysis of the first *EcoEvoRxiv* preprints.
+Our data-driven approach has allowed us to better understand some of the key elements of uncertainty surrounding preprints and identify shortcomings and areas in need of clarification for authors.
+Several key insights follow from our analysis of the first *EcoEvoRxiv* preprints:
 
-- First, authors need not be afraid of sharing data and code early in the preprint stage.
+- First, authors are encouraged to share their data and code at the preprint stage.
 Sharing data and code early can help improve the quality of research, establish precedence, and improve the transparency and computational reproducibility of scientific findings [@sarabipour2019value].
-If authors are worried about data being used unintentionally, clear information surrounding its reuse and withholding some data or meta-data needed to understand the dataset may be options.
-- Second, authors need to be aware of the benefits of posting preprints and post-prints for constructive feedback [@bourne2017ten].
-While it is clear preprints help establish precedence and allow findings to be openly accessible, it is still rare that constructive discussions form around preprints in an open form, which is consistent with findings on other preprint servers (e.g.
+Reassuringly, sharing data and code is rarely associated with 'scooping' of research findings [@soeharjono2021reported].
+If authors are worried about data being used unintentionally, clear information surrounding its reuse can include in a license (see https://choosealicense.com).
+Data can also be achived with an embargo on its reuse [@roche2014troubleshooting].
+- Second, authors need to be aware of the benefits of posting preprints and postprints for constructive feedback [@bourne2017ten].
+While it is clear preprints help establish precedence and allow findings to be openly accessible, it is still seems rare that constructive discussions form around preprints in an open forum (e.g.
 bioRxiv [@anderson2020biorxiv]).
+Unfortunately, the *EcoEvoRxiv* website does not provide opportunities for discussion given the limitations of the web server at this point in time.
+As such, we could not accurately assess how much discourse around a given preprint occurs.
 Clearly, as a community, we need to provide better platforms that document discussions around preprint findings.
 Such discussions help the authors improve their work and communicate their findings more effectively (when done constructively, of course).
-One way to facilitate such discussions may be to use open peer reviewing services such as *Peer Community In* (PCI) or *PubPeer* to provide feedback on preprints that ultimately is associated with a preprint.
-- Third, it remains clear that the time between preprinting and publication is still quite long.
+One way to facilitate such discussions may be to use open peer reviewing services, such as *Peer Community In* (PCI) or *PubPeer* (see also [@avissar2024recommendations] for more options), to provide feedback on preprints.
+- Third, it remains clear that the time between posting a preprint and publication is still quite long.
 One possible explanation is that preprints are not being sent to suitable journals.
@@
 # Acknowledgements
-We would like to thank the California Digital Library (CDL) and the CDL team (particularly Alainna Wrigley) for their support in hosting and maintaining *EcoEvoRxiv* for the Society for Open, Reliable, and Transparent Ecology and Evolution (SORTEE).
+We would like to thank the California Digital Library (CDL) and the CDL team (particularly Alainna Wrigley) for their support in hosting and maintaining *EcoEvoRxiv* for the Society for Open, Reliable, and Transparent Ecology and Evolutionary biology (SORTEE).
 We would also like to thank Gabriela Hidalgo and Daisy Larios for helping connect us with the IUCN and facilitating discussions to make *EcoEvoRxiv* a place where IUCN reports can be posted.

### 2024-05-04 ms/ms.qmd
Some text changes, some bigger comments to change yet. Including re-organising percentages

@@
   sum_types <- preprints  %>% tabyl(type_of_preprint)  %>% rename("type" = type_of_preprint, "n" = n)  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))
-  sum(sum_types$n) #620
+  #sum(sum_types$n) #620
   p4 <- ggplot(sum_types, aes(x = "", y = perc, fill = type)) +
@@
 #| label: fig-pubsummary
+#| echo: false
+#| warning: false
+#| message: false
 #| fig-cap: Summary of the publication status of preprints on *EcoEvoRxiv*.
@@
 Interestingly, out of the `r nrow(data2)` preprints, only `r pci[2,2]` (`r pci[2,3]*100`%) used Peer Community In (PCI) as a preprint peer-review service.
-Using PCI provides authors with quicker reviews of a paper and a more realistic recommendation of where such work is likely to be published.
-Many journals now also accept PCI reviews and recommendations when publishing a paper.
-As such, we would encourage more authors to consider sending their preprints for PCI review to possibly speed up the publication process.
-- Finally, while most preprints get seamlessly connected with and merged with their published version some remain disconnected.
-Incorrect cross-linking can create confusion and lead to frustration among authors.
+Using PCI circumvents editorial decisions without review.
+As such, it ensures that authors receive faster feedback on a paper and a more realistic recommendation of where such work is likely to be published.
+Many journals now accept PCI reviews and recommendations when publishing a paper, which may help facilitate faster publication; though more journals could incorperate PCI in thier policies.
+- Finally, while most preprints get seamlessly connected and merged with their published version some remain disconnected.
+Incorrect cross-linking by indexing platforms (e.g., Google Scholar) can create confusion and lead to frustration among authors.
 Thankfully, the reasons for unmatched preprints and publications are well understood and easily rectified.
@@
 We found that mismatched metadata almost always contributed to preprints and published articles not being matched automatically in Google Scholar.
-We recommend that authors ensure that, when preprints are published in a journal, they update their preprint with the publication DOI.
-Especially if their title has changed, this is quite easy for authors to do on *EcoEvoRxiv*, and it will ensure that the preprint is linked to the published article and that the citations are merged.
+We recommend that authors ensure that, when preprints are published in a journal, they update their preprint with the publication DOI, especially if their title has changed.
+This is quite easy for authors to do on *EcoEvoRxiv*, and it will ensure that the preprint is linked to the published article and that the citations are merged.
 It will also create a link between the final preprint and the published paper so that, no matter the open access status of the publication, the research findings will remain openly accessible, saving costs for authors and improving the visibility and use of research.
 
-Despite the early successes of the new initiatives taken by *EcoEvoRxiv*, much work needs to be done to improve our community’s understanding and use of preprints (and post-prints).
-We view this perspective piece as one small step in achieving that goal.
+Despite the early successes of the new initiatives taken by *EcoEvoRxiv*, much work needs to be done to improve our community’s understanding and use of pre- and post-prints.
+We view this perspective piece as a small step towards achieving that goal.
 Authors must also be aware of the benefits of using community-driven preprint servers and the unique initiatives being pursued.
@@
 Supporting these initiatives should be a priority for all researchers.
-Volunteers at *EcoEvoRxiv* should remain open to new and innovative ways to improve publication and open science practices.
+Volunteers at *EcoEvoRxiv* are encouraged to remain open to new and innovative ways to improve publication and open science practices.
 We believe that the future of preprints is bright, and community-driven initiatives, such as *EcoEvoRxiv*, are set to play a crucial role in the future of scientific publishing.

### 2024-05-04 ms/ms.qmd
Adding in Zoe's code

@@
 #remotes::install_github("lmullen/genderdata")
-pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, gender,genderdata, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot, viridis, cowplot, magick, lme4, lmerTest)
+pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, gender,genderdata, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot, viridis, cowplot, magick, lme4, lmerTest, data.table)
 
@@
   p1 <- ggplot(data2, aes(x = preprint_pub_date)) +
-    geom_histogram(fill = "black", color = "black") +
-    labs(x = "Published Date", y = "Number of Papers") +
-    theme_bw() +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin") + ylim(0, 130) + 
+    geom_histogram(fill = "white", color = "black") +
+    scale_y_continuous(limits = c(0, 130), expand = c(0, 0)) +
+    labs(x = "Published date", y = "Number of papers") +
+    theme_classic() +
+    #theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+    theme(plot.tag = element_text(size = 16, face = "bold")) + 
       # Soft Launch of EcoEvoRxiv
-    annotate( "segment", x = as.POSIXct("2018-06-01"),  xend = as.POSIXct("2018-07-01"), y = 0, yend = 82, color = "#ffd966", linetype = "dashed", size = 1.5) + 
-    annotate("text", x = as.POSIXct("2018-06-01"), y = 85, label = "Soft Launch", color = "#ffd966", size = 4, angle = angle, hjust = 0) +
+    annotate( "segment", x = as.POSIXct("2018-06-01"),  xend = as.POSIXct("2018-06-01"), y = 0, yend = 82, color = "black", linetype = "dashed", size = 0.5) + 
+    annotate("text", x = as.POSIXct("2018-06-01"), y = 85, label = "Soft Launch", size = 4, angle = angle, hjust = 0) +
     # Launch of EcoEvoRxiv
-    annotate( "segment", x = as.POSIXct("2018-11-11"),  xend = as.POSIXct("2018-11-11"), y = 0, yend = 82, color = "#2986cc", linetype = "dashed", size = 1.5) + 
-    annotate("text", x = as.POSIXct("2018-11-11"), y = 85, label = "Launch", color = "#2986cc", size = 4, angle = angle, hjust = 0) +
+    annotate( "segment", x = as.POSIXct("2018-11-11"),  xend = as.POSIXct("2018-11-11"), y = 0, yend = 82, color = "black", linetype = "dashed", size = 0.5) + 
+    annotate("text", x = as.POSIXct("2018-11-11"), y = 85, label = "Launch", size = 4, angle = angle, hjust = 0) +
     # Spanish and Port
-    annotate( "segment", x = as.POSIXct("2023-02-14"),  xend = as.POSIXct("2023-02-14"), y = 0, yend = 82, color = "#3d85c6", linetype = "dashed", size = 1.5) + 
-    annotate("text", x = as.POSIXct("2022-11-14"), y = 85, label = "Spanish and Portug.", color = "#3d85c6", size = 4, angle = angle, hjust = 0) +
+    annotate( "segment", x = as.POSIXct("2023-02-14"),  xend = as.POSIXct("2023-02-14"), y = 0, yend = 82, color = "black", linetype = "dashed", size = 0.5) + 
+    annotate("text", x = as.POSIXct("2022-11-14"), y = 85, label = "Spanish and Portug.", size = 4, angle = angle, hjust = 0) +
     # Transition to CDL
-    annotate( "segment", x = as.POSIXct("2022-09-14"),  xend = as.POSIXct("2022-09-14"), y = 0, yend = 82, color = "#008000", linetype = "dashed", size = 1.5) + 
-    annotate("text", x = as.POSIXct("2022-07-14"), y = 85, label = "CDL", color = "#008000", size = 4, angle = angle, hjust = 0) +
+    annotate( "segment", x = as.POSIXct("2022-09-14"),  xend = as.POSIXct("2022-09-14"), y = 0, yend = 82, color = "black", linetype = "dashed", size = 0.5) + 
+    annotate("text", x = as.POSIXct("2022-07-14"), y = 85, label = "CDL", size = 4, angle = angle, hjust = 0) +
    # IUCN Red Eco submission 29 August 2023
    # 1000 preprints
-    annotate( "segment", x = as.POSIXct("2023-08-29"),  xend = as.POSIXct("2023-08-29"), y = 0, yend = 82, color = "#cc0000", linetype = "dashed", size = 1.5) + 
-    annotate("text", x = as.POSIXct("2023-04-29"), y = 85, label = "IUCN Report", color = "#cc0000", size = 4, angle = angle, hjust = 0) 
+    annotate( "segment", x = as.POSIXct("2023-08-29"),  xend = as.POSIXct("2023-08-29"), y = 0, yend = 82, color = "black", linetype = "dashed", size = 0.5) + 
+    annotate("text", x = as.POSIXct("2023-04-29"), y = 85, label = "IUCN Report", size = 4, angle = angle, hjust = 0)
+
+  ggsave(here("output", "figs", "published_date.svg"), p1, width = 7.5, height = 2)
+
+  #Plot was then imported to illustrator for aesthetic touches and to combine with other plots in Figure 1. - Zoe X
 ##---------------------##
@@
 
-  p2 <- ggplot(countries) +
+    map_fig <- ggplot(countries) +
     geom_map(aes(map_id = country, fill = valid_percent_dis), map = world_map) +
@@
     expand_limits(x = world_map$long, y = world_map$lat) +
-    theme_void() + expand_limits(x = world_map$long, y = world_map$lat) + scale_fill_viridis(discrete = TRUE) + coord_fixed() + labs(fill="Precentage (%) of Total") +  coord_map("moll") + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")
+    theme_void() + expand_limits(x = world_map$long, y = world_map$lat) + scale_fill_viridis(option = "G", discrete = TRUE, direction = -1) +
+    coord_fixed() + labs(fill="Percentage (%) of Total") + theme(plot.tag = element_text(size = 16, face = "bold"))
+
+  ggsave(here("output", "figs", "worldmap.svg"), map_fig, width = 15, height = 20)
+  #removed Antarctica and sub-antarctic islands in Illustrator and combined with other plots to create Figure 1. -Zoe X
 
@@
 
-  p3 <- ggplot(sum_taxa, aes(x = "", y = perc, fill = taxa)) +
-    geom_col(color = "black") +
-    geom_label_repel(aes(label = labels),
-              position = position_stack(vjust = 0.6),
-            show.legend = FALSE) +
-    scale_fill_viridis_d() +
-    coord_polar(theta = "y") + 
-    theme_void() + labs(fill = "Taxa") + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")
+  # Use data to create a pie chart and clean up colour palette
+  taxa_fig <- ggplot(sum_taxa, aes(x = fct_reorder(taxa, perc), y = perc)) +
+    geom_col(color = "black", fill = "white") +
+    scale_y_continuous(expand = c(0, 0)) +
+    #scale_fill_viridis_d() +
+    #coord_polar(theta = "y") + 
+    theme_classic() + labs(y = "Percentage (%) of preprints", x = "Studied taxa") + 
+    theme(plot.tag = element_text(size = 16, face = "bold")) + coord_flip() +
+    scale_fill_colorhex_d(palette = 1042984, discrete = TRUE)
 
@@
   #sum(sum_types$n) #620
-  p4 <- ggplot(sum_types, aes(x = "", y = perc, fill = type)) +
-    geom_col(color = "black") +
-    geom_label_repel(aes(label = labels),
-              position = position_stack(vjust = 0.6),
-            show.legend = FALSE) +
-    scale_fill_viridis_d() +
-    coord_polar(theta = "y") + 
-    theme_void() + labs(fill = "Article Type") + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")
+
+  type_fig <- ggplot(sum_types, aes(x = fct_reorder(type, perc), y = perc)) +
+    geom_col(color = "black", fill = "white") +
+    scale_y_continuous(expand = c(0, 0)) +
+    #scale_fill_viridis_d() +
+    #coord_polar(theta = "y") + 
+    theme_classic() + labs(y = "Percentage (%) of preprints", x = "Article type") + 
+    theme(plot.tag = element_text(size = 16, face = "bold")) + coord_flip() +
+    scale_fill_colorhex_d(palette = 1042984, discrete = TRUE) + theme(legend.position = "none")
+
+type_taxa <- cowplot::plot_grid(taxa_fig, 
+                   type_fig, 
+                   align = "v", ncol = 2, labels = c('c', 'd'))
+
+  ggsave(here("output", "figs", "taxa_type.svg"), type_taxa)
+
+  #Plot was then imported to illustrator for aesthetic touches and to combine with other plots in Figure 1. - Zoe X
 
@@
 
-p5 <- ggplot(preprints, aes(x = submitting_author_first_publication_year)) +
-  geom_histogram(binwidth = 1, fill = "grey", color = "black") +
-  labs(x = "Year of submitting authors first publication", y = "Number of preprints") +
-  theme_bw() +
+#compute academic age! (Zoe X)
+preprints <- preprints %>% 
+  mutate(preprint_published_year_z = year(preprint_published_date)) %>% 
+  mutate(academic_age = (preprint_published_year_z-submitting_author_first_publication_year))
+
+academic_age <- ggplot(preprints, aes(x = academic_age)) +
+  geom_histogram(binwidth = 1, fill = "white", color = "black") +
+  scale_y_continuous(expand = c(0, 0)) +
+  labs(x = "Years since submitting author's first publication (academic age)", y = "Number of preprints") +
+  geom_vline(aes(xintercept = median(academic_age)), color = "black", linetype = "dashed", size = 0.5) +
+  theme_classic() +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
-count_dat  <- preprints  %>% group_by(submitting_author_first_publication_year)  %>% summarise(n = n())
+#mean(age$academic_age)
 
-model <- glm.nb(n ~ submitting_author_first_publication_year, data = count_dat)
+ggsave(here("output", "figs", "academic_age.svg"), academic_age, width = 7.5, height = 2)
+
+  #Plot was then imported to illustrator for aesthetic touches and to combine with other plots in Figure 1. - Zoe X
+
+count_dat  <- preprints  %>% 
+              distinct(submitting_author, academic_age) %>% 
+              group_by(academic_age) %>% 
+              summarise(n = n())
+
+model <- glm.nb(n ~ academic_age, data = count_dat)
 res <- summary(model)$coefficients
@@
 # Plot the data
-p6 <- data4 %>% filter(!is.na(gender))  %>% tabyl(gender)  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))  %>%  ggplot(aes(x = "", y = percent, fill = gender)) +
-    geom_col(color = "black") +
-    geom_label_repel(aes(label = labels),
-              position = position_stack(vjust = 0.6),
-            show.legend = FALSE) +
+###Zoe's gender pie###
+#female - 37.8, male - 62.2
+
+gender <- c("female", "male")
+percentage <- c(37.8, 62.2)
+sex_ratio<- data.frame(gender, percentage)
+
+sex_ratio <- sex_ratio %>% ggplot(aes(x = "", y = percentage, fill = gender)) +
+    geom_col(color = "black")+
+  scale_fill_manual(values = c("white", "black")) +
     coord_polar(theta = "y") + 
-    theme_void() + labs(fill = "Gender") + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")
+    theme_void()
 
-p7  <- ggdraw() + draw_plot(p5) + draw_plot(p6, x = 0.05, y = 0.40, width = 0.6, height = 0.6)
+ggsave(here("output", "figs", "sex_ratio.svg"), sex_ratio)
 
-## Final plot. World map in the middle with others around
+##Pie was then imported to illustrator for aesthetic touches and to combine with other plots in Figure 1. - Zoe X
 
-layout <- "
-#AAAAAA#
-#AAAAAA#
-#AAAAAA#
-BBBBBBBB
-BBBBBBBB
-BBBBBBBB
-CCCCDDDD
-CCCCDDDD
-##EEEE##
-##EEEE##
-"
+# Load in and plot the final figure
+  fig <- image_read(here("output", "figs", "Figure 1_FINAL.png")) 
+  fig
 
-p_summary <- p1+p2+p3+p4+p7 + plot_layout(design = layout)+ plot_annotation(tag_levels = 'A', tag_suffix=")") + theme(plot.tag = element_text(size = 16, face = "bold"))
-ggsave(p_summary, filename = here("output", "figs", "summary.png"), width = 11, height = 12)
-
-fig1 <- image_read(here("output", "figs", "summary.png"))
-fig1
 ```
@@
 
-After removing five duplicate titles – suggesting a few authors created multiple submissions for the same preprint rather than updating an existing submission – we had data for a total of `r pr` articles with ~55--60 preprints published each month in the last two years ([@fig-summary]A).
+After removing five duplicate titles – suggesting a few authors created multiple submissions for the same preprint rather than updating an existing submission – we had data for a total of `r pr` articles with ~55--60 preprints published bi-monthly in the last two years ([@fig-summary]A).
 *EcoEvoRxiv* hosts papers from authors based in `r length(unique(countries$country))-1` countries, with 90% of the articles coming from just `r nrow(most_use)-1` countries.
@@
 
-p1_pub <- preprints %>% ggplot(aes(x = time_between_preprint_and_pub_days)) + geom_histogram(binwidth = 30) + geom_vline(aes(xintercept = sum_preprints$median), colour = "red", linetype = "dashed", linewidth = 1) + annotate("text", x = sum_preprints$median + 650, y = 60, label = paste0(sum_preprints$median, " days", "(~ ", sum_preprints$median/30, " months)"), size = 10, colour = "red") + labs(x = "Time to Publication (days)", y = "Number of Papers") + theme_classic() + theme(axis.title = element_text(size = 14))
+p1_pub_zoe <- preprints %>% ggplot(aes(x = time_between_preprint_and_pub_days)) +
+  geom_histogram(binwidth = 30, fill = "white", color = "black") +
+  theme_classic() +  geom_vline(aes(xintercept = sum_preprints$median), colour = "black", linetype = "dashed", linewidth = 0.5) + annotate("text", x = sum_preprints$median + 650, y = 60, label = paste0(sum_preprints$median, " days", "(~ ", sum_preprints$median/30, " months)"), colour = "black") + labs(x = "Time to publication (days)", y = "Number of preprints") + theme_classic() + theme(axis.title = element_text(size = 10)) +
+  scale_y_continuous(limits = c(0, 80), expand = c(0, 0))
+
+ggsave(here("output", "figs", "time_to_publication.svg"), p1_pub_zoe)
+
+#Plot was then imported to illustrator for aesthetic touches and to combine with other plots in Figure 2. - Zoe X
 
@@
 
-p2_pub <- preprints  %>% ggplot(aes(x = is_oa)) + geom_bar() + labs(x = "Open Access", y = "Number of Papers") + theme_classic() + theme(axis.title = element_text(size = 14))
+p2_pub <- preprints  %>% ggplot(aes(x = is_oa)) + geom_bar() + labs(x = "Open Access", y = "Number of papers") + theme_classic()  + scale_y_continuous(expand = c(0, 0))
 
-p3_pub <- preprints  %>% ggplot(aes(x = oa_status, fill = oa_status)) + geom_bar() + labs(x = "Open Access Status", y = "Number of Papers") + theme_classic() + theme(axis.title = element_text(size = 14), legend.position = "none") + scale_fill_manual(values = c("bronze" = "#9b6023", "gold" = "#ffd700", "green" = "#008000", "hybrid" = "#6fa8dc", "NA" = "grey", "closed" = "black"))
+ggsave(here("output", "figs", "Open_access_TRUE_FALSE.svg"), p2_pub)
 
-p_pubsummary <- (p1_pub + p2_pub + p3_pub) + plot_annotation(tag_levels = 'A', tag_suffix=")")
-ggsave(p_pubsummary, filename = here("output", "figs", "pubsummary.png"), width = 20, height = 7)
+#Plot was then imported to illustrator for aesthetic touches and to combine with other plots in Figure 2. - Zoe X
+
+p3_pub <- preprints %>% mutate(oa_status = (fct_relevel(oa_status, c("gold","hybrid", "bronze", "green", "closed", "NA"))))  %>% ggplot(aes(x = oa_status, fill = oa_status)) + geom_bar() + labs(x = "Open Access type", y = "Number of papers") + theme_classic() + theme(axis.title = element_text(size = 14), legend.position = "none") + scale_fill_manual(values = c("bronze" = "#9b6023", "gold" = "#ffd700", "green" = "#008000", "hybrid" = "#6fa8dc", "NA" = "grey", "closed" = "black"))+ scale_y_continuous(expand = c(0, 0))
+
+ggsave(here("output", "figs", "Open_Access_type.svg"), p3_pub)
+
+#Plot was then imported to illustrator for aesthetic touches and to combine with other plots in Figure 2. - Zoe X
 
@@
 
-fig2 <- image_read(here("output", "figs", "pubsummary.png"))
+fig2 <- image_read(here("output", "figs", "Figure 2_final.png"))
 fig2

### 2024-05-04 ms/ms.qmd
Flipping some % around in the later paragraphs

@@
 `r utils::packageVersion("roadoi")`) to connect to the Unpaywall platform [@jahn2024].
-Most of the published articles arising from preprints were open access [`r sum_is_oa$n[2]` (`r sum_is_oa$percent[2]*100`%) [@fig-pubsummary]A]; however, the status of many were unknown [`r sum_is_oa$n[3]` (`r sum_is_oa$percent[3]*100`%)], and `r sum_is_oa$n[1]` (`r sum_is_oa$percent[1]*100`%) were published behind paywalls.
+Most of the published articles arising from preprints were open access [`r sum_is_oa$percent[2]*100`% (*n* = `r sum_is_oa$n[2]`); [@fig-pubsummary]A]; however, the status of many were unknown [`r sum_is_oa$percent[3]*100`% (*n* = `r sum_is_oa$n[3]`)], and `r sum_is_oa$percent[1]*100`% (*n* = `r sum_is_oa$n[1]`) were published behind paywalls.
 The type of open access for a published paper in an open-access journal also varied widely ([@fig-pubsummary]B).
@@
 In the spirit of 'openness', we expected data and code sharing among preprints to be greater than in many papers published in research journals [@roche2015public; @o2021preferred].
-Despite this, we found that `r preprint_data[1,2]` (`r preprint_data[1,"percent"]*100`%) of preprints relying on data on *EcoEvoRxiv* did not share data, and `r preprint_code[1,2]` (`r preprint_code[1,"percent"]*100`%) did not share code.
+Despite this, we found that `r preprint_data[1,"percent"]*100`%  (*n* = `r preprint_data[1,2]`) of preprints relying on data on *EcoEvoRxiv* did not share data, and `r preprint_code[1,"percent"]*100`% (*n* = `r preprint_code[1,2]`) did not share code.
 Authors may be reluctant to share data and code for preprints because of the perceived concern that others may acquire and use such data and code prior to publication in a journal.
-Notably, authors of `r pre_article_data[3,2]` (`r pre_article_data[3,"percent"]*100`%) preprints that did not share data at the preprint stage ultimately did share data when the article was published; authors for `r pre_article_data[2,2]` (`r pre_article_data[2,"percent"]*100`%) preprints never shared data.
+Notably, authors of `r pre_article_data[3,"percent"]*100`% (*n* = `r pre_article_data[3,2]`) preprints that did not share data at the preprint stage ultimately did share data when the article was published; authors for `r pre_article_data[2,"percent"]*100`% (*n* = `r pre_article_data[2,2]`) preprints never shared data.
 The same was true for code.
-Overall, `r pre_article_code[3,2]` (`r pre_article_code[3,"percent"]*100`%) preprints had no open code at the preprint stage but did at the published article stage; authors of `r pre_article_code[2,2]` (`r pre_article_code[2,"percent"]*100`%) preprints did not share code on publication.
+Overall, `r pre_article_code[3,"percent"]*100`% (*n* = `r pre_article_code[3,2]`) preprints had no open code at the preprint stage but did at the published article stage; authors of `r pre_article_code[2,"percent"]*100`% (*n* = `r pre_article_code[2,2]`) preprints did not share code on publication.
 Code and data-sharing patterns in our sample of preprints are consistent with analyses sharing practices for published articles (e.g., [@o2021preferred]), even for journals with strict public data archiving policies [@roche2015public].
@@
 One possible explanation is that preprints are not being sent to suitable journals.
-Interestingly, out of the `r nrow(data2)` preprints, only `r pci[2,2]` (`r pci[2,3]*100`%) used Peer Community In (PCI) as a preprint peer-review service.
+Interestingly, out of the `r nrow(data2)` preprints, only `r pci[2,3]*100`% (*n* = `r pci[2,2]`) used Peer Community In (PCI) as a preprint peer-review service.
 Using PCI circumvents editorial decisions without review.
@@
 They often result from a mismatch between preprint and published metadata (e.g., titles and author details).
-In fact, it was reasonably common for titles of preprints to change between the preprint and the published article (`r titles[2,2]` or `r titles[2,3]*100`%).
+In fact, it was reasonably common for titles of preprints to change between the preprint and the published article [`r titles[2,3]*100`% (*n* = `r titles[2,2]`)].
 We found that mismatched metadata almost always contributed to preprints and published articles not being matched automatically in Google Scholar.

### 2024-05-09 ms/ms.qmd
Some changes to intro

@@
 While preprint use in biology has had a slower uptake [@Berg2016], in ecology and evolution, new discipline-specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disseminate research findings.
+Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed, visibility and output of research findings which can lead to more citations [e.g., @colavizza2024analysis]; 2) helping establish precedence of research findings; 3) removing financial barriers to publication; and 4) encouraging constructive and critical feedback from the research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
 Preprints are expected to promote open science, increase the visibility of research (e.g., [@fu2019releasing]), and facilitate the rapid sharing of new discoveries that can have significant impacts on fundamental and applied knowledge globally.
-Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed, visibility and output of research findings which can lead to more citations [e.g., @colavizza2024analysis]; 2) helping establish precedence of research findings; 3) removing financial barriers to publication; and 4) encouraging constructive and critical feedback from the research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
 
-Preprint servers can empower researchers to make their findings more accessible, open, and transparent but only if they are used as forums for spreading and discussing findings within a research community.
-Significant barriers to preprint use still exist globally – from a lack of clarity around preprint policies at journals [@Klebel2020] to a stigma that preprints are viewed by the research community to be of poor quality [@Chiarelli2019] (but see [@Faser2022]).
+Preprint servers can empower researchers to make their research findings more accessible, open, and transparent but only if they are used as forums for spreading and discussing findings within a research community.
+Significant barriers to preprint use still exist globally – from a lack of clarity around preprint policies at journals [@Klebel2020], to a stigma that preprints are viewed by the research community to be of poor quality [@Chiarelli2019] (but see [@Faser2022]).
 Nonetheless, we lack a systematic understanding of the factors that influence preprint use in ecology and evolution.

### 2024-05-10 ms/ms.qmd
Update authors next in line

@@
 
-Authors: Daniel W.A. Noble ^1^, $\ddagger$, Hackathon Participants, Shinichi Nakagawa^2,\*^,Malgorzata Lagisz^2,\*^
+Authors: Daniel W.A. Noble ^1^, $\ddagger$, Zoe A. Xirocostas, Nicholas C. Wu, April R. Martinig, Shinichi Nakagawa^2,\*^,Malgorzata Lagisz^2,\*^
 
@@
 Here, we explore the first 1000+ preprints uploaded to *EcoEvoRxiv* to understand preprint practices and uses in ecology and evolution.
-We focus our attention on better understanding: 1) in what countries authors who use *EcoEvoRxiv* are located; 2) how career stage and gender impact preprint server use; 3) the extent to which authors make use of preprint servers for registered reports and community-driven peer review; 4) the extent to which data and code are shared in preprints; and 5) how many preprints remain unpublished, and for those that are published, how long it took them to become published.
+We focus our attention on better understanding: 1) in what countries authors who use *EcoEvoRxiv* are located; 2) how career stage and gender are associated with preprint server use; 3) the extent to which authors make use of preprint servers for registered reports and community-driven peer review; 4) the extent to which data and code are shared in preprints; and 5) how many preprints remain unpublished, and for those that are published, how long it took them to become published.
 In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other preprint servers to help further educate researchers about the benefits of using community-driven preprint servers to post their research findings.

### 2024-05-14 ms/ms.qmd
Added new ref and dealing with soem additonal comments

@@
 Publishing preprints -- papers communicating non-peer-reviewed research findings -- is now an entrenched practice across a multitude of scientific disciplines [@Ginsparg2011].
-While preprint use in biology has had a slower uptake [@Berg2016], in ecology and evolution, new discipline-specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disseminate research findings.
-Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed, visibility and output of research findings which can lead to more citations [e.g., @colavizza2024analysis]; 2) helping establish precedence of research findings; 3) removing financial barriers to publication; and 4) encouraging constructive and critical feedback from the research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
-Preprints are expected to promote open science, increase the visibility of research (e.g., [@fu2019releasing]), and facilitate the rapid sharing of new discoveries that can have significant impacts on fundamental and applied knowledge globally.
+While the adoption of preprints in biology have been slower relative to other disciplines [@Berg2016], in ecology and evolution, new discipline-specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disseminate research findings.
+Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed and visibility of research findings which can lead to more citations [e.g., @colavizza2024analysis]; 2) helping establish precedence of research findings; 3) removing financial barriers to open access publication; and 4) enabling feedback from the research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
+Preprints are expected to promote open science, increase the visibility of research (e.g., [@fu2019releasing]), and facilitate the rapid sharing of new discoveries that can have significant impacts on fundamental and applied knowledge globally [@ni2024preprint].
 
 Preprint servers can empower researchers to make their research findings more accessible, open, and transparent but only if they are used as forums for spreading and discussing findings within a research community.
-Significant barriers to preprint use still exist globally – from a lack of clarity around preprint policies at journals [@Klebel2020], to a stigma that preprints are viewed by the research community to be of poor quality [@Chiarelli2019] (but see [@Faser2022]).
+Significant barriers to preprint use still exist globally, from a lack of clarity around preprint policies at journals [@Klebel2020] to a stigma that preprints are viewed by the research community to be of poor quality [@Chiarelli2019] (but see [@Faser2022]).
 Nonetheless, we lack a systematic understanding of the factors that influence preprint use in ecology and evolution.
@@
 Here, we explore the first 1000+ preprints uploaded to *EcoEvoRxiv* to understand preprint practices and uses in ecology and evolution.
-We focus our attention on better understanding: 1) in what countries authors who use *EcoEvoRxiv* are located; 2) how career stage and gender are associated with preprint server use; 3) the extent to which authors make use of preprint servers for registered reports and community-driven peer review; 4) the extent to which data and code are shared in preprints; and 5) how many preprints remain unpublished, and for those that are published, how long it took them to become published.
+We aim to better understand: 1) in what countries authors who use *EcoEvoRxiv* are located; 2) how career stage and gender are associated with preprint server use; 3) the extent to which authors make use of preprint servers for registered reports and community-driven peer review; 4) the extent to which data and code are shared in preprints; and 5) how many preprints remain unpublished, and for those that are published, how long it took them to become published.
 In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other preprint servers to help further educate researchers about the benefits of using community-driven preprint servers to post their research findings.
@@
 Originally launched in 2018 on the Center for Open Science preprint platform, *EcoEvoRxiv* has grown to become a popular preprint server for researchers in ecology and evolutionary biology.
-It has since been adopted by the California Digital Library (CDL) to be hosted in perpetuity without fees.
+The server has since been adopted by the California Digital Library (CDL) to be hosted in perpetuity without fees.
 Editors are researchers from across the globe (currently eight different countries) in the fields of ecology and evolutionary biology who volunteer their time to screen papers and push new initiatives in the preprint space.
@@
 Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication (assuming the journal has a policy that recognises pre- and post-prints -- though most do; see https://www.sherpa.ac.uk/romeo/).
-To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the articles available on *EcoEvoRxiv* as of `r gsub("UTC", "", dates[2])` (see Supplement for more details on methods).
-For the purpose of summarising articles on *EcoEvoRxiv* we include both preprints and postprints as 'articles' in our overview analysis.
 
@@
 
+To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the articles available on *EcoEvoRxiv* as of `r gsub("UTC", "", dates[2])` (see Supplement for more details on methods).
+For the purpose of summarising articles on *EcoEvoRxiv* we include both preprints and postprints as 'articles' in our overview analysis.
 After removing five duplicate titles – suggesting a few authors created multiple submissions for the same preprint rather than updating an existing submission – we had data for a total of `r pr` articles with ~55--60 preprints published bi-monthly in the last two years ([@fig-summary]A).

### 2024-05-31 ms/ms.qmd
Intro

@@
 Publishing preprints -- papers communicating non-peer-reviewed research findings -- is now an entrenched practice across a multitude of scientific disciplines [@Ginsparg2011].
-While the adoption of preprints in biology have been slower relative to other disciplines [@Berg2016], in ecology and evolution, new discipline-specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disseminate research findings.
-Preprints attempt to break down barriers to scientific publishing by: 1) increasing the speed and visibility of research findings which can lead to more citations [e.g., @colavizza2024analysis]; 2) helping establish precedence of research findings; 3) removing financial barriers to open access publication; and 4) enabling feedback from the research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
-Preprints are expected to promote open science, increase the visibility of research (e.g., [@fu2019releasing]), and facilitate the rapid sharing of new discoveries that can have significant impacts on fundamental and applied knowledge globally [@ni2024preprint].
+Preprints in biology have had a slower uptake relative to other disciplines [@Berg2016], in ecology and evolution, new discipline-specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disseminate research findings.
+Preprints attempt to break down barriers to scientific publishing by: 1) increasing the visibility of research and the speed at which research findings become available which can lead to more citations [e.g., @colavizza2024analysis]; 2) helping establish precedence of research findings; 3) removing financial barriers to open access publication; and 4) enabling feedback from the research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
+Preprints increase the visibility of research (e.g., [@fu2019releasing]), and facilitate the rapid sharing of scientific knowledge that can have significant impacts on fundamental and applied knowledge globally [@ni2024preprint].
 
 Preprint servers can empower researchers to make their research findings more accessible, open, and transparent but only if they are used as forums for spreading and discussing findings within a research community.
-Significant barriers to preprint use still exist globally, from a lack of clarity around preprint policies at journals [@Klebel2020] to a stigma that preprints are viewed by the research community to be of poor quality [@Chiarelli2019] (but see [@Faser2022]).
-Nonetheless, we lack a systematic understanding of the factors that influence preprint use in ecology and evolution.
-Such an understanding can help inform future initiatives and allow us to work harder in further breaking down barriers to scientific publishing.
+However, significant barriers to the widespread adoption of preprints remain, ranging from a lack of clarity around preprint policies in journals [@Klebel2020] to a stigma within the research community that preprints are of poor quality [@Chiarelli2019] (but see [@Faser2022]).
+Nonetheless, we lack an understanding of the factors that influence preprint use in ecology and evolution.
+Such an understanding may help improve current initiatives (see below), inform future ones and allow us to work harder in further breaking down barriers to scientific publishing.
 
-*EcoEvoRxiv* is one of the few community-driven preprint servers that has paved the way for new initiatives, by accepting multilingual preprints, recognising registered reports and non-traditional research reports, and promoting peer review and community discussion which we hope will improve the quality of preprints and speed up their peer-reviewed publication (e.g., Peer Community In -- PCI [@guillemaud2019peer]).
+*EcoEvoRxiv* is one of the few community-driven preprint servers that has paved the way for new initiatives, by accepting multilingual preprints, registered reports, and non-traditional research reports.
+*EcoEvoRxiv* also promotes peer review and community discussion in the hopes of improving the quality of preprints and speeding up their peer-reviewed publication (e.g., Peer Community In -- PCI [@guillemaud2019peer]).
 Peer Community In allows for fast constructive peer review around a preprint.
@@
 
-Here, we explore the first 1000+ preprints uploaded to *EcoEvoRxiv* to understand preprint practices and uses in ecology and evolution.
-We aim to better understand: 1) in what countries authors who use *EcoEvoRxiv* are located; 2) how career stage and gender are associated with preprint server use; 3) the extent to which authors make use of preprint servers for registered reports and community-driven peer review; 4) the extent to which data and code are shared in preprints; and 5) how many preprints remain unpublished, and for those that are published, how long it took them to become published.
-In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other preprint servers to help further educate researchers about the benefits of using community-driven preprint servers to post their research findings.
+Here, we explore the first 1000+ preprints uploaded to *EcoEvoRxiv* to understand preprint practices and use in ecology and evolution.
+We aim to understand: 1) in what countries authors who use *EcoEvoRxiv* are located; 2) the taxonomic diversity across preprints; 3) whether preprint server use depends on career stage and gender; 4) the extent to which authors make use of preprint servers for registered reports and community-driven peer review; 5) the extent to which data and code are shared in preprints; and 6) how many preprints remain unpublished, and for those that are published, how long it took for them to become published.
+In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other preprint servers to help further clarify the benefits of using community-driven preprint servers to disseminate their research findings.
 

### 2024-06-03 ms/ms.qmd
Up to Breaking down barriers

@@
 
-*EcoEvoRxiv* is run by the Society for Open, Reliable, and Transparent Ecology and Evolutionary biology (SORTEE)[@o2021towards].
-Originally launched in 2018 on the Center for Open Science preprint platform, *EcoEvoRxiv* has grown to become a popular preprint server for researchers in ecology and evolutionary biology.
+*EcoEvoRxiv* is run by the Society for Open, Reliable, and Transparent Ecology and Evolutionary Biology (SORTEE)[@o2021towards].
+Originally launched in 2018 on the Center for Open Science preprint platform, *EcoEvoRxiv* has become a popular preprint server for ecologist and evolutionary biologists.
 The server has since been adopted by the California Digital Library (CDL) to be hosted in perpetuity without fees.
-Editors are researchers from across the globe (currently eight different countries) in the fields of ecology and evolutionary biology who volunteer their time to screen papers and push new initiatives in the preprint space.
-*EcoEvoRxiv* allows authors to post both preprints and postprints, or author-accepted manuscripts -  a version of an accepted or published article without typesetting and formatting by a journal.
-Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication (assuming the journal has a policy that recognises pre- and post-prints -- though most do; see https://www.sherpa.ac.uk/romeo/).
+Editors are ecologists and evolutionary biologists from across the globe who volunteer their time to screen papers and push new initiatives in the preprint space.
+*EcoEvoRxiv* allows authors to post both preprints and postprints (also known as author-accepted manuscripts).
+While preprints are versions of manuscripts by authors before peer-review, postprints are versions of peer-reviewed and accepted articles but without typesetting and formatting by a journal.
+The main reason for publishing postprints on a preprint server is to ensure published articles are openly accessible to everyone without a paywall (i.e., green open access).
+The publication of postprints can be done anytime after publication, provided that journals allow it (which most do; see https://www.sherpa.ac.uk/romeo/).
 
@@
 #| fig-cap: Summary of articles posted to *EcoEvoRxiv*.
-A) Number of articles (preprints and postprints) published monthly to *EcoEvoRxiv* between 2018 and 2023.
-*EcoEvoRxiv* was established in June 2018 before the soft launch in November 2018.
-Notable milestones include when *EcoEvoRxiv* transitioned to the California Digital Library (CDL), the acceptance of Spanish and Portuguese preprints and postprints and when the first IUCN Red list Ecosystem report was accepted; B) Countries that are posting articles (preprints and postprints) to *EcoEvoRxiv* as inferred from the country of affiliation of the submitting author; C) Taxa used / covered in the articles posted to *EcoEvoRxiv* (*n* = 1080 papers); D) Types of preprints accepted on *EcoEvoRxiv* (*n* = 620 papers).
-E) Career stage of authors posting to *EcoEvoRxiv* along with the gender of the submitting author.
+A) Number of articles (preprints and postprints) published on EcoEvoRxiv between 2018 and 2023.
+EcoEvoRxiv was established in June 2018 before the launch in November 2018.
+Notable milestones include EcoEvoRxiv transitioning to the California Digital Library (CDL), the acceptance of preprints and postprints in Spanish and Portuguese, and the acceptance of the first IUCN Red List Ecosystem report; B) Geographic origin of the preprints and postprints uploaded to EcoEvoRxiv, inferred from the country of affiliation of the submitting author; C) Taxa used/covered in the articles posted to EcoEvoRxiv (n = 1080 articles); D) Types of preprints accepted on EcoEvoRxiv (n = 620 articles).
+E) Career stage of authors posting to EcoEvoRxiv along with the gender of the submitting author.
+Values lower than zero are indicative of authors who uploaded preprints before their first scientific publication in a journal.
+
 #| echo: false
@@
 To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the articles available on *EcoEvoRxiv* as of `r gsub("UTC", "", dates[2])` (see Supplement for more details on methods).
-For the purpose of summarising articles on *EcoEvoRxiv* we include both preprints and postprints as 'articles' in our overview analysis.
-After removing five duplicate titles – suggesting a few authors created multiple submissions for the same preprint rather than updating an existing submission – we had data for a total of `r pr` articles with ~55--60 preprints published bi-monthly in the last two years ([@fig-summary]A).
-*EcoEvoRxiv* hosts papers from authors based in `r length(unique(countries$country))-1` countries, with 90% of the articles coming from just `r nrow(most_use)-1` countries.
-North America, Australia, and European countries upload the most preprints with much fewer coming from countries in Africa, Central America, and parts of Asia ([@fig-summary]B).
-Articles covered all major taxonomic groups, with the most common being vertebrates (`r sum_taxa$perc[6]`%), plants (`r sum_taxa$perc[1]`%), and invertebrates (`r sum_taxa$perc[5]`%) ([@fig-summary]C).
+We consider both preprints and postprints as ‘articles’.
+After removing five duplicate titles – suggesting that a few authors created multiple submissions for the same preprint rather than updating the existing submission – we had data for a total of `r pr` articles with ~55--60 preprints published bi-monthly in the last two years ([@fig-summary]A).
+*EcoEvoRxiv* hosts articles from authors based in `r length(unique(countries$country))-1` countries, with 90% of the articles coming from just `r nrow(most_use)-1` countries.
+North America, Australia, and European countries upload the most preprints with many fewer coming from countries in Africa, Central America, and parts of Asia ([@fig-summary]B).
+Articles covered all major taxonomic groups, with the most common being vertebrates (`r round(sum_taxa$perc[6], digits = 1)`%), plants (`r round(sum_taxa$perc[1], digits = 1)`%), and invertebrates (`r round(sum_taxa$perc[5], digits = 1)`%) ([@fig-summary]C).
 
@@
 Given that *EcoEvoRxiv* is a community-driven preprint server it has managed to diversify the types of articles accepted.
-It accepts reports and books that are often not easily accessible, but may contain important data of relevance to research syntheses or for practitioners.
-As a result, articles on *EcoEvoRxiv* are more diverse than those on preprint servers that have more restrictive submission policies; nonetheless, typical research articles are still the most common type of preprint (`r sum_types[sum_types$type == "research article",]$perc`%), followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]D).
+*EcoEvoRxiv* accepts reports and books that are often not easily accessible and may contain important data relevant to research synthesists or practitioners.
+As a result, articles on *EcoEvoRxiv* are more diverse than those on preprint servers that have more restrictive submission policies.
+For example, *bioRxiv* only accepts research articles (https://www.biorxiv.org/submit-a-manuscript).
+Typical research articles are still still the most common type of preprint (`r round(sum_types[sum_types$type == "research article",]$perc, digits = 1)`%), followed by reviews and meta-analyses (`r round(sum_types[sum_types$type == "reviews and meta-analyses",]$perc, digits = 1)`%) and opinion papers (`r round(sum_types[sum_types$type == "opinion",]$perc, digits = 1)`%) ([@fig-summary]D).
 
-Accepting a greater diversity of article types allows *EcoEvoRxiv* to begin dealing with the 'grey literature' problem whereby data that are relevant for research syntheses are not published in typical peer-reviewed journals[@haddaway2015shades; @haddaway2020eight].
-This is reflected by `r nt`% of articles on *EcoEvoRxiv* that could be considered ‘grey literature’ in ecology and evolutionary biology: books, book chapters, reports, and other research output types.
-Currently, *EcoEvoRxiv* does not host many reports (`r sum_types[sum_types$type == "report", "perc"]`%), particularly from governments or industry.
-We would encourage authors to consider posting books, book chapters and reports to ensure they are openly accessible and more easily found.
+Accepting a greater diversity of article types allows *EcoEvoRxiv* to help deal with the 'grey literature' problem, whereby data that are relevant for research syntheses are not published in typical peer-reviewed journals[@haddaway2015shades; @haddaway2020eight].
+This is reflected by `r nt`% of the articles on *EcoEvoRxiv* being books, book chapters, reports, and other research output types, which are typically considered ‘grey literature’ in ecology and evolutionary biology.
+Currently, *EcoEvoRxiv* does not host many reports, particularly from government or industry.
+We would encourage authors to consider posting books, book chapters, and reports to ensure that they are openly accessible and more easily found.
 *EcoEvoRxiv* articles are given a unique DOI and indexed on Google Scholar.

### 2024-06-03 ms/ms.qmd
Up to generational with edits

@@
 
-A significant barrier to the communication of research findings is due to the fact that they are primarily communicated in English [@amano2016languages; @amano2013four; @amano2021ten].
-Communication of research through a single language has major consequences for the global distribution of knowledge resulting in knowledge gaps across some of the most biodiverse and threatened regions in the world [@amano2023role; @zenni2023multi].
-Such gaps also have flow on effects for research syntheses and meta-analyses because they create a distorted picture of our knowledge base that can lead to bias and inadequate sampling that affects policy development and decision-making [@hannah2024language; @zenni2023multi; @white2021geographical; @konno2020ignoring].
+A significant barrier to the communication of research findings is the fact that they are primarily communicated in English [@amano2016languages; @amano2013four; @amano2021ten].
+Communication of research through a single language has major consequences for the global distribution of knowledge, resulting in knowledge gaps across some of the most biodiverse and threatened regions in the world [@amano2023role; @zenni2023multi].
+Such gaps also impact research syntheses and meta-analyses because they create a distorted picture of our knowledge base leading to bias and inadequate sampling that can affect policy development and decision-making [@hannah2024language; @zenni2023multi; @white2021geographical; @konno2020ignoring].
 
-*EcoEvoRxiv* is the only preprint server to date breaking down language barriers to scientific communication; currently accepting English, Spanish, Portuguese and French manuscripts.
+*EcoEvoRxiv* is the only preprint server to date that breaks down language barriers to scientific communication by accepting English, Spanish, Portuguese and French articles.
+*EcoEvoRxiv* plans to expand to other languages as new non-English editors become available.
 Such initiatives are incredibly important if we are to begin filling global voids of scientific knowledge.
-However, multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish preprints and a single Portuguese preprint posted to date.
-Part of the challenge in getting authors to submit non-English preprints is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries and the fact that it accepts preprints in different languages, cultural differences in the perception of preprints, and a strong reliance on traditional publishing models which typically mandate publishing in English.
+However, multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish articles, and a single Portuguese article, posted since starting to accept non-English articles in 2023.
+Part of the challenge in getting authors to submit non-English articles is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries, cultural differences in the perception of articles, and a strong reliance on traditional publishing models which typically mandate publishing in English [@arenas2024academic].
 

### 2024-06-03 supp/supp.qmd
Need to add more details on some analyses
Adding GLM analysis details

@@
 
+## Data Analysis
+
+#### Generational Analysis
+To test whether a greater number of preprints were submitted by authors of earlier 'academic age', as quantified by the submitting authors first year of publication, we used a generalised linear model (GLM) with a negative binomial error distribution.
+We included the number of preprints submitted in a given year as the response variable and the first year of publication as the predictor variable.
+A negative, and significant, slope coefficient indicates support for researchers of earlier career stages submitting more preprints.
+
 # Supplementary Results

### 2024-06-05 ms/ms.qmd
up to cautious open-mindedness

@@
 # Set rounding options
-options(scipen = 1, digits = 2)
+options(scipen = 1, digits = 1)
 
@@
 
-Research papers can take long periods of time to become published (see below).
-However, Early and Mid-Career Researchers (EMCRs) (~10 years post-PhD) are under pressure to publish rapidly to be competitive in job applications, promotions, and obtaining grants to accelerate their careers [@vale2015accelerating; @sarabipour2019value].
+Research papers can take a while to be published (see below).
+However, Early and Mid-Career Researchers (EMCRs) (~10 years post-PhD) are under pressure to publish rapidly to be competitive in job applications, promotions, and obtaining grants to progress their careers [@vale2015accelerating; @sarabipour2019value].
 Preprints are one way EMCRs can achieve faster dissemination and greater visibility [@fu2019releasing].
-As such, we expect EMCRs to accept and adopt preprints more than colleagues at later career stages.
-At the same time, gender differences in preprint use and publication outcomes have been observed in a number of other research fields, including ecology and evolutionary biology [@fox2019gender; @wehner2020comparison].
+As such, EMCRs may be expected to make use of preprints more than colleagues at later career stages.
+At the same time, gender differences in preprint use and publication outcomes have been observed in several research fields, including ecology and evolutionary biology [@fox2019gender; @wehner2020comparison].
 Therefore, such discrepancies are expected to manifest in preprint use on *EcoEvoRxiv*, but it is unclear to what extent.
 Understanding gender publishing patterns is challenging with observational data such as ours because we cannot know the gender of authors for certain but we can use a data-driven approach to ascertain the probability that a particular name is of a given gender (man or women).
-To obtain an idea of an author's gender, we used the R package *gender* (vers.
-`r utils::packageVersion("gender")`; @mullen2021predict) to predict the most likely gender of the submitting author of a preprint.
+To obtain an idea of an author's gender, we used the R package *gender* (v.`r utils::packageVersion("gender")`; @mullen2021predict) to predict the most likely gender of the submitting author of a preprint.
 We acknowledge that our approach does not capture self-assigned and non-binary genders.
@@
 
-Overall, women were less likely to publish preprints on *EcoEvoRxiv* compared to men (women: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`% compared to men: `r (table(data4$gender)[2] / sum(table(data4$gender))*100)`%), which is likely a reflection of the broader publishing disparities between male and female scientists [@fox2019gender].
+Overall, women were less likely to publish preprints on *EcoEvoRxiv* compared to men (women: `r digits((table(data4$gender)[1] / sum(table(data4$gender))*100), 1)`% compared to men: `r digits((table(data4$gender)[2] / sum(table(data4$gender))*100),1)`%), which is likely a reflection of the broader publishing disparities between male and female scientists [@fox2019gender].
 There was also strong evidence that the number of preprints posted decreases with later career stages (negative binomial glm: year slope = `r res[2, "Estimate"]`, SE: `r res[2, "Std.
-Error"]`, *p* < 0.001, N = `r nrow(count_dat[complete.cases(count_dat),])`).
-The majority of preprints were submitted by authors who published their first paper in the last 10 years ([@fig-summary]E), with the median year of first publication of submitting authors being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r round(mean(data2$submitting_author_first_publication_year, na.rm = TRUE),0)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`).
+Error"]`, *p* < 0.001, n = `r nrow(count_dat[complete.cases(count_dat),])` years).
+The majority of preprints were submitted by authors who published their first paper in the last ~10 years ([@fig-summary]E), with the median year since first publication being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r round(mean(data2$submitting_author_first_publication_year, na.rm = TRUE),0)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`).
 These patterns support the expectation that EMCRs may value preprints as a way to make their work more visible and disseminate their findings more quickly.
@@
 #| message: false
-#| fig-cap: Summary of the publication status of preprints on *EcoEvoRxiv*.
-A) Time between submission and publication of preprints on *EcoEvoRxiv*.
-'Preprints' that were published within 2 months (60 days) of being submitted are considered postprints.
-B) Number of preprints that were published in open access journals.
-C) Open access status of preprints published on *EcoEvoRxiv*.
+#| fig-cap: Summary of the publication status of articles on *EcoEvoRxiv*.
+A) Time between uploading article to *EcoEvoRxiv* and publication in peer-reviewed journals.
+Articles that were published within 2 months (60 days) of being submitted are considered postprints and are not included in this figure.
+B) Number of articles that were published in open access journals.
+Artcile DOI's not identified as being open access or not were classified as "Unknown" C) Open access status of published articles uploaded to *EcoEvoRxiv*.
 
@@
 Increased competition in science has raised the bar with respect to the amount of data required for publication [@vale2015accelerating].
-This is a good outcome if it results in more comprehensive research that better clarifies our understanding of the natural world, but it does come at a cost for the rate at which research findings can be disseminated [@vale2015accelerating].
+This requirement is a good outcome if it results in higher impact research that better clarifies our understanding of the natural world, but it does come at a cost for the speed of research dissemination [@vale2015accelerating].
 Preprints have been proposed as a way to disseminate research more quickly as it can take a long time before results are ultimately published [@bourne2017ten; @vale2015accelerating].
-However, data on the time to publication is sparse, and the real benefit of preprints in this context would be reinforced if preprinting can dramatically speed up dissemination.
-We evaluated how long it takes to publish a research paper in ecology and evolution by ascertaining the time between when a preprint was first posted and finally accepted in a peer-reviewed journal.
-In total, `r unpub` papers were still unpublished out of the `r nrow(data2)` (`r (unpub / nrow(data2))*100`%) when these data were collected.
+However, data on the time to publication is needed to quantify the real benefit of preprints in this context.
+
+We estimated how long it takes to publish a research paper in ecology and evolution by recording the time between when a article was first posted on *EcoEvoRxiv*, and its final acceptance in a peer-reviewed journal.
+In total, `r unpub` papers remained unpublished (`r (unpub / nrow(data2))*100`%, n = `r nrow(data2)`) when these data were collected.
 Not all of these papers, however, are anticipated to be published in a peer-reviewed journal (e.g., reports).
-The maximum time between preprint submission and publication was `r sum_preprints$max` days or `r sum_preprints$max/365` years ([@fig-pubsummary]A), and the median time to publication was `r sum_preprints$median` days (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days).
+The median time to publication was `r sum_preprints$median` days (8 months) (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days) with the maximum time to publication being `r sum_preprints$max` days or `r sum_preprints$max/365` years ([@fig-pubsummary]A).
 Our results largely confirm the extended timeframes that most authors experience between writing their research papers and their publication.

### 2024-06-05 ms/ms.qmd
Feedback incorperated

@@
 Publishing preprints -- papers communicating non-peer-reviewed research findings -- is now an entrenched practice across a multitude of scientific disciplines [@Ginsparg2011].
-Preprints in biology have had a slower uptake relative to other disciplines [@Berg2016], in ecology and evolution, new discipline-specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disseminate research findings.
+Preprints in biology have had a slower uptake relative to other disciplines [@Berg2016], but new discipline-specific preprint servers, such as *EcoEvoRxiv* (https://ecoevorxiv.org), provide a means by which ecologists and evolutionary biologists can disseminate research findings.
 Preprints attempt to break down barriers to scientific publishing by: 1) increasing the visibility of research and the speed at which research findings become available which can lead to more citations [e.g., @colavizza2024analysis]; 2) helping establish precedence of research findings; 3) removing financial barriers to open access publication; and 4) enabling feedback from the research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
@@
 We aim to understand: 1) in what countries authors who use *EcoEvoRxiv* are located; 2) the taxonomic diversity across preprints; 3) whether preprint server use depends on career stage and gender; 4) the extent to which authors make use of preprint servers for registered reports and community-driven peer review; 5) the extent to which data and code are shared in preprints; and 6) how many preprints remain unpublished, and for those that are published, how long it took for them to become published.
-In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other preprint servers to help further clarify the benefits of using community-driven preprint servers to disseminate their research findings.
+In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other preprint servers to help further clarify the benefits of using community-driven preprint servers to disseminate research findings.
 
@@
 *EcoEvoRxiv* is run by the Society for Open, Reliable, and Transparent Ecology and Evolutionary Biology (SORTEE)[@o2021towards].
-Originally launched in 2018 on the Center for Open Science preprint platform, *EcoEvoRxiv* has become a popular preprint server for ecologist and evolutionary biologists.
+Originally launched in 2018 on the Center for Open Science preprint platform, *EcoEvoRxiv* has become a popular preprint server for ecologists and evolutionary biologists.
 The server has since been adopted by the California Digital Library (CDL) to be hosted in perpetuity without fees.
@@
 *EcoEvoRxiv* allows authors to post both preprints and postprints (also known as author-accepted manuscripts).
-While preprints are versions of manuscripts by authors before peer-review, postprints are versions of peer-reviewed and accepted articles but without typesetting and formatting by a journal.
+While preprints are versions of manuscripts posted by authors before peer-review, postprints are versions of peer-reviewed and accepted articles but without typesetting and formatting by a journal.
 The main reason for publishing postprints on a preprint server is to ensure published articles are openly accessible to everyone without a paywall (i.e., green open access).
@@
 #| fig-cap: Summary of articles posted to *EcoEvoRxiv*.
-A) Number of articles (preprints and postprints) published on EcoEvoRxiv between 2018 and 2023.
-EcoEvoRxiv was established in June 2018 before the launch in November 2018.
-Notable milestones include EcoEvoRxiv transitioning to the California Digital Library (CDL), the acceptance of preprints and postprints in Spanish and Portuguese, and the acceptance of the first IUCN Red List Ecosystem report; B) Geographic origin of the preprints and postprints uploaded to EcoEvoRxiv, inferred from the country of affiliation of the submitting author; C) Taxa used/covered in the articles posted to EcoEvoRxiv (n = 1080 articles); D) Types of preprints accepted on EcoEvoRxiv (n = 620 articles).
-E) Career stage of authors posting to EcoEvoRxiv along with the gender of the submitting author.
+A) Number of articles (preprints and postprints) published on *EcoEvoRxiv* between 2018 and 2023.
+*EcoEvoRxiv* was established in June 2018 before the launch in November 2018.
+Notable milestones include *EcoEvoRxiv* transitioning to the California Digital Library (CDL), the acceptance of preprints and postprints in Spanish and Portuguese, and the acceptance of the first IUCN Red List Ecosystem report; B) Geographic origin of the preprints and postprints uploaded to *EcoEvoRxiv*, inferred from the country of affiliation of the submitting author; C) Taxa used/covered in the articles posted to *EcoEvoRxiv* (n = 1080 articles); D) Types of preprints accepted on *EcoEvoRxiv* (n = 620 articles).
+E) Career stage of authors posting to *EcoEvoRxiv* along with the gender of the submitting author.
 Values lower than zero are indicative of authors who uploaded preprints before their first scientific publication in a journal.
@@
       replace <- c("United States Of America" = "USA",  "United Kingdom" = "UK",  "Czechia" = "Czech Republic") 
-    countries <- countries  %>% mutate(country = str_replace_all(country, replace))  %>% filter(!is.na(valid_percent ))  %>% mutate(valid_percent_dis = factor(round(valid_percent, 3)*100, ordered = TRUE))
+    countries <- countries  %>% mutate(country = str_replace_all(country, replace))  %>% filter(!is.na(valid_percent ))  %>% mutate(valid_percent_dis = factor(valid_percent, 3)*100, ordered = TRUE)
 
@@
 North America, Australia, and European countries upload the most preprints with many fewer coming from countries in Africa, Central America, and parts of Asia ([@fig-summary]B).
-Articles covered all major taxonomic groups, with the most common being vertebrates (`r round(sum_taxa$perc[6], digits = 1)`%), plants (`r round(sum_taxa$perc[1], digits = 1)`%), and invertebrates (`r round(sum_taxa$perc[5], digits = 1)`%) ([@fig-summary]C).
+Articles covered all major taxonomic groups, with the most common being vertebrates (`r sum_taxa$perc[6]`%), plants (`r sum_taxa$perc[1]`%), and invertebrates (`r sum_taxa$perc[5]`%) ([@fig-summary]C).
 
@@
 For example, *bioRxiv* only accepts research articles (https://www.biorxiv.org/submit-a-manuscript).
-Typical research articles are still still the most common type of preprint (`r round(sum_types[sum_types$type == "research article",]$perc, digits = 1)`%), followed by reviews and meta-analyses (`r round(sum_types[sum_types$type == "reviews and meta-analyses",]$perc, digits = 1)`%) and opinion papers (`r round(sum_types[sum_types$type == "opinion",]$perc, digits = 1)`%) ([@fig-summary]D).
+Typical research articles are still the most common type of preprint (`r sum_types[sum_types$type == "research article",]$perc`%), followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]D).
 
@@
 However, multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish articles, and a single Portuguese article, posted since starting to accept non-English articles in 2023.
-Part of the challenge in getting authors to submit non-English articles is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries, cultural differences in the perception of articles, and a strong reliance on traditional publishing models which typically mandate publishing in English [@arenas2024academic].
+Part of the challenge in getting authors to submit non-English articles is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries, cultural differences in the perception of preprints, and a strong reliance on traditional publishing models which typically mandate publishing in English [@arenas2024academic].
 
@@
 We acknowledge that our approach does not capture self-assigned and non-binary genders.
-As such, our assumptions about an authors gender idendity could be incorrect.
+As such, our assumptions about an author gender identity may be incorrect.
 We only used algorithm-assigned names where the gender was identified with 95% certainty.
@@
 
-Overall, women were less likely to publish preprints on *EcoEvoRxiv* compared to men (women: `r digits((table(data4$gender)[1] / sum(table(data4$gender))*100), 1)`% compared to men: `r digits((table(data4$gender)[2] / sum(table(data4$gender))*100),1)`%), which is likely a reflection of the broader publishing disparities between male and female scientists [@fox2019gender].
-There was also strong evidence that the number of preprints posted decreases with later career stages (negative binomial glm: year slope = `r res[2, "Estimate"]`, SE: `r res[2, "Std.
-Error"]`, *p* < 0.001, n = `r nrow(count_dat[complete.cases(count_dat),])` years).
-The majority of preprints were submitted by authors who published their first paper in the last ~10 years ([@fig-summary]E), with the median year since first publication being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r round(mean(data2$submitting_author_first_publication_year, na.rm = TRUE),0)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`).
-These patterns support the expectation that EMCRs may value preprints as a way to make their work more visible and disseminate their findings more quickly.
+Overall, women were less likely to publish on *EcoEvoRxiv* compared to men (women: `r (table(data4$gender)[2] / sum(table(data4$gender))*100)`%), which is likely a reflection of the broader publishing disparities between male and female scientists [@fox2019gender].
+There was also evidence that the number of preprints posted decreases with later career stages (negative binomial glm: year slope = `r res[2, "Estimate"]`, SE: `r round(res[2, "Std.
+Error"], 2)`, *p* < 0.001, n = `r nrow(count_dat[complete.cases(count_dat),])` years).
+The majority of preprints were submitted by authors who published their first paper in the last ~10 years ([@fig-summary]E), with the median year since first publication being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r mean(data2$submitting_author_first_publication_year, na.rm = TRUE)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`).
+These patterns support the expectation that EMCRs may value preprints as a way to make their work more visible and disseminate their findings more quickly, but it does require more rigorous experimental approaches to validate these findings.
 
@@
 #| fig-cap: Summary of the publication status of articles on *EcoEvoRxiv*.
-A) Time between uploading article to *EcoEvoRxiv* and publication in peer-reviewed journals.
+A) Time between uploading an article to *EcoEvoRxiv* and its publication in a peer-reviewed journal.
 Articles that were published within 2 months (60 days) of being submitted are considered postprints and are not included in this figure.
@@
 Artcile DOI's not identified as being open access or not were classified as "Unknown" C) Open access status of published articles uploaded to *EcoEvoRxiv*.
+For full details on the meaning of each category see https://support.unpaywall.org/support/solutions/articles/44001777288-what-do-the-types-of-oa-status-green-gold-hybrid-and-bronze-mean-.
 
@@
 ### *Cautious 'open'-mindedness of research in preprints*
-In addition to speeding up dissemination, preprints can also be a useful way to ensure that research remains open and accessible to the research community because the paper is available online no matter what the open access status of the publication ends up being [@bourne2017ten; @vale2015accelerating].
-Using the published articles on *EcoEvoRxiv*, we evaluated the open access status of each paper using the R package *roadoi* (vers.
-`r utils::packageVersion("roadoi")`) to connect to the Unpaywall platform [@jahn2024].
-Most of the published articles arising from preprints were open access [`r sum_is_oa$percent[2]*100`% (*n* = `r sum_is_oa$n[2]`); [@fig-pubsummary]A]; however, the status of many were unknown [`r sum_is_oa$percent[3]*100`% (*n* = `r sum_is_oa$n[3]`)], and `r sum_is_oa$percent[1]*100`% (*n* = `r sum_is_oa$n[1]`) were published behind paywalls.
-The type of open access for a published paper in an open-access journal also varied widely ([@fig-pubsummary]B).
+In addition to speeding up dissemination, preprints and postprints can also be a useful way to ensure that research remains open and accessible to the research community irrespective of the accessibility of the final peer-reviewed paper [@bourne2017ten; @vale2015accelerating].
+We evaluated whether articles hosted at *EcoEvoRxiv*, and that were also published in a journal, were published open access.
+The open access status of each published article was obtained using the R package *roadoi* (v.`r utils::packageVersion("roadoi")`) to connect to the Unpaywall platform [@jahn2024].
+Most of the published articles were open access [`r sum_is_oa$percent[2]*100`% (*n* = `r sum_is_oa$n[2]`); [@fig-pubsummary]A]; however, the status of many were unknown [`r sum_is_oa$percent[3]*100`% (*n* = `r sum_is_oa$n[3]`)], and `r sum_is_oa$percent[1]*100`% (*n* = `r sum_is_oa$n[1]`) were published behind paywalls.
+For articles published in open access journals, the degree of open-access also varied widely (e.g., Gold, Hybrid, Green OA etc., [@fig-pubsummary]B).
 
@@
 In the spirit of 'openness', we expected data and code sharing among preprints to be greater than in many papers published in research journals [@roche2015public; @o2021preferred].
-Despite this, we found that `r preprint_data[1,"percent"]*100`%  (*n* = `r preprint_data[1,2]`) of preprints relying on data on *EcoEvoRxiv* did not share data, and `r preprint_code[1,"percent"]*100`% (*n* = `r preprint_code[1,2]`) did not share code.
-Authors may be reluctant to share data and code for preprints because of the perceived concern that others may acquire and use such data and code prior to publication in a journal.
-Notably, authors of `r pre_article_data[3,"percent"]*100`% (*n* = `r pre_article_data[3,2]`) preprints that did not share data at the preprint stage ultimately did share data when the article was published; authors for `r pre_article_data[2,"percent"]*100`% (*n* = `r pre_article_data[2,2]`) preprints never shared data.
+Despite this, we found that `r preprint_data[1,"percent"]*100`%  (*n* = `r preprint_data[1,2]`) of articles relying on data on *EcoEvoRxiv* did not share data, and `r preprint_code[1,"percent"]*100`% (*n* = `r preprint_code[1,2]`) did not share code.
+Authors may be reluctant to share data and code for preprints because of the perceived concern that others may acquire and use such data and code before publication in a journal.
+Notably, authors of `r pre_article_data[3,"percent"]*100`% (*n* = `r pre_article_data[3,2]`) articles that did not share data at the preprint stage ultimately did share data when the article was published; whereas authors of `r pre_article_data[2,"percent"]*100`% (*n* = `r pre_article_data[2,2]`) never shared data.
 The same was true for code.
-Overall, `r pre_article_code[3,"percent"]*100`% (*n* = `r pre_article_code[3,2]`) preprints had no open code at the preprint stage but did at the published article stage; authors of `r pre_article_code[2,"percent"]*100`% (*n* = `r pre_article_code[2,2]`) preprints did not share code on publication.
-Code and data-sharing patterns in our sample of preprints are consistent with analyses sharing practices for published articles (e.g., [@o2021preferred]), even for journals with strict public data archiving policies [@roche2015public].
+Overall, `r pre_article_code[3,"percent"]*100`% (*n* = `r pre_article_code[3,2]`) preprints had no open code at the preprint stage but did at the published article stage; authors of `r pre_article_code[2,"percent"]*100`% (*n* = `r pre_article_code[2,2]`) preprints did not share code with the published article.
+Relatively low code and data-sharing practices in our sample is consistent with analyses of sharing practices for published articles (e.g., [@o2021preferred]), even for journals with strict public data archiving policies [@roche2015public].
 
-# Paving *our* own future of open, transparent and community-driven science
+# Paving our future to open, transparent and community-driven science
 
-Our data-driven approach has allowed us to better understand some of the key elements of uncertainty surrounding preprints and identify shortcomings and areas in need of clarification for authors.
-Several key insights follow from our analysis of the first *EcoEvoRxiv* preprints:
+Our analysis has allowed us to better understand preprinting/postprinting practices in *EcoEvoRxiv*.
+Based on the insights from our analysis, we provide recommendations to authors on ways they can further promote open and transparent research:
 
-- First, authors are encouraged to share their data and code at the preprint stage.
+- First, share your data and code at the preprint stage.
 Sharing data and code early can help improve the quality of research, establish precedence, and improve the transparency and computational reproducibility of scientific findings [@sarabipour2019value].
 Reassuringly, sharing data and code is rarely associated with 'scooping' of research findings [@soeharjono2021reported].
-If authors are worried about data being used unintentionally, clear information surrounding its reuse can include in a license (see https://choosealicense.com).
+If authors are worried about data being used unintentionally, clear information surrounding its reuse can be included in a license (see https://choosealicense.com).
 Data can also be achived with an embargo on its reuse [@roche2014troubleshooting].
-- Second, authors need to be aware of the benefits of posting preprints and postprints for constructive feedback [@bourne2017ten].
-While it is clear preprints help establish precedence and allow findings to be openly accessible, it is still seems rare that constructive discussions form around preprints in an open forum (e.g.
+- Second, take advantage of peer-reviewing services such as Peer Community In (PCI).
+It is clear that the time between posting a preprint and publication is still quite long (~8 months).
+One possible explanation is that preprints are not being sent to suitable journals or are struggling to get into review slowing down constructive feedback that can improve a papers quality.
+Using PCI circumvents editorial decisions without review, yet only `r pci[2,3]*100`% (*n* = `r pci[2,2]`) used PCI.
+Using such services will ensure that authors receive faster feedback on a paper.
+Ninety-three journals currently accept PCI reviews and recommendations when considering a paper for publication (https://peercommunityin.org/pci-friendly-journals/).
+- Third, seek out and contribute to constructive feedback on preprints [@bourne2017ten].
+While it is clear that preprints help establish precedence and allow findings to be openly accessible, it is still seems rare that constructive discussions form around preprints in an open forum (e.g.
 bioRxiv [@anderson2020biorxiv]).
@@
 Clearly, as a community, we need to provide better platforms that document discussions around preprint findings.
-Such discussions help the authors improve their work and communicate their findings more effectively (when done constructively, of course).
-One way to facilitate such discussions may be to use open peer reviewing services, such as *Peer Community In* (PCI) or *PubPeer* (see also [@avissar2024recommendations] for more options), to provide feedback on preprints.
-- Third, it remains clear that the time between posting a preprint and publication is still quite long.
-One possible explanation is that preprints are not being sent to suitable journals.
-Interestingly, out of the `r nrow(data2)` preprints, only `r pci[2,3]*100`% (*n* = `r pci[2,2]`) used Peer Community In (PCI) as a preprint peer-review service.
-Using PCI circumvents editorial decisions without review.
-As such, it ensures that authors receive faster feedback on a paper and a more realistic recommendation of where such work is likely to be published.
-Many journals now accept PCI reviews and recommendations when publishing a paper, which may help facilitate faster publication; though more journals could incorperate PCI in thier policies.
-- Finally, while most preprints get seamlessly connected and merged with their published version some remain disconnected.
+Such discussions help authors improve their work and communicate their findings more effectively (when done constructively, of course).
+One way to facilitate such discussions may be to use open preprint peer-review services such as *Peer Community In* (PCI) or *PubPeer* (see also [@avissar2024recommendations]) to provide feedback on preprints.
+- Finally, keep your preprints updated.
+While most preprints get seamlessly connected and merged with their published version, some remain 'disconnected' as separate articles.
 Incorrect cross-linking by indexing platforms (e.g., Google Scholar) can create confusion and lead to frustration among authors.
-Thankfully, the reasons for unmatched preprints and publications are well understood and easily rectified.
+Thankfully, the reasons for unmatched preprints and publications are well-understood and easily rectified.
 They often result from a mismatch between preprint and published metadata (e.g., titles and author details).
-In fact, it was reasonably common for titles of preprints to change between the preprint and the published article [`r titles[2,3]*100`% (*n* = `r titles[2,2]`)].
+For example, nearly one theird of articles changed their title from preprint submission to publication [`r titles[2,3]*100`% (*n* = `r titles[2,2]`)].
 We found that mismatched metadata almost always contributed to preprints and published articles not being matched automatically in Google Scholar.
-We recommend that authors ensure that, when preprints are published in a journal, they update their preprint with the publication DOI, especially if their title has changed.
-This is quite easy for authors to do on *EcoEvoRxiv*, and it will ensure that the preprint is linked to the published article and that the citations are merged.
-It will also create a link between the final preprint and the published paper so that, no matter the open access status of the publication, the research findings will remain openly accessible, saving costs for authors and improving the visibility and use of research.
+We recommend that authors update their preprints accepted to journals with the publication’s DOI, especially if their title has changed.
+This is very easy for authors to do on *EcoEvoRxiv*, and ensures that the preprint is correctly linked to the published article and citations are appropriately merged.
+Adding DOIs will also create a link between the final preprint and the published paper so that, no matter the open access status of the publication, the research findings will remain openly accessible, saving costs for authors (i.e., but not having to pay open access fees) and improving the visibility and use of research.
 
-Despite the early successes of the new initiatives taken by *EcoEvoRxiv*, much work needs to be done to improve our community’s understanding and use of pre- and post-prints.
+Despite the early successes of the new initiatives taken by *EcoEvoRxiv*, much work remains to be done to improve the understanding and use of pre- and postprints within our community.
 We view this perspective piece as a small step towards achieving that goal.
-Authors must also be aware of the benefits of using community-driven preprint servers and the unique initiatives being pursued.
+We hope that authors are more aware of the benefits of using community-driven preprint servers and the unique initiatives they are able to persue.
 Community-driven preprint servers are capable of setting their own agenda and are driven by the needs and desires of the community.
@@
 Volunteers at *EcoEvoRxiv* are encouraged to remain open to new and innovative ways to improve publication and open science practices.
-We believe that the future of preprints is bright, and community-driven initiatives, such as *EcoEvoRxiv*, are set to play a crucial role in the future of scientific publishing.
+We believe that the future of preprints is bright, and community-driven initiatives, such as *EcoEvoRxiv* will play a crucial role in the future of scientific publishing.
 
 # Acknowledgements
-We would like to thank the California Digital Library (CDL) and the CDL team (particularly Alainna Wrigley) for their support in hosting and maintaining *EcoEvoRxiv* for the Society for Open, Reliable, and Transparent Ecology and Evolutionary biology (SORTEE).
-We would also like to thank Gabriela Hidalgo and Daisy Larios for helping connect us with the IUCN and facilitating discussions to make *EcoEvoRxiv* a place where IUCN reports can be posted.
+We would like to thank the California Digital Library (CDL) and the CDL team (particularly Alainna Wrigley) for their support in hosting and maintaining *EcoEvoRxiv* for the Society for Open, Reliable, and Transparent Ecology and Evolutionary Biology (SORTEE).
+We would like to thank Gabriela Hidalgo and Daisy Larios for helping connect us with the IUCN and facilitating discussions to make *EcoEvoRxiv* a place where IUCN reports can be posted.
 Finally, we would also like to thank the endless number of SORTEE volunteers, and those especially on the *EcoEvoRxiv* Committee, who have helped to make *EcoEvoRxiv* a success.
@@
 
+# Conflicts of Interest
+The authors would like to awknowledge competing interests on the perspectives presented in this paper given that many are founding members of *EcoEvoRxiv* (DWAN, SN, ML) and/or are part of the *EcoEvoRxiv* committee.
+
 # References

### 2024-06-05 ms/ms.qmd
Some fixes

@@
 Our analysis has allowed us to better understand preprinting/postprinting practices in *EcoEvoRxiv*.
+In summary, *EcoEvoRxiv* articles are diverse but with primary research articles on vertebrates comprising most of the articles posted.
+North America, Europe and Australia use *EcoEvoRxiv* the most with very few non-English language articles to date.
+Earlier career researchers and submitting authors with 'male-associated names' tended to use *EcoEvoRxiv* the most.
+Articles posted to *EcoEvoRxiv* tend to take up to 8 months to become published with many articles not be open access.
+Code and data sharing was also relatively uncommon at the preprint stage.
 Based on the insights from our analysis, we provide recommendations to authors on ways they can further promote open and transparent research:
@@
 
-# Conflicts of Interest
+# Conflict of Interest
 The authors would like to awknowledge competing interests on the perspectives presented in this paper given that many are founding members of *EcoEvoRxiv* (DWAN, SN, ML) and/or are part of the *EcoEvoRxiv* committee.

### 2024-06-05 ms/ms.qmd
Fixed up percentages and numbers in the text

@@
       replace <- c("United States Of America" = "USA",  "United Kingdom" = "UK",  "Czechia" = "Czech Republic") 
-    countries <- countries  %>% mutate(country = str_replace_all(country, replace))  %>% filter(!is.na(valid_percent ))  %>% mutate(valid_percent_dis = factor(valid_percent, 3)*100, ordered = TRUE)
+    countries <- countries  %>% mutate(country = str_replace_all(country, replace))  %>% filter(!is.na(valid_percent ))  %>% mutate(valid_percent_dis = factor(round(valid_percent, 3)*100, ordered = TRUE))
 
@@
 ##---------------------##
-# Types pf preprints
+# Types of preprints
 ##---------------------##
@@
 We consider both preprints and postprints as ‘articles’.
-After removing five duplicate titles – suggesting that a few authors created multiple submissions for the same preprint rather than updating the existing submission – we had data for a total of `r pr` articles with ~55--60 preprints published bi-monthly in the last two years ([@fig-summary]A).
-*EcoEvoRxiv* hosts articles from authors based in `r length(unique(countries$country))-1` countries, with 90% of the articles coming from just `r nrow(most_use)-1` countries.
+After removing five duplicate titles – suggesting that a few authors created multiple submissions for the same preprint rather than updating the existing submission – we had data for a total of `r pr` articles with ~55--60 preprints published approximately monthly in the last two years ([@fig-summary]A).
+*EcoEvoRxiv* hosts articles from authors based in `r length(unique(countries$country))` countries, with 90% of the articles coming from just `r nrow(most_use)-1` countries.
 North America, Australia, and European countries upload the most preprints with many fewer coming from countries in Africa, Central America, and parts of Asia ([@fig-summary]B).
@@
 
-Overall, women were less likely to publish on *EcoEvoRxiv* compared to men (women: `r (table(data4$gender)[2] / sum(table(data4$gender))*100)`%), which is likely a reflection of the broader publishing disparities between male and female scientists [@fox2019gender].
+Overall, women were less likely to publish on *EcoEvoRxiv* compared to men (women: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`%), which is likely a reflection of the broader publishing disparities between male and female scientists [@fox2019gender].
 There was also evidence that the number of preprints posted decreases with later career stages (negative binomial glm: year slope = `r res[2, "Estimate"]`, SE: `r round(res[2, "Std.
 Error"], 2)`, *p* < 0.001, n = `r nrow(count_dat[complete.cases(count_dat),])` years).
-The majority of preprints were submitted by authors who published their first paper in the last ~10 years ([@fig-summary]E), with the median year since first publication being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r mean(data2$submitting_author_first_publication_year, na.rm = TRUE)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`).
+The majority of preprints were submitted by authors who published their first paper in the last ~10 years ([@fig-summary]E), with the median year since first publication being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r mean(data2$submitting_author_first_publication_year, na.rm = TRUE)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`, n = `r sum(complete.cases(data2$submitting_author_first_publication_year))`).
 These patterns support the expectation that EMCRs may value preprints as a way to make their work more visible and disseminate their findings more quickly, but it does require more rigorous experimental approaches to validate these findings.
@@
 Not all of these papers, however, are anticipated to be published in a peer-reviewed journal (e.g., reports).
-The median time to publication was `r sum_preprints$median` days (8 months) (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days) with the maximum time to publication being `r sum_preprints$max` days or `r sum_preprints$max/365` years ([@fig-pubsummary]A).
+The median time to publication for preprints was `r sum_preprints$median` days (8 months) (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days) with the maximum time to publication being `r sum_preprints$max` days or `r sum_preprints$max/365` years ([@fig-pubsummary]A).
 Our results largely confirm the extended timeframes that most authors experience between writing their research papers and their publication.
@@
 The open access status of each published article was obtained using the R package *roadoi* (v.`r utils::packageVersion("roadoi")`) to connect to the Unpaywall platform [@jahn2024].
-Most of the published articles were open access [`r sum_is_oa$percent[2]*100`% (*n* = `r sum_is_oa$n[2]`); [@fig-pubsummary]A]; however, the status of many were unknown [`r sum_is_oa$percent[3]*100`% (*n* = `r sum_is_oa$n[3]`)], and `r sum_is_oa$percent[1]*100`% (*n* = `r sum_is_oa$n[1]`) were published behind paywalls.
+Most of the published articles were open access [`r sum_is_oa$valid_percent[2]*100`% (*n* = `r sum_is_oa$n[2]` out of `r sum(sum_is_oa$n[1:2])` where the status was known); [@fig-pubsummary]A]; however, `r sum_is_oa$valid_percent[1]*100`% (*n* = `r sum_is_oa$n[1]`) were published behind paywalls.
 For articles published in open access journals, the degree of open-access also varied widely (e.g., Gold, Hybrid, Green OA etc., [@fig-pubsummary]B).
@@
 In the spirit of 'openness', we expected data and code sharing among preprints to be greater than in many papers published in research journals [@roche2015public; @o2021preferred].
-Despite this, we found that `r preprint_data[1,"percent"]*100`%  (*n* = `r preprint_data[1,2]`) of articles relying on data on *EcoEvoRxiv* did not share data, and `r preprint_code[1,"percent"]*100`% (*n* = `r preprint_code[1,2]`) did not share code.
-Authors may be reluctant to share data and code for preprints because of the perceived concern that others may acquire and use such data and code before publication in a journal.
-Notably, authors of `r pre_article_data[3,"percent"]*100`% (*n* = `r pre_article_data[3,2]`) articles that did not share data at the preprint stage ultimately did share data when the article was published; whereas authors of `r pre_article_data[2,"percent"]*100`% (*n* = `r pre_article_data[2,2]`) never shared data.
+Despite this, we found that `r (preprint_data[1,"n"]/sum(preprint_data[c(1,3),"n"]))*100`%  (*n* = `r preprint_data[1,2]`) of articles relying on data on *EcoEvoRxiv* did not share data, and `r (preprint_code[1,"n"]/sum(preprint_code[c(1,3),"n"]))*100`% (*n* = `r preprint_code[1,2]`) did not share code.
+
+Authors may be reluctant to share data and code for preprints because of the perceived concern that others may acquire and use their data and code before publication in a journal.
+Authors of `r pre_article_data[3,"percent"]*100`% (*n* = `r pre_article_data[3,2]`) articles that did not share data at the preprint stage did ultimately share data when the article was published; whereas authors of `r pre_article_data[2,"percent"]*100`% (*n* = `r pre_article_data[2,2]`) never shared data.
+However, `r pre_article_data[1,"percent"]*100`% (*n* = `r pre_article_data[1,2]`) shared data at both stages.
 The same was true for code.
-Overall, `r pre_article_code[3,"percent"]*100`% (*n* = `r pre_article_code[3,2]`) preprints had no open code at the preprint stage but did at the published article stage; authors of `r pre_article_code[2,"percent"]*100`% (*n* = `r pre_article_code[2,2]`) preprints did not share code with the published article.
+Overall, `r pre_article_code[3,"percent"]*100`% (*n* = `r pre_article_code[3,2]`) preprints had no open code at the preprint stage but did at the published article stage and authors of `r pre_article_code[2,"percent"]*100`% (*n* = `r pre_article_code[2,2]`) preprints did not share code at either stage.
+However, `r pre_article_code[1,"percent"]*100`% (*n* = `r pre_article_code[1,2]`) shared code at both stages.
 Relatively low code and data-sharing practices in our sample is consistent with analyses of sharing practices for published articles (e.g., [@o2021preferred]), even for journals with strict public data archiving policies [@roche2015public].

### 2024-06-06 ms/ms.qmd
editing in places to streamline writing

@@
 Preprints in biology have had a slower uptake relative to other disciplines [@Berg2016], but new discipline-specific preprint servers, such as *EcoEvoRxiv* (https://ecoevorxiv.org), provide a means by which ecologists and evolutionary biologists can disseminate research findings.
-Preprints attempt to break down barriers to scientific publishing by: 1) increasing the visibility of research and the speed at which research findings become available which can lead to more citations [e.g., @colavizza2024analysis]; 2) helping establish precedence of research findings; 3) removing financial barriers to open access publication; and 4) enabling feedback from the research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
-Preprints increase the visibility of research (e.g., [@fu2019releasing]), and facilitate the rapid sharing of scientific knowledge that can have significant impacts on fundamental and applied knowledge globally [@ni2024preprint].
+Preprints attempt to break down barriers to scientific publishing by: 1) increasing the visibility of research and the speed at which research findings become available which can lead to more citations [e.g., @colavizza2024analysis; @fu2019releasing]; 2) helping establish precedence of research findings; 3) removing financial barriers to open access publication; and 4) enabling feedback from the research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
+Ultimately, preprints can facilitate the rapid sharing of scientific knowledge that can have significant impacts on fundamental and applied knowledge globally [@ni2024preprint].
 
@@
 Peer Community In allows for fast constructive peer review around a preprint.
-Peer reviews are transparent and published online and the community makes a recommendation on where the reasearch findings should be published [@guillemaud2019peer].
+Peer reviews are transparent and published online [@guillemaud2019peer].
 
-Here, we explore the first 1000+ preprints uploaded to *EcoEvoRxiv* to understand preprint practices and use in ecology and evolution.
+Here, we explore the first preprints uploaded to *EcoEvoRxiv* to understand preprint practices and use in ecology and evolution.
 We aim to understand: 1) in what countries authors who use *EcoEvoRxiv* are located; 2) the taxonomic diversity across preprints; 3) whether preprint server use depends on career stage and gender; 4) the extent to which authors make use of preprint servers for registered reports and community-driven peer review; 5) the extent to which data and code are shared in preprints; and 6) how many preprints remain unpublished, and for those that are published, how long it took for them to become published.
@@
 
-Given that *EcoEvoRxiv* is a community-driven preprint server it has managed to diversify the types of articles accepted.
-*EcoEvoRxiv* accepts reports and books that are often not easily accessible and may contain important data relevant to research synthesists or practitioners.
+Accepting a greater diversity of article types allows *EcoEvoRxiv* to help deal with the 'grey literature' problem, whereby data that are relevant for research syntheses are not published in typical peer-reviewed journals [@haddaway2015shades; @haddaway2020eight].
+*EcoEvoRxiv* has made a concerted effort to diversify the types of articles accepted.
+This is reflected by `r nt`% of the articles on *EcoEvoRxiv* being books, book chapters, reports, and other research output types, which are typically considered ‘grey literature’ in ecology and evolutionary biology.
 As a result, articles on *EcoEvoRxiv* are more diverse than those on preprint servers that have more restrictive submission policies.
 For example, *bioRxiv* only accepts research articles (https://www.biorxiv.org/submit-a-manuscript).
-Typical research articles are still the most common type of preprint (`r sum_types[sum_types$type == "research article",]$perc`%), followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]D).
 
-Accepting a greater diversity of article types allows *EcoEvoRxiv* to help deal with the 'grey literature' problem, whereby data that are relevant for research syntheses are not published in typical peer-reviewed journals[@haddaway2015shades; @haddaway2020eight].
-This is reflected by `r nt`% of the articles on *EcoEvoRxiv* being books, book chapters, reports, and other research output types, which are typically considered ‘grey literature’ in ecology and evolutionary biology.
+Typical research articles are still the most common type of preprint on *EcoEvoRxiv* (`r sum_types[sum_types$type == "research article",]$perc`%), followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]D).
 Currently, *EcoEvoRxiv* does not host many reports, particularly from government or industry.
@@
 *EcoEvoRxiv* has already formed fruitful partnerships with the International Union for Conservation of Nature (IUCN) as a place where IUCN reports can be hosted to make them more easily accessible to the broader research community.
-For example, IUCN Red Ecosystem Reports are now posted to *EcoEvoRxiv* and our community has been able to work closely with the IUCN to ensure these documents meet the IUCN requirements.
+For example, IUCN Red-list Ecosystem Reports are now posted to *EcoEvoRxiv* and our community has been able to work closely with the IUCN to ensure these documents meet the IUCN requirements.
 

### 2024-06-06 ms/ms.qmd
Mored edits of main body of text

@@
 *EcoEvoRxiv* also promotes peer review and community discussion in the hopes of improving the quality of preprints and speeding up their peer-reviewed publication (e.g., Peer Community In -- PCI [@guillemaud2019peer]).
-Peer Community In allows for fast constructive peer review around a preprint.
-Peer reviews are transparent and published online [@guillemaud2019peer].
+Peer Community In allows for fast, constructive peer review around a preprint with peer reviews being transparent and published online [@guillemaud2019peer].
 
 Here, we explore the first preprints uploaded to *EcoEvoRxiv* to understand preprint practices and use in ecology and evolution.
-We aim to understand: 1) in what countries authors who use *EcoEvoRxiv* are located; 2) the taxonomic diversity across preprints; 3) whether preprint server use depends on career stage and gender; 4) the extent to which authors make use of preprint servers for registered reports and community-driven peer review; 5) the extent to which data and code are shared in preprints; and 6) how many preprints remain unpublished, and for those that are published, how long it took for them to become published.
+We aim to understand: 1) in what countries authors who use *EcoEvoRxiv* are located; 2) the taxonomic diversity across preprints; 3) whether preprint server use depends on career stage and gender; 4) the extent to which authors make use of preprint servers for reports and community-driven peer review; 5) the extent to which data and code are shared in preprints; and 6) how many preprints remain unpublished, and for those that are published, how long it took for them to become published.
 In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other preprint servers to help further clarify the benefits of using community-driven preprint servers to disseminate research findings.
@@
 As such, EMCRs may be expected to make use of preprints more than colleagues at later career stages.
-At the same time, gender differences in preprint use and publication outcomes have been observed in several research fields, including ecology and evolutionary biology [@fox2019gender; @wehner2020comparison].
-Therefore, such discrepancies are expected to manifest in preprint use on *EcoEvoRxiv*, but it is unclear to what extent.
-Understanding gender publishing patterns is challenging with observational data such as ours because we cannot know the gender of authors for certain but we can use a data-driven approach to ascertain the probability that a particular name is of a given gender (man or women).
-To obtain an idea of an author's gender, we used the R package *gender* (v.`r utils::packageVersion("gender")`; @mullen2021predict) to predict the most likely gender of the submitting author of a preprint.
-We acknowledge that our approach does not capture self-assigned and non-binary genders.
-As such, our assumptions about an author gender identity may be incorrect.
-We only used algorithm-assigned names where the gender was identified with 95% certainty.
-For the remaining names, we performed manual searches to determine gender based on the pronouns and photographs from professional and personal websites.
-Our data on gender has only two missing values--one where the first name of the submitting author was missing and the other one for a collective submission.
-
-Overall, women were less likely to publish on *EcoEvoRxiv* compared to men (women: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`%), which is likely a reflection of the broader publishing disparities between male and female scientists [@fox2019gender].
-There was also evidence that the number of preprints posted decreases with later career stages (negative binomial glm: year slope = `r res[2, "Estimate"]`, SE: `r round(res[2, "Std.
+We collected data on 'academic age' of submitting authors by looking at Google Scholar profiles of authors (when avioable) and recording their first year of publication in a peer-reviewed journal.
+While this is a rough estimate of career stage, there was evidence that the number of preprints posted decreases with later career stages (negative binomial glm: year slope = `r res[2, "Estimate"]`, SE: `r round(res[2, "Std.
 Error"], 2)`, *p* < 0.001, n = `r nrow(count_dat[complete.cases(count_dat),])` years).
@@
 These patterns support the expectation that EMCRs may value preprints as a way to make their work more visible and disseminate their findings more quickly, but it does require more rigorous experimental approaches to validate these findings.
+
+Gender differences in preprint use and publication outcomes have also been observed in several research fields, including ecology and evolutionary biology [@fox2019gender; @wehner2020comparison].
+Therefore, such discrepancies are expected to manifest in preprint use on *EcoEvoRxiv*, but it is unclear to what extent.
+Understanding gender publishing patterns is challenging with observational data such as ours because we cannot know the gender of authors for certain but we can use a data-driven approach to ascertain the probability that a particular name is of a given gender (man or women).
+To obtain a rough idea of an author's gender, we used the R package *gender* (v.`r utils::packageVersion("gender")`; @mullen2021predict) to predict the most likely gender of the submitting author of a preprint.
+We only used algorithm-assigned names where the gender was identified with 95% certainty.
+For the remaining names, we performed manual searches to determine gender based on the pronouns and photographs from professional and personal websites.
+We acknowledge that our approach does not capture self-assigned and non-binary genders.
+As such, our assumptions about an author gender identity may be incorrect.
+Our data on gender had only two missing values--one where the first name of the submitting author was missing and the other one for a collective submission.
+As expected, women were less likely to publish on *EcoEvoRxiv* compared to men (women: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`%), which may be a reflection of the broader publishing disparities between male and female scientists [@fox2019gender].
 
@@
 Not all of these papers, however, are anticipated to be published in a peer-reviewed journal (e.g., reports).
-The median time to publication for preprints was `r sum_preprints$median` days (8 months) (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days) with the maximum time to publication being `r sum_preprints$max` days or `r sum_preprints$max/365` years ([@fig-pubsummary]A).
+Nonetheless, the median time to publication for preprints was `r sum_preprints$median` days (8 months) (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days) with the maximum time to publication being `r sum_preprints$max` days or `r sum_preprints$max/365` years ([@fig-pubsummary]A).
 Our results largely confirm the extended timeframes that most authors experience between writing their research papers and their publication.
@@
 Code and data sharing was also relatively uncommon at the preprint stage.
-Based on the insights from our analysis, we provide recommendations to authors on ways they can further promote open and transparent research:
+While we attempted to collect data on community discussion around preprints no such data was found on preprint landing pages, likely reflecting inadequate functionality and cross-linking with sources where such discussion is occuring.
+Based on the insights from our analysis, we provide recommendations to authors, editors and the scientific community on ways they can further promote open and transparent research through preprints:
 
@@
 This is very easy for authors to do on *EcoEvoRxiv*, and ensures that the preprint is correctly linked to the published article and citations are appropriately merged.
-Adding DOIs will also create a link between the final preprint and the published paper so that, no matter the open access status of the publication, the research findings will remain openly accessible, saving costs for authors (i.e., but not having to pay open access fees) and improving the visibility and use of research.
+Adding DOIs will also create a link between the final preprint and the published paper so that, no matter the open access status of the publication, the research findings will remain openly accessible, saving costs for authors (i.e., by not having to pay open access fees) and improving the visibility and use of research.
 

### 2024-06-06 ms/ms.qmd
Shinichi's edits and some additoonal fixes

@@
 Preprints in biology have had a slower uptake relative to other disciplines [@Berg2016], but new discipline-specific preprint servers, such as *EcoEvoRxiv* (https://ecoevorxiv.org), provide a means by which ecologists and evolutionary biologists can disseminate research findings.
-Preprints attempt to break down barriers to scientific publishing by: 1) increasing the visibility of research and the speed at which research findings become available which can lead to more citations [e.g., @colavizza2024analysis; @fu2019releasing]; 2) helping establish precedence of research findings; 3) removing financial barriers to open access publication; and 4) enabling feedback from the research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
+Preprints attempt to break down barriers to scientific publishing by: 1) increasing the visibility of research and the speed at which research findings become available, which can lead to more citations [e.g., @colavizza2024analysis; @fu2019releasing]; 2) helping establish the precedence of research findings; 3) removing financial barriers to open access publication; and 4) enabling feedback from the research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
 Ultimately, preprints can facilitate the rapid sharing of scientific knowledge that can have significant impacts on fundamental and applied knowledge globally [@ni2024preprint].
@@
 Originally launched in 2018 on the Center for Open Science preprint platform, *EcoEvoRxiv* has become a popular preprint server for ecologists and evolutionary biologists.
-The server has since been adopted by the California Digital Library (CDL) to be hosted in perpetuity without fees.
+The server has since been adopted by the California Digital Library (CDL).
 Editors are ecologists and evolutionary biologists from across the globe who volunteer their time to screen papers and push new initiatives in the preprint space.
@@
 The main reason for publishing postprints on a preprint server is to ensure published articles are openly accessible to everyone without a paywall (i.e., green open access).
-The publication of postprints can be done anytime after publication, provided that journals allow it (which most do; see https://www.sherpa.ac.uk/romeo/).
+Postprints can be published anytime, provided that journals allow it (which most do; see https://www.sherpa.ac.uk/romeo/).
 
@@
 *EcoEvoRxiv* hosts articles from authors based in `r length(unique(countries$country))` countries, with 90% of the articles coming from just `r nrow(most_use)-1` countries.
-North America, Australia, and European countries upload the most preprints with many fewer coming from countries in Africa, Central America, and parts of Asia ([@fig-summary]B).
+North America, Australia, and European countries upload the most preprints, with many fewer coming from countries in Africa, Central America, and parts of Asia ([@fig-summary]B).
 Articles covered all major taxonomic groups, with the most common being vertebrates (`r sum_taxa$perc[6]`%), plants (`r sum_taxa$perc[1]`%), and invertebrates (`r sum_taxa$perc[5]`%) ([@fig-summary]C).
@@
 This is reflected by `r nt`% of the articles on *EcoEvoRxiv* being books, book chapters, reports, and other research output types, which are typically considered ‘grey literature’ in ecology and evolutionary biology.
-As a result, articles on *EcoEvoRxiv* are more diverse than those on preprint servers that have more restrictive submission policies.
+As a result, articles on *EcoEvoRxiv* are more diverse than those on preprint servers which have more restrictive submission policies.
 For example, *bioRxiv* only accepts research articles (https://www.biorxiv.org/submit-a-manuscript).
@@
 A significant barrier to the communication of research findings is the fact that they are primarily communicated in English [@amano2016languages; @amano2013four; @amano2021ten].
-Communication of research through a single language has major consequences for the global distribution of knowledge, resulting in knowledge gaps across some of the most biodiverse and threatened regions in the world [@amano2023role; @zenni2023multi].
+Research communication through a single language has major consequences for the global distribution of knowledge, resulting in knowledge gaps across some of the most biodiverse and threatened regions in the world [@amano2023role; @zenni2023multi].
 Such gaps also impact research syntheses and meta-analyses because they create a distorted picture of our knowledge base leading to bias and inadequate sampling that can affect policy development and decision-making [@hannah2024language; @zenni2023multi; @white2021geographical; @konno2020ignoring].
@@
 However, multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish articles, and a single Portuguese article, posted since starting to accept non-English articles in 2023.
-Part of the challenge in getting authors to submit non-English articles is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries, cultural differences in the perception of preprints, and a strong reliance on traditional publishing models which typically mandate publishing in English [@arenas2024academic].
+Part of the challenge in getting authors to submit non-English articles is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries, cultural differences in the perception of preprints, and a strong reliance on traditional publishing models that typically mandate publishing in English [@arenas2024academic].
 
@@
 As such, EMCRs may be expected to make use of preprints more than colleagues at later career stages.
-We collected data on 'academic age' of submitting authors by looking at Google Scholar profiles of authors (when avioable) and recording their first year of publication in a peer-reviewed journal.
+We collected data on the 'academic age' of submitting authors by looking at Google Scholar profiles of authors (when available) and recording their first year of publication in a peer-reviewed journal.
 While this is a rough estimate of career stage, there was evidence that the number of preprints posted decreases with later career stages (negative binomial glm: year slope = `r res[2, "Estimate"]`, SE: `r round(res[2, "Std.
 Error"], 2)`, *p* < 0.001, n = `r nrow(count_dat[complete.cases(count_dat),])` years).
-The majority of preprints were submitted by authors who published their first paper in the last ~10 years ([@fig-summary]E), with the median year since first publication being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r mean(data2$submitting_author_first_publication_year, na.rm = TRUE)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`, n = `r sum(complete.cases(data2$submitting_author_first_publication_year))`).
-These patterns support the expectation that EMCRs may value preprints as a way to make their work more visible and disseminate their findings more quickly, but it does require more rigorous experimental approaches to validate these findings.
+Most preprints were submitted by authors who published their first paper in the last ~10 years ([@fig-summary]E), with the median year since first publication being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r mean(data2$submitting_author_first_publication_year, na.rm = TRUE)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`, n = `r sum(complete.cases(data2$submitting_author_first_publication_year))`).
+These patterns support the expectation that EMCRs may value preprints to make their work more visible and disseminate their findings more quickly, but it does require more rigorous experimental approaches to validate these findings.
 
@@
 Therefore, such discrepancies are expected to manifest in preprint use on *EcoEvoRxiv*, but it is unclear to what extent.
-Understanding gender publishing patterns is challenging with observational data such as ours because we cannot know the gender of authors for certain but we can use a data-driven approach to ascertain the probability that a particular name is of a given gender (man or women).
+Understanding gender publishing patterns is challenging with observational data such as ours because we cannot know the gender of authors for certain, but we can use a data-driven approach to ascertain the probability that a particular name is of a given gender (man or woman).
 To obtain a rough idea of an author's gender, we used the R package *gender* (v.`r utils::packageVersion("gender")`; @mullen2021predict) to predict the most likely gender of the submitting author of a preprint.
@@
 We acknowledge that our approach does not capture self-assigned and non-binary genders.
-As such, our assumptions about an author gender identity may be incorrect.
+As such, our assumptions about an author's gender identity may be incorrect.
 Our data on gender had only two missing values--one where the first name of the submitting author was missing and the other one for a collective submission.
-As expected, women were less likely to publish on *EcoEvoRxiv* compared to men (women: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`%), which may be a reflection of the broader publishing disparities between male and female scientists [@fox2019gender].
+As expected, women were less likely to publish on *EcoEvoRxiv* compared to men (women: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`%), which may reflect the broader publishing disparities between male and female scientists [@fox2019gender].
 
@@
 Increased competition in science has raised the bar with respect to the amount of data required for publication [@vale2015accelerating].
-This requirement is a good outcome if it results in higher impact research that better clarifies our understanding of the natural world, but it does come at a cost for the speed of research dissemination [@vale2015accelerating].
+This requirement is a good outcome if it results in higher-impact research that better clarifies our understanding of the natural world, but it does come at a cost for the speed of research dissemination [@vale2015accelerating].
 Preprints have been proposed as a way to disseminate research more quickly as it can take a long time before results are ultimately published [@bourne2017ten; @vale2015accelerating].
@@
 
-We estimated how long it takes to publish a research paper in ecology and evolution by recording the time between when a article was first posted on *EcoEvoRxiv*, and its final acceptance in a peer-reviewed journal.
+We estimated how long it takes to publish a research paper in ecology and evolution by recording the time between when an article was first posted on *EcoEvoRxiv*, and its final acceptance in a peer-reviewed journal.
 In total, `r unpub` papers remained unpublished (`r (unpub / nrow(data2))*100`%, n = `r nrow(data2)`) when these data were collected.
@@
 Authors may be reluctant to share data and code for preprints because of the perceived concern that others may acquire and use their data and code before publication in a journal.
-Authors of `r pre_article_data[3,"percent"]*100`% (*n* = `r pre_article_data[3,2]`) articles that did not share data at the preprint stage did ultimately share data when the article was published; whereas authors of `r pre_article_data[2,"percent"]*100`% (*n* = `r pre_article_data[2,2]`) never shared data.
+Authors of `r pre_article_data[3,"percent"]*100`% (*n* = `r pre_article_data[3,2]`) of articles that did not share data at the preprint stage did ultimately share data when the article was published; whereas authors of `r pre_article_data[2,"percent"]*100`% (*n* = `r pre_article_data[2,2]`) never shared data.
 However, `r pre_article_data[1,"percent"]*100`% (*n* = `r pre_article_data[1,2]`) shared data at both stages.
@@
 Earlier career researchers and submitting authors with 'male-associated names' tended to use *EcoEvoRxiv* the most.
-Articles posted to *EcoEvoRxiv* tend to take up to 8 months to become published with many articles not be open access.
+Articles posted to *EcoEvoRxiv* tend to take up to 8 months to become published with many articles not being open access.
 Code and data sharing was also relatively uncommon at the preprint stage.
-While we attempted to collect data on community discussion around preprints no such data was found on preprint landing pages, likely reflecting inadequate functionality and cross-linking with sources where such discussion is occuring.
+At the same time, we attempted to collect data on community discussion around preprints no such data was found on preprint landing pages, likely reflecting inadequate functionality and cross-linking with sources where such discussion is occuring.
 Based on the insights from our analysis, we provide recommendations to authors, editors and the scientific community on ways they can further promote open and transparent research through preprints:
@@
 Sharing data and code early can help improve the quality of research, establish precedence, and improve the transparency and computational reproducibility of scientific findings [@sarabipour2019value].
-Reassuringly, sharing data and code is rarely associated with 'scooping' of research findings [@soeharjono2021reported].
+Reassuringly, sharing data and code is rarely associated with the 'scooping' of research findings [@soeharjono2021reported].
 If authors are worried about data being used unintentionally, clear information surrounding its reuse can be included in a license (see https://choosealicense.com).
@@
 - Second, take advantage of peer-reviewing services such as Peer Community In (PCI).
-It is clear that the time between posting a preprint and publication is still quite long (~8 months).
-One possible explanation is that preprints are not being sent to suitable journals or are struggling to get into review slowing down constructive feedback that can improve a papers quality.
+The time between posting a preprint and publication is still quite long (~8 months).
+One possible explanation is that preprints are not being sent to suitable journals or are struggling to get into review, slowing down constructive feedback that can improve the quality of a paper.
 Using PCI circumvents editorial decisions without review, yet only `r pci[2,3]*100`% (*n* = `r pci[2,2]`) used PCI.
@@
 - Third, seek out and contribute to constructive feedback on preprints [@bourne2017ten].
-While it is clear that preprints help establish precedence and allow findings to be openly accessible, it is still seems rare that constructive discussions form around preprints in an open forum (e.g.
+While it is clear that preprints help establish precedence and allow findings to be openly accessible, it still seems rare that constructive discussions form around preprints in an open forum (e.g.
 bioRxiv [@anderson2020biorxiv]).
@@
 They often result from a mismatch between preprint and published metadata (e.g., titles and author details).
-For example, nearly one theird of articles changed their title from preprint submission to publication [`r titles[2,3]*100`% (*n* = `r titles[2,2]`)].
+For example, nearly one-third  of articles changed their title from preprint submission to publication [`r titles[2,3]*100`% (*n* = `r titles[2,2]`)].
 We found that mismatched metadata almost always contributed to preprints and published articles not being matched automatically in Google Scholar.
@@
 We view this perspective piece as a small step towards achieving that goal.
-We hope that authors are more aware of the benefits of using community-driven preprint servers and the unique initiatives they are able to persue.
-Community-driven preprint servers are capable of setting their own agenda and are driven by the needs and desires of the community.
+We hope that authors are more aware of the benefits of using community-driven preprint servers and the unique initiatives they can pursue.
+Community-driven preprint servers can set their own agenda and are driven by the needs and desires of the community.
 Supporting these initiatives should be a priority for all researchers.
@@
 # Acknowledgements
-We would like to thank the California Digital Library (CDL) and the CDL team (particularly Alainna Wrigley) for their support in hosting and maintaining *EcoEvoRxiv* for the Society for Open, Reliable, and Transparent Ecology and Evolutionary Biology (SORTEE).
+We would like to thank the California Digital Library (CDL) and the CDL team (particularly, Alainna Wrigley, Justin Gonder, Lisa Schiff, Catherine Mitchell, Hardy Pottinger and Amanda Karby) for their support in hosting and maintaining *EcoEvoRxiv* for the Society for Open, Reliable, and Transparent Ecology and Evolutionary Biology (SORTEE).
 We would like to thank Gabriela Hidalgo and Daisy Larios for helping connect us with the IUCN and facilitating discussions to make *EcoEvoRxiv* a place where IUCN reports can be posted.

### 2024-06-07 ms/ms.qmd
Add some map details
Losia's final comments

@@
 
-Here, we explore the first preprints uploaded to *EcoEvoRxiv* to understand preprint practices and use in ecology and evolution.
-We aim to understand: 1) in what countries authors who use *EcoEvoRxiv* are located; 2) the taxonomic diversity across preprints; 3) whether preprint server use depends on career stage and gender; 4) the extent to which authors make use of preprint servers for reports and community-driven peer review; 5) the extent to which data and code are shared in preprints; and 6) how many preprints remain unpublished, and for those that are published, how long it took for them to become published.
+Here, we explore the first preprints uploaded to *EcoEvoRxiv* to characterise preprint practices in ecology and evolution.
+We aim to understand: 1) in what countries authors who use *EcoEvoRxiv* are located; 2) the taxonomic diversity study systems across preprints; 3) whether preprint server use depends on career stage and gender; 4) the extent to which authors make use of preprint servers for reports and community-driven peer review; 5) the extent to which data and code are shared in preprints; and 6) how many preprints remain unpublished, and for those that are published, how long it took for them to become published.
 In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other preprint servers to help further clarify the benefits of using community-driven preprint servers to disseminate research findings.
@@
 Notable milestones include *EcoEvoRxiv* transitioning to the California Digital Library (CDL), the acceptance of preprints and postprints in Spanish and Portuguese, and the acceptance of the first IUCN Red List Ecosystem report; B) Geographic origin of the preprints and postprints uploaded to *EcoEvoRxiv*, inferred from the country of affiliation of the submitting author; C) Taxa used/covered in the articles posted to *EcoEvoRxiv* (n = 1080 articles); D) Types of preprints accepted on *EcoEvoRxiv* (n = 620 articles).
-E) Career stage of authors posting to *EcoEvoRxiv* along with the gender of the submitting author.
+E) Academic age of authors posting to *EcoEvoRxiv* along with the gender of the submitting author.
 Values lower than zero are indicative of authors who uploaded preprints before their first scientific publication in a journal.
+Map base source: R Package "maps" v.3.4.2.
+Shapefile: Natural Earth https://www.naturalearthdata.com/about/terms-of-use/.
 
@@
 Typical research articles are still the most common type of preprint on *EcoEvoRxiv* (`r sum_types[sum_types$type == "research article",]$perc`%), followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]D).
-Currently, *EcoEvoRxiv* does not host many reports, particularly from government or industry.
+Currently, *EcoEvoRxiv* does not host many reports, particularly from government or industry, but has formed fruitful partnerships with the International Union for Conservation of Nature (IUCN).
+For example, IUCN Red-list Ecosystem Reports are now posted to *EcoEvoRxiv* and our community has been able to work closely with the IUCN to ensure these documents meet the IUCN requirements.
 We would encourage authors to consider posting books, book chapters, and reports to ensure that they are openly accessible and more easily found.
-*EcoEvoRxiv* articles are given a unique DOI and indexed on Google Scholar.
-*EcoEvoRxiv* has already formed fruitful partnerships with the International Union for Conservation of Nature (IUCN) as a place where IUCN reports can be hosted to make them more easily accessible to the broader research community.
-For example, IUCN Red-list Ecosystem Reports are now posted to *EcoEvoRxiv* and our community has been able to work closely with the IUCN to ensure these documents meet the IUCN requirements.
+*EcoEvoRxiv* articles are given a unique DOI and are indexed on Google Scholar.
 
@@
 Research communication through a single language has major consequences for the global distribution of knowledge, resulting in knowledge gaps across some of the most biodiverse and threatened regions in the world [@amano2023role; @zenni2023multi].
-Such gaps also impact research syntheses and meta-analyses because they create a distorted picture of our knowledge base leading to bias and inadequate sampling that can affect policy development and decision-making [@hannah2024language; @zenni2023multi; @white2021geographical; @konno2020ignoring].
+Such gaps also impact research syntheses and meta-analyses because they create a distorted picture of our knowledge base that can affect future research, policy development and decision-making [@hannah2024language; @zenni2023multi; @white2021geographical; @konno2020ignoring].
 
-*EcoEvoRxiv* is the only preprint server to date that breaks down language barriers to scientific communication by accepting English, Spanish, Portuguese and French articles.
+*EcoEvoRxiv* is the only preprint server to date that breaks down language barriers to scientific communication by accepting not only English, but also Spanish, Portuguese and French language articles.
 *EcoEvoRxiv* plans to expand to other languages as new non-English editors become available.
@@
 Most preprints were submitted by authors who published their first paper in the last ~10 years ([@fig-summary]E), with the median year since first publication being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r mean(data2$submitting_author_first_publication_year, na.rm = TRUE)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`, n = `r sum(complete.cases(data2$submitting_author_first_publication_year))`).
-These patterns support the expectation that EMCRs may value preprints to make their work more visible and disseminate their findings more quickly, but it does require more rigorous experimental approaches to validate these findings.
+These patterns support the expectation that EMCRs may use preprints to make their work more visible and disseminate their findings more quickly.
+However, we acknowledge that validating this conclusion does require more rigorous experimental approaches.
 
@@
 Our data on gender had only two missing values--one where the first name of the submitting author was missing and the other one for a collective submission.
-As expected, women were less likely to publish on *EcoEvoRxiv* compared to men (women: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`%), which may reflect the broader publishing disparities between male and female scientists [@fox2019gender].
+As expected, we found that women were less likely to publish on *EcoEvoRxiv* compared to men (women: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`%), which may reflect the broader publishing disparities between male and female scientists [@fox2019gender].
 
@@
 #| fig-cap: Summary of the publication status of articles on *EcoEvoRxiv*.
-A) Time between uploading an article to *EcoEvoRxiv* and its publication in a peer-reviewed journal.
+A) Time between uploading an preprint to *EcoEvoRxiv* and its publication as a peer-reviewed journal article.
 Articles that were published within 2 months (60 days) of being submitted are considered postprints and are not included in this figure.
-B) Number of articles that were published in open access journals.
-Artcile DOI's not identified as being open access or not were classified as "Unknown" C) Open access status of published articles uploaded to *EcoEvoRxiv*.
+B) Access status of articles linked to *EcoEvoRxiv* preprints classified as “Open Access” or “Not Open Access”.
+“Unknown” status is for articles not explicitly identified as being open access or not on the Unpaywall platform.
+C) Sub-types of open access status of articles linked to *EcoEvoRxiv* preprints.
 For full details on the meaning of each category see  https://support.unpaywall.org/support/solutions/articles/44001777288-what-do-the-types-of-oa-status-green-gold-hybrid-and-bronze-mean-.
@@
 We estimated how long it takes to publish a research paper in ecology and evolution by recording the time between when an article was first posted on *EcoEvoRxiv*, and its final acceptance in a peer-reviewed journal.
-In total, `r unpub` papers remained unpublished (`r (unpub / nrow(data2))*100`%, n = `r nrow(data2)`) when these data were collected.
+In total, `r unpub` papers remained unpublished (`r (unpub / nrow(data2))*100`%, n = `r nrow(data2)`) at the time when these data were collected.
 Not all of these papers, however, are anticipated to be published in a peer-reviewed journal (e.g., reports).
@@
 Most of the published articles were open access [`r sum_is_oa$valid_percent[2]*100`% (*n* = `r sum_is_oa$n[2]` out of `r sum(sum_is_oa$n[1:2])` where the status was known); [@fig-pubsummary]A]; however, `r sum_is_oa$valid_percent[1]*100`% (*n* = `r sum_is_oa$n[1]`) were published behind paywalls.
-For articles published in open access journals, the degree of open-access also varied widely (e.g., Gold, Hybrid, Green OA etc., [@fig-pubsummary]B).
+For articles published in open access journals, the type of open-access also varied widely (e.g., Gold, Hybrid, Green OA etc., [@fig-pubsummary]B).
 
@@
 In the spirit of 'openness', we expected data and code sharing among preprints to be greater than in many papers published in research journals [@roche2015public; @o2021preferred].
-Despite this, we found that `r (preprint_data[1,"n"]/sum(preprint_data[c(1,3),"n"]))*100`%  (*n* = `r preprint_data[1,2]`) of articles relying on data on *EcoEvoRxiv* did not share data, and `r (preprint_code[1,"n"]/sum(preprint_code[c(1,3),"n"]))*100`% (*n* = `r preprint_code[1,2]`) did not share code.
+Despite this, we found that `r (preprint_data[1,"n"]/sum(preprint_data[c(1,3),"n"]))*100`%  (*n* = `r preprint_data[1,2]`) of articles relying on data on *EcoEvoRxiv* did not share data, and `r (preprint_code[1,"n"]/sum(preprint_code[c(1,3),"n"]))*100`% (*n* = `r preprint_code[1,2]`) did not share code (counting only data-based articles, i.e excluding reviews, commentaries or theoretical works).
 
@@
 Our analysis has allowed us to better understand preprinting/postprinting practices in *EcoEvoRxiv*.
-In summary, *EcoEvoRxiv* articles are diverse but with primary research articles on vertebrates comprising most of the articles posted.
+Overall, *EcoEvoRxiv* articles are diverse but with primary research articles on vertebrates comprising most of the articles posted.
 North America, Europe and Australia use *EcoEvoRxiv* the most with very few non-English language articles to date.
-Earlier career researchers and submitting authors with 'male-associated names' tended to use *EcoEvoRxiv* the most.
+Submitting authors who were earlier in their career and more often with ‘male-associated names’ tended to use  *EcoEvoRxiv* the most.
 Articles posted to *EcoEvoRxiv* tend to take up to 8 months to become published with many articles not being open access.
 Code and data sharing was also relatively uncommon at the preprint stage.
-At the same time, we attempted to collect data on community discussion around preprints no such data was found on preprint landing pages, likely reflecting inadequate functionality and cross-linking with sources where such discussion is occuring.
-Based on the insights from our analysis, we provide recommendations to authors, editors and the scientific community on ways they can further promote open and transparent research through preprints:
+At the same time, we attempted to collect data on community discussion around preprints no such data was found on preprint landing pages, likely reflecting inadequate functionality and cross-linking with sources where such discussion is occurring.
+Based on the insights from our analysis, we provide recommendations to authors and the scientific community on ways they can further promote open and transparent research through preprints:
 
@@
 We found that mismatched metadata almost always contributed to preprints and published articles not being matched automatically in Google Scholar.
-We recommend that authors update their preprints accepted to journals with the publication’s DOI, especially if their title has changed.
-This is very easy for authors to do on *EcoEvoRxiv*, and ensures that the preprint is correctly linked to the published article and citations are appropriately merged.
+We recommend that authors update their preprints with the publication DOI when accepted to journals, especially if their title has changed.
+This is very easy for authors to do on *EcoEvoRxiv* and ensures that the preprint is correctly linked to the published article and citations are appropriately merged.
 Adding DOIs will also create a link between the final preprint and the published paper so that, no matter the open access status of the publication, the research findings will remain openly accessible, saving costs for authors (i.e., by not having to pay open access fees) and improving the visibility and use of research.
 
-Despite the early successes of the new initiatives taken by *EcoEvoRxiv*, much work remains to be done to improve the understanding and use of pre- and postprints within our community.
+Despite the early successes of the new initiatives taken by *EcoEvoRxiv*, as described above, much work remains to be done to improve the understanding and use of pre- and postprints within our community.
 We view this perspective piece as a small step towards achieving that goal.
-We hope that authors are more aware of the benefits of using community-driven preprint servers and the unique initiatives they can pursue.
+We hope that readers are more familiar with the benefits of using community-driven preprint servers and the unique initiatives they can pursue.
 Community-driven preprint servers can set their own agenda and are driven by the needs and desires of the community.
@@
 DWAN would also like to thank the Australian Research Council for a Future Fellowship (FT220100276).
+SN and ML are supported by the Australian Research Council (ARC) Discovery Project Grants (DP210100812 and DP230101248).
 
@@
 # Conflict of Interest
-The authors would like to awknowledge competing interests on the perspectives presented in this paper given that many are founding members of *EcoEvoRxiv* (DWAN, SN, ML) and/or are part of the *EcoEvoRxiv* committee.
+The authors would like to acknowledge competing interests on the perspectives presented in this paper given that many (DWAN, SN, ML) are founding members of *EcoEvoRxiv* and/or are part of the *EcoEvoRxiv* committee.
 

### 2024-06-07 ms/ms.qmd
fixes

@@
 Most of the published articles were open access [`r sum_is_oa$valid_percent[2]*100`% (*n* = `r sum_is_oa$n[2]` out of `r sum(sum_is_oa$n[1:2])` where the status was known); [@fig-pubsummary]A]; however, `r sum_is_oa$valid_percent[1]*100`% (*n* = `r sum_is_oa$n[1]`) were published behind paywalls.
-For articles published in open access journals, the type of open-access also varied widely (e.g., Gold, Hybrid, Green OA etc., [@fig-pubsummary]B).
+For articles published in open access journals, the type of open access also varied widely (e.g., Gold, Hybrid, Green OA etc., [@fig-pubsummary]B).
 
@@
 In the spirit of 'openness', we expected data and code sharing among preprints to be greater than in many papers published in research journals [@roche2015public; @o2021preferred].
-Despite this, we found that `r (preprint_data[1,"n"]/sum(preprint_data[c(1,3),"n"]))*100`%  (*n* = `r preprint_data[1,2]`) of articles relying on data on *EcoEvoRxiv* did not share data, and `r (preprint_code[1,"n"]/sum(preprint_code[c(1,3),"n"]))*100`% (*n* = `r preprint_code[1,2]`) did not share code (counting only data-based articles, i.e excluding reviews, commentaries or theoretical works).
+Despite this, we found that `r (preprint_data[1,"n"]/sum(preprint_data[c(1,3),"n"]))*100`%  (*n* = `r preprint_data[1,2]`) of articles relying on data on *EcoEvoRxiv* did not share data, and `r (preprint_code[1,"n"]/sum(preprint_code[c(1,3),"n"]))*100`% (*n* = `r preprint_code[1,2]`) did not share code (counting only data-based articles, i.e., excluding reviews, commentaries or theoretical works).
 
@@
 If authors are worried about data being used unintentionally, clear information surrounding its reuse can be included in a license (see https://choosealicense.com).
-Data can also be achived with an embargo on its reuse [@roche2014troubleshooting].
+Data can also be archived with an embargo on its reuse [@roche2014troubleshooting].
 - Second, take advantage of peer-reviewing services such as Peer Community In (PCI).

### 2024-06-20 ms/ms.qmd
Update format for Proc B and adding in a abstract

@@
 bibliography: ../bib/refs.bib
-csl: ../bib/nature.csl
+csl: ../bib/proceedings-of-the-royal-society-b.csl
 format:
@@
   title-delim: "-"
-  fig-prefix: "Figure"
-  tbl-prefix: "Table"
+  fig-prefix: "figure"
+  tbl-prefix: "table"
 ---
@@
 
-# Introduction
+# Abstract
+Publishing preprints has become an entrenched practice across a multitude of scientific disciplines and it is quickly becoming commonplace in ecology and evolutionary biology.
+Preprints can facilitate the rapid sharing of scientific knowledge to establish precedence, speed up the dissemination of research findings, and enable feedback from the research community before peer review.
+Yet, significant barriers to preprint use exist including language barriers, a lack of understanding about the benefits of preprints and a lack of diversity in the types of research outputs accepted (e.g., reports).
+Community driven preprint initiatives can allow a research community to come together to break down these barriers and move scientific publishing practices into new and exciting directions that promote greater equity and better coverage of global knowledge.
+Here, we explore the first preprints uploaded to *EcoEvoRxiv*, a community-driven preprint server for ecologists and evolutionary biologists, to characterise preprint practices in ecology, evolution and conservation.
+Our perspective piece highlights some of the unique initiatives that *EcoEvoRxiv* has taken to break down barriers to scientific publishing by exploring the composition of articles, how gender and career stage influence preprint use, whether preprints are associated with greater open science principles (e.g., code and data sharing), and tracking preprint publication outcomes.
+Our analysis identifies areas that we still need to improve upon but highlight how community-driven initiatives, such as *EcoEvoRxiv*, can play a crucial role in shaping publishing practices in biology.
+
+# 1. Introduction
 
@@
 
-# Getting to know your *EcoEvoRxiv* preprint server
+# 2. Getting to know your *EcoEvoRxiv* preprint server
 
@@
 #| label: fig-summary
-#| fig-cap: Summary of articles posted to *EcoEvoRxiv*.
+#| fig-cap: "Summary of articles posted to *EcoEvoRxiv*.
 A) Number of articles (preprints and postprints) published on *EcoEvoRxiv* between 2018 and 2023.
@@
 E) Academic age of authors posting to *EcoEvoRxiv* along with the gender of the submitting author.
-Values lower than zero are indicative of authors who uploaded preprints before their first scientific publication in a journal.
-Map base source: R Package "maps" v.3.4.2.
-Shapefile: Natural Earth https://www.naturalearthdata.com/about/terms-of-use/.
+Values lower than zero are indicative of authors who uploaded preprints before their first scientific publication in a journal."
 
@@
 
-### *Overview of **EcoEvoRxiv** preprints (and postprints)*
+### (a) *Overview of **EcoEvoRxiv** preprints (and postprints)*
 
@@
 
-### *Diversifying article types on **EcoEvoRxiv**: overcoming the 'grey literature' problem*
+### (b) *Diversifying article types on **EcoEvoRxiv**: overcoming the 'grey literature' problem*
 
@@
 
-### *Breaking down language barriers to scientific communication: improving diversity and data representation globally*
+### (c) *Breaking down language barriers to scientific communication: improving diversity and data representation globally*
 
@@
 
-### *Generational and gender-based gaps in preprinting practices*
+### (d) *Generational and gender-based gaps in preprinting practices*
 
@@
 
-# Following the journey of a preprint on *EcoEvoRxiv*: from submission to publication
+# 3. Following the journey of a preprint on *EcoEvoRxiv*: from submission to publication
 ```{r, fig-pubsummary}
@@
 
-### *Science takes time, but publication could take longer*
+### (a) *Science takes time, but publication could take longer*
 Increased competition in science has raised the bar with respect to the amount of data required for publication [@vale2015accelerating].
@@
 
-### *Cautious 'open'-mindedness of research in preprints*
+### (b) *Cautious 'open'-mindedness of research in preprints*
 In addition to speeding up dissemination, preprints and postprints can also be a useful way to ensure that research remains open and accessible to the research community irrespective of the accessibility of the final peer-reviewed paper [@bourne2017ten; @vale2015accelerating].
@@
 
-# Paving our future to open, transparent and community-driven science
+# 4. Paving our future to open, transparent and community-driven science
 
@@
 
+# Data accessibility
+All data and code can be found on GitHub at: https://github.com/daniel1noble/ecoevo_1000
+
+# Competing interests
+The authors would like to acknowledge competing interests on the perspectives presented in this paper given that many (DWAN, SN, ML) are founding members of *EcoEvoRxiv* and/or are part of the *EcoEvoRxiv* committee.
+
+# Funding
+DWAN would also like to thank the Australian Research Council for a Future Fellowship (FT220100276).
+SN and ML are supported by the Australian Research Council (ARC) Discovery Project Grants (DP210100812 and DP230101248).
+
 # Acknowledgements
@@
 This paper emerged from a hackathon at the 2023 SORTEE conference, and we thank delegates who attended the session but could not be part of this paper.
-DWAN would also like to thank the Australian Research Council for a Future Fellowship (FT220100276).
-SN and ML are supported by the Australian Research Council (ARC) Discovery Project Grants (DP210100812 and DP230101248).
-
-# Data and Code Availability
-All data and code can be found on GitHub at: https://github.com/daniel1noble/ecoevo_1000
-
-# Conflict of Interest
-The authors would like to acknowledge competing interests on the perspectives presented in this paper given that many (DWAN, SN, ML) are founding members of *EcoEvoRxiv* and/or are part of the *EcoEvoRxiv* committee.
 

### 2024-06-20 ms/ms.qmd
200 words

@@
 # Abstract
-Publishing preprints has become an entrenched practice across a multitude of scientific disciplines and it is quickly becoming commonplace in ecology and evolutionary biology.
-Preprints can facilitate the rapid sharing of scientific knowledge to establish precedence, speed up the dissemination of research findings, and enable feedback from the research community before peer review.
+Publishing preprints is quickly becoming commonplace in ecology and evolutionary biology.
+Preprints can facilitate the rapid sharing of scientific knowledge establishing precedence and enabling feedback from the research community before peer review.
 Yet, significant barriers to preprint use exist including language barriers, a lack of understanding about the benefits of preprints and a lack of diversity in the types of research outputs accepted (e.g., reports).
-Community driven preprint initiatives can allow a research community to come together to break down these barriers and move scientific publishing practices into new and exciting directions that promote greater equity and better coverage of global knowledge.
-Here, we explore the first preprints uploaded to *EcoEvoRxiv*, a community-driven preprint server for ecologists and evolutionary biologists, to characterise preprint practices in ecology, evolution and conservation.
-Our perspective piece highlights some of the unique initiatives that *EcoEvoRxiv* has taken to break down barriers to scientific publishing by exploring the composition of articles, how gender and career stage influence preprint use, whether preprints are associated with greater open science principles (e.g., code and data sharing), and tracking preprint publication outcomes.
-Our analysis identifies areas that we still need to improve upon but highlight how community-driven initiatives, such as *EcoEvoRxiv*, can play a crucial role in shaping publishing practices in biology.
+Community driven preprint initiatives can allow a research community to come together to break down these barriers to improve equity and coverage of global knowledge.
+Here, we explore the first preprints uploaded to EcoEvoRxiv, a community-driven preprint server for ecologists and evolutionary biologists, to characterise preprint practices in ecology, evolution and conservation.
+Our perspective piece highlights some of the unique initiatives that EcoEvoRxiv has taken to break down barriers to scientific publishing by exploring the composition of articles, how gender and career stage influence preprint use, whether preprints are associated with greater open science principles (e.g., code and data sharing), and tracking preprint publication outcomes.
+Our analysis identifies areas that we still need to improve upon but highlight how community-driven initiatives, such as EcoEvoRxiv, can play a crucial role in shaping publishing practices in biology.
 

### 2024-09-25 R/3_final_dat_analysis.R
MOre organisation

@@ -1,81 +1,0 @@
-########################################
-# Analysis of the final checked data file
-########################################
-
-###-------------------------###
-# Load packages
-###-------------------------###
-	pacman::p_load(tidyverse, googlesheets4, janitor, here, roadoi)
-
-###-------------------------###
-# Load data from Google Sheets 
-# and save raw files
-###-------------------------###
-
-	# Load data	
-	data <- read_csv(here("data", "final_data.csv"))  %>% 
-	mutate(
-		preprint_published_date = as.Date(preprint_published_date, format = "%d/%m/%Y"),
-	    publication_date = as.Date(publication_date, format = "%d/%m/%Y"),
-		time_between_preprint_and_pub_days = as.numeric(publication_date - preprint_published_date))
-	
-	# Have a look at columns
-	str(data)
-
-###-------------------------###
-# Extract whether a paper is open access or not
-###-------------------------###
-
-# Use the DOI for the published paper to get OA
-dois <- unique(data$publisher_doi)[-1] # Remove 1 NA in first position
-length(dois) # 509
-
-#connect and fetch the data
-OA_df <- roadoi::oadoi_fetch(dois = dois, email = "daniel.wa.noble@gmail.com") 
-
-#save fetched data
-readr::write_csv(OA_df, file = here("output", "data","OA_article_data_Unpaywall.csv")) 
-dim(OA_df) # 509
-
-OA_df <- OA_df  %>% select(doi, journal_name, is_oa, oa_status)
-
-# Merge dois with OA data
-OA_df2 <- data.frame(doi = dois, OA_df)
-
-# Merge with the main data
-data2 <- data  %>% left_join(OA_df2, by = c("publisher_doi" = "doi"))
-
-# We have now cross checked the paper in more detail to see if we missed any published papers. So, we should update the new time between preprint and publication dates, which is a time difference between the preprint and the published paper dates. CRoss checked two times to make sure they were calculated correct. Good!
-
-data2 <- data2  %>% mutate(time_between_preprint_and_pub_days = ymd(publication_date) - ymd(preprint_published_date))
-write.csv(data2, file = here("data", "final_data2.csv"))
-
-########-------------------------###
-### Excluding postprints, how long does it take for a preprint to be published in Ecology and Evolution?
-########-------------------------###
-
[…]

### 2024-09-25 supp/supp.qmd
Update supp and remove unecessary csl

@@
 ---
-title: "Supplementary Materials for: Empowering the use of community driven preprints in ecology and evolution"
+title: "Supplementary Materials for: The promise of community-driven preprints in ecology and evolution"
 bibliography: ../bib/refs.bib
-csl: ../bib/nature.csl
+csl: ../bib/proceedings-of-the-royal-society-b.csl
 format:
@@
 crossref:
-  fig-title: 'Figure'
+  fig-title: 'FigureS'
   fig-labels: arabic
   title-delim: "-"
-  fig-prefix: "Figure"
-  tbl-prefix: "Table"
+  fig-prefix: "FigureS"
+  tbl-prefix: "TableS"
 ---
@@
 Participants assigned themselves to collect data from between `r range(contr_extract$n)[1]` to `r range(contr_extract$n)[2]` preprints (mean = `r mean(contr_extract$n)`, standard deviation = `r sd(contr_extract$n)`).
-Data collection was achieved using a Google Form to standardise data input.
+Data collection was achieved using a Google Form to standardize data input.
 Participants collected the following information for each of their assigned preprints:
@@
 If there were multiple authors then the first author listed on the preprint was used.
-- **Country of the corresponding / submitting author**: Country of affiliation for the author submitting the preprint collecting accoring to standard ISO 3166 names.
+- **Country of the corresponding / submitting author**: Country of affiliation for the author submitting the preprint collecting according to standard ISO 3166 names.
 If teh country could not be determined the affiliation was considered as "NA".
 - **Year of first publication for corresponding/submitted author**: We used [Google Scholar](https://scholar.google.com.au) to collect publication year of the first journal article published by author submitting the preprint.
-If the submitting author had no profile or did not publish the value enetred was '0'.
+If the submitting author had no profile or did not publish the value entered was '0'.
 - **Taxa being studied**: We collected information about the broad group of taxa that were the focus of the preprint.
@@
 We therefore collected data on article type.
-The categories were: *Research Article*: any article-like manuscript intended for publication in research journals with new empirical findings; *Methods paper*: papers presenting new methodological or computational approaches; *Reviews and Meta-analyses*: papers quantitatively or qualitatively synthesising a given topic;  *Opinions*: usually short papers providing new perspectives on a topic; *Comments*: papers that explicitly comment on an already published research article; and *Other*: which includes any other category of preprint which may also be government, non-profit, or industry reports, white papers, or other documents that are not intended for publication in a research journal.
-- **Link to Data for Preprint**: We were explicitly interested in whether data for the preprint was already publically available.
+The categories were: *Research Article*: any article-like manuscript intended for publication in research journals with new empirical findings; *Methods paper*: papers presenting new methodological or computational approaches; *Reviews and Meta-analyses*: papers quantitatively or qualitatively synthesizing a given topic;  *Opinions*: usually short papers providing new perspectives on a topic; *Comments*: papers that explicitly comment on an already published research article; and *Other*: which includes any other category of preprint which may also be government, non-profit, or industry reports, white papers, or other documents that are not intended for publication in a research journal.
+- **Link to Data for Preprint**: We were explicitly interested in whether data for the preprint was already publicly available.
 To collect these data we scrolled through the first version of the preprint and any related files on *EcoEvoRxiv* to see if a link (or accession number) to underlying data was provided.
@@
 If multiple links were provided we took one.
-- **Link to Code for Preprint**: We were also interested in whether code for data analysis was already publically available.
+- **Link to Code for Preprint**: We were also interested in whether code for data analysis was already publicly available.
 To collect these data we scrolled through the first version of the preprint and any related files on *EcoEvoRxiv* to see if a link (or accession number) to underlying code was provided.
@@
 If multiple links were provided we took one.
-- **Number of citations to preprint**: To understand citation patterns of preprints on *EcoEvoRxiv* we used Google Sscholar to search for the number of citations attributed to the preprint.
+- **Number of citations to preprint**: To understand citation patterns of preprints on *EcoEvoRxiv* we used Google Scholar to search for the number of citations attributed to the preprint.
 If the preprint version was not on Google Scholar or was merged with an already published version we considered it as 'NA' (coded as '999').
@@
 As such, we do not anticipate that citation counts would have changed significantly between the time of data collection and the time of submission of this manuscript.
-- **PCI recommendation**: We also deteremined if the preprint been recomended by Peer Community In (PCI).
+- **PCI recommendation**: We also determined if the preprint been recommended by Peer Community In (PCI).
 To do this, we searched for any PCI recommendations associated with the preprint on the preprint landing page.
@@
 - **Link to Data for Publication**: If the preprint was published we collected the link to any published data provided on the publishers webpage or within the published paper.
-If a link to the data was not visble we recorded the paper as not having provided data ('none').
+If a link to the data was not visible we recorded the paper as not having provided data ('none').
 If the paper had not been published or not based on data and data analyses (opinions, comments, narrative reviews, theoretical paper, etc.) we entered 'NA'.
 - **Link to Code for Publication**: If the preprint was published we collected the link to any published code provided on the publishers webpage or within the published paper.
-If a link to the data was not visble we recorded the paper as not having provided data ('none').
+If a link to the data was not visible we recorded the paper as not having provided data ('none').
 If the paper had not been published or not based on data and data analyses (opinions, comments, narrative reviews, theoretical paper, etc.) we entered 'NA'.
 
-Additional variables of interest (i.e., journal impact factor, preprint and review policy, gender of submitting author) could be determined oustide of this data collection period.
+Additional variables of interest (i.e., journal impact factor, preprint and review policy, gender of submitting author) could be determined outside of this data collection period.
 
 ## Data Checking and Validation
-Data from each preprint was cross checked by two authors to ensure accuracy and consistency of the data collected. Any discrepencies were either discussed or fixed prior to analysis.
+Data from each preprint was cross checked by two authors to ensure accuracy and consistency of the data collected. Any discrepancies were either discussed or fixed prior to analysis.
 
@@
 #### Generational Analysis
-To test whether a greater number of preprints were submitted by authors of earlier 'academic age', as quantified by the submitting authors first year of publication, we used a generalised linear model (GLM) with a negative binomial error distribution.
+To test whether a greater number of preprints were submitted by authors of earlier 'academic age', as quantified by the submitting authors first year of publication, we used a generalized linear model (GLM) with a negative binomial error distribution.
 We included the number of preprints submitted in a given year as the response variable and the first year of publication as the predictor variable.
@@
 
-Interestingly, a highly cited preprint did not necessarily become a highly cited published article over time, although some of this descrepency is related to whether and how preprints and articles are linked through crossref (Spearman Rank Correlation: `r spear$estimate`, S = `r spear$statistic`, *p* = `r spear$p.value`; @fig-citations).
+Interestingly, a highly cited preprint did not necessarily become a highly cited published article over time, although some of this discrepancy is related to whether and how preprints and articles are linked through crossref (Spearman Rank Correlation: `r spear$estimate`, S = `r spear$statistic`, *p* = `r spear$p.value`; @fig-citations).

### 2024-09-26 proc_b/authors.qmd
Moving

---
title: ""
format:
  docx:
    reference-doc: ./bib/template.docx
---

Rafaela Almeida^1^, Kevin Bairos-Novak^2^, Heikel Balti^3^, Michael Bertram^4^, Louis Bliard^5^, Jack Brand^6^, Ilha Byrne^7^, Ying-Chi Chan^8^, Dena Clink^9^, Quentin Corbel^10^, Ricardo Correia^11^, Jordann Crawford-Ash^12^, Antica Culina^13^, Elvira D'Bastiani^14^, Gideon Gywa Deme^15^, Félicie Dhellemmes^16^, Shreya Dimri^17^, Szymek Drobniak^18^, Alexander Elsy^19^, Susan Everingham^20^, Samuel J. L. Gascoigne^21^, Matt Grainger^22^, Gavin Hossack^23^, Knut Anders Hovstad^24^, Ed Ivimey-Cook^25^, Matt Jones^26^, Ineta Kačergytė^27^, Georg Küstner^28^, Dalton Leibold^29^, Magdalena M. Mair^30^, Jake Martin^31^, April Robin Martinig^32^, Ayumi Mizuno^33^, Iain Moodie^34^, David Moreau^35^, Rose O'Dea^36^, James Orr^37^, Matthieu Paquet^38^, Rabindra Parajuli^39^, Joel Pick^40^, Patrice Pottier^41^, Marija Purgar^42^, Pablo Recio^43^, Dominique Roche^44^, Raphaël Royauté^45^, Saeed Shafiei Sabet^46^, Inês Silva^47^, Bruno E. Soares^48^, Birgit Szabo^49^, Alfredo Sánchez-Tójar^50^, Elina Takola^51^, Eli Thoré^52^, Bishnu Timilsina^53^, Wilco Verberk^54^, Stefan J.G. Vriend^55^, Kristoffer Wild^56^, Coralie Williams^57^, Nicholas Wu^58^, Zoe Xirocostas^59^, Yefeng Yang^60^, Melina de Souza Leite^61^, Natalie E. van Dis^62^, NA NA^63^

^1^KU Leuven, Belgium

^2^School of the Environment, University of Queensland, Australia

^3^UMR 6249 Chrono-Environnement, University of Bourgogne Franche-Comté, France

^4^Swedish University of Agricultural Sciences

^5^Department of Evolutionary Biology and Environmental Studies, University of Zurich

^6^Department of Wildlife, Fish, and Environmental Studies, Swedish University of Agricultural Sciences

^7^Scholf of the Environment, The University of Queensland

^8^Swiss Ornithological Institute, Switzerland

^9^K. Lisa Yang Center for Conservation Bioacoustics, Cornell University

^10^Station d'Ecologie Théorique et Experimentale, CNRS, France

^11^Biodiversity Unit, University of Turku, Finland

^12^Fenner School of Environment and Society, Australian National University, Canberra ACT

^13^Institute Ruder Boskovic, Zagreb. Croatia

^14^Department of Ecology and Evolutionary Biology, University of California, Los Angeles

^15^Case Western Reserve University

^16^Science of Intellingence, Berlin, Germany; Max Planck Institute for Human Development, Berlin, Germany

^17^Department of Evolutionary Biology, Bielefeld Univeristy, Germany

^18^UNSW/Jgaiellonian University

^19^ETH Zürich, Switzerland

^20^Institute of Plant Sciences and Oeschger Centre for Climate Change Research, University of Bern

^21^Department of Biology, University of Oxford, United Kingdom

^22^Norwegian Institute for Nature Research, Trondheim, Norway

^23^n/a

^24^Norwegian Biodiversity Information Centre, Trondheim, Norway

^25^University of Glasgow

^26^University of Exeter

^27^Ecology department, Swedish University of Agricultural sciences, Sweden

^28^Department of Animal Ecology and Tropical Biology, University of Würzburg, Germany

^29^Division of Ecology and Evolution, Research School of Biology, Australian National University

^30^Statistical Ecotoxicology, Bayreuth Center of Ecology and Environmental Research (BayCEER), University of Bayreuth, Germany

^31^Swedish university of agricultural sciences, Umeå, Sweden

^32^School of Biological, Earth and Environmental Sciences, UNSW, Sydney

^33^Department of Biology, Faculty of Science, Hokkaido University, Japan

^34^Department of Biology, Lund University, Sweden

^35^Centre for Brain Research, University of Auckland, New Zealand

^36^School of Agriculture, Food and Ecosystem Sciences, University of Melbourne

^37^Department of Biology, University of Oxford

^38^Station d'Ecologie Théorique et Experimentale, CNRS, France

^39^Department of Geosciences, Florida Atlantic University, Boca Raton, FL

^40^Institute of Ecology and Evolution, University of Edinburgh, UK

^41^School of Biological, Earth and Environmental Sciences, UNSW, Sydney

^42^Ruđer Bošković Institute, Zagreb, Croatia

^43^Department of Ecology and Evolution, RSB, Australian National University

^44^Department of Biology, Carleton University, Canada

^45^Université ParisSaclay, INRAE, AgroParisTech, UMR EcoSys, Palaiseau, France

^46^Fisheries Department, Faculty of Natural Sciences, University of Guilan

^47^Center for Advanced Systems Understanding, Görlitz, Germany

^48^University of Regina

^49^Division of Behavioural Ecology, University of Bern, Switzerland

^50^Department of Evolutionary Biology, Bielefeld University, Germany

^51^Helmholtz Center for Environmental Research (UFZ), Leipzig, Germany

^52^Department of Wildlife, Fish, and Environmental Studies, Swedish University of Agricultural Sciences

^53^Faculty of Biosciences, Fisheries and Economics, The Arctic University of Norway, Norway

^54^Radboud University Nijmegen

^55^Netherlands Institute of Ecology (NIOO-KNAW), Wageningen, Netherlands

^56^The University of Melbourne, School of BioSciences, Melbourne, VIC

^57^School of Biological, Earth and Environmental Sciences, UNSW, Sydney

^58^Hawkesbury Institute for the Environment, Western Sydney University

^59^School of Life Sciences, University of Technology Sydney

^60^School of Biological, Earth and Environmental Sciences, UNSW, Sydney

^61^Department of Ecology, University of São Paulo, Brazil

^62^Helsinki Institute of Life Sciences, Helsinki University, Finland

^63^NA

### 2024-09-26 docs/supp.qmd
Udpated supp

--- 2024-09-25 supp/supp.qmd
@@
     toc: true
+    output-file: index.html
     toc-location: left

### 2024-09-26 ms/ms.qmd
Some updates to MS for session info and renamed to r1

@@
     reference-doc: ../bib/template.docx
+    output-file: ms-r1.docx
   pdf:
@@
 # References
+
+```{r}
+#| echo: TRUE
+#| warning: FALSE
+#| message: FALSE
+
+sessionInfo()
+```

### 2024-10-03 ms/ms.qmd
Small edit to aboid refs being put in wrong place when rendered
Update to submissions and preprints/postprints

@@
 *EcoEvoRxiv* is one of the few community-driven preprint servers that has paved the way for new initiatives, by accepting multilingual preprints, registered reports, and non-traditional research reports.
+Such initiatives are distinct from other preprint servers, such as bioRxiv, which only accepts empirical research in English.
 *EcoEvoRxiv* also promotes peer review and community discussion in the hopes of improving the quality of preprints and speeding up their peer-reviewed publication (e.g., Peer Community In -- PCI [@guillemaud2019peer]).
@@
 #| label: fig-summary
-#| fig-cap: "Summary of articles posted to *EcoEvoRxiv*.
-A) Number of articles (preprints and postprints) published on *EcoEvoRxiv* between 2018 and 2023.
+#| fig-cap: "Summary of submissions to *EcoEvoRxiv*.
+A) Number of submissions (preprints and postprints) published on *EcoEvoRxiv* between 2018 and 2023.
 *EcoEvoRxiv* was established in June 2018 before the launch in November 2018.
-Notable milestones include *EcoEvoRxiv* transitioning to the California Digital Library (CDL), the acceptance of preprints and postprints in Spanish and Portuguese, and the acceptance of the first IUCN Red List Ecosystem report; B) Geographic origin of the preprints and postprints uploaded to *EcoEvoRxiv*, inferred from the country of affiliation of the submitting author; C) Taxa used/covered in the articles posted to *EcoEvoRxiv* (n = 1080 articles); D) Types of preprints accepted on *EcoEvoRxiv* (n = 620 articles).
-E) Academic age of authors posting to *EcoEvoRxiv* along with the gender of the submitting author.
-Values lower than zero are indicative of authors who uploaded preprints before their first scientific publication in a journal."
+Notable milestones include *EcoEvoRxiv* transitioning to the California Digital Library (CDL), the acceptance of submissions in Spanish and Portuguese, and the acceptance of the first IUCN Red List Ecosystem report; B) Geographic origin of the preprints and postprints uploaded to *EcoEvoRxiv*, inferred from the country of affiliation of the submitting author; C) Taxa used/covered in the articles posted to *EcoEvoRxiv* (n = 1080 articles); D) Types of preprints accepted on *EcoEvoRxiv* (n = 620 articles).
+E) Academic age of authors submitting to *EcoEvoRxiv* along with the gender of the submitting author.
+Values lower than zero are indicative of authors who uploaded preprints before their first scientific publication in a journal.
+Map base source:  R Package "maps" v.3.4.2.
+Shapefile: Natural Earth https://www.naturalearthdata.com/about/terms-of-use/."
 
@@
 
-To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the articles available on *EcoEvoRxiv* as of `r gsub("UTC", "", dates[2])` (see Supplement for more details on methods).
-We consider both preprints and postprints as ‘articles’.
-After removing five duplicate titles – suggesting that a few authors created multiple submissions for the same preprint rather than updating the existing submission – we had data for a total of `r pr` articles with ~55--60 preprints published approximately monthly in the last two years ([@fig-summary]A).
-*EcoEvoRxiv* hosts articles from authors based in `r length(unique(countries$country))` countries, with 90% of the articles coming from just `r nrow(most_use)-1` countries.
+To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the accepted submissions in EcoEvoRxiv as of  `r gsub("UTC", "", dates[2])` (see Supplement for more details on methods).
+We consider both preprints and postprints as ‘submissions’.
+After removing five duplicate titles – suggesting that a few authors created multiple submissions for the same preprint rather than updating the existing submission – we had data for a total of `r pr` articles with ~55--60 submissions published approximately monthly in the last two years ([@fig-summary]A).
+*EcoEvoRxiv* hosts submissions from authors based in `r length(unique(countries$country))` countries, with 90% coming from just `r nrow(most_use)-1` countries.
 North America, Australia, and European countries upload the most preprints, with many fewer coming from countries in Africa, Central America, and parts of Asia ([@fig-summary]B).
-Articles covered all major taxonomic groups, with the most common being vertebrates (`r sum_taxa$perc[6]`%), plants (`r sum_taxa$perc[1]`%), and invertebrates (`r sum_taxa$perc[5]`%) ([@fig-summary]C).
+Submissions covered all major taxonomic groups, with the most common groups being vertebrates (`r sum_taxa$perc[6]`%), plants (`r sum_taxa$perc[1]`%), and invertebrates (`r sum_taxa$perc[5]`%) ([@fig-summary]C).
 
@@
 Accepting a greater diversity of article types allows *EcoEvoRxiv* to help deal with the 'grey literature' problem, whereby data that are relevant for research syntheses are not published in typical peer-reviewed journals [@haddaway2015shades; @haddaway2020eight].
-*EcoEvoRxiv* has made a concerted effort to diversify the types of articles accepted.
-This is reflected by `r nt`% of the articles on *EcoEvoRxiv* being books, book chapters, reports, and other research output types, which are typically considered ‘grey literature’ in ecology and evolutionary biology.
-As a result, articles on *EcoEvoRxiv* are more diverse than those on preprint servers which have more restrictive submission policies.
+*EcoEvoRxiv* has made a concerted effort to diversify the types of submissions accepted.
+This is reflected by `r nt`% of the submissions on *EcoEvoRxiv* being books, book chapters, reports, and other research output types, which are typically considered ‘grey literature’ in ecology and evolutionary biology.
+As a result, submissions to *EcoEvoRxiv* are more diverse than those on preprint servers which have more restrictive submission policies.
 For example, *bioRxiv* only accepts research articles (https://www.biorxiv.org/submit-a-manuscript).
 
-Typical research articles are still the most common type of preprint on *EcoEvoRxiv* (`r sum_types[sum_types$type == "research article",]$perc`%), followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]D).
+Typical research articles are still the most common type of submission to *EcoEvoRxiv* (`r sum_types[sum_types$type == "research article",]$perc`%), followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]D).
 Currently, *EcoEvoRxiv* does not host many reports, particularly from government or industry, but has formed fruitful partnerships with the International Union for Conservation of Nature (IUCN).
@@
 We would encourage authors to consider posting books, book chapters, and reports to ensure that they are openly accessible and more easily found.
-*EcoEvoRxiv* articles are given a unique DOI and are indexed on Google Scholar.
+Accepted *EcoEvoRxiv* submissions are given a unique DOI and are indexed on Google Scholar.
 
@@
 
+# Session Information
 ```{r}

### 2024-10-03 ms/ms.qmd
Checking on submissions preprints and types

@@
 
-# How many preprints?
+# How many submissions? (everything)
   pr <- length(unique(data$`Preprint ID`))
 
-# Dates preprints were published, range and graph
+# Dates submissions were published, range and graph (everything)
   dates <- range(data$`Published Date`)
@@
 ##---------------------##
-# Articles on EcoEvoRxiv over time
+# Submissions to  EcoEvoRxiv over time (everything)
 ##---------------------##
@@
 ##---------------------##
-# Countries using EcoEvoRxiv
+# Submissions by Country to EcoEvoRxiv (everything)
 ##---------------------##
@@
 ##---------------------##
-# Taxa
+# Taxa (everything)
 ##---------------------##
@@
 ##---------------------##
-# Types of preprints
+# Types of preprints (preprints only)
 ##---------------------##
@@
 ##-------------------##
-# Career Stage & Gender
+# Career Stage & Gender (preprints only, but all article types)
 ##-------------------##
@@
 Such initiatives are incredibly important if we are to begin filling global voids of scientific knowledge.
-However, multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish articles, and a single Portuguese article, posted since starting to accept non-English articles in 2023.
-Part of the challenge in getting authors to submit non-English articles is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries, cultural differences in the perception of preprints, and a strong reliance on traditional publishing models that typically mandate publishing in English [@arenas2024academic].
+However, multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish submissions, and a single Portuguese submitted, since starting in 2023.
+Part of the challenge in getting authors to submit in non-English languages is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries, cultural differences in the perception of preprints, and a strong reliance on traditional publishing models that typically mandate publishing in English  [@arenas2024academic].
 
@@
 
-Research papers can take a while to be published (see below).
+Research can take a while to be published (see below).
 However, Early and Mid-Career Researchers (EMCRs) (~10 years post-PhD) are under pressure to publish rapidly to be competitive in job applications, promotions, and obtaining grants to progress their careers [@vale2015accelerating; @sarabipour2019value].
@@
 Our data on gender had only two missing values--one where the first name of the submitting author was missing and the other one for a collective submission.
-As expected, we found that women were less likely to publish on *EcoEvoRxiv* compared to men (women: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`%), which may reflect the broader publishing disparities between male and female scientists [@fox2019gender].
+As expected, we found that women were less likely to submit to *EcoEvoRxiv* compared to men (women: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`%), which may reflect the broader publishing disparities between male and female scientists [@fox2019gender].
 
@@
 
-# How many remain unpublished?
-unpub <- data2  %>% filter(is.na(publication_doi))  %>% nrow()
+# How many preprints remain unpublished? (preprints only)
+unpub <- preprints  %>% filter(is.na(publication_doi))  %>% nrow()
 
-# Summary of the data
+# Summary of the data (preprints only)
 # what is the range
@@
 ##-------------------##
-# Open access
+# Open access (preprints only, but all article types)
 ##-------------------##
@@
 ##-------------------##
-# Data and Code Sharing
+# Data and Code Sharing (preprints only, but all article types)
 ##-------------------##
@@
 
-We estimated how long it takes to publish a research paper in ecology and evolution by recording the time between when an article was first posted on *EcoEvoRxiv*, and its final acceptance in a peer-reviewed journal.
-In total, `r unpub` papers remained unpublished (`r (unpub / nrow(data2))*100`%, n = `r nrow(data2)`) at the time when these data were collected.
-Not all of these papers, however, are anticipated to be published in a peer-reviewed journal (e.g., reports).
+We estimated how long it takes to publish a research paper in ecology and evolution by recording the time between initial submission to *EcoEvoRxiv*, and its final acceptance in a peer-reviewed journal.
+In total, `r unpub` submissions remained unpublished (`r (unpub / nrow(data2))*100`%, n = `r nrow(data2)`) at the time when these data were collected.
+Not all of these submissions, however, are anticipated to be published in a peer-reviewed journal (e.g., reports).
 Nonetheless, the median time to publication for preprints was `r sum_preprints$median` days (8 months) (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days) with the maximum time to publication being `r sum_preprints$max` days or `r sum_preprints$max/365` years ([@fig-pubsummary]A).
@@
 In addition to speeding up dissemination, preprints and postprints can also be a useful way to ensure that research remains open and accessible to the research community irrespective of the accessibility of the final peer-reviewed paper [@bourne2017ten; @vale2015accelerating].
-We evaluated whether articles hosted at *EcoEvoRxiv*, and that were also published in a journal, were published open access.
+We evaluated whether preprints and postprints hosted at *EcoEvoRxiv*, and that were also published in a journal, were published open access.
 The open access status of each published article was obtained using the R package *roadoi* (v.`r utils::packageVersion("roadoi")`) to connect to the Unpaywall platform [@jahn2024].
-Most of the published articles were open access [`r sum_is_oa$valid_percent[2]*100`% (*n* = `r sum_is_oa$n[2]` out of `r sum(sum_is_oa$n[1:2])` where the status was known); [@fig-pubsummary]A]; however, `r sum_is_oa$valid_percent[1]*100`% (*n* = `r sum_is_oa$n[1]`) were published behind paywalls.
-For articles published in open access journals, the type of open access also varied widely (e.g., Gold, Hybrid, Green OA etc., [@fig-pubsummary]B).
+Most of the published preprints and postprints were open access [`r sum_is_oa$valid_percent[2]*100`% (*n* = `r sum_is_oa$n[2]` out of `r sum(sum_is_oa$n[1:2])` where the status was known); [@fig-pubsummary]A]; however, `r sum_is_oa$valid_percent[1]*100`% (*n* = `r sum_is_oa$n[1]`) were published behind paywalls.
+For preprints and postprints published in open access journals, the type of open access also varied widely (e.g., Gold, Hybrid, Green OA etc., [@fig-pubsummary]B).
 
 Data and code sharing are also key components of open science [@roche2015public].
-In the spirit of 'openness', we expected data and code sharing among preprints to be greater than in many papers published in research journals [@roche2015public; @o2021preferred].
+In the spirit of 'openness', we expected data and code sharing among preprints and postprints to be greater than in many papers published in research journals [@roche2015public; @o2021preferred].
 Despite this, we found that `r (preprint_data[1,"n"]/sum(preprint_data[c(1,3),"n"]))*100`%  (*n* = `r preprint_data[1,2]`) of articles relying on data on *EcoEvoRxiv* did not share data, and `r (preprint_code[1,"n"]/sum(preprint_code[c(1,3),"n"]))*100`% (*n* = `r preprint_code[1,2]`) did not share code (counting only data-based articles, i.e., excluding reviews, commentaries or theoretical works).

### 2024-10-03 ms/ms.qmd
Some text edits

@@
 *EcoEvoRxiv* is one of the few community-driven preprint servers that has paved the way for new initiatives, by accepting multilingual preprints, registered reports, and non-traditional research reports.
-Such initiatives are distinct from other preprint servers, such as bioRxiv, which only accepts empirical research in English.
+Such initiatives are distinct from other preprint servers, such as bioRxiv, which only accept empirical research in English.
 *EcoEvoRxiv* also promotes peer review and community discussion in the hopes of improving the quality of preprints and speeding up their peer-reviewed publication (e.g., Peer Community In -- PCI [@guillemaud2019peer]).
@@
 
+# Dataframes
+            submissions <- data2          # Cntains all submissions, preprints, postprints and all article types
+              preprints <- data2  %>% filter(time_between_preprint_and_pub_days >= 60) # Contains only preprints and not postprints
+preprints_research_only <- data2  %>% filter(time_between_preprint_and_pub_days >= 60 & type_of_preprint == "research article") # Limits preprints to research only articles
+
   # Subset the preprints
-  preprints <- data2  %>% filter(time_between_preprint_and_pub_days >= 60)
-
   dates_preprints <- range(preprints$preprint_published_date)
@@
 Research can take a while to be published (see below).
-However, Early and Mid-Career Researchers (EMCRs) (~10 years post-PhD) are under pressure to publish rapidly to be competitive in job applications, promotions, and obtaining grants to progress their careers [@vale2015accelerating; @sarabipour2019value].
-Preprints are one way EMCRs can achieve faster dissemination and greater visibility [@fu2019releasing].
+Early and Mid-Career Researchers (EMCRs) (~10 years post-PhD) are under pressure to publish rapidly to be competitive in job applications, promotions, and obtaining grants to progress their careers [@vale2015accelerating; @sarabipour2019value].
+Preprints are especially useful for EMCRs because they can achieve faster dissemination and greater visibility [@fu2019releasing].
 As such, EMCRs may be expected to make use of preprints more than colleagues at later career stages.

### 2024-10-04 ms/ms.qmd
Dealing with more comments

@@
 Community driven preprint initiatives can allow a research community to come together to break down these barriers to improve equity and coverage of global knowledge.
-Here, we explore the first preprints uploaded to EcoEvoRxiv, a community-driven preprint server for ecologists and evolutionary biologists, to characterise preprint practices in ecology, evolution and conservation.
-Our perspective piece highlights some of the unique initiatives that EcoEvoRxiv has taken to break down barriers to scientific publishing by exploring the composition of articles, how gender and career stage influence preprint use, whether preprints are associated with greater open science principles (e.g., code and data sharing), and tracking preprint publication outcomes.
-Our analysis identifies areas that we still need to improve upon but highlight how community-driven initiatives, such as EcoEvoRxiv, can play a crucial role in shaping publishing practices in biology.
+Here, we explore the first preprints uploaded to *EcoEvoRxiv*, a community-driven preprint server for ecologists and evolutionary biologists, to characterise preprint practices in ecology, evolution and conservation.
+Our perspective piece highlights some of the unique initiatives that *EcoEvoRxiv* has taken to break down barriers to scientific publishing by exploring the composition of articles, how gender and career stage influence preprint use, whether preprints are associated with greater open science principles (e.g., code and data sharing), and tracking preprint publication outcomes.
+Our analysis identifies areas that we still need to improve upon but highlight how community-driven initiatives, such as *EcoEvoRxiv*, can play a crucial role in shaping publishing practices in biology.
 
@@
 Editors are ecologists and evolutionary biologists from across the globe who volunteer their time to screen papers and push new initiatives in the preprint space.
-*EcoEvoRxiv* allows authors to post both preprints and postprints (also known as author-accepted manuscripts).
+*EcoEvoRxiv* allows authors to submit both preprints and postprints (also known as author-accepted manuscripts).
 While preprints are versions of manuscripts posted by authors before peer-review, postprints are versions of peer-reviewed and accepted articles but without typesetting and formatting by a journal.
@@
 #| label: fig-summary
-#| fig-cap: "Summary of submissions to *EcoEvoRxiv*.
-A) Number of submissions (preprints and postprints) published on *EcoEvoRxiv* between 2018 and 2023.
+#| fig-cap: "Summary of articles posted to *EcoEvoRxiv*.
+A) Number of articles (preprints and postprints) published on *EcoEvoRxiv* between 2018 and 2023.
 *EcoEvoRxiv* was established in June 2018 before the launch in November 2018.
-Notable milestones include *EcoEvoRxiv* transitioning to the California Digital Library (CDL), the acceptance of submissions in Spanish and Portuguese, and the acceptance of the first IUCN Red List Ecosystem report; B) Geographic origin of the preprints and postprints uploaded to *EcoEvoRxiv*, inferred from the country of affiliation of the submitting author; C) Taxa used/covered in the articles posted to *EcoEvoRxiv* (n = 1080 articles); D) Types of preprints accepted on *EcoEvoRxiv* (n = 620 articles).
-E) Academic age of authors submitting to *EcoEvoRxiv* along with the gender of the submitting author.
+Notable milestones include *EcoEvoRxiv* transitioning to the California Digital Library (CDL), the acceptance of preprints and postprints in Spanish and Portuguese, and the acceptance of the first IUCN Red List Ecosystem report; B) Geographic origin of the preprints and postprints uploaded to *EcoEvoRxiv*, inferred from the country of affiliation of the submitting author; C) Taxa used/covered in the articles posted to *EcoEvoRxiv* (n = 1080 articles); D) Types of preprints accepted on *EcoEvoRxiv* (n = 620 articles).
+E) Academic age of authors posting to *EcoEvoRxiv* along with the gender of the submitting author.
 Values lower than zero are indicative of authors who uploaded preprints before their first scientific publication in a journal.
@@
 
-To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the accepted submissions in EcoEvoRxiv as of  `r gsub("UTC", "", dates[2])` (see Supplement for more details on methods).
-We consider both preprints and postprints as ‘submissions’.
-After removing five duplicate titles – suggesting that a few authors created multiple submissions for the same preprint rather than updating the existing submission – we had data for a total of `r pr` articles with ~55--60 submissions published approximately monthly in the last two years ([@fig-summary]A).
-*EcoEvoRxiv* hosts submissions from authors based in `r length(unique(countries$country))` countries, with 90% coming from just `r nrow(most_use)-1` countries.
+To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the accepted articles available on *EcoEvoRxiv* as of  `r gsub("UTC", "", dates[2])` (see Supplement for more details on methods).
+We consider both preprints and postprints as ‘articles’.
+After removing five duplicate titles – suggesting that a few authors uploaded the article as separate submissions rather than updating the existing article – we had data for a total of `r pr` articles with ~55--60 posted approximately monthly in the last two years ([@fig-summary]A).
+*EcoEvoRxiv* hosts articles from authors based in `r length(unique(countries$country))` countries, with 90% coming from just `r nrow(most_use)-1` countries.
 North America, Australia, and European countries upload the most preprints, with many fewer coming from countries in Africa, Central America, and parts of Asia ([@fig-summary]B).
-Submissions covered all major taxonomic groups, with the most common groups being vertebrates (`r sum_taxa$perc[6]`%), plants (`r sum_taxa$perc[1]`%), and invertebrates (`r sum_taxa$perc[5]`%) ([@fig-summary]C).
+Articles covered all major taxonomic groups, with the most common groups being vertebrates (`r sum_taxa$perc[6]`%), plants (`r sum_taxa$perc[1]`%), and invertebrates (`r sum_taxa$perc[5]`%) ([@fig-summary]C).
 
@@
 Accepting a greater diversity of article types allows *EcoEvoRxiv* to help deal with the 'grey literature' problem, whereby data that are relevant for research syntheses are not published in typical peer-reviewed journals [@haddaway2015shades; @haddaway2020eight].
-*EcoEvoRxiv* has made a concerted effort to diversify the types of submissions accepted.
-This is reflected by `r nt`% of the submissions on *EcoEvoRxiv* being books, book chapters, reports, and other research output types, which are typically considered ‘grey literature’ in ecology and evolutionary biology.
-As a result, submissions to *EcoEvoRxiv* are more diverse than those on preprint servers which have more restrictive submission policies.
+*EcoEvoRxiv* has made a concerted effort to diversify the types of articles hosted.
+This is reflected by `r nt`% of of the articles being books, book chapters, reports, and other research output types, which are typically considered ‘grey literature’ in ecology and evolutionary biology.
+As a result, articles on *EcoEvoRxiv* are more diverse than those on other preprint servers which have more restrictive submission policies.
 For example, *bioRxiv* only accepts research articles (https://www.biorxiv.org/submit-a-manuscript).
 
-Typical research articles are still the most common type of submission to *EcoEvoRxiv* (`r sum_types[sum_types$type == "research article",]$perc`%), followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]D).
+Empirical research articles are still the most common type of article submitted to *EcoEvoRxiv* (`r sum_types[sum_types$type == "research article",]$perc`%), followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]D).
 Currently, *EcoEvoRxiv* does not host many reports, particularly from government or industry, but has formed fruitful partnerships with the International Union for Conservation of Nature (IUCN).
@@
 Preprints are especially useful for EMCRs because they can achieve faster dissemination and greater visibility [@fu2019releasing].
-As such, EMCRs may be expected to make use of preprints more than colleagues at later career stages.
+EMCRs may therefore be expected to make use of preprints more than colleagues at later career stages because they are more often in charge of article submission and have developed their careers in an environment where preprints are a normal part of the publication process.
 We collected data on the 'academic age' of submitting authors by looking at Google Scholar profiles of authors (when available) and recording their first year of publication in a peer-reviewed journal.
@@
 Our data on gender had only two missing values--one where the first name of the submitting author was missing and the other one for a collective submission.
-As expected, we found that women were less likely to submit to *EcoEvoRxiv* compared to men (women: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`%), which may reflect the broader publishing disparities between male and female scientists [@fox2019gender].
+As expected, we found that women were less likely to post to *EcoEvoRxiv* compared to men (women: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`%), which may reflect the broader publishing disparities between male and female scientists [@fox2019gender].
 
@@
 A) Time between uploading an preprint to *EcoEvoRxiv* and its publication as a peer-reviewed journal article.
-Articles that were published within 2 months (60 days) of being submitted are considered postprints and are not included in this figure.
-B) Access status of articles linked to *EcoEvoRxiv* preprints classified as “Open Access” or “Not Open Access”.
+Preprints were considered those articles that were published a minimum of 2 months (60 days) after being posted to *EcoEvoRxiv*.
+B) Access status of published articles (both preprints and postprints) linked to *EcoEvoRxiv* preprints classified as “Open Access” or “Not Open Access”.
 “Unknown” status is for articles not explicitly identified as being open access or not on the Unpaywall platform.
-C) Sub-types of open access status of articles linked to *EcoEvoRxiv* preprints.
-For full details on the meaning of each category see  https://support.unpaywall.org/support/solutions/articles/44001777288-what-do-the-types-of-oa-status-green-gold-hybrid-and-bronze-mean-.
+C) Sub-types of open access status of published articles on *EcoEvoRxiv*.
+Sub-type meanings are as follows: ‘Green’, articles published in ‘toll-access journals but achieved in an open access repository; ‘Bronze’, articles are free to read on publishers website without a license but grants no other rights and can be delayed free-to-read; ‘Hybrid’, articles are free to read upon publication with an open access license; ‘Gold’, articles published in fully open access journals.
+For full details on the meaning of each category see  https://support.unpaywall.org/support/solutions/articles/44001777288-what-do-the-types-of-oa-status-green-gold-hybrid-and-bronze-mean-
 
@@
 
-We estimated how long it takes to publish a research paper in ecology and evolution by recording the time between initial submission to *EcoEvoRxiv*, and its final acceptance in a peer-reviewed journal.
+We estimated how long it takes to publish a preprint in ecology and evolution by recording the time between when a preprint was first posted on *EcoEvoRxiv*, and its final acceptance in a peer-reviewed journal.
 In total, `r unpub` submissions remained unpublished (`r (unpub / nrow(data2))*100`%, n = `r nrow(data2)`) at the time when these data were collected.
-Not all of these submissions, however, are anticipated to be published in a peer-reviewed journal (e.g., reports).
+Not all of these preprints, however, are anticipated to be published in a peer-reviewed journal (e.g., reports).
 Nonetheless, the median time to publication for preprints was `r sum_preprints$median` days (8 months) (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days) with the maximum time to publication being `r sum_preprints$max` days or `r sum_preprints$max/365` years ([@fig-pubsummary]A).

### 2024-10-09 ms/ms.qmd
C8 dealt with
C2 dealt with

@@
 For preprints and postprints published in open access journals, the type of open access also varied widely (e.g., Gold, Hybrid, Green OA etc., [@fig-pubsummary]B).
+Such a result may not be too surprising given that authors using preprint servers are probably already ‘pro-open access’; particularly given that *EcoEvoRxiv* is run by Society for Open, Reliable, and Transparent Ecology and Evolutionary Biology (SORTEE).
 
@@
 While it is clear that preprints help establish precedence and allow findings to be openly accessible, it still seems rare that constructive discussions form around preprints in an open forum (e.g.
-bioRxiv [@anderson2020biorxiv]).
+*bioRxiv* [@anderson2020biorxiv]).
 Unfortunately, the *EcoEvoRxiv* website does not provide opportunities for discussion given the limitations of the web server at this point in time.
 As such, we could not accurately assess how much discourse around a given preprint occurs.
-Clearly, as a community, we need to provide better platforms that document discussions around preprint findings.
+One way to facilitate such discussions may be to use open preprint peer-review services such as *Peer Community In* (PCI) or *PubPeer* (see also [@avissar2024recommendations]) to provide feedback on preprints.
+Both *PCI* and *PubPeer* provide opportunities for open peer review around a preprint that are given a unique DOI which can then be associated with a preprint on *EcoEvoRxiv*.
+However, *EcoEvoRxiv* currently lacks connection to *PCI*, *PubPeer* and Altmetric data which would allow for discussion to be assimilated around a preprint in one place and make it easy for readers to see discourse around a preprint.
+Clearly, as a community, we need to provide better platforms and workflows that document discussions around preprint findings.
 Such discussions help authors improve their work and communicate their findings more effectively (when done constructively, of course).
-One way to facilitate such discussions may be to use open preprint peer-review services such as *Peer Community In* (PCI) or *PubPeer* (see also [@avissar2024recommendations]) to provide feedback on preprints.
+An important future goal of *EcoEvoRxiv* is to provide better community discussion forums and integration with existing preprint peer review services.
 - Finally, keep your preprints updated.

### 2024-10-11 ms/ms.qmd
C17 done
C18 and C21

@@
 *EcoEvoRxiv* also promotes peer review and community discussion in the hopes of improving the quality of preprints and speeding up their peer-reviewed publication (e.g., Peer Community In -- PCI [@guillemaud2019peer]).
-Peer Community In allows for fast, constructive peer review around a preprint with peer reviews being transparent and published online [@guillemaud2019peer].
+For example, we encourage authors to use services such as PCI, which allow for fast, constructive peer review around a preprint with peer reviews being transparent and published online [@guillemaud2019peer].
 
@@
 To obtain a rough idea of an author's gender, we used the R package *gender* (v.`r utils::packageVersion("gender")`; @mullen2021predict) to predict the most likely gender of the submitting author of a preprint.
-We only used algorithm-assigned names where the gender was identified with 95% certainty.
+We used an algorithm to assign gender based on the submitting author’s name.
+We only used the algorithm-assigned gender when the gender of a given name was identified with 95% certainty.
 For the remaining names, we performed manual searches to determine gender based on the pronouns and photographs from professional and personal websites.
@@
 This requirement is a good outcome if it results in higher-impact research that better clarifies our understanding of the natural world, but it does come at a cost for the speed of research dissemination [@vale2015accelerating].
-Preprints have been proposed as a way to disseminate research more quickly as it can take a long time before results are ultimately published [@bourne2017ten; @vale2015accelerating].
+Preprints have been proposed as a way to disseminate research more quickly as it can take a long time before results are ultimately published after formal peer review [@bourne2017ten; @vale2015accelerating].
 However, data on the time to publication is needed to quantify the real benefit of preprints in this context.

### 2024-10-11 ms/ms.qmd
Dealing with a whole bunch of new comments

@@
 Preprints in biology have had a slower uptake relative to other disciplines [@Berg2016], but new discipline-specific preprint servers, such as *EcoEvoRxiv* (https://ecoevorxiv.org), provide a means by which ecologists and evolutionary biologists can disseminate research findings.
-Preprints attempt to break down barriers to scientific publishing by: 1) increasing the visibility of research and the speed at which research findings become available, which can lead to more citations [e.g., @colavizza2024analysis; @fu2019releasing]; 2) helping establish the precedence of research findings; 3) removing financial barriers to open access publication; and 4) enabling feedback from the research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
+Preprints attempt to break down barriers to scientific publishing by: 1) increasing the visibility of research and the speed at which research findings become available, which can lead to more citations [e.g., @colavizza2024analysis; @fu2019releasing]; 2) helping establish the precedence of research findings; 3) removing financial barriers to open access publication; and 4) enabling earlier feedback from the research community [@Proulx2013; @bourne2017ten; @vale2015accelerating].
 Ultimately, preprints can facilitate the rapid sharing of scientific knowledge that can have significant impacts on fundamental and applied knowledge globally [@ni2024preprint].
@@
 Most of the published preprints and postprints were open access [`r sum_is_oa$valid_percent[2]*100`% (*n* = `r sum_is_oa$n[2]` out of `r sum(sum_is_oa$n[1:2])` where the status was known); [@fig-pubsummary]A]; however, `r sum_is_oa$valid_percent[1]*100`% (*n* = `r sum_is_oa$n[1]`) were published behind paywalls.
+Published articles behind paywalls would otherwise remain inaccessible if it were not for *EcoEvoRxiv*.
 For preprints and postprints published in open access journals, the type of open access also varied widely (e.g., Gold, Hybrid, Green OA etc., [@fig-pubsummary]B).
@@
 In the spirit of 'openness', we expected data and code sharing among preprints and postprints to be greater than in many papers published in research journals [@roche2015public; @o2021preferred].
-Despite this, we found that `r (preprint_data[1,"n"]/sum(preprint_data[c(1,3),"n"]))*100`%  (*n* = `r preprint_data[1,2]`) of articles relying on data on *EcoEvoRxiv* did not share data, and `r (preprint_code[1,"n"]/sum(preprint_code[c(1,3),"n"]))*100`% (*n* = `r preprint_code[1,2]`) did not share code (counting only data-based articles, i.e., excluding reviews, commentaries or theoretical works).
+Despite this, we found that `r (preprint_data[1,"n"]/sum(preprint_data[c(1,3),"n"]))*100`%  (*n* = `r preprint_data[1,2]`) of articles relying on data (i.e., classified as ‘research articles’) on *EcoEvoRxiv* did not share data, and `r (preprint_code[1,"n"]/sum(preprint_code[c(1,3),"n"]))*100`% (*n* = `r preprint_code[1,2]`) did not share code.
 
@@
 The same was true for code.
-Overall, `r pre_article_code[3,"percent"]*100`% (*n* = `r pre_article_code[3,2]`) preprints had no open code at the preprint stage but did at the published article stage and authors of `r pre_article_code[2,"percent"]*100`% (*n* = `r pre_article_code[2,2]`) preprints did not share code at either stage.
+Overall, `r pre_article_code[3,"percent"]*100`% (*n* = `r pre_article_code[3,2]`) of preprints had no open code at the preprint stage but did at the published article stage and authors of `r pre_article_code[2,"percent"]*100`% (*n* = `r pre_article_code[2,2]`) preprints did not share code at either stage.
 However, `r pre_article_code[1,"percent"]*100`% (*n* = `r pre_article_code[1,2]`) shared code at both stages.
@@
 Code and data sharing was also relatively uncommon at the preprint stage.
-At the same time, we attempted to collect data on community discussion around preprints no such data was found on preprint landing pages, likely reflecting inadequate functionality and cross-linking with sources where such discussion is occurring.
+At the same time, we attempted to collect data on community discussion around preprints.
+However, no such data was found on preprint landing pages, likely reflecting inadequate functionality and cross-linking with sources where such discussion is occurring.
 Based on the insights from our analysis, we provide recommendations to authors and the scientific community on ways they can further promote open and transparent research through preprints:
@@
 - First, share your data and code at the preprint stage.
-Sharing data and code early can help improve the quality of research, establish precedence, and improve the transparency and computational reproducibility of scientific findings [@sarabipour2019value].
+Sharing data and code early can help improve the quality of research, establish precedence, and improve the transparency and computational reproducibility of scientific findings [@sarabipour2019value; @gomes2022don].
 Reassuringly, sharing data and code is rarely associated with the 'scooping' of research findings [@soeharjono2021reported].

### 2024-10-13 ms/ms.qmd
Adding some clarity to C30

@@
 Our data on gender had only two missing values--one where the first name of the submitting author was missing and the other one for a collective submission.
-As expected, we found that women were less likely to post to *EcoEvoRxiv* compared to men (women: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`%), which may reflect the broader publishing disparities between male and female scientists [@fox2019gender].
+As expected, we found that women were less likely to post to *EcoEvoRxiv* compared to men (women: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`%), reinforcing existing disparities between male and female scientists.
+For example, studies have shown that female first authors have lower acceptance rates and are cited less (~2%) compared to males [e.g., @fox2019gender].
 

### 2024-10-13 ms/ms.qmd
C3, but also moving around blocks of text
Adjusting C3 and adding more clarity to 3rd paragraph

@@
 Such initiatives are distinct from other preprint servers, such as bioRxiv, which only accept empirical research in English.
+In addition, community-driven servers like EcoEvoRxiv aggregate papers presenting research on similar topics, improving discoverability and opportunities for within-community debate compared with broader preprint servers.
 *EcoEvoRxiv* also promotes peer review and community discussion in the hopes of improving the quality of preprints and speeding up their peer-reviewed publication (e.g., Peer Community In -- PCI [@guillemaud2019peer]).
 For example, we encourage authors to use services such as PCI, which allow for fast, constructive peer review around a preprint with peer reviews being transparent and published online [@guillemaud2019peer].
+*EcoEvoRxiv* allows authors to submit both preprints and postprints (also known as author-accepted manuscripts).
+While preprints are versions of manuscripts posted by authors before peer-review, postprints are versions of peer-reviewed and accepted articles but without typesetting and formatting by a journal.
+The main reason for publishing postprints on a preprint server is to ensure published articles are openly accessible to everyone without a paywall (i.e., green open access).
+Postprints can be published anytime, if journals allow it (which most do; see https://www.sherpa.ac.uk/romeo/).
 
@@
 Editors are ecologists and evolutionary biologists from across the globe who volunteer their time to screen papers and push new initiatives in the preprint space.
-*EcoEvoRxiv* allows authors to submit both preprints and postprints (also known as author-accepted manuscripts).
-While preprints are versions of manuscripts posted by authors before peer-review, postprints are versions of peer-reviewed and accepted articles but without typesetting and formatting by a journal.
-The main reason for publishing postprints on a preprint server is to ensure published articles are openly accessible to everyone without a paywall (i.e., green open access).
-Postprints can be published anytime, provided that journals allow it (which most do; see https://www.sherpa.ac.uk/romeo/).
+To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the accepted articles available on *EcoEvoRxiv* as of  `r gsub("UTC", "", dates[2])` (see Supplement for more details on methods).
+We consider both preprints and postprints as ‘articles’.
+After removing five duplicate titles – suggesting that a few authors uploaded the article as separate submissions rather than updating the existing article – we had data for a total of `r pr` articles with ~55--60 posted approximately monthly in the last two years ([@fig-summary]A).
 
@@
 
-To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the accepted articles available on *EcoEvoRxiv* as of  `r gsub("UTC", "", dates[2])` (see Supplement for more details on methods).
-We consider both preprints and postprints as ‘articles’.
-After removing five duplicate titles – suggesting that a few authors uploaded the article as separate submissions rather than updating the existing article – we had data for a total of `r pr` articles with ~55--60 posted approximately monthly in the last two years ([@fig-summary]A).
 *EcoEvoRxiv* hosts articles from authors based in `r length(unique(countries$country))` countries, with 90% coming from just `r nrow(most_use)-1` countries.

### 2024-10-13 ms/ms.qmd
C27

@@
 *EcoEvoRxiv* was established in June 2018 before the launch in November 2018.
-Notable milestones include *EcoEvoRxiv* transitioning to the California Digital Library (CDL), the acceptance of preprints and postprints in Spanish and Portuguese, and the acceptance of the first IUCN Red List Ecosystem report; B) Geographic origin of the preprints and postprints uploaded to *EcoEvoRxiv*, inferred from the country of affiliation of the submitting author; C) Taxa used/covered in the articles posted to *EcoEvoRxiv* (n = 1080 articles); D) Types of preprints accepted on *EcoEvoRxiv* (n = 620 articles).
+Notable milestones include *EcoEvoRxiv* transitioning to the California Digital Library (CDL), the acceptance of preprints and postprints in Spanish and Portuguese, and the acceptance of the first IUCN Red List Ecosystem report; B) Geographic origin of the preprints and postprints uploaded to *EcoEvoRxiv*, inferred from the country of affiliation of the submitting author; C) Taxa used/covered in the articles posted to *EcoEvoRxiv* (n = 1080 articles covering relevant taxa); D) Types of preprints accepted on *EcoEvoRxiv* (n = 620 articles).
 E) Academic age of authors posting to *EcoEvoRxiv* along with the gender of the submitting author.
@@
 Accepted *EcoEvoRxiv* submissions are given a unique DOI and are indexed on Google Scholar.
+Having a unique DOI means that the article can be accessed in perpetuity.
+If the preprint becomes published, then this DOI is merged with the published DOI.
 

### 2024-10-14 ms/ms.qmd
added in lack of discussion point
C38 & C41

@@
 Such discussions help authors improve their work and communicate their findings more effectively (when done constructively, of course).
-An important future goal of *EcoEvoRxiv* is to provide better community discussion forums and integration with existing preprint peer review services.
+Lack of discussion around preprints more generally might also be a function of time constraints researchers face and the lack of credit received for such a community service.
+An important future goal of EcoEvoRxiv is to provide better community discussion forums and integration with existing preprint peer review services.
+We also need to find new ways to give credit to colleagues that contribute to community discussion.
 - Finally, keep your preprints updated.

### 2024-10-15 ms/ms.qmd
C11
C10

@@
 Gender differences in preprint use and publication outcomes have also been observed in several research fields, including ecology and evolutionary biology [@fox2019gender; @wehner2020comparison].
+For example, gender gaps in preprint submissions were observed during COVID-19 lockdowns [@ucar2022mind], and previous surveys have shown that female participants are less likely to suggest posting articles as preprints, suggesting gender differences in views around preprints [@fraser2022motivations].
 Therefore, such discrepancies are expected to manifest in preprint use on *EcoEvoRxiv*, but it is unclear to what extent.
@@
 Volunteers at *EcoEvoRxiv* are encouraged to remain open to new and innovative ways to improve publication and open science practices.
+Our analysis can be used to drive changes in *EcoEvoRxiv* to make it a better platform for our community.
 We believe that the future of preprints is bright, and community-driven initiatives, such as *EcoEvoRxiv* will play a crucial role in the future of scientific publishing.

### 2024-10-15 docs/supp.qmd
Update supplement

--- 2024-09-25 supp/supp.qmd
@@
     code-overflow: wrap
-  docx:
-    reference-doc: ../bib/template.docx
-  pdf:
-    include-in-header: 
-      text: '\usepackage{lineno}\linenumbers'
 editor_options: 
@@
 
-As part of the Society for Open, Reliable and Transparent Ecology and Evolutionary Biology's (SORTEE - https://www.sortee.org) conference, we ran a workshop (i.e., Hackathon) where we invited interested SORTEE members and conference registrants to participate in the data collection process.
+As part of the Society for Open, Reliable and Transparent Ecology and Evolutionary Biology's (SORTEE - https://www.sortee.org) conference, we ran a workshop (i.e., Hackathon - entitled "The first 1000 *EcoEvoRxiv* preprints: did they get published and where?") where we invited interested SORTEE members and conference registrants to participate in the data collection process.
 We provided a detailed data collection protocol to all delegates prior to the workshop ([vers.
@@
 
-## Data Checking and Validation
-Data from each preprint was cross checked by two authors to ensure accuracy and consistency of the data collected. Any discrepancies were either discussed or fixed prior to analysis.
+## Data Checking, Merging and Validation
+The initial dataset collected by participants from the Hackathon was cleaned, merged (with master meta-data file provided by the California Digital Library) and reorganised (see `1_data_processing.R` and `2_data_cleaning.R` in the `R/` folder of the main GitHub repository).
+This new dataset was again placed in a Google Sheet and co-authors were randomly allocated a number of pre-prints for cross-checking.
+The number of preprints allocated reflected contributions of authors during earlier data collection stages.
+Co-authors who did less work during initial data collection stages were given more papers to cross-check to ensure equitable contributions to the paper.
+This meant that the number of papers given to an author to cross-check ranged from ~10-50 papers.
+
+Data from each preprint was cross checked by one additional author to ensure accuracy and consistency of the data collected.
+Any discrepancies were either discussed or fixed prior to analysis.
+Most data that was corrected included data such as missed DOI's for published preprints, missing or incorrect citation counts to preprints and published articles, and missing or incorrect publication dates.
+It became evident that missing citation counts to preprints were largely the result of preprints and published articles not being correctly merged in Google Scholar.
+As such, checking citations to preprints involved looking carefully at all papers on the submitting author's Google Scholar profile and cross checking titles.
+Often it was clear redundant articles existed that were not merged.
+We then checked that the unmerged preprint and the published article were in fact the same study before updating preprint and publication citation counts.
+We also made note when any titles changed from preprint to publication.
+At times, preprints had been merged with published versions of the same study.
+To cross-check citation count to the preprint itself, we looked at the version history of the publication.
+If we found a clear preprint version, we took the citation count from that version.
+If it was not provided we assumed no data existed on citation counts for the preprint and it was assigned 'NA'.
+
+As indicated in the main manuscript.
+We collected data on the ‘academic age’ of submitting authors by looking at Google Scholar profiles of authors (when available) and recording their first year of publication in a peer-reviewed journal.
+If no google Scholar profile for the submitting author was availabel we attempted to acquire the information from other online research profiles (e.g., ResearchGate, ORCID, etc.).
+If no information was available we entered '0' as the first year of publication.
+
+One of us, ML, acquired the submitting authors gender using the R package gender [v.0.6.0; @mullen2021predict] to predict the most likely gender of the submitting author of a preprint.
+We used an algorithm to assign gender based on the submitting author’s name.
+We only used the algorithm-assigned gender when the gender of a given name was identified with 95% certainty.
+For the remaining names, ML performed manual searches to determine gender based on the pronouns and photographs from professional and personal websites.
 

### 2024-10-15 docs/supp.qmd
Open access status too

@@
 If it was not provided we assumed no data existed on citation counts for the preprint and it was assigned 'NA'.
-
 As indicated in the main manuscript.
 We collected data on the ‘academic age’ of submitting authors by looking at Google Scholar profiles of authors (when available) and recording their first year of publication in a peer-reviewed journal.
-If no google Scholar profile for the submitting author was availabel we attempted to acquire the information from other online research profiles (e.g., ResearchGate, ORCID, etc.).
+If no google Scholar profile for the submitting author was available we attempted to acquire the information from other online research profiles (e.g., ResearchGate, ORCID, etc.).
 If no information was available we entered '0' as the first year of publication.
+
+## Data collected computationally
 
@@
 For the remaining names, ML performed manual searches to determine gender based on the pronouns and photographs from professional and personal websites.
+
+The open access status of each published article was obtained using the R package *roadoi* (v.`r utils::packageVersion("roadoi")`) to connect to the Unpaywall platform [@jahn2024].
+This R package provided data on whether the published article was open access or not (i.e., whether the article was behind a paywall or not), and categorized the open access status of teh article (Sub-type meanings included: ‘Green’, articles published in ‘toll-access journals but achieved in an open access repository; ‘Bronze’, articles are free to read on publishers website without a license but grants no other rights and can be delayed free-to-read; ‘Hybrid’, articles are free to read upon publication with an open access license; ‘Gold’, articles published in fully open access journals.
+For full details on the meaning of each category see  https://support.unpaywall.org/support/solutions/articles/44001777288-what-do-the-types-of-oa-status-green-gold-hybrid-and-bronze-mean- ).
 

### 2024-10-15 docs/supp.qmd
Fix supp errors

@@
 
-# Materials and Methods
+# Supplemental Materials and Methods
 
@@
 The open access status of each published article was obtained using the R package *roadoi* (v.`r utils::packageVersion("roadoi")`) to connect to the Unpaywall platform [@jahn2024].
-This R package provided data on whether the published article was open access or not (i.e., whether the article was behind a paywall or not), and categorized the open access status of teh article (Sub-type meanings included: ‘Green’, articles published in ‘toll-access journals but achieved in an open access repository; ‘Bronze’, articles are free to read on publishers website without a license but grants no other rights and can be delayed free-to-read; ‘Hybrid’, articles are free to read upon publication with an open access license; ‘Gold’, articles published in fully open access journals.
+This R package provided data on whether the published article was open access or not (i.e., whether the article was behind a paywall or not), and categorized the open access status of the article (Sub-type meanings included: ‘Green’, articles published in ‘toll-access journals but achieved in an open access repository; ‘Bronze’, articles are free to read on publishers website without a license but grants no other rights and can be delayed free-to-read; ‘Hybrid’, articles are free to read upon publication with an open access license; ‘Gold’, articles published in fully open access journals.
 For full details on the meaning of each category see  https://support.unpaywall.org/support/solutions/articles/44001777288-what-do-the-types-of-oa-status-green-gold-hybrid-and-bronze-mean- ).

### 2024-10-15 docs/supp.qmd
Update to supplement by adding new Table S1

@@
 crossref:
-  fig-title: 'FigureS'
+  fig-title: 'Figure S'
+  tbl-title: 'Table S'
   fig-labels: arabic
   title-delim: "-"
-  fig-prefix: "FigureS"
-  tbl-prefix: "TableS"
+  fig-prefix: "Figure S"
+  tbl-prefix: "Table S"
 ---
@@
 
+## Publication time by article type 
+@tbl-time provides a breakdown of publication time by article type.
+
+```{r}
+#| label: tbl-time
+#| tbl-cap: Time between preprint submission and publication for different article types.
+
+# Load in the table(
+  tbl_time <- read.csv(here("output", "tables", "preprints_pub_only_stats.csv"))[,-1]
+
+# Flx
+  tbl <- flextable::flextable(tbl_time)  %>% 
+    flextable::set_table_properties(width = .5)  %>% 
+    flextable::set_header_labels("type_of_preprint" = "Article Type", "mean_time" = "Mean (days)", "sd_time" = "SD (days)", "n" = "N") %>% flextable::align(align = "center") 
+    tbl
+```
+
 ## Preprint citations versus published article citations

### 2024-10-15 ms/ms.qmd
Adding link to supplement
Added Table S1 ref in main MS for addressing C5

@@
 After removing five duplicate titles – suggesting that a few authors uploaded the article as separate submissions rather than updating the existing article – we had data for a total of `r pr` articles with ~55--60 posted approximately monthly in the last two years ([@fig-summary]A).
+For more details on the data collection process, see the Supplement (https://daniel1noble.github.io/ecoevo_1000/).
 
@@
 # Dataframes
-            submissions <- data2          # Cntains all submissions, preprints, postprints and all article types
               preprints <- data2  %>% filter(time_between_preprint_and_pub_days >= 60) # Contains only preprints and not postprints
-preprints_research_only <- data2  %>% filter(time_between_preprint_and_pub_days >= 60 & type_of_preprint == "research article") # Limits preprints to research only articles
+     preprints_pub_only <- data2  %>% filter(time_between_preprint_and_pub_days >= 60 & !is.na(preprint_published_date))
 
-  # Subset the preprints
+# Some descriptions
+
   dates_preprints <- range(preprints$preprint_published_date)
+
 ##---------------------##
@@
 
+# Publication time by article type
+  preprints_pub_only_stats <- preprints_pub_only                                                                    %>% 
+                              group_by(type_of_preprint)                                                            %>% 
+                              summarise(mean_time = mean(time_between_preprint_and_pub_days, na.rm = TRUE), 
+                                          sd_time = sd(time_between_preprint_and_pub_days, na.rm = TRUE), 
+                                                n = n())                                                             %>% 
+                              filter(!type_of_preprint == "report")                                                   %>% 
+                              mutate(mean_time = round(mean_time, 2), sd_time = round(sd_time, 2))
+  write.csv(preprints_pub_only_stats, here("output", "tables", "preprints_pub_only_stats.csv"))
+
 # Summary of the data (preprints only)
@@
 Not all of these preprints, however, are anticipated to be published in a peer-reviewed journal (e.g., reports).
-Nonetheless, the median time to publication for preprints was `r sum_preprints$median` days (8 months) (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days) with the maximum time to publication being `r sum_preprints$max` days or `r sum_preprints$max/365` years ([@fig-pubsummary]A).
+Nonetheless, the median time to publication for preprints was `r sum_preprints$median` days (8 months) for all preprints that ended up being published (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days) with the maximum time to publication being `r sum_preprints$max` days or `r sum_preprints$max/365` years ([@fig-pubsummary]A).
+For a full breakdown on the time to publication based on article type see Supplement (Table S1).
 Our results largely confirm the extended timeframes that most authors experience between writing their research papers and their publication.

### 2024-10-16 ms/ms.qmd
Fixed for C22

@@
 These patterns support the expectation that EMCRs may use preprints to make their work more visible and disseminate their findings more quickly.
-However, we acknowledge that validating this conclusion does require more rigorous experimental approaches.
+However, we acknowledge that understanding the reasons why EMCRs might adopt preprint servers more does require community surveys as has been done in other studies [e.g., @fraser2022motivations].
 

### 2024-10-16 ms/ms.qmd
Only one more comment to deal with

@@
 Preprints were considered those articles that were published a minimum of 2 months (60 days) after being posted to *EcoEvoRxiv*.
-B) Access status of published articles (both preprints and postprints) linked to *EcoEvoRxiv* preprints classified as “Open Access” or “Not Open Access”.
+B) Access status of published articles (both preprints and postprints) on *EcoEvoRxiv* classified as “Open Access” or “Not Open Access”.
 “Unknown” status is for articles not explicitly identified as being open access or not on the Unpaywall platform.
@@
 This requirement is a good outcome if it results in higher-impact research that better clarifies our understanding of the natural world, but it does come at a cost for the speed of research dissemination [@vale2015accelerating].
+Long publication times can adversely affect EMCRs who rely on publications for job applications, promotions, and obtaining grants.
+Getting research out quickly can also be critical for the development of new knowledge that can re-shape research landscapes, which was important during the COVID-19 pandemic [@algaa2021development].
 Preprints have been proposed as a way to disseminate research more quickly as it can take a long time before results are ultimately published after formal peer review [@bourne2017ten; @vale2015accelerating].
@@
 Incorrect cross-linking by indexing platforms (e.g., Google Scholar) can create confusion and lead to frustration among authors.
-Thankfully, the reasons for unmatched preprints and publications are well-understood and easily rectified.
+The reasons for unmatched preprints and publications are well-understood and usually easily rectified.
 They often result from a mismatch between preprint and published metadata (e.g., titles and author details).
@@
 We found that mismatched metadata almost always contributed to preprints and published articles not being matched automatically in Google Scholar.
-We recommend that authors update their preprints with the publication DOI when accepted to journals, especially if their title has changed.
-This is very easy for authors to do on *EcoEvoRxiv* and ensures that the preprint is correctly linked to the published article and citations are appropriately merged.
+At times further manual merging by authors is needed to connect the preprint and published article (this can be done in Google Scholar).
+Regardless, we recommend that authors update their preprints with the publication DOI when accepted to journals, especially if their title has changed.
+This is very easy for authors to do on *EcoEvoRxiv* and should increase the chances that the preprint is correctly linked to the published article and citations are appropriately merged.
 Adding DOIs will also create a link between the final preprint and the published paper so that, no matter the open access status of the publication, the research findings will remain openly accessible, saving costs for authors (i.e., by not having to pay open access fees) and improving the visibility and use of research.

### 2024-10-16 ms/ms.qmd
Fixed last comment

@@
 Authors may be reluctant to share data and code for preprints because of the perceived concern that others may acquire and use their data and code before publication in a journal.
-Authors of `r pre_article_data[3,"percent"]*100`% (*n* = `r pre_article_data[3,2]`) of articles that did not share data at the preprint stage did ultimately share data when the article was published; whereas authors of `r pre_article_data[2,"percent"]*100`% (*n* = `r pre_article_data[2,2]`) never shared data.
-However, `r pre_article_data[1,"percent"]*100`% (*n* = `r pre_article_data[1,2]`) shared data at both stages.
+Authors of `r pre_article_data[3,"percent"]*100`% (*n* = `r pre_article_data[3,2]`) preprints did not share data at the preprint stage, but ultimately did share data when the article was published; whereas authors of `r pre_article_data[2,"percent"]*100`% (*n* = `r pre_article_data[2,2]`) never shared data and `r pre_article_data[1,"percent"]*100`% (*n* = `r pre_article_data[1,2]`) shared data at both stages.
 The same was true for code.
-Overall, `r pre_article_code[3,"percent"]*100`% (*n* = `r pre_article_code[3,2]`) of preprints had no open code at the preprint stage but did at the published article stage and authors of `r pre_article_code[2,"percent"]*100`% (*n* = `r pre_article_code[2,2]`) preprints did not share code at either stage.
-However, `r pre_article_code[1,"percent"]*100`% (*n* = `r pre_article_code[1,2]`) shared code at both stages.
+Overall, `r pre_article_code[3,"percent"]*100`% (*n* = `r pre_article_code[3,2]`) of preprints had no open code at the preprint stage, but ultimately did share code at the published article stage.
+In contrast, authors of `r pre_article_code[2,"percent"]*100`% (*n* = `r pre_article_code[2,2]`) preprints did not share code at either stage and `r pre_article_code[1,"percent"]*100`% (*n* = `r pre_article_code[1,2]`) shared code at both stages.
 Relatively low code and data-sharing practices in our sample is consistent with analyses of sharing practices for published articles (e.g., [@o2021preferred]), even for journals with strict public data archiving policies [@roche2015public].

### 2024-10-20 ms/ms.qmd
Shina nd Losia's comments fixed

@@
 Community driven preprint initiatives can allow a research community to come together to break down these barriers to improve equity and coverage of global knowledge.
-Here, we explore the first preprints uploaded to *EcoEvoRxiv*, a community-driven preprint server for ecologists and evolutionary biologists, to characterise preprint practices in ecology, evolution and conservation.
-Our perspective piece highlights some of the unique initiatives that *EcoEvoRxiv* has taken to break down barriers to scientific publishing by exploring the composition of articles, how gender and career stage influence preprint use, whether preprints are associated with greater open science principles (e.g., code and data sharing), and tracking preprint publication outcomes.
+Here, we explore the first preprints uploaded to *EcoEvoRxiv* (*n* = 1216), a community-driven preprint server for ecologists and evolutionary biologists, to characterise preprint practices in ecology, evolution and conservation.
+Our perspective piece highlights some of the unique initiatives that *EcoEvoRxiv* has taken to break down barriers to scientific publishing by exploring the composition of articles, how gender and career stage influence preprint use, whether preprints are associated with greater open science practices (e.g., code and data sharing), and tracking preprint publication outcomes.
 Our analysis identifies areas that we still need to improve upon but highlight how community-driven initiatives, such as *EcoEvoRxiv*, can play a crucial role in shaping publishing practices in biology.
@@
 In addition, community-driven servers like EcoEvoRxiv aggregate papers presenting research on similar topics, improving discoverability and opportunities for within-community debate compared with broader preprint servers.
-*EcoEvoRxiv* also promotes peer review and community discussion in the hopes of improving the quality of preprints and speeding up their peer-reviewed publication (e.g., Peer Community In -- PCI [@guillemaud2019peer]).
-For example, we encourage authors to use services such as PCI, which allow for fast, constructive peer review around a preprint with peer reviews being transparent and published online [@guillemaud2019peer].
+*EcoEvoRxiv* also promotes peer review and community discussion in the hopes of improving the quality of preprints and speeding up their peer-reviewed publication.
+For example, we encourage authors to use services such as Peer Community In -- PCI [@guillemaud2019peer], which allow for fast, constructive peer review around a preprint with peer reviews being transparent and published online [@guillemaud2019peer].
 *EcoEvoRxiv* allows authors to submit both preprints and postprints (also known as author-accepted manuscripts).
@@
 
-Here, we explore the first preprints uploaded to *EcoEvoRxiv* to characterise preprint practices in ecology and evolution.
+Here, we explore the first preprints (*n* = 1216) uploaded to *EcoEvoRxiv* to characterise preprint practices in ecology and evolution.
 We aim to understand: 1) in what countries authors who use *EcoEvoRxiv* are located; 2) the taxonomic diversity study systems across preprints; 3) whether preprint server use depends on career stage and gender; 4) the extent to which authors make use of preprint servers for reports and community-driven peer review; 5) the extent to which data and code are shared in preprints; and 6) how many preprints remain unpublished, and for those that are published, how long it took for them to become published.
@@
 The server has since been adopted by the California Digital Library (CDL).
-Editors are ecologists and evolutionary biologists from across the globe who volunteer their time to screen papers and push new initiatives in the preprint space.
+Editors are ecologists and evolutionary biologists from across the globe who volunteer their time to screen submitted papers and push new initiatives in the preprint space.
 To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the accepted articles available on *EcoEvoRxiv* as of  `r gsub("UTC", "", dates[2])` (see Supplement for more details on methods).
@@
 As a result, articles on *EcoEvoRxiv* are more diverse than those on other preprint servers which have more restrictive submission policies.
-For example, *bioRxiv* only accepts research articles (https://www.biorxiv.org/submit-a-manuscript).
+For example, *bioRxiv* only accepts empirical research articles (https://www.biorxiv.org/submit-a-manuscript).
 
@@
 To obtain a rough idea of an author's gender, we used the R package *gender* (v.`r utils::packageVersion("gender")`; @mullen2021predict) to predict the most likely gender of the submitting author of a preprint.
-We used an algorithm to assign gender based on the submitting author’s name.
+We used an algorithm to assign binary gender based on the submitting author’s name.
 We only used the algorithm-assigned gender when the gender of a given name was identified with 95% certainty.
@@
 A) Time between uploading an preprint to *EcoEvoRxiv* and its publication as a peer-reviewed journal article.
-Preprints were considered those articles that were published a minimum of 2 months (60 days) after being posted to *EcoEvoRxiv*.
+Preprints were considered those articles that were published in a journal a minimum of 2 months (60 days) after being posted to *EcoEvoRxiv*.
 B) Access status of published articles (both preprints and postprints) on *EcoEvoRxiv* classified as “Open Access” or “Not Open Access”.
@@
 In addition to speeding up dissemination, preprints and postprints can also be a useful way to ensure that research remains open and accessible to the research community irrespective of the accessibility of the final peer-reviewed paper [@bourne2017ten; @vale2015accelerating].
-We evaluated whether preprints and postprints hosted at *EcoEvoRxiv*, and that were also published in a journal, were published open access.
+We evaluated whether preprints and postprints hosted at *EcoEvoRxiv* and that were also published in a journal were published open access.
 The open access status of each published article was obtained using the R package *roadoi* (v.`r utils::packageVersion("roadoi")`) to connect to the Unpaywall platform [@jahn2024].
@@
 For preprints and postprints published in open access journals, the type of open access also varied widely (e.g., Gold, Hybrid, Green OA etc., [@fig-pubsummary]B).
-Such a result may not be too surprising given that authors using preprint servers are probably already ‘pro-open access’; particularly given that *EcoEvoRxiv* is run by Society for Open, Reliable, and Transparent Ecology and Evolutionary Biology (SORTEE).
+Such a result may not be too surprising given that authors using preprint servers are probably already ‘pro-open access’, particularly given that *EcoEvoRxiv* is run by the Society for Open, Reliable, and Transparent Ecology and Evolutionary Biology (SORTEE).
 
@@
 Authors may be reluctant to share data and code for preprints because of the perceived concern that others may acquire and use their data and code before publication in a journal.
-Authors of `r pre_article_data[3,"percent"]*100`% (*n* = `r pre_article_data[3,2]`) preprints did not share data at the preprint stage, but ultimately did share data when the article was published; whereas authors of `r pre_article_data[2,"percent"]*100`% (*n* = `r pre_article_data[2,2]`) never shared data and `r pre_article_data[1,"percent"]*100`% (*n* = `r pre_article_data[1,2]`) shared data at both stages.
+Authors of `r pre_article_data[3,"percent"]*100`% (*n* = `r pre_article_data[3,2]`) preprints did not share data at the preprint stage but ultimately did share data when the article was published, whereas authors of `r pre_article_data[2,"percent"]*100`% (*n* = `r pre_article_data[2,2]`) never shared data and `r pre_article_data[1,"percent"]*100`% (*n* = `r pre_article_data[1,2]`) shared data at both stages.
 The same was true for code.
@@
 Overall, *EcoEvoRxiv* articles are diverse but with primary research articles on vertebrates comprising most of the articles posted.
-North America, Europe and Australia use *EcoEvoRxiv* the most with very few non-English language articles to date.
+North America, Europe and Australia use *EcoEvoRxiv* the most with very few non-English language articles deposited to date.
 Submitting authors who were earlier in their career and more often with ‘male-associated names’ tended to use  *EcoEvoRxiv* the most.
@@
 Code and data sharing was also relatively uncommon at the preprint stage.
-At the same time, we attempted to collect data on community discussion around preprints.
+We attempted to collect data on community discussion around preprints.
 However, no such data was found on preprint landing pages, likely reflecting inadequate functionality and cross-linking with sources where such discussion is occurring.
@@
 One way to facilitate such discussions may be to use open preprint peer-review services such as *Peer Community In* (PCI) or *PubPeer* (see also [@avissar2024recommendations]) to provide feedback on preprints.
-Both *PCI* and *PubPeer* provide opportunities for open peer review around a preprint that are given a unique DOI which can then be associated with a preprint on *EcoEvoRxiv*.
+Both *PCI* and *PubPeer* provide opportunities for open peer review around a preprint.
+Peer discussions are given a unique DOI which can then be associated with a preprint on *EcoEvoRxiv*.
 However, *EcoEvoRxiv* currently lacks connection to *PCI*, *PubPeer* and Altmetric data which would allow for discussion to be assimilated around a preprint in one place and make it easy for readers to see discourse around a preprint.
@@
 
-Despite the early successes of the new initiatives taken by *EcoEvoRxiv*, as described above, much work remains to be done to improve the understanding and use of pre- and postprints within our community.
+Despite the early successes of the new initiatives taken by *EcoEvoRxiv*, as described above, much work remains to be done to improve the understanding and use of preprints and postprints within our community.
 We view this perspective piece as a small step towards achieving that goal.

### 2024-10-21 proc_b/ms_ZX.qmd
Updated figs from Zoe

--- 2024-10-20 ms/ms.qmd
@@
 # Dataframes
-              preprints <- data2  %>% filter(time_between_preprint_and_pub_days >= 60) # Contains only preprints and not postprints
+
+     preprints <- data2  %>% filter(time_between_preprint_and_pub_days >= 60) 
+     # Contains only preprints and not postprints (Does not contain preprints that haven't been published! -ZX)
+
      preprints_pub_only <- data2  %>% filter(time_between_preprint_and_pub_days >= 60 & !is.na(preprint_published_date)) 
+     # Contains only preprints that have been published
+
+     all_preprints <- data2  %>% filter(time_between_preprint_and_pub_days >= 60 | is.na(preprint_published_date))
+     # Contains preprints that have and have not been published -ZX
 
@@
     scale_y_continuous(limits = c(0, 130), expand = c(0, 0)) +
-    labs(x = "Published date", y = "Number of papers") +
+    labs(x = "Published date", y = "Number of articles") +
     theme_classic() +
@@
     #coord_polar(theta = "y") + 
-    theme_classic() + labs(y = "Percentage (%) of preprints", x = "Studied taxa") + 
-    theme(plot.tag = element_text(size = 16, face = "bold")) + coord_flip() +
-    scale_fill_colorhex_d(palette = 1042984, discrete = TRUE)
+    theme_classic() + labs(y = "Percentage (%) of articles", x = "Studied taxa") + 
+    theme(plot.tag = element_text(size = 16, face = "bold")) + coord_flip()
 
 ##---------------------##
-# Types of preprints (preprints only)
+# Types of articles (preprints AND postprints)
 ##---------------------##
 # Summary of the data
-  sum_types <- preprints  %>% tabyl(type_of_preprint)  %>% rename("type" = type_of_preprint, "n" = n)  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))
-  #sum(sum_types$n) #620
+  sum_types <- data2  %>% tabyl(type_of_preprint)  %>% rename("type" = type_of_preprint, "n" = n)  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))
+  #sum(sum_types$n) #1216
 
@@
     #coord_polar(theta = "y") + 
-    theme_classic() + labs(y = "Percentage (%) of preprints", x = "Article type") + 
+    theme_classic() + labs(y = "Percentage (%) of articles", x = "Article type") + 
     theme(plot.tag = element_text(size = 16, face = "bold")) + coord_flip() +
-    scale_fill_colorhex_d(palette = 1042984, discrete = TRUE) + theme(legend.position = "none")
+    theme(legend.position = "none")
 
@@
   scale_y_continuous(expand = c(0, 0)) +
-  labs(x = "Years since submitting author's first publication (academic age)", y = "Number of preprints") +
+  labs(x = "Years since submitting author's first publication (academic age)", y = "Number of articles") +
   geom_vline(aes(xintercept = median(academic_age)), color = "black", linetype = "dashed", size = 0.5) +
@@
 # How many preprints remain unpublished? (preprints only)
-unpub <- preprints  %>% filter(is.na(publication_doi))  %>% nrow()
+#unpub <- preprints  %>% filter(is.na(publication_doi))  %>% nrow() #ZOE REMOVED BECAUSE "preprints" DOESN'T INCLUDE UNPUBLISHED PREPRINTS
+
+unpub <- all_preprints %>% filter(is.na(publication_doi)) %>% nrow() #196 -ZX
+total_preprints <- all_preprints %>% nrow() #945 -ZX
+
+perc_unpub <- (unpub/total_preprints)*100 #percentage of unpublished preprints - ZX
+
+#unpub number changes if you do filter(is.na()) by a different parameter (eg., publication_date) - ZX
 

### 2024-10-21 ms/ms.qmd
Updating objects to preprints and published preprints only. A couple of teh panels in Fig 1 need to change to all articles because they are only of preprints. I think given it's a summary we can use ALL artciles here not just "preprints" as postprints are useful.

@@
 # Dataframes
-              preprints <- data2  %>% filter(time_between_preprint_and_pub_days >= 60) # Contains only preprints and not postprints
+    # Contains only preprints and not postprints, but contains published AND unpublished preprints
+      preprints <- data2  %>% filter(time_between_preprint_and_pub_days >= 60 | is.na(time_between_preprint_and_pub_days))
+
+    # Contains only preprints that have been published ONLY
       preprints_pub_only <- data2  %>% filter(time_between_preprint_and_pub_days >= 60 & !is.na(preprint_published_date))
@@
 # Some descriptions
-
-  dates_preprints <- range(preprints$preprint_published_date)
+      dates_preprints <- range(preprints_pub_only$preprint_published_date)
 
@@
   #Plot was then imported to illustrator for aesthetic touches and to combine with other plots in Figure 1. - Zoe X
+
 ##---------------------##
@@
 ##---------------------##
-# Types of preprints (preprints only)
+# Types of articles (everything)
 ##---------------------##
 # Summary of the data
-  sum_types <- preprints  %>% tabyl(type_of_preprint)  %>% rename("type" = type_of_preprint, "n" = n)  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))
-  #sum(sum_types$n) #620
+  sum_types <- data2  %>% tabyl(type_of_preprint)  %>% rename("type" = type_of_preprint, "n" = n)  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))
+  #sum(sum_types$n) #1135
 
@@
     #coord_polar(theta = "y") + 
-    theme_classic() + labs(y = "Percentage (%) of preprints", x = "Article type") + 
+    theme_classic() + labs(y = "Percentage (%) of Articles", x = "Article type") + 
     theme(plot.tag = element_text(size = 16, face = "bold")) + coord_flip() +
@@
 ##-------------------##
-# Career Stage & Gender (preprints only, but all article types)
+# Career Stage (everything)
 ##-------------------##
-
 #compute academic age! (Zoe X)
-preprints <- preprints %>% 
+ age <- data2 %>% 
   mutate(preprint_published_year_z = year(preprint_published_date)) %>% 
@@
 
-academic_age <- ggplot(preprints, aes(x = academic_age)) +
+academic_age <- ggplot(age, aes(x = academic_age)) +
   geom_histogram(binwidth = 1, fill = "white", color = "black") +
@@
 
-#mean(age$academic_age)
+  #mean(age$academic_age, na.rm = TRUE)
 
+ #Plot was then imported to illustrator for aesthetic touches and to combine with other plots in Figure 1. - Zoe X
   ggsave(here("output", "figs", "academic_age.svg"), academic_age, width = 7.5, height = 2)
 
-  #Plot was then imported to illustrator for aesthetic touches and to combine with other plots in Figure 1. - Zoe X
-
-count_dat  <- preprints  %>% 
+# Model number of articles as a function of academic age
+  count_dat  <- age  %>% 
                 distinct(submitting_author, academic_age) %>% 
@@
   res <- summary(model)$coefficients
+
+##-------------------##
+# Gender (everythig)
+##-------------------##
 

### 2024-10-21 ms/ms.qmd
Updated panel D academic age and gender to only be about preprints not articles (postprints removed)

@@
 #compute academic age! (Zoe X)
- age <- data2 %>% 
+ age <- preprints %>% 
   mutate(preprint_published_year_z = year(preprint_published_date)) %>% 
@@
   data4 <- rename(data4, gender = gender.x)
-  #table(data4$gender, useNA = "always") #more males than females, two NA ue to missing first name / collective authorship
+
+  # Now, isolate just preprints because this question is focused on preprints.This object is used for the pie chart.
+  data4_preprints <- data4  %>% filter(time_between_preprint_and_pub_days >= 60 | is.na(time_between_preprint_and_pub_days))
+
+  #more males than females, two NA ue to missing first name / collective authorship
+  gender_table <- data4_preprints  %>% tabyl(gender)  %>% filter(!is.na(gender))
 
@@
   ###Zoe's gender pie###
-  #female - 37.8, male - 62.2
 
-  gender <- c("female", "male")
-  percentage <- c(37.8, 62.2)
-  sex_ratio<- data.frame(gender, percentage)
-
-  sex_ratio <- sex_ratio %>% ggplot(aes(x = "", y = percentage, fill = gender)) +
+  sex_ratio <- gender_table %>% ggplot(aes(x = "", y = percent, fill = gender)) +
       geom_col(color = "black")+
@@
 
+   ##Pie was then imported to illustrator for aesthetic touches and to combine with other plots in Figure 1. - Zoe X
   ggsave(here("output", "figs", "sex_ratio.svg"), sex_ratio)
 
-  ##Pie was then imported to illustrator for aesthetic touches and to combine with other plots in Figure 1. - Zoe X
-
   # Load in and plot the final figure
-    fig <- image_read(here("output", "figs", "Figure 1_FINAL.png")) 
+    fig <- image_read(here("output", "figs", "Figure 1_Revised.png")) 
     fig
@@
 Error"], 2)`, *p* < 0.001, n = `r nrow(count_dat[complete.cases(count_dat),])` years).
-Most preprints were submitted by authors who published their first paper in the last ~10 years ([@fig-summary]E), with the median year since first publication being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r mean(data2$submitting_author_first_publication_year, na.rm = TRUE)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`, n = `r sum(complete.cases(data2$submitting_author_first_publication_year))`).
+Most preprints were submitted by authors who published their first paper in the last ~10 years ([@fig-summary]E), with the median year since first publication being `r median(prepints$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r mean(prepints$submitting_author_first_publication_year, na.rm = TRUE)`; SD = `r sd(prepints$submitting_author_first_publication_year, na.rm = TRUE)`, n = `r sum(complete.cases(prepints$submitting_author_first_publication_year))`).
 These patterns support the expectation that EMCRs may use preprints to make their work more visible and disseminate their findings more quickly.

### 2024-10-22 ms/ms.qmd
Just checked numbers
re-render and fixing a few small typos

@@
     output-file: ms-r1.docx
-  pdf:
-    include-in-header: 
-      text: '\usepackage{lineno}\linenumbers'
 editor_options: 
@@
 
-Authors: Daniel W.A. Noble ^1^, $\ddagger$, Zoe A. Xirocostas, Nicholas C. Wu, April R. Martinig, Shinichi Nakagawa^2,\*^,Malgorzata Lagisz^2,\*^
-
-Affiliations:
-
-^1^ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia &NewLine;  
-^2^ Ecology and Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia &NewLine;
-
-$\ddagger$ corresponding author, daniel.noble@anu.edu.au &NewLine;
-
-\* equal contribution
-
 # Abstract
@@
 Here, we explore the first preprints (*n* = 1216) uploaded to *EcoEvoRxiv* to characterise preprint practices in ecology and evolution.
-We aim to understand: 1) in what countries authors who use *EcoEvoRxiv* are located; 2) the taxonomic diversity study systems across preprints; 3) whether preprint server use depends on career stage and gender; 4) the extent to which authors make use of preprint servers for reports and community-driven peer review; 5) the extent to which data and code are shared in preprints; and 6) how many preprints remain unpublished, and for those that are published, how long it took for them to become published.
+We aim to understand: 1) in what countries authors who use *EcoEvoRxiv* are located; 2) the taxonomic diversity of study systems used across articles; 3) whether preprint server use depends on career stage and gender; 4) the extent to which authors make use of preprint servers for reports and community-driven peer review; 5) the extent to which data and code are shared in preprints; and 6) how many preprints remain unpublished, and for those that are published, how long it took for them to become published.
 In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other preprint servers to help further clarify the benefits of using community-driven preprint servers to disseminate research findings.
@@
 *EcoEvoRxiv* was established in June 2018 before the launch in November 2018.
-Notable milestones include *EcoEvoRxiv* transitioning to the California Digital Library (CDL), the acceptance of preprints and postprints in Spanish and Portuguese, and the acceptance of the first IUCN Red List Ecosystem report; B) Geographic origin of the preprints and postprints uploaded to *EcoEvoRxiv*, inferred from the country of affiliation of the submitting author; C) Taxa used/covered in the articles posted to *EcoEvoRxiv* (n = 1080 articles covering relevant taxa); D) Types of preprints accepted on *EcoEvoRxiv* (n = 620 articles).
-E) Academic age of authors posting to *EcoEvoRxiv* along with the gender of the submitting author.
+Notable milestones include *EcoEvoRxiv* transitioning to the California Digital Library (CDL), the acceptance of preprints and postprints in Spanish and Portuguese, and the acceptance of the first IUCN Red List Ecosystem report; B) Geographic origin of articles uploaded to *EcoEvoRxiv*, inferred from the country of affiliation of the submitting author; C) Taxa covered in the articles posted to *EcoEvoRxiv* (*n* = 1080 articles covering relevant taxa); D) Types of articles accepted on *EcoEvoRxiv* (*n* = 1216 articles).
+E) Academic age of authors posting preprints to *EcoEvoRxiv* (*n* = 1135 published and unpublished preprints) along with the gender of the submitting author.
 Values lower than zero are indicative of authors who uploaded preprints before their first scientific publication in a journal.
-Map base source:  R Package "maps" v.3.4.2.
+Map base source: R Package maps v.3.4.2.
 Shapefile: Natural Earth https://www.naturalearthdata.com/about/terms-of-use/."
-
-#| echo: false
-#| warning: false
-#| message: false
 
@@
     # Contains only preprints that have been published ONLY
-      preprints_pub_only <- data2  %>% filter(time_between_preprint_and_pub_days >= 60 & !is.na(preprint_published_date))
+      preprints_pub_only <- data2  %>% filter(time_between_preprint_and_pub_days >= 60 & !is.na(time_between_preprint_and_pub_days))
 
@@
 ##---------------------##
-# Submissions to  EcoEvoRxiv over time (everything)
+# Articles to EcoEvoRxiv over time (everything)
 ##---------------------##
@@
 ##---------------------##
-# Submissions by Country to EcoEvoRxiv (everything)
+# Articles by Country (everything)
 ##---------------------##
@@
 ##-------------------##
-# Career Stage (everything)
+# Career Stage (preprints)
 ##-------------------##
@@
 
+  # Whats the median/mean academic age?
     #mean(age$academic_age, na.rm = TRUE)
+    median(age$academic_age, na.rm = TRUE) #8
 
@@
 ##-------------------##
-# Gender (everythig)
+# Gender (preprints)
 ##-------------------##
@@
 Error"], 2)`, *p* < 0.001, n = `r nrow(count_dat[complete.cases(count_dat),])` years).
-Most preprints were submitted by authors who published their first paper in the last ~10 years ([@fig-summary]E), with the median year since first publication being `r median(prepints$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r mean(prepints$submitting_author_first_publication_year, na.rm = TRUE)`; SD = `r sd(prepints$submitting_author_first_publication_year, na.rm = TRUE)`, n = `r sum(complete.cases(prepints$submitting_author_first_publication_year))`).
+Most preprints were submitted by authors who published their first paper in the last ~10 years ([@fig-summary]E), with the median year since first publication being `r median(age$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r mean(age$submitting_author_first_publication_year, na.rm = TRUE)`; SD = `r sd(age$submitting_author_first_publication_year, na.rm = TRUE)`, n = `r sum(complete.cases(age$submitting_author_first_publication_year))`).
 These patterns support the expectation that EMCRs may use preprints to make their work more visible and disseminate their findings more quickly.
@@
 Our data on gender had only two missing values--one where the first name of the submitting author was missing and the other one for a collective submission.
-As expected, we found that women were less likely to post to *EcoEvoRxiv* compared to men (women: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`%), reinforcing existing disparities between male and female scientists.
+As expected, we found that women were less likely to post to *EcoEvoRxiv* compared to men (women: `r gender_table[1, 3]*100`%, [@fig-summary]E), reinforcing existing disparities between male and female scientists.
 For example, studies have shown that female first authors have lower acceptance rates and are cited less (~2%) compared to males [e.g., @fox2019gender].
@@
 #| message: false
-#| fig-cap: Summary of the publication status of articles on *EcoEvoRxiv*.
+#| fig-cap: "Summary of the publication status of preprints on *EcoEvoRxiv*.
 A) Time between uploading an preprint to *EcoEvoRxiv* and its publication as a peer-reviewed journal article.
 Preprints were considered those articles that were published in a journal a minimum of 2 months (60 days) after being posted to *EcoEvoRxiv*.
-B) Access status of published articles (both preprints and postprints) on *EcoEvoRxiv* classified as “Open Access” or “Not Open Access”.
+B) Access status of published preprints on *EcoEvoRxiv* classified as “Open Access” or “Not Open Access”.
 “Unknown” status is for articles not explicitly identified as being open access or not on the Unpaywall platform.
-C) Sub-types of open access status of published articles on *EcoEvoRxiv*.
+C) Sub-types of open access status of published preprints on *EcoEvoRxiv*.
 Sub-type meanings are as follows: ‘Green’, articles published in ‘toll-access journals but achieved in an open access repository; ‘Bronze’, articles are free to read on publishers website without a license but grants no other rights and can be delayed free-to-read; ‘Hybrid’, articles are free to read upon publication with an open access license; ‘Gold’, articles published in fully open access journals.
-For full details on the meaning of each category see  https://support.unpaywall.org/support/solutions/articles/44001777288-what-do-the-types-of-oa-status-green-gold-hybrid-and-bronze-mean-
+For full details on the meaning of each category see  https://support.unpaywall.org/support/solutions/articles/44001777288-what-do-the-types-of-oa-status-green-gold-hybrid-and-bronze-mean-"
 
@@
 # How many preprints remain unpublished? (preprints only)
-unpub <- preprints  %>% filter(is.na(publication_doi))  %>% nrow()
+unpub <- nrow(preprints) - nrow(preprints_pub_only)
+per_unpublished <- nrow(preprints_pub_only)/ nrow(preprints)
 
@@
 # what is the range
-sum_preprints <- preprints  %>% summarise(min = min(time_between_preprint_and_pub_days), max = max(time_between_preprint_and_pub_days), mean = mean(time_between_preprint_and_pub_days), median = median(time_between_preprint_and_pub_days), sd = sd(time_between_preprint_and_pub_days))
+sum_preprints <- preprints  %>% summarise(min = min(time_between_preprint_and_pub_days, na.rm = TRUE), max = max(time_between_preprint_and_pub_days,na.rm = TRUE), mean = mean(time_between_preprint_and_pub_days, na.rm = TRUE), median = median(time_between_preprint_and_pub_days,na.rm = TRUE), sd = sd(time_between_preprint_and_pub_days, na.rm = TRUE))
 
-p1_pub_zoe <- preprints %>% ggplot(aes(x = time_between_preprint_and_pub_days)) +
+p1_pub_zoe <- preprints_pub_only %>% ggplot(aes(x = time_between_preprint_and_pub_days)) +
   geom_histogram(binwidth = 30, fill = "white", color = "black") +
@@
 # Summary of the data
-sum_is_oa <- tabyl(preprints$is_oa)
-sum_oa_status <- tabyl(preprints$oa_status)
+    sum_is_oa <- tabyl(preprints_pub_only$is_oa)
+sum_oa_status <- tabyl(preprints_pub_only$oa_status)
 
-p2_pub <- preprints  %>% ggplot(aes(x = is_oa)) + geom_bar() + labs(x = "Open Access", y = "Number of papers") + theme_classic()  + scale_y_continuous(expand = c(0, 0))
+p2_pub <- preprints_pub_only  %>% ggplot(aes(x = is_oa)) + geom_bar() + labs(x = "Open Access", y = "Number of papers") + theme_classic()  + scale_y_continuous(expand = c(0, 0))
 
@@
 
-p3_pub <- preprints %>% mutate(oa_status = (fct_relevel(oa_status, c("gold","hybrid", "bronze", "green", "closed", "NA"))))  %>% ggplot(aes(x = oa_status, fill = oa_status)) + geom_bar() + labs(x = "Open Access type", y = "Number of papers") + theme_classic() + theme(axis.title = element_text(size = 14), legend.position = "none") + scale_fill_manual(values = c("bronze" = "#9b6023", "gold" = "#ffd700", "green" = "#008000", "hybrid" = "#6fa8dc", "NA" = "grey", "closed" = "black"))+ scale_y_continuous(expand = c(0, 0))
+p3_pub <- preprints_pub_only %>% mutate(oa_status = (fct_relevel(oa_status, c("gold","hybrid", "bronze", "green", "closed", "NA"))))  %>% ggplot(aes(x = oa_status, fill = oa_status)) + geom_bar() + labs(x = "Open Access type", y = "Number of papers") + theme_classic() + theme(axis.title = element_text(size = 14), legend.position = "none") + scale_fill_manual(values = c("bronze" = "#9b6023", "gold" = "#ffd700", "green" = "#008000", "hybrid" = "#6fa8dc", "NA" = "grey", "closed" = "black"))+ scale_y_continuous(expand = c(0, 0))
 
@@
 # Summary of the data
-  preprint_data <- preprints  %>% tabyl(data_link_preprint_cleaned) 
-  preprint_code <- preprints  %>% tabyl(code_link_preprint_cleaned) 
-  article_data <- preprints  %>% tabyl(data_link_article_cleaned) 
-  article_code <- preprints  %>% tabyl(code_link_article_cleaned)
+  preprint_data <- preprints  %>% tabyl(data_link_preprint_cleaned) # Note that this contains both published AND unpublished preprints
+  preprint_code <- preprints  %>% tabyl(code_link_preprint_cleaned) # Note that this contains both published AND unpublished preprints
+   article_data <- preprints_pub_only  %>% tabyl(data_link_article_cleaned) 
+   article_code <- preprints_pub_only  %>% tabyl(code_link_article_cleaned)
 
-# Check if it was shared not in preprint but then in article
-  pre_article_data <- preprints   %>%  filter(!data_link_preprint_cleaned == "not applicable") %>% mutate(data_shared = ifelse(data_link_preprint_cleaned == "no" & data_link_article_cleaned == "yes", "yes", ifelse(code_link_preprint_cleaned == "yes" & code_link_article_cleaned == "yes", "always", "no")))  %>% tabyl(data_shared)
-  pre_article_code <- preprints  %>%  filter(!data_link_preprint_cleaned == "not applicable") %>% mutate(code_shared = ifelse(code_link_preprint_cleaned == "no" & code_link_article_cleaned == "yes", "yes", ifelse(code_link_preprint_cleaned == "yes" & code_link_article_cleaned == "yes", "always", "no")))  %>% tabyl(code_shared)
+# Check if it was shared not in preprint but then in publication
+  pre_article_data <- preprints_pub_only   %>%  filter(!data_link_preprint_cleaned == "not applicable") %>% mutate(data_shared = ifelse(data_link_preprint_cleaned == "no" & data_link_article_cleaned == "yes", "yes", ifelse(code_link_preprint_cleaned == "yes" & code_link_article_cleaned == "yes", "always", "no")))  %>% tabyl(data_shared)
+  pre_article_code <- preprints_pub_only  %>%  filter(!data_link_preprint_cleaned == "not applicable") %>% mutate(code_shared = ifelse(code_link_preprint_cleaned == "no" & code_link_article_cleaned == "yes", "yes", ifelse(code_link_preprint_cleaned == "yes" & code_link_article_cleaned == "yes", "always", "no")))  %>% tabyl(code_shared)
 
@@
 
-fig2 <- image_read(here("output", "figs", "Figure 2_final.png"))
+fig2 <- image_read(here("output", "figs", "Figure 2_Revised.png"))
 fig2
@@
 We estimated how long it takes to publish a preprint in ecology and evolution by recording the time between when a preprint was first posted on *EcoEvoRxiv*, and its final acceptance in a peer-reviewed journal.
-In total, `r unpub` submissions remained unpublished (`r (unpub / nrow(data2))*100`%, n = `r nrow(data2)`) at the time when these data were collected.
+In total, `r unpub` preprints remained unpublished (`r per_unpublished*100`%, n = `r nrow(preprints)`) at the time when these data were collected.
 Not all of these preprints, however, are anticipated to be published in a peer-reviewed journal (e.g., reports).

### 2024-10-22 ms/ms.qmd
Few final fixes before render

@@
 Shapefile: Natural Earth https://www.naturalearthdata.com/about/terms-of-use/."
+#| echo: false
+#| warning: false
+#| message: false
 
@@
           unpub <- nrow(preprints) - nrow(preprints_pub_only)
-per_unpublished <- nrow(preprints_pub_only)/ nrow(preprints)
+per_unpublished <- unpub / nrow(preprints)
 

### 2024-10-22 ms/ms.qmd
Final fixes

@@
 *EcoEvoRxiv* is one of the few community-driven preprint servers that has paved the way for new initiatives, by accepting multilingual preprints, registered reports, and non-traditional research reports.
-Such initiatives are distinct from other preprint servers, such as bioRxiv, which only accept empirical research in English.
-In addition, community-driven servers like EcoEvoRxiv aggregate papers presenting research on similar topics, improving discoverability and opportunities for within-community debate compared with broader preprint servers.
+Such initiatives are distinct from other preprint servers, such as *bioRxiv*, which only accept empirical research in English.
+In addition, community-driven servers like *EcoEvoRxiv* aggregate papers presenting research on similar topics, improving discoverability and opportunities for within-community debate compared with broader preprint servers.
 *EcoEvoRxiv* also promotes peer review and community discussion in the hopes of improving the quality of preprints and speeding up their peer-reviewed publication.
@@
 
-Here, we explore the first preprints (*n* = 1216) uploaded to *EcoEvoRxiv* to characterise preprint practices in ecology and evolution.
+Here, we explore the first preprints/postprints (*n* = 1216) uploaded to *EcoEvoRxiv* to characterise preprint practices in ecology and evolution.
 We aim to understand: 1) in what countries authors who use *EcoEvoRxiv* are located; 2) the taxonomic diversity of study systems used across articles; 3) whether preprint server use depends on career stage and gender; 4) the extent to which authors make use of preprint servers for reports and community-driven peer review; 5) the extent to which data and code are shared in preprints; and 6) how many preprints remain unpublished, and for those that are published, how long it took for them to become published.
@@
 Lack of discussion around preprints more generally might also be a function of time constraints researchers face and the lack of credit received for such a community service.
-An important future goal of EcoEvoRxiv is to provide better community discussion forums and integration with existing preprint peer review services.
+An important future goal of *EcoEvoRxiv* is to provide better community discussion forums and integration with existing preprint peer review services.
 We also need to find new ways to give credit to colleagues that contribute to community discussion.

### 2024-10-23 ms/ms.qmd
Fix Doms points

@@
 The main reason for publishing postprints on a preprint server is to ensure published articles are openly accessible to everyone without a paywall (i.e., green open access).
-Postprints can be published anytime, if journals allow it (which most do; see https://www.sherpa.ac.uk/romeo/).
+Even for articles published open access, depositing the postprint in a repository (e.g.
+Zenodo) or a preprint server strengthens permanence and access to the content of the article in the event of a journal’s collapse or disappearance.
+Postprints can be published anytime, if journals allow it (which many do; see https://www.sherpa.ac.uk/romeo/).
 
@@
 Accepted *EcoEvoRxiv* submissions are given a unique DOI and are indexed on Google Scholar.
-Having a unique DOI means that the article can be accessed in perpetuity.
-If the preprint becomes published, then this DOI is merged with the published DOI.
+DOIs can be used in grant applications, CVs, and other documents to provide a link to the work.
 
@@
 Most of the published preprints and postprints were open access [`r sum_is_oa$valid_percent[2]*100`% (*n* = `r sum_is_oa$n[2]` out of `r sum(sum_is_oa$n[1:2])` where the status was known); [@fig-pubsummary]A]; however, `r sum_is_oa$valid_percent[1]*100`% (*n* = `r sum_is_oa$n[1]`) were published behind paywalls.
-Published articles behind paywalls would otherwise remain inaccessible if it were not for *EcoEvoRxiv*.
+Published articles behind paywalls may otherwise remain inaccessible if it were not for *EcoEvoRxiv*.
 For preprints and postprints published in open access journals, the type of open access also varied widely (e.g., Gold, Hybrid, Green OA etc., [@fig-pubsummary]B).
@@
 This is very easy for authors to do on *EcoEvoRxiv* and should increase the chances that the preprint is correctly linked to the published article and citations are appropriately merged.
-Adding DOIs will also create a link between the final preprint and the published paper so that, no matter the open access status of the publication, the research findings will remain openly accessible, saving costs for authors (i.e., by not having to pay open access fees) and improving the visibility and use of research.
 

### 2024-10-23 ms/ms.qmd
Check figure numbers/labels. Should be correct just Fig 2 A and B mix up.

@@
 The open access status of each published article was obtained using the R package *roadoi* (v.`r utils::packageVersion("roadoi")`) to connect to the Unpaywall platform [@jahn2024].
-Most of the published preprints and postprints were open access [`r sum_is_oa$valid_percent[2]*100`% (*n* = `r sum_is_oa$n[2]` out of `r sum(sum_is_oa$n[1:2])` where the status was known); [@fig-pubsummary]A]; however, `r sum_is_oa$valid_percent[1]*100`% (*n* = `r sum_is_oa$n[1]`) were published behind paywalls.
+Most of the published preprints and postprints were open access [`r sum_is_oa$valid_percent[2]*100`% (*n* = `r sum_is_oa$n[2]` out of `r sum(sum_is_oa$n[1:2])` where the status was known); [@fig-pubsummary]B]; however, `r sum_is_oa$valid_percent[1]*100`% (*n* = `r sum_is_oa$n[1]`) were published behind paywalls.
 Published articles behind paywalls may otherwise remain inaccessible if it were not for *EcoEvoRxiv*.
-For preprints and postprints published in open access journals, the type of open access also varied widely (e.g., Gold, Hybrid, Green OA etc., [@fig-pubsummary]B).
+For preprints and postprints published in open access journals, the type of open access also varied widely (e.g., Gold, Hybrid, Green OA etc., [@fig-pubsummary]C).
 Such a result may not be too surprising given that authors using preprint servers are probably already ‘pro-open access’, particularly given that *EcoEvoRxiv* is run by the Society for Open, Reliable, and Transparent Ecology and Evolutionary Biology (SORTEE).

### 2024-10-28 ms/ms.qmd
Updated Kevin's comments

@@
 *EcoEvoRxiv* also promotes peer review and community discussion in the hopes of improving the quality of preprints and speeding up their peer-reviewed publication.
-For example, we encourage authors to use services such as Peer Community In -- PCI [@guillemaud2019peer], which allow for fast, constructive peer review around a preprint with peer reviews being transparent and published online [@guillemaud2019peer].
+For example, we encourage authors to use peer community review services such as Peer Community In (PCI) [@guillemaud2019peer], which allow for fast, constructive peer review around a preprint with peer reviews being transparent and published online [@guillemaud2019peer].
 *EcoEvoRxiv* allows authors to submit both preprints and postprints (also known as author-accepted manuscripts).
@@
 We consider both preprints and postprints as ‘articles’.
-After removing five duplicate titles – suggesting that a few authors uploaded the article as separate submissions rather than updating the existing article – we had data for a total of `r pr` articles with ~55--60 posted approximately monthly in the last two years ([@fig-summary]A).
+After removing five duplicate titles (suggesting that a few authors uploaded their articles as separate submissions rather than updating the existing article), we extracted data for a total of 1216 articles, or ~55–60 articles per month over the last two years ([@fig-summary]A).
 For more details on the data collection process, see the Supplement (https://daniel1noble.github.io/ecoevo_1000/).
@@
 *EcoEvoRxiv* was established in June 2018 before the launch in November 2018.
-Notable milestones include *EcoEvoRxiv* transitioning to the California Digital Library (CDL), the acceptance of preprints and postprints in Spanish and Portuguese, and the acceptance of the first IUCN Red List Ecosystem report; B) Geographic origin of articles uploaded to *EcoEvoRxiv*, inferred from the country of affiliation of the submitting author; C) Taxa covered in the articles posted to *EcoEvoRxiv* (*n* = 1080 articles covering relevant taxa); D) Types of articles accepted on *EcoEvoRxiv* (*n* = 1216 articles).
-E) Academic age of authors posting preprints to *EcoEvoRxiv* (*n* = 1135 published and unpublished preprints) along with the gender of the submitting author.
+Notable milestones include *EcoEvoRxiv* transitioning to the California Digital Library (CDL), the acceptance of preprints and postprints in Spanish and Portuguese, and the acceptance of the first IUCN Red List Ecosystem report; B) Geographic origin of articles uploaded to *EcoEvoRxiv*, inferred from the country of affiliation of the submitting author; C) Taxa covered in the articles posted to *EcoEvoRxiv* (*n* = 1080 articles covering relevant taxa); D) Types of articles accepted on *EcoEvoRxiv* (*n* = 1216 articles); and E) Academic age of authors posting preprints to *EcoEvoRxiv* (*n* = 1135 published and unpublished preprints) along with the gender of the submitting author.
 Values lower than zero are indicative of authors who uploaded preprints before their first scientific publication in a journal.
@@
 For example, IUCN Red-list Ecosystem Reports are now posted to *EcoEvoRxiv* and our community has been able to work closely with the IUCN to ensure these documents meet the IUCN requirements.
-We would encourage authors to consider posting books, book chapters, and reports to ensure that they are openly accessible and more easily found.
+We encourage authors to consider posting books, book chapters, and reports to ensure that they are openly accessible and more easily found.
 Accepted *EcoEvoRxiv* submissions are given a unique DOI and are indexed on Google Scholar.
@@
 *EcoEvoRxiv* is the only preprint server to date that breaks down language barriers to scientific communication by accepting not only English, but also Spanish, Portuguese and French language articles.
-*EcoEvoRxiv* plans to expand to other languages as new non-English editors become available.
-Such initiatives are incredibly important if we are to begin filling global voids of scientific knowledge.
-However, multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish submissions, and a single Portuguese submitted, since starting in 2023.
-Part of the challenge in getting authors to submit in non-English languages is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries, cultural differences in the perception of preprints, and a strong reliance on traditional publishing models that typically mandate publishing in English  [@arenas2024academic].
+*EcoEvoRxiv* plans to expand to other languages as new non-English editors for different languages become available.
+Such initiatives are incredibly important if we are to begin filling global gaps in scientific knowledge.
+However, multilingual initiatives have been slow to take off on *EcoEvoRxiv*, with only a few Spanish submissions, and a single Portuguese posted since *EcoEvoRxiv* began accepting non-English articles in 2023.
+Part of the challenge in getting authors to submit articles in non-English languages is the lack of awareness of *EcoEvoRxiv* in non-English speaking countries, cultural differences in the perception of preprints, and a strong reliance on traditional publishing models that typically mandate publishing in English  [@arenas2024academic].
 
@@
 These patterns support the expectation that EMCRs may use preprints to make their work more visible and disseminate their findings more quickly.
-However, we acknowledge that understanding the reasons why EMCRs might adopt preprint servers more does require community surveys as has been done in other studies [e.g., @fraser2022motivations].
+However, we acknowledge that to understand the reasons why EMCRs might adopt preprint servers more readily requires community surveys, as have been done in previous studies [e.g., @fraser2022motivations].
 
@@
 A) Time between uploading an preprint to *EcoEvoRxiv* and its publication as a peer-reviewed journal article.
-Preprints were considered those articles that were published in a journal a minimum of 2 months (60 days) after being posted to *EcoEvoRxiv*.
-B) Access status of published preprints on *EcoEvoRxiv* classified as “Open Access” or “Not Open Access”.
-“Unknown” status is for articles not explicitly identified as being open access or not on the Unpaywall platform.
-C) Sub-types of open access status of published preprints on *EcoEvoRxiv*.
+Preprints were considered those articles that were published in a journal a minimum of 2 months (60 days) after being posted to *EcoEvoRxiv*; B) Access status of published preprints on *EcoEvoRxiv* classified as “Open Access” or “Not Open Access”.
+“Unknown” status is for articles who status was unclear on the Unpaywall platform; and C) Sub-types of open access status of published preprints on *EcoEvoRxiv*.
 Sub-type meanings are as follows: ‘Green’, articles published in ‘toll-access journals but achieved in an open access repository; ‘Bronze’, articles are free to read on publishers website without a license but grants no other rights and can be delayed free-to-read; ‘Hybrid’, articles are free to read upon publication with an open access license; ‘Gold’, articles published in fully open access journals.
@@
 Nonetheless, the median time to publication for preprints was `r sum_preprints$median` days (8 months) for all preprints that ended up being published (mean = `r sum_preprints$mean`; SD = `r sum_preprints$sd` days) with the maximum time to publication being `r sum_preprints$max` days or `r sum_preprints$max/365` years ([@fig-pubsummary]A).
-For a full breakdown on the time to publication based on article type see Supplement (Table S1).
+For a full breakdown on the time to publication based on article type, refer to the Supplement (Table S1).
 Our results largely confirm the extended timeframes that most authors experience between writing their research papers and their publication.
@@
 Overall, `r pre_article_code[3,"percent"]*100`% (*n* = `r pre_article_code[3,2]`) of preprints had no open code at the preprint stage, but ultimately did share code at the published article stage.
-In contrast, authors of `r pre_article_code[2,"percent"]*100`% (*n* = `r pre_article_code[2,2]`) preprints did not share code at either stage and `r pre_article_code[1,"percent"]*100`% (*n* = `r pre_article_code[1,2]`) shared code at both stages.
+In contrast, authors of `r pre_article_code[2,"percent"]*100`% (*n* = `r pre_article_code[2,2]`) preprints did not share code at either stage while `r pre_article_code[1,"percent"]*100`% (*n* = `r pre_article_code[1,2]`) shared code at both stages.
 Relatively low code and data-sharing practices in our sample is consistent with analyses of sharing practices for published articles (e.g., [@o2021preferred]), even for journals with strict public data archiving policies [@roche2015public].
@@
 Peer discussions are given a unique DOI which can then be associated with a preprint on *EcoEvoRxiv*.
-However, *EcoEvoRxiv* currently lacks connection to *PCI*, *PubPeer* and Altmetric data which would allow for discussion to be assimilated around a preprint in one place and make it easy for readers to see discourse around a preprint.
+However, *EcoEvoRxiv* currently lacks connection to *PCI*, *PubPeer* and Altmetric data which would allow for discussion to be assimilated around a preprint in one place and make it easier for readers to follow discourse around a preprint.
 Clearly, as a community, we need to provide better platforms and workflows that document discussions around preprint findings.
 Such discussions help authors improve their work and communicate their findings more effectively (when done constructively, of course).
-Lack of discussion around preprints more generally might also be a function of time constraints researchers face and the lack of credit received for such a community service.
+Lack of discussion around preprints more generally might also be a function of time constraints researchers face and the lack of credit received for such community service.
 An important future goal of *EcoEvoRxiv* is to provide better community discussion forums and integration with existing preprint peer review services.

### 2024-10-29 ms/ms.qmd
Fix

@@
 We consider both preprints and postprints as ‘articles’.
-After removing five duplicate titles (suggesting that a few authors uploaded their articles as separate submissions rather than updating the existing article), we extracted data for a total of 1216 articles, or ~55–60 articles per month over the last two years ([@fig-summary]A).
+After removing five duplicate titles (suggesting that a few authors uploaded their articles as separate submissions rather than updating the existing article), we extracted data for a total of 1216 articles over the last two years ([@fig-summary]A).
 For more details on the data collection process, see the Supplement (https://daniel1noble.github.io/ecoevo_1000/).

### 2025-01-04 ms/ms.qmd
?

@@
 Community driven preprint initiatives can allow a research community to come together to break down these barriers to improve equity and coverage of global knowledge.
-Here, we explore the first preprints uploaded to *EcoEvoRxiv* (*n* = 1216), a community-driven preprint server for ecologists and evolutionary biologists, to characterise preprint practices in ecology, evolution and conservation.
+Here, we explore the first preprints uploaded to *EcoEvoRxiv* (*n* = 1216), a community-driven preprint server for ecologists and evolutionary biologists, to characterise preprint use in ecology, evolution and conservation.
 Our perspective piece highlights some of the unique initiatives that *EcoEvoRxiv* has taken to break down barriers to scientific publishing by exploring the composition of articles, how gender and career stage influence preprint use, whether preprints are associated with greater open science practices (e.g., code and data sharing), and tracking preprint publication outcomes.
@@
 Understanding gender publishing patterns is challenging with observational data such as ours because we cannot know the gender of authors for certain, but we can use a data-driven approach to ascertain the probability that a particular name is of a given gender (man or woman).
-To obtain a rough idea of an author's gender, we used the R package *gender* (v.`r utils::packageVersion("gender")`; @mullen2021predict) to predict the most likely gender of the submitting author of a preprint.
+We used the R package *gender* (v.`r utils::packageVersion("gender")`; @mullen2021predict) to predict the most likely gender of the submitting author of a preprint.
 We used an algorithm to assign binary gender based on the submitting author’s name.
@@
 
-### (a) *Science takes time, but publication could take longer*
+### (a) *Science takes time, but publication can take longer*
 Increased competition in science has raised the bar with respect to the amount of data required for publication [@vale2015accelerating].
